### 2023-06-08 thesis.tex
first commit

\documentclass[a4paper,oneside,12pt]{report}
\usepackage{styles/fbe_tez}
\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
\usepackage{amsmath, amsthm} % Some extra symbols
\usepackage[bottom]{footmisc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{subfigure} % 
\usepackage{amsmath}
\usepackage{notoccite}

\interdisplaylinepenalty=2500
\hyphenation{lists} \makeatletter

\newcommand{\field}[1]{\mathbb{#1} }
\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
\setlength\belowdisplayskip{5pt}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\defn}{\stackrel{\triangle}{=}}
\newcommand{\nn}{\nonumber}
\newcommand{\nnl}{\nonumber \\}
\renewcommand{\theequation}{\arabic{equation}}
\renewcommand{\labelenumi}{(\roman{enumi})}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\def\ifundefined{\@ifundefined}
\def\bfat{\left[ \begin{array}}
\def\emat{\end{array} \right]}
\def\bfatt{\left\{ \begin{array}}
\def\ematt{\end{array} \right.}
\def\bset{\left\{ \begin{array}}
\def\eset{\end{array} \right\}}
\def\bpar{\left( \begin{array}}
\def\epar{\end{array} \right)}

\graphicspath{{figures/}} % Graphics will be here

\newtheorem{thm}{Theorem}[chapter]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

\numberwithin{equation}{chapter}

% COVER PAGE
\title{THESIS TITLE}
\turkcebaslik{TEZ BAŞLIĞI}
\degree{B.S., Program Name, Boğaziçi University, 2010\\
	M.S., Program Name, Boğaziçi University, 2013}
\author{Name Surname}
\program{Program Name}
\subyear{2019}

% APPROVED BY PAGE
\supervisor{Prof. Name Surname}
%\cosuperi{Title and Name of Cosupervisor I}
%\cosuperii{Title and Name of Cosupervisor II}
\examineri{Assoc. Prof. Name Surname}
\examinerii{Assist. Prof. Name Surname}
\examineriii{Name Surname, Ph.D.}
%\examineriv{}
%\examinerv{}
\dateofapproval{DD.MM.YYYY}

% BEGIN OF DOCS
\begin{document}
\pagenumbering{roman}
\makemstitle % M.S. thesis
\makeapprovalpage

% ACK PAGE
\begin{acknowledgements}
Acknowledgements come here...
\end{acknowledgements}

% ABS PAGE
\begin{abstract}
One page abstract will come here.  
\end{abstract}

% OZET PAGE
\begin{ozet}
Bir sayfa uzunluğunda özet gelecektir.
\end{ozet}

% CONTENTS AND LIST OF FIG AND TABLE PAGES
\tableofcontents
\listoffigures
\listoftables

% LIST OF SYMBOLS PAGE
\begin{symbols}
% The title will be typeset as "LIST OF SYMBOLS".
% Use a separate \sym command for each symbols definition.
% First, Latin symbols in alphabetical order
\sym{$a_{ij}$}{Description of $a_{ij}$}
\sym{$\mathbf{A}$}{State transition matrix of a hidden Markov model}
% 1 EMPTY LINE BETWEEN LATIN AND GREEK SYMBOLS GROUP!!!
\sym{}{}
% Then Greek symbols in alphabetical order
\sym{$\alpha$}{Blending parameter \textit{or} scale}
\sym{$\beta_t(i)$}{Backward variable}
\sym{$\Theta$}{Parameter set}
\sym{ }{}
\end{symbols}

% LIST OF ABBREV PAGE
\begin{abbreviations}
 % Abbreviations in alphabetical order
\sym{2D}{Two Dimensional}
\sym{3D}{Three Dimensional}
\sym{AAM}{Active Appearance Model}
\sym{ASM}{Active Shape Model}
\end{abbreviations}

\chapter{INTRODUCTION}
\label{chapter:introduction}
\pagenumbering{arabic}

The requirements and explanations presented in the following pages aim to
provide guidance to graduate students preparing theses to be submitted to the Institute for
Graduate Studies in Science and Engineering at Bo\u{g}azi\c{c}i
University (henceforth referred to as `the Institute'). These guidelines are not intended, however, as a
complete manual for the writing of theses.

Every thesis must comply with grammatical and formatting rules and must possess clarity of expression. The responsibility for such compliance and
clarity rests primarily upon the candidate; nevertheless, every thesis should be scrutinized for these qualities by the student's Thesis Supervisor and the Defense Jury.

\begin{verbatim}
    vector3d RFField::actOn(Electron2D& e){
        vector3d Efield = getField(e.pos);                            // Calculate E vector
        vector3d F_m = Efield*1E6*eQMratio;                           // Calculate F/m vector
        vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();     // Calculate a vector
        return acc;
    }
\end{verbatim}

\chapter{FORMAT}
\label{chapter:format}

\section{Character Fonts}

Text should be typed in Times, Times New Roman or Computer Modern
(standard serif font provided by \LaTeX). The font size must be 12 points in the text including formulas, equations, Table headings, Table and Figure captions. Text appearing in Figures and Tables, as well as the text used in superscripts or subscripts, should be at least 8 points. Footnotes, long biographical quotes and extensive quotations should be 10 points.

\section{Spacing}

Spacing of the text material should be 1.5 or, when necessary, integer multiples thereof. The following are exceptions:
\begin{itemize}
 \item Footnotes: single spacing
 \item Long biographical quotes: single spacing
 \item Extensive quotations: single spacing and indented 1 cm relative to the text material.
 \item Equations and equation arrays: single spacing before and after,
 \item Footnotes: single spacing,
 \item Long biographical quotes: single spacing,
 \item Extensive quotations: single spacing and indented 1 cm relative to the text ma-
terial.
\end{itemize}

\clearpage
Spacing of figures is given in the ordered list below:
\begin{enumerate}
 \item Last line of a paragraph,
 \item One line of empty space,
 \item Figure,
 \item One line of empty space,
 \item Figure Caption ,
 \item One line of empty space,
 \item First line of a new paragraph.
\end{enumerate}

Spacing of tables is given in the ordered list below:
\begin{enumerate}
 \item Last line of a paragraph,
 \item One line of empty space,
 \item Table caption,
 \item Half a line of empty space,
 \item Table,
 \item One line of empty space,
 \item First line of a new paragraph.
\end{enumerate}

These spacing may be handed automatically by latex, but not always guaranteed. You should also check manually your thesis for this spacing order

\section{Centering}
\label{sec:centering}

The center point of titles and headings should be 112 mm from the left
edge of the paper or 98 mm from the right edge. This can be accomplished
via the standard centering commands in editors such as Microsoft Word and \LaTeX after margins are set as per explained in the following section. Centering manually is \emph{not} recommended practice because it is prone to errors.

\section{Margins}

Margins of pages should conform to the following specifications:
\begin{itemize}
 \item Left margin: 3.5 cm from the left edge of the paper
 \item Right margin: 2 cm from the right edge of the paper
 \item Top margin: 3.5 cm from the top edge of the paper (page numbers must be 2 cm from the top edge of the paper)
 \item Bottom margin: (at least) 2 cm from the bottom edge of the paper
\end{itemize}

Figures and Tables should also adhere to these margins. Folded pages will not be accepted unless there is absolutely no other way for the material to be presented.

\section{Pagination}

Each page in the thesis should bear a page number except for the title page and the pages on which a Figure or a Table is placed in landscape orientation. Only one side of the paper should be used.

The preliminary section comprising the Title Page, Page of Approval, Dedication Page (if present), Acknowledgements Page (if present) and the other pages in Table \ref{table:pagination} should be numbered, using lower case Roman numerals (i.e. i, ii, iii, ...). The Title Page counts as page i but the page number is not printed.  The preliminary section must follow the sequence shown in Table \ref{table:pagination}. An example of this sequence is provided in Appendix A.

\begin{table}[H]
\centering
\caption{Pagination Table: Page numbers are given as an example where each part takes only one page.}
\vskip\baselineskip
\begin{tabular}{|c|c|}
\hline
 \textbf{Page Title}& \textbf{Number}\\\hline
(Title Page) & Page i (number does not appear) \\\hline
(Page of Approval)  & Page ii \\\hline
(Dedication) & Page iii (if present) \\\hline
ACKNOWLEDGEMENTS & Page iv (if present)\\\hline
ABSTRACT  & Page v \\\hline
ÖZET  & Page vi \\\hline
TABLE OF CONTENTS  & Page vii \\\hline
LIST OF FIGURES  & Page viii (if present) \\\hline
LIST OF TABLES  & Page ix (if present) \\\hline
LIST OF SYMBOLS & Page x (if present) \\\hline
LIST OF ACRONYMS/ABBREVIATIONS & Page xi (if present) \\\hline
\end{tabular}
\label{table:pagination}
\end{table}

For the remainder of the thesis, Arabic numerals should be used. Each page should be numbered unless there is a full-page landscape Figure or Table present on a page; page numbers are not printed on such pages, but the
numbers continue to increment. Page numbers should to be placed two centimeters from the top and the right edges of the pages and they should be in 12 points. Use of suffixes (such as 25a, 25b, etc.) or punctuation (such as a dash or a period) is not permitted in page numbers. The numbering in the main body of the thesis should begin with page 1 and run consecutively to the last page.

\section{Headings}

Headings should be in the same font as the rest of the text and should feature no quotation nor punctuation marks other than the period following the Heading number. There may be at most four levels of Headings: Main Headings, Second Headings, First Subheadings and Second Subheadings. Additionally, special captions to designate Theorems, Corollaries, Lemmas, Definitions, Remarks and Propositions may be deployed.

Headings should be followed by at least one line of text (i.e. Headings should not directly be followed by Tables or Figures).

\begin{table}[H]
    \centering
    \vskip\baselineskip
    \caption{Summary of Heading specifications.}
    \vskip\baselineskip
    \begin{tabular}{|c|c|c|c|c|m{2cm}|}
  \hline
  Main Headings & centered & capital letters & bold face & 14 pt & no period\newline at the end \\
  \hline
  Second Headings & centered & title case letters & bold face & 12 pt & no period\newline at the end \\
  \hline
\end{tabular}
\end{table}

\subsection{Main Headings}

Main Headings should be numbered as 1., 2., ..., and they should comply with the following rules:
\begin{itemize}
 \item Main Headings should begin a new page and should be centered according to
Section \ref{sec:centering}. They should be typed in bold face and should be in capital letters and in
14 points. There should be no period at the end of the heading text.
\item Main Headings should reflect the content of the text that follows.
Main Headings are not to be called as chapters.
\item Heading number should be followed by a period and two spaces.
\item Main Headings should be separated from the succeeding text or second heading by two empty lines of text.
\end{itemize}

\subsection{Second Headings}

Second Headings should be numbered as 2.1., 2.2., ..., and they should comply with the following rules:
\begin{itemize}
 \item Second Headings should be centered according to Section \ref{sec:centering} and be typed in 12 points, bold face and title case letters (i.e., the first letter of each word except conjunctions, prepositions and articles must be a capitalized). There should be no period at the end of the heading text.
\item Heading number should be followed by a period and two spaces.
\item Second headings should be separated from the preceding text or main heading and succeeding text or first subheading by two empty lines of text.
\end{itemize}

\subsection{First Subheadings}

First Subheadings should be numbered as 2.1.1., 2.1.2., ..., and they should comply with the following rules:

\begin{itemize}
\item First Subheadings should be typed in bold face in 12 points and with title
case letters, beginning at the left
margin of the text. There should be no period at the end of the heading text.
%\item There should be no leading text on the line of the first heading.
\item Heading number should be followed by a period and two spaces.
\item First Subheadings should be separated from the preceding text or second heading and succeeding text by one empty line of text.
\end{itemize}

\subsection{Second Subheadings}

Second Subheadings should be avoided if possible. If they can't be avoided, they should be numbered as 2.1.1.1., 2.1.1.2., ..., and they should comply with the following rules:
\begin{itemize}
\item Second Subheadings should be aligned with the left margin of the text (with no indent), should be typed in 12 points and in title case letters, and they should be underlined.
\item Heading number should be followed by a period and
two spaces.
\item Heading text should be followed by a period and the leading text.
\item Second Subheadings should be separated from the preceding text or First Subheading by an empty line of text.
\end{itemize}

\subsection {Special Captions}

Special captions may be deployed to initiate Theorems, Lemmas, Propositions, Corollaries and Definitions. Special captions should obey the following rules:
\begin{itemize}
\item Special captions should be bold and in 12 points, typed in title case letters.
\item Special captions should be on the same line as their leading text, and they should be aligned with the left text margin (with no indent).
\item Leading text appearing after a special caption should be in italics and not more than one paragraph.
\item Each special caption should be succeeded with a numbering label in the form X.Y, where the first number X indicates the number of the current main heading and the second number Y starts with unity for each main heading and increases sequentially and separately for each caption type. For example, 3.5 would mean the fifth special caption of a certain type appearing under the third main heading (e.g. Theorem 3.5). When the main heading pertains to an Appendix, the first indicator is a letter such as A, B, ... .
\item For Theorems, Lemmas and Corollaries, a series of proof or remark blocks may follow. The first proof block should begin with the word \textit{Proof} written in italics and followed by a period; the remaining text of the block and the following blocks are regular type. The last block in a Proof environment should terminate with a $\Box$ at the lower right corner.
\end{itemize}

\section{Paragraphs}

First lines of all paragraphs should be indented by one centimeter. A new paragraph should not begin at the bottom of a page unless \textit{at least two lines} of the paragraph may be printed on that page. Each paragraph should be separated from the preceding and succeeding paragraphs by an empty line of text.

\section{List Items}
Lists composed of successive lines of text or paragraphs may, for clarity, be preceded by a bullet ($\bullet$) or enumerated as (i), (ii), (iii), etc.

Bold face or italic characters should not be used in list items. Certain information such as enzyme lists and lists of chemical supplies should be presented in tables rather than paragraph lists.

Second level of list items are permitted and they must be preceded by a bullet if the first level items are enumerated; on the other hand, if the first level items are preceded by a bullet, then the second level items must be enumerated.

Third level list items are not allowed.

\section{Footnotes}

Footnotes should be avoided whenever possible. If and when they must be used, they should comply with the following rules.
\begin{itemize}
\item Footnote references should be indicated in the text by a superscript Arabic number immediately following the word, phrase or sentence which the footnote concerns.
\item Footnotes should be sequentially numbered on each page and in the entire thesis.
\item Footnotes should be placed at the bottom of the page on which they are indicated. They should be indented from the left margin of the text by one centimeter and should be separated from the main text by a short horizontal line. Footnotes should be single-spaced and 10 points.
\end{itemize}

\section{Bibliographical Material}

The references are listed in the bibliography in the order of appearance in the text and they are numbered accordingly using Arabic numerals as 1., 2. ... (this will be referred to as the ``enumerated reference list"). The numerical reference of bibliographical material should be indicated in the text by an Arabic numeral in square brackets (for example ``[8]") placed in the text immediately following the name, word, phrase, or sentence
which the reference concerns (in some cases, this may be the author's
name). When two bibliographical references are to be cited, they should be separated by a comma (for example ``[8,9]"); when three or more consecutive
bibliographical references are to be cited, the first and the last should be given, separated by a dash line (for example ``[8-12]", ``[6], [8-12], [17]").

In the References section, references which do not exceed 10 authors must be written openly. "et al." expression can only be used when there are more than 10 authors for a reference.

\subsection{Enumerated Reference Lists}

The following schemes should be used in the enumerated reference lists:

\begin{flushleft}

\leftskip 5mm \parindent -5mm \textbf{Books:}

\leftskip 5mm \parindent -5mm 1. Firstauthorsurname, F.A. and S.A. Surname, \textit{Title of the Book}, Second Edition (only if other than the first), Publisher Name, City, Year.

\leftskip 5mm \parindent -5mm 2. Ross, S., \textit{A First Course in Probability}, Seventh Edition, Pearson Prentice Hall, New Jersey, 2006.

\leftskip 5mm \parindent -5mm 3. Ang, A.H-S. and W.H. Tang, \textit{Probability Concepts in Engineering}, John Wiley \& Sons, New Jersey, 2007.

\leftskip 5mm \parindent -5mm 4. Ang, A.H-S., W.H. Tang and S. Ross, \textit{Probability Concepts in Engineering}, John Wiley \& Sons, New Jersey, 2007.\newline

\leftskip 5mm \parindent -5mm \textbf{Journal Articles:}

\leftskip 5mm \parindent -5mm 1. Firstauthorsurname, F.A. and S.A. Surname, ``Title of the Article", \textit{Title of the Journal}, Vol. X, No. Y, page number (p. 5 or pp. 5-10), year of publication.

\leftskip 5mm \parindent -5mm 2. Maiers, J. and Y.S. Sherif, ``Application of Fuzzy Set Theory", \textit{IEEE Transactions on Systems, Man, and Cybernatics}, Vol. 15, No. 1, pp. 41-48, 1985.\newline

\leftskip 5mm \parindent -5mm \textbf{Conference Proceedings:}

\leftskip 5mm \parindent -5mm 1. Firstauthorsurname, F.A. and S.A. Surname, ``Title of the Article", in \textit{Title of the Proceedings}, Editors, Location, Vol. X (if exists), page number (p. 5 or pp. 5-10), year.

\leftskip 5mm \parindent -5mm 2. Brown, D. and D. Clair, ``Integrated R-transportation", paper presented at the \textit{14th International Conference of Transportation Logistics}, Istanbul, Turkey, 2008.\newline

\clearpage
\leftskip 5mm \parindent -5mm \textbf{Dissertations:}

\leftskip 5mm \parindent -5mm 1. Authorsurname, F.A., \textit{Title of the Dissertation}, Level (Ph.D. Thesis or M.S. Thesis), Name of Higher Education Institute, Year.

\leftskip 5mm \parindent -5mm 2. İşgüder, E., \textit{Human Computer Interaction in the 21st Century}, M.S. Thesis, Boğaziçi University, 2015.

\leftskip 5mm \parindent -5mm 3. İşgüder, E., \textit{Human Computer Interaction in the 22st Century}, Ph.D. Thesis, Boğaziçi University, 2021.\newline

\leftskip 5mm \parindent -5mm \textbf{Websites:}

\leftskip 5mm \parindent -5mm 1. Authorsurname, F.A. AND/OR Name of Authoring Body/Organization, ``Title of the Web Material", Publishing Year, URL, last access date.

\leftskip 5mm \parindent -5mm 2. Sarp, B., ``Observations", 2001, http://sarp.com.tr/obs.html, accessed on November 21, 2015.

\leftskip 5mm \parindent -5mm 3. Wikipedia, ``John von Neumann", http://en.wikipedia.org/wiki/John\_von\_Neumann, accessed on October 30, 2015.

\leftskip 5mm \parindent -5mm 4. Wikipedia, http://en.wikipedia.org/, accessed on October 29, 2015.

\leftskip 5mm \parindent -5mm 5. http://encyclopedia.org/, accessed on October 21, 2015.\newline

\clearpage
\leftskip 5mm \parindent -5mm \textbf{Patents:}

\leftskip 5mm \parindent -5mm 1. Lastname F., "Title of Patent", U.S. Patent Number, Month Day, Year. Available: URL or Database Name, Accessed on: Month Day, Year.

\leftskip 5mm \parindent -5mm 2. Shatner W., L. a. Christel, D. A. Borkholder and S. J. Young, ``Apparatus for Analysis of a Nucleic Acid Amplification Reaction", U.S. Patent 6942971 B2, September 13, 2005. https://www.google.com/patents/US6942971, Accessed on December 12, 2017.\newline

\leftskip 5mm \parindent -5mm \textbf{Manuals:}

\leftskip 5mm \parindent -5mm 1. Name of Manual/Handbook, xth ed. Name of Comp.,  Country, Month. Year, pp. xxx-xxx (pages if relevant). Accessed on: Month, Day, Year. [Online].site/path/file

\leftskip 5mm \parindent -5mm 2. The MakerBot Replicator Desktop 3D Printer (Fifth Generation Model) User Manual, MakerBot Industries, Brooklyn, NY, 2014.\newline

\leftskip 5mm \parindent -5mm \textbf{Preprints:}

\leftskip 5mm \parindent -5mm 1. Authorsurname, F.A., ``Title of the 
Material", arxiv Preprint number, Publishing Year.

\leftskip 5mm \parindent -5mm 2. Nettelblahd J. and C. Nettelblahd, “CannyFS: Opportunistically Maximizing I/O Throughput Exploiting the Transactional Nature of Batch-Mode Data Processing”, arXiv:1612.06830 [cs], 2016.\newline
\end{flushleft}

\subsection{Surname Reference Lists}

The following schemes should be used in the surname reference lists:\newline

\leftskip 5mm \parindent -5mm \textbf{Books:}

\leftskip 5mm \parindent -5mm Firstauthorsurname, F.A. and S.A. Surname, Year \textit{Title of the Book}, Second Edition (only if other than the first), Publisher Name, City.

\leftskip 5mm \parindent -5mm Ross, S., 2006, \textit{A First Course in Probability}, Seventh Edition, Pearson Prentice Hall, New Jersey.

\leftskip 5mm \parindent -5mm Ang, A.H-S. and W.H. Tang, 2007, \textit{Probability Concepts in Engineering}, John Wiley \& Sons, New Jersey.

\leftskip 5mm \parindent -5mm Ang, A.H-S., W.H. Tang and S. Ross, 2007, \textit{Probability Concepts in Engineering}, John Wiley \& Sons, New Jersey.\newline

\leftskip 5mm \parindent -5mm \textbf{Journal Articles:}

\leftskip 5mm \parindent -5mm Firstauthorsurname, F.A. and S.A. Surname, year of publication, ``Title of the Article", \textit{Title of the Journal}, Vol. X, No. Y, page number (p. 5 or pp. 5-10).

\leftskip 5mm \parindent -5mm Maiers, J. and Y.S. Sherif, 1985, ``Application of Fuzzy Set Theory", \textit{IEEE Transactions on Systems, Man, and Cybernatics}, Vol. 15, No. 1, pp. 41-48.\newline

\clearpage
\leftskip 5mm \parindent -5mm \textbf{Conference Proceedings:}

\leftskip 5mm \parindent -5mm Firstauthorsurname, F.A. and S.A. Surname, year, ``Title of the Article", in \textit{Title of the Proceedings}, Editors, Location, Vol. X (if exists), page number (p. 5 or pp. 5-10).

\leftskip 5mm \parindent -5mm Brown, D. and D. Clair, 2008, ``Integrated R-transportation", paper presented at the \textit{14th International Conference of Transportation Logistics}, Istanbul, Turkey.\newline

\leftskip 5mm \parindent -5mm \textbf{Dissertations:}

\leftskip 5mm \parindent -5mm Authorsurname, F.A., Year, \textit{Title of the Dissertation}, Level (Ph.D. Thesis or M.S. Thesis), Name of Higher Education Institute, Year.

\leftskip 5mm \parindent -5mm İşgüder, E., 2015, \textit{Human Computer Interaction in the 21st Century}, M.S. Thesis, Boğaziçi University.

\leftskip 5mm \parindent -5mm İşgüder, E., 2021, \textit{Human Computer Interaction in the 22st Century}, Ph.D. Thesis, Boğaziçi University.\newline

\leftskip 5mm \parindent -5mm \textbf{Websites:}

\leftskip 5mm \parindent -5mm Authorsurname, F.A. AND/OR Name of Authoring Body/Organization, Publishing Year, ``Title of the Web Material", URL, last access date.

\leftskip 5mm \parindent -5mm Sarp, B., 2001, ``Observations", http://sarp.com.tr/obs.html, accessed on November 21, 2015.

\clearpage
\leftskip 5mm \parindent -5mm Wikipedia, ``John von Neumann", http://en.wikipedia.org/wiki/John\_von\_Neumann, accessed on October 30, 2015.

\leftskip 5mm \parindent -5mm Wikipedia, http://en.wikipedia.org/, accessed on October 29, 2015.

\leftskip 5mm \parindent -5mm http://encyclopedia.org/, accessed on October 21, 2015.\newline

\leftskip 5mm \parindent -5mm \textbf{Patents:}

\leftskip 5mm \parindent -5mm Lastname F., Year, "Title of Patent", U.S. Patent Number. Available: URL or Database Name, Accessed on: Month Day, Year.

\leftskip 5mm \parindent -5mm Shatner W., L. a. Christel, D. A. Borkholder and S. J. Young, 2005, ``Apparatus for Analysis of a Nucleic Acid Amplification Reaction", U.S. Patent 6942971 B2, September 13, 2005. https://www.google.com/patents/US6942971, Accessed on December 12, 2017.

\leftskip 5mm \parindent -5mm \textbf{Manuals:}

\leftskip 5mm \parindent -5mm Name of Manual/Handbook, Year, xth ed. Name of Comp.,  Country, pp. xxx-xxx (pages if relevant). Accessed on: Month, Day, Year. [Online].site/path/file

\leftskip 5mm \parindent -5mm The MakerBot Replicator Desktop 3D Printer (Fifth Generation Model) User Manual, 2014, MakerBot Industries, Brooklyn, NY.\newline

\leftskip 5mm \parindent -5mm \textbf{Preprints:}

\leftskip 5mm \parindent -5mm Authorsurname, F.A., Publishing Year, ``Title of the 
Material", arXiv Preprint number.

\leftskip 5mm \parindent -5mm Nettelblahd J. and C. Nettelblahd, 2016, “CannyFS: Opportunistically Maximizing I/O Throughput Exploiting the Transactional Nature of Batch-Mode Data Processing”, arXiv:1612.06830 [cs].

\leftskip -5mm
\parindent 10mm

\section{Mathematical Expressions}
Mathematical expressions such as equations, formulas, etc. should be typeset in accordance with the following rules:

\begin{itemize}
\item Mathematical symbols and expressions within the text should be written with the same font used in the equation or equation array environments in order to separate them from the regular text. Italic font is the typical choice. \\

\item  Mathematical expressions, equations and equation arrays should be part of the text and should not be treated as images or floating objects. This means that i) they should be placed with one line spacing between the preceding and following text, ii) if they finish the sentence they should be ended with a full stop (.), iii) if the sentence continues after the mathematical expression it should not have a paragraph indentation or it should not start with a capital letter. \\

\item Multiple equations or mathematical expressions should be written in an equation array environment. This guarantees the single line spacing between these expressions. In equation arrays, the individual lines should be aligned such that the first equality (or inequality or similarity) signs are in line with each other.\\

\item Mathematical expressions should be referred to after they appear first and not before. Try to avoid from forward referencing. \\

This equation template should be followed strictly. You can see detailed examples in the Examples section.

\end{itemize}

\section{Tables and Figures}

All floating items such as graphs,
charts, photographs, illustrations and lists should be considered and
designated as a Figure or a Table, whichever is appropriate. To ensure acceptable print, all drawings, graphs, illustrations and similar graphical material should be prepared with sufficient resolution. All text in Figures and Tables should be clearly legible with and should appear in at least 8 points.

All Tables and Figures should be captioned and enumerated in the form ``X.Y" wherein ``X" refers to the number (or letter, if in Appendix) of the current Main Heading, and ``Y" increases sequentially staring with unity at each Main Heading, separately for Figures and Tables. Table captions should be located above the Tables whereas Figure captions should be placed below the Figures.  All captions should include the label and the number followed by a period and a space (such as ``Table 3.1. " or ``Figure A.1. " if in appendix), followed by an explanatory text referring to the content of the Table or Figure. Only the first word of the caption text should be capitalized and the text should end with a period; it should not be boldface or italic.

All Figures, Tables and their captions should be centered in accordance with Section \ref{sec:centering}. Captions should continue at most for 5 lines. Further explanation should be provided in the main text. Reference to a Figure/Table may come before or after the Figure/Table as long as the reference is clearly indicated and understood. If there are too many consecutive and related Figures/Tables, they should be presented in the appendix.

When a Figure contains sub-figures, each sub-figure must be marked with a lowercase letter in parenthesis starting with ``(a)". There is to be a single caption for the whole Figure within which each sub-figure is explicitly referred to and explained (such as ``Figure 3.8. (a) The picture, (b) the bigger picture.").

Figures should not be divided to and continued on multiple pages. When a Table is divided into two or more pages, each part should have the same label, number and text in its caption, but the captions of the second and the latter parts should end with the expression ``(cont.)." to indicate continuation.

When a Table or a Figure is referenced in the text, the reference should include the label and the number with the first letter of the label in capital case (such as
``Table 4.5" or ``Figure 3.8" - note that no period is placed after the number). A sub-figure may be directly referenced by indicating its label, number and sequence (such as ``Figure 3.8a" or ``Figure 3.8a and c").

All Tables should be framed, both externally and internally, with single-line borders. Tables should not have any background color, and the text fonts used in the Tables should
be consistent with the rest of the text. Table headers may be boldface
but colored texts are not allowed in these headers. Figures may be
colored where necessary. Figures should not have an embedded title in
the graphics/charts/photographs/etc., and the Figure caption should include all the necessary information.

All axes of graphs should have titles.

\chapter{ARRANGEMENT}

\section{Title Page}
The Title Page is the first page of the thesis. Please refer to the example for all pertinent details, including proper scaling and positioning. In particular,
\begin{itemize}
\item Page number should not be printed on the Title Page (whose page number is i).
\item The title of the thesis should be centered and in all capital letters in 14 points.
\item All prior higher education degrees of the candidate should be listed on the Title Page, showing the majors, the degree granting institutions and
graduation years in chronological order.
\item The submission requirement (``[...] of the requirements for the degree of Master of Science" or ``[...] of the requirements for the degree of Doctor of Philosophy") should be specified.
\item The name of the graduate program enrolled to and the year in which the thesis is approved should appear at the bottom of the Title Page.
\end{itemize}

\section{Approval Page}
All copies of the submitted thesis should include original signatures
of the Defense Jury on the Approval Page. The Approval Page should appear right after the Title Page.

The names of the members of the Defense Jury
should be listed in the alphabetical order of their surnames except for the
Thesis Supervisor's, whose name should be the first one on the list. If a Co-Supervisor exists, her/his name should appear right after the Supervisor's.
Titles of the Jury members should be presented in the North American
style with either ``Prof.",  ``Assoc. Prof." or ``Assist. Prof." preceding a Jury
member's name. If desired and appropriate, the term `Ph.D.' may follow
a Jury member's name (separated by a comma from the name). Space for the
signature of each Jury member should be left beside each name.

The date at the bottom of the Approval Page is the date at which the thesis is
approved by the Defense Jury.

\section{Dedication}
Dedication is rare and it should be thought of as an honorific statement to explicitly recognize someone who has provided exceptional support to the author, especially in the completion of the thesis. The Dedication Page should come right after the Approval Page.
Dedications should be simple phrases (such as `To my mother."), in English, and placed at the lower right corner of the page.

\section{Acknowledgements}
The candidate may desire to include a page with a brief note of an
acknowledgement of help received from particular people in the preparation of the thesis. All organizations proving financial support must be acknowledged and
grant numbers should be included.

\section{Abstract}
The Abstract should briefly describe the thesis work including its objectives, methods, results and conclusions. Two abstracts, one in
English and the other in Turkish, should be included. The Abstract
should not contain headings, tabular material, chemical formulae, footnotes or references, but author citing is allowed. Each abstract should be at most one page long.

The Abstract Page should contain the title of the thesis. The Turkish Abstract (``\"{O}zet") must follow the English Abstract in the same format.

\section{Table of Contents, List of Figures, List of
Tables, List
of Symbols and List of Acronyms/Abbreviations}
Theses are expected to have a `Table of Contents' for the convenience
of the reader. The Table of Contents should not list itself.

If Figures and Tables are scattered throughout the text, a
separate `List of Figures' (and/or `List of Tables') must be included
after the Table of Contents. These lists should include page numbers.

Similarly, a `List of Symbols' and/or `List of Symbols/Abbreviations', whichever is
appropriate, should be included. `List of Symbols' should list symbols alphabetically as separate groups in the order of Latin symbols, Greek symbols, and other symbols. `List of Accronyms/Abbreviations' should contain abbreviations listed alphabetically.

\section{The Main Body of the Thesis}
The main body of the thesis begins with the first Main Heading. The main body
should be composed of a series of Main Headings, starting with an
`Introduction' and ending with a `Conclusion'. The
main body generally includes one or more of the following: `Literature Survey', `Problem Statement', `Materials and Methods', `Results and Discussions' or other relevant topics.

The first page of the first Main Heading should be the first page
enumerated in Arabic numerals.

Attention should be paid to the precautions listed below:

\begin{itemize}
\item The whole text should be left and right justified.
\item Please note the spelling of `Foreword'.
\item Periods, commas, semicolons and colons go outside the quotation
marks.
\item The word `data' is plural and requires a plural verb.
\item Integers from one to nine, inclusive, should be spelled out
except when they represent a chapter or a section; for numbers 10 and
above, use numerals. Numbers should be spelled out when they begin a
sentence.
\item Do not spell out per cent; use \%.
\end{itemize}

\section{Appendices}
A thesis may present supporting data in the form of one or more Appendices. Examples of Appendix material include data sheets, questionnaire samples, flowcharts, illustrations, maps,
software listings, charts, etc. If the appended data need to include
oversized illustrations or maps, several alternative methods of
inclusions are available.

If a Table, Figure, Equation etc., is to be included in an
Appendix, the numbering should follow the same rules used within
the main body of the thesis. In this case, however, the numbering should begin with the letter
of the respective Appendix such as ``Table A.1", ``Equation B.4" etc.
Each Appendix should have a descriptive title, as should all Main Headings.

Software/computer programs developed in the thesis should be submitted on a separate CD. The format and contents of this CD is explained in Appendix B.

\chapter{PREPARATION OF THE FINAL COPIES}

\section{Typesetting}
Typesetting is generally accomplished using custom programs such as \TeX{}, \LaTeX{} or Microsoft Word\textsuperscript{\textregistered}. Template files may be provided by the Institute. It is the responsibility of the author to ensure that the typeset manuscript complies with the rules and regulations specified in this guide.

\section{Paper Quality}
The original copy should be printed on 75 or 80 gr/m\textsuperscript{2}, white, A4 paper. All reproduced copies should be of the same grade of paper.

\section{Printer}
The printer used in printing the thesis copies should provide high quality outputs such as laser or ink jet printers. Printer settings should comply with A4 and there should be no resizing of the page in printing.

\section{Reproduction}
Photocopy reproduction is acceptable while mimeographed or ditto
copies are not acceptable for all parts or copies of the thesis
submitted to the Institute or to the Library. Care should be taken to
insure that the proper grade of paper is used at all times and that
copying contrast is dark.

\section{Binding}
The thesis should be bound in dark blue, hard cover. The size of final, bound
copy of the thesis should conform to A4 paper size. The name and surname of
the candidate, the degree obtained and the year should be
printed, in the order specified, on the spine of the cover. When the thesis
is placed front cover up, the spine should read from left to right.

\chapter{PUBLICATION OF THESES}

\section{Use of Copyrighted Material}
The thesis author is solely responsible for use of any
copyrighted material in the thesis.

Permission to quote extensively from copyrighted material or to
reproduce a figure should be obtained by the thesis author from the author 
or the publisher of the copy righted material, whichever holds the copyright. Customarily,
authorization is granted on the condition that proper acknowledgement
is given. In some instances, however, the thesis author should keep on file the copyright granting permission to address possible future inquiries.

\section{Publications}
Theses or extracts thereof may be published in scholarly journals, proceedings, books or other media only upon release for publication by the major supervisor and provided proper credit is
given to Bo\u{g}azi\c{c}i University. No thesis may be published as
such before it has been approved by the major supervisor. All theses
and separately submitted abstracts are the property of Bo\u{g}azi\c{c}i
University.

As many theses will be important to other scholars and to a more
general body of readers, candidates for degrees should plan for
publication of their work.

\chapter{EXAMPLES}
\label{chapter:experiments-and-results}

Experiments and results come here... 
\section{Sample Section}
Always place some text after headings before putting a graphics into a section as seen in Figure~\ref{fig:sinAndCosineSample}.

\begingroup
\vskip\baselineskip % Only use if necessary
\begin{figure}[htbp]
	 \centering
		\includegraphics[width=0.5\columnwidth]{figures/cover.jpg}
		\vskip\baselineskip % Leave a vertical skip below the figure
		\caption{FBE Booklet.}
		\label{fig:sinAndCosineSample}
\end{figure}
\endgroup
Also, below, you can find how to arrange figures that can span multiple pages.

Descriptive text explaining the continuation of Figure~\ref{fig:sampleWithContinuation}. Normally FBE expects this page to be fully filled with content, hence the need for shifting text from following pages into here.

\newpage
Now, let us cite some studies: one source as \cite{ArticleRef},  two
sources as \cite{ArticleRef,BookRef} or you may cite three or
more sources as 
\cite{ConferenceRef,Webref,ThesisRef}.
Observe that they are ordered in the references chapter in the same
order as
they are cited. Both the IEEE referencing and APA referencing methods are allowed.

\begingroup
\begin{figure}[H]
\vskip\baselineskip % Only use if necessary
	\centering
		\includegraphics[width=\textwidth, keepaspectratio]{figures/ana-sayfa-cover-03.jpg}
		\caption{Sample Figure.}
		\label{fig:sampleWithContinuation}
		%\vskip\baselineskip 
\end{figure}
\endgroup

\clearpage

\begingroup
\setlength{\belowcaptionskip}{-20pt} %%Only use when there is tto much space below the caption.
\begin{figure}[H]
%\vskip\baselineskip % Only use if necessary
	\centering
		\includegraphics[width=\textwidth, keepaspectratio]{figures/View.jpg}
		\caption{Sample Figure (cont.).}
		\label{fig:sampleWithContinuation2}
\end{figure}
\endgroup

Let us put a sample table as seen in Table~\ref{table:shortTable}. Please pay attention that the caption is followed
by a period.

\begingroup
\begin{table}[thbp]
\vskip\baselineskip 
\caption[Sample table]{Sample table.} %You can also use belowcaptionskip or abovecaptionskip here
\begin{center}
\begin{tabular}{|c|c|c|} \hline
 & \textbf{Header 1}& \textbf{Header 2}\\\hline
\textbf{Row 1} & blah blah blah& blah blah blah \\\hline
\textbf{Row 2} & blah blah blah  & blah blah blah \\\hline
\end{tabular}
\label{table:shortTable}
\end{center}
\end{table}
\endgroup

Next up, there is a sample table that spans multiple pages. Normally the packages that are used for this breaks the formatting package provided by FBE, but if done like this, you won't encounter the ``package conflict" error stated in the FrequentlySeenMistakes.pdf in the FBE web site.
\clearpage

\begingroup
\begin{table}[thbp]
	\caption[Sample table that spans multiple pages.]{Sample table that spans multiple pages.}
	\label{table:multiPageSample}
\end{table}
\begin{center}
	\addtocounter{table}{-1}
	\begin{longtable}{|l|l|}\hline
		\endfirsthead
		\multicolumn{2}{c}{Table \ref{table:multiPageSample}. Sample table that spans multiple pages. (cont.) \vspace{1em}} \\\hline
		\endhead
		\endfoot
		\endlastfoot

		\textbf{Header 1}& \textbf{Header 2}\\\hline
		blah blah blah & blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\\hline

		blah blah blah & blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\\hline

		blah blah blah & blah blah blah \\
		& blah blah blah \\\hline
		blah blah blah & blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\\hline

		\pagebreak
		\textbf{Header 1}& \textbf{Header 2}\\\hline
		blah blah blah & blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\\hline

		blah blah blah & blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\\hline

		blah blah blah & blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\
		& blah blah blah \\\hline
	\end{longtable}
\end{center}
\vskip -2cm %This is used to remove excessive space after the longtable. It's not mandatory, can be removed if the final output isn't as desired.
\endgroup

You can use the code of Table~\ref{table:multiPageSample} to create multiple page spanning longtables.

Footnotes should be avoided as possible. If there is an absolute
necessity, footnotes should be used as this.\footnote{Example of a
footnote}  Please be informed that URLs are not allowed within thesis text, even in footnotes. Provide them as citations instead.

Item lists may be represented as follows:

\begin{itemize}
 \item This is an item. Do not use boldface for the items.
\begin{enumerate}
 \item This is a sub-item. Subsub-items are not allowed.
\end{enumerate}
\item Another item.
\end{itemize}
%  \item 
% \end{enumerate}

Item lists may also be represented as follows:
\begin{enumerate}
 \item This is another enumerated item.
\begin{itemize}
 \item This is another sub-item.
\end{itemize}

\end{enumerate}

{\textbf{Good Equation Example 1:}}

``Notice that the spectral efficiency of the system is $R=n+m=\log_2(NM)$ bits per channel use (bpcu).  At each transmission instant,  each set of $n+m$ bits is split into groups of $n$ and $m$ bits." (Because the letters $N$, $M$, $n$, and $m$ are used to denote some mathematical entities they are written in the math environment.)\\

{\textbf{Good Equation Example 2:}}
The received signal is expressed as
\beq
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}} 
\eeq where ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively. \\

{\textbf{Good Equation Example 3:}}
The received signal is expressed as
\beq
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}}. 
\eeq In this expression, ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively. \\

{\textbf{Good Equation Example 4 (Equation Group):}}
Notice that under the signal model presented in the previous section, ${\mathbf z}$ forms a zero-mean proper complex Gaussian random vector with the mean vector, ${\bf m}_{\bf z}$, that can be written as
\bea{\bf m}_{\bf z} &=& \mbox{E} \left[{\bf z}\right]= \sqrt{\frac{\rho K}{K+1}}\left( \bar{\bf h}_u \psi_u X_v -\bar{\bf h}_{\hat{u}} \psi_{\hat{u}} X_{\hat{v}}\right)\nnl
&=&\sqrt{\frac{\rho K}{K+1}}\left( \bar{\bf h}_u a_u X_v e^{j\theta_u}-\bar{\bf h}_{\hat{u}} a_{\hat{u}} X_{\hat{v}}e^{j\theta_{\hat{u}}}\right)\eea and the covariance matrix,  ${\bf \Sigma}_{\bf z}$, that can be computed as
\beq
{\bf \Sigma}_{\bf z} =\frac{\rho  \gamma(u, \hat{u}, v, \hat{v}, \psi_u, \psi_{\hat{u}}) {\bf \Sigma}_r}{K+1} 
\eeq 
where $\rho$  and ${\bf \Sigma}_r$ are  as defined before.\\

{ \textbf{Good Equation Example 5:} }

The SINR for the users in $\hat{U}_1$, the SNR for the users in $U_2$ on each subcarrier $n$ and the SNR for the remaining users in $\tilde{U}_1$ on each subcarrier $k$ can be written as
\bea
\Gamma^{(n)}_{\hat{U}_1} &=& \frac{P_n |h_n|^2}{P_{N+n} |h_{N+n}|^2 + \sigma^2} = \frac{P_t |g_n|^2}{\epsilon P_t |g_{N+n}|^2 + \sigma^2} \\
\Gamma^{(n)}_{U_2} &=& \frac{P_{N+n} |h_{N+n}|^2}{P_n |a_n - \hat{a}_n|^2 |h_n|^2 + \sigma^2} \nonumber \\
&=& \frac{\epsilon P_t |g_{N+n}|^2}{P_t |a_n - \hat{a}_n|^2 |g_{n}|^2 + \sigma^2}\\
\Gamma^{(k)}_{\tilde{U}_1} &=& \frac{P_{k} |h_{k}|^2}{\sigma^2} = \frac{P_t |g_{k}|^2}{\sigma^2}
\eea
respectively, where $n \in \{1, ..., M\}$, $k \in \{M+1, ..., N\}$. \\

{ \textbf{Bad Equation Example 1:} (Extra space between the text and the mathematical expressions.)}

The received signal is expressed as\

\beq
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}} 
\eeq\

 where ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively. \\

{\textbf{ Bad Equation Example 2:} (Paragraph indent and/or capital letter use after an equation despite the fact that the sentence is continued.)}

The received signal is expressed as

\beq
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}} 
\eeq

\hspace{.2in} Where ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively. \\

{ \textbf{Bad Equation Example 3:} (Equation appearing as a floating object instead being attached to a sentence.)}

The received signal is expressed as follows:
\beq
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}} 
\eeq In this expression, ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively. \\

{ \textbf{Bad Equation Example 4:} (Spacing) }

The SINR for the users in $\hat{U}_1$, the SNR for the users in $U_2$ on each subcarrier $n$ and the SNR for the remaining users in $\tilde{U}_1$ on each subcarrier $k$ can be written as\

\beq
\Gamma^{(n)}_{\hat{U}_1} = \frac{P_n |h_n|^2}{P_{N+n} |h_{N+n}|^2 + \sigma^2} = \frac{P_t |g_n|^2}{\epsilon P_t |g_{N+n}|^2 + \sigma^2}\eeq\

\beq \Gamma^{(n)}_{U_2} = \frac{P_{N+n} |h_{N+n}|^2}{P_n |a_n - \hat{a}_n|^2 |h_n|^2 + \sigma^2} = \frac{\epsilon P_t |g_{N+n}|^2}{P_t |a_n - \hat{a}_n|^2 |g_{n}|^2 + \sigma^2} \eeq\

\beq \Gamma^{(k)}_{\tilde{U}_1} = \frac{P_{k} |h_{k}|^2}{\sigma^2} = \frac{P_t |g_{k}|^2}{\sigma^2} \eeq\

respectively, where $n \in \{1, ..., M\}$, $k \in \{M+1, ..., N\}$. \

{ \textbf{Bad Equation Example 5:} (Forward Referencing)}

The received signal is expressed as in Equation (\ref{rec_sig5-}) given below:
\beq
\label{rec_sig5-}
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}}. 
\eeq
 ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively. \\

{ \textbf{Bad Equation Example 6:} }

The received signal is expressed as
\beq
\label{rec_sig6-}
{\mathbf y}={\mathbf H}{\bf \Psi}{\mathbf x} + {\bm{\nu}}.
\eeq
 In Equation (\ref{rec_sig6-}), ${\bf H}$ is the $N_r \times N_t$ dimensional channel matrix and ${\mathbf y}$ and ${\bm{\nu}} $ are the $N_r \times 1$ dimensional received signal and channel noise vectors, respectively.

\chapter{CONCLUSION}
\label{chapter:conclusion}

The conclusions of the thesis should come
here.
% \nocite{NewEntry1,NewEntry2,NewEntry3,NewEntry4,NewEntry5,
% NewEntry6,
% NewEntry7,NewEntry8,NewEntry9,NewEntry10,NewEntry11,NewEntry12}

\nocite{*}
 \bibliographystyle{styles/fbe_tez_v11.bst} %Still may have problems
\bibliography{references} %Still may have problems

\chapter*{REFERENCES FOR APA STYLE}

\leftskip 5mm \parindent -5mm Ang, A.H-S., W.H. Tang and S. Ross, \textit{Probability Concepts in Engineering}, John Wiley \& Sons, New Jersey, 2007.

\leftskip 5mm \parindent -5mm Brown, D. and D. Clair, 2008, ``Integrated R-transportation", paper presented at the \textit{14th International Conference of Transportation Logistics}, Istanbul, Turkey.

\leftskip 5mm \parindent -5mm İşgüder, E., 2021, \textit{Human Computer Interaction in the 22st Century}, Ph.D. Thesis, Boğaziçi University.

\leftskip 5mm \parindent -5mm Maiers, J. and Y.S. Sherif, 1985, ``Application of Fuzzy Set Theory", \textit{IEEE Transactions on Systems, Man, and Cybernatics}, Vol. 15, No. 1, pp. 41-48.

\leftskip 5mm \parindent -5mm Nettelblahd J. and C. Nettelblahd, 2016, “CannyFS: Opportunistically Maximizing I/O Throughput Exploiting the Transactional Nature of Batch-Mode Data Processing”, arXiv:1612.06830 [cs].

\leftskip 5mm \parindent -5mm Sarp, B., 2001, ``Observations", http://sarp.com.tr/obs.html, accessed on November 21, 2015.

\leftskip 5mm \parindent -5mm Shatner W., L. a. Christel, D. A. Borkholder and S. J. Young, 2005, ``Apparatus for Analysis of a Nucleic Acid Amplification Reaction", U.S. Patent 6942971 B2, September 13, 2005. https://www.google.com/patents/US6942971, Accessed on December 12, 2017.

\leftskip 5mm \parindent -5mm The MakerBot Replicator Desktop 3D Printer (Fifth Generation Model) User Manual, 2014, MakerBot Industries, Brooklyn, NY.

\appendix
\chapter[AN APPENDIX TITLE THAT IS LONG AND THEREFORE\\
	\hspace*{2.95cm} NEEDS MANUAL ADJUSTMENT IN LATEX CODE TO FIT\\
	\hspace*{2.95cm} PROPERLY IN TABLE OF CONTENTS]{AN APPENDIX TITLE THAT IS LONG AND THEREFORE NEEDS MANUAL ADJUSTMENT IN LATEX CODE TO FIT PROPERLY IN TABLE OF CONTENTS}

The appendices start here. After references section.

\chapter{SAMPLE PAGES}
This booklet (except its title page) is typeset in the
format required for the theses.

\end{document}

### 2023-06-11 merged/merged.tex
structure changed

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{float}
\usepackage{wrapfig,lipsum}
\usepackage{svg}
\usepackage{mathtools}
\usepackage{tabu}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\begin{document}

\newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
\newcommand{\vecthree}[1]{\vec{#1}}

\newcommand{\parDeriv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\parDerivS}[2]{\frac{\partial^2 #1}{\partial #2^2}}

\newcommand{\dotProdBF}[2]{\vecthreeBF{#1} \cdot \vecthreeBF{#2}}
\newcommand{\dotProd}[2]{\vecthree{#1} \cdot \vecthree{#2}}

\newcommand{\crossProdBF}[2]{\vecthreeBF{#1} \times \vecthreeBF{#2}}
\newcommand{\crossProd}[2]{\vecthree{#1} \times \vecthree{#2}}

\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}

\section{Theory}

\subsection{Relation between momentum and acceleration}
In classical mechanics, Newton's second law defines momentum and states

\begin{equation}
    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
\end{equation}
\newline
In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
\begin{equation*}
    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
\end{equation*}
\newline
Considering these two statements, we can find the relation between momentum and acceleration as follows
\begin{eqnarray*}
    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
\end{eqnarray*}

\begin{equation} \label{eq:Frel}
    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
\end{equation}
\newline
It is clear that acceleration is not necessarily parallel to the force. To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;

\begin{equation} \label{eq:a_F_parallels}
    \begin{aligned}
        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
    \end{aligned}
\end{equation}

\begin{eqnarray*}
    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
\end{eqnarray*}

Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,

\begin{equation*}
    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
\end{equation*}

Inserting this
\begin{eqnarray}
    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
\end{eqnarray}

Therefore from \fromeqs{Frel}{Frel_parallel}

\begin{eqnarray*}
    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
\end{eqnarray*}

\begin{equation} \label{eq:Frel_para_and_perp}
    \begin{aligned}
        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
    \end{aligned}
\end{equation}

\subsection{Lorentz Force}
Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
\newline
\begin{equation} \label{eq:lf}
    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
\end{equation}
\newline
where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle. Replacing

\subsection{Relativistic Lorentz Force}
Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
\newline
\begin{equation}
    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
\end{equation}
\newline
Where $ \partial \tau = \partial t / \gamma $,

\begin{equation}
    \begin{aligned}
        p^{\mu} = 
        \begin{bmatrix}
            W/c \\
            p_x         \\
            p_y \\
            p_z
        \end{bmatrix}    
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        F^{\mu\nu} = 
        \begin{bmatrix}
                0       & -E_x/c   & -E_y/c    & -E_z/c \\
                E_x/c   &   0      & -B_z      & B_y     \\
                E_y/c   &   B_z    &  0        & -B_x     \\
                E_z/c   &   -B_y   & B_x       & 0   
        \end{bmatrix} 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        u_{\nu} = \gamma
        \begin{bmatrix}
                 c \\
                -v_x \\
                -v_y \\
                -v_z \\
        \end{bmatrix} 
    \end{aligned}
\end{equation}
\newline
Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
\newline

For $ \mu = 0 $, we have the time component of the equation;
\newline
\begin{equation}
    \frac{\gamma}{c}\frac{\partial W}{\partial t} = \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t}
\end{equation}
\begin{equation}
    \frac{\partial W}{\partial t} = q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
\end{equation}
\newline

This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
\newline
\begin{equation*}
    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
\end{equation*}
\newline
Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.

\subsection{Acceleration caused by lorentz force}
Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. Therefore the acceleration of the magnetic field is straightforward

\begin{equation*}
    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
\end{equation*}
\newline
The same thing cannot be said about electric field however. It can create force in any direction with respect to velocity. Therefore, we have the following equality;

\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
    \begin{aligned}
        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
    \end{aligned}    
\end{equation}
\newline
Acceleration due to electric field can be simplified as;
\begin{eqnarray*}
    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
\end{eqnarray*}

Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have

\begin{equation} \label{eq:acc_of_E_and_B}
    \begin{aligned}
        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
    \end{aligned}
\end{equation}

\newpage
\subsection{Leap Frog}
Leapfrog is a method that is used to numarically intergenerate that are in the form of

\begin{equation*}
    \parDerivS{x}{t} = f(x)
\end{equation*}

It is also known as the Störmer-Verlet method, commonly used to numerically calculate the trejectory of particles. 
The name comes from the fact that calculation of updated $\textbf{x}$ and $\textbf{v}$ are done in some order and calculated for different time slices. 
The energy is approximately conserved during the calculation. 
It is stable in oscillatory motion as long as the time-step $\Delta t$ is constant, and satisfies $\Delta t\leq 2/\omega$ \cite{leapfrog_osc}.
The idea is straight forward; in the time interval $\Delta t$,

\begin{eqnarray}
    a(t_0) &=& f(x_0) \nonumber \\
    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
\end{eqnarray}

For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,

\begin{eqnarray} \label{eq:leapfrog}
    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
\end{eqnarray}

This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.

\subsection{Runge Kutta}

Runge Kutta is another

\begin{thebibliography}{9}
\bibitem{leapfrog_osc}
C. K. Birdsall and A. B. Langdon, \emph{Plasma Physics via Computer Simulations}, McGraw-Hill Book Company, 1985, p. 56.
\end{thebibliography}

\end{document}

### 2023-06-11 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
structure changed

--- 2023-06-11 merged/merged.tex
@@
 \newcommand{\parDerivS}[2]{\frac{\partial^2 #1}{\partial #2^2}}
+\newcommand{\derivS}[2]{\frac{d^2 #1}{d#2^2}}
 
@@
 
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines momentum and states
+\subsection{Numerical Integration Methods}
 
-\begin{equation}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-\newline
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-\newline
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-\newline
-It is clear that acceleration is not necessarily parallel to the force.
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
-
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-
-Therefore from \fromeqs{Frel}{Frel_parallel}
-
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle. Replacing
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\newline
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-\newline
-Where $ \partial \tau = \partial t / \gamma $,
-
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-\newline
-Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\newline
-\begin{equation}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} = \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t}
-\end{equation}
-\begin{equation}
-    \frac{\partial W}{\partial t} = q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{equation}
-\newline
-
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\newline
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-\newline
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle.
-Therefore the acceleration of the magnetic field is straightforward
-
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-\newline
-The same thing cannot be said about electric field however. It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-\newline
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-\subsection{Leap Frog}
+\subsubsection{Leap Frog}
 Leapfrog is a method that is used to numarically intergenerate that are in the form of
@@
 \begin{equation*}
-    \parDerivS{x}{t} = f(x)
+    \ddot{x} = \derivS{x}{t} = f(x)
 \end{equation*}
@@
 
-\subsection{Runge Kutta}
+\subsubsection{Runge Kutta}
 
-Runge Kutta is another
+Runge Kutta is another numerical integration method that is
 

### 2023-06-11 subsections/theory/rhodotron/rhodotron.tex
structure changed

--- 2023-06-11 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
@@
 
-\subsection{Numerical Integration Methods}
+\subsection{Practical}
 
-\subsubsection{Leap Frog}
-Leapfrog is a method that is used to numarically intergenerate that are in the form of
+\subsubsection{Accelerating Cavity}
 
-\begin{equation*}
-    \ddot{x} = \derivS{x}{t} = f(x)
-\end{equation*}
-
-It is also known as the Störmer-Verlet method, commonly used to numerically calculate the trejectory of particles. 
-The name comes from the fact that calculation of updated $\textbf{x}$ and $\textbf{v}$ are done in some order and calculated for different time slices. 
-The energy is approximately conserved during the calculation. 
-It is stable in oscillatory motion as long as the time-step $\Delta t$ is constant, and satisfies $\Delta t\leq 2/\omega$ \cite{leapfrog_osc}.
-The idea is straight forward; in the time interval $\Delta t$,
-
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsubsection{Runge Kutta}
-
-Runge Kutta is another numerical integration method that is
-
-\begin{thebibliography}{9}
-\bibitem{leapfrog_osc}
-C. K. Birdsall and A. B. Langdon, \emph{Plasma Physics via Computer Simulations}, McGraw-Hill Book Company, 1985, p. 56.
-\end{thebibliography}
+\subsubsection{}
 

### 2023-06-15 mythesis.tex
merge the sections

--- 2023-06-11 merged/merged.tex
@@
-\documentclass{article}
+\documentclass[a4paper,oneside,12pt]{report}
+\usepackage{styles/fbe_tez}
+\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
+\usepackage{amsmath, amsthm} % Some extra symbols
+\usepackage[bottom]{footmisc}
+\usepackage{cite}
+\usepackage{graphicx}
+\usepackage{longtable}
+\usepackage{float}
+\usepackage{multirow}
+\usepackage{subfigure}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{array}
+\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
+\usepackage{epsfig}
+\usepackage{epstopdf}
+\usepackage{subfigure} % 
+\usepackage{amsmath}
+\usepackage{notoccite}
 
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{tikz}
-\usepackage{float}
-\usepackage{wrapfig,lipsum}
-\usepackage{svg}
-\usepackage{mathtools}
-\usepackage{tabu}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\interdisplaylinepenalty=2500
+\hyphenation{lists} \makeatletter
 
+\newcommand{\field}[1]{\mathbb{#1} }
+\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
+\setlength\belowdisplayskip{5pt}}
+\newcommand{\eeq}{\end{equation}}
+\newcommand{\bea}{\begin{eqnarray}}
+\newcommand{\eea}{\end{eqnarray}}
+\newcommand{\defn}{\stackrel{\triangle}{=}}
+\newcommand{\nn}{\nonumber}
+\newcommand{\nnl}{\nonumber \\}
+\renewcommand{\theequation}{\arabic{equation}}
+\renewcommand{\labelenumi}{(\roman{enumi})}
+
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+
+\def\ifundefined{\@ifundefined}
+\def\bfat{\left[ \begin{array}}
+\def\emat{\end{array} \right]}
+\def\bfatt{\left\{ \begin{array}}
+\def\ematt{\end{array} \right.}
+\def\bset{\left\{ \begin{array}}
+\def\eset{\end{array} \right\}}
+\def\bpar{\left( \begin{array}}
+\def\epar{\end{array} \right)}
+
+\graphicspath{{figures/}} % Graphics will be here
+
+\newtheorem{thm}{Theorem}[chapter]
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{cor}[thm]{Corollary}
+
+\numberwithin{equation}{chapter}
+
+% COVER PAGE
+\title{THESIS TITLE}
+\turkcebaslik{TEZ BAŞLIĞI}
+\degree{B.S., Program Name, Boğaziçi University, 2010\\
+	M.S., Program Name, Boğaziçi University, 2013}
+\author{Name Surname}
+\program{Program Name}
+\subyear{2019}
+
+% APPROVED BY PAGE
+\supervisor{Prof. Name Surname}
+%\cosuperi{Title and Name of Cosupervisor I}
+%\cosuperii{Title and Name of Cosupervisor II}
+\examineri{Assoc. Prof. Name Surname}
+\examinerii{Assist. Prof. Name Surname}
+\examineriii{Name Surname, Ph.D.}
+%\examineriv{}
+%\examinerv{}
+\dateofapproval{DD.MM.YYYY}
+
+% BEGIN OF DOCS
 \begin{document}
+\pagenumbering{roman}
+\makemstitle % M.S. thesis
+\makeapprovalpage
+
+% ACK PAGE
+\begin{acknowledgements}
+Acknowledgements come here...
+\end{acknowledgements}
+
+% ABS PAGE
+\begin{abstract}
+One page abstract will come here.  
+\end{abstract}
+
+% OZET PAGE
+\begin{ozet}
+Bir sayfa uzunluğunda özet gelecektir.
+\end{ozet}
+
+% CONTENTS AND LIST OF FIG AND TABLE PAGES
+\tableofcontents
+\listoffigures
+\listoftables
+
+% LIST OF SYMBOLS PAGE
+\begin{symbols}
+% The title will be typeset as "LIST OF SYMBOLS".
+% Use a separate \sym command for each symbols definition.
+% First, Latin symbols in alphabetical order
+\sym{$a_{ij}$}{Description of $a_{ij}$}
+\sym{$\mathbf{A}$}{State transition matrix of a hidden Markov model}
+% 1 EMPTY LINE BETWEEN LATIN AND GREEK SYMBOLS GROUP!!!
+\sym{}{}
+% Then Greek symbols in alphabetical order
+\sym{$\alpha$}{Blending parameter \textit{or} scale}
+\sym{$\beta_t(i)$}{Backward variable}
+\sym{$\Theta$}{Parameter set}
+\sym{ }{}
+\end{symbols}
 
@@
 
-\section{Theory}
+\newpage
+\chapter{THEORY}
 
-\subsection{Relation between momentum and acceleration}
+\section{Relation between momentum and acceleration}
 In classical mechanics, Newton's second law defines momentum and states 
-
 \begin{equation}
@@
 \end{equation}
-\newline
 In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
@@
 \end{equation*}
-\newline
 Considering these two statements, we can find the relation between momentum and acceleration as follows
@@
 \end{eqnarray*}
-
 \begin{equation} \label{eq:Frel}
@@
 \end{equation}
-\newline
 It is clear that acceleration is not necessarily parallel to the force.
 To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
-
 \begin{equation} \label{eq:a_F_parallels}
@@
 \end{equation}
-
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
 Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-
 \begin{equation*}
@@
 \end{equation*}
-
 Inserting this
@@
 \end{eqnarray}
-
 Therefore from \fromeqs{Frel}{Frel_parallel}
-
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
 \begin{equation} \label{eq:Frel_para_and_perp}
@@
 
-\subsection{Lorentz Force}
+\section{Lorentz Force}
 Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
@@
 \newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle. Replacing
+where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
 
-\subsection{Relativistic Lorentz Force}
+\section{Relativistic Lorentz Force}
 Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\newline
 \begin{equation}
@@
 \end{equation}
-\newline
 Where $ \partial \tau = \partial t / \gamma $,
-
 \begin{equation}
@@
 \end{equation}
-\newline
 Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
@@
 For $ \mu = 0 $, we have the time component of the equation;
-\newline
-\begin{equation}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} = \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t}
-\end{equation}
-\begin{equation}
-    \frac{\partial W}{\partial t} = q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{equation}
-\newline
-
+\begin{eqnarray}
+    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
+    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
+\end{eqnarray}
 This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\newline
 \begin{equation*}
@@
 \end{equation*}
-\newline
 Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
 
-\subsection{Acceleration caused by lorentz force}
+\section{Acceleration caused by lorentz force}
 Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
 Therefore the acceleration of the magnetic field is straightforward
-
 \begin{equation*}
@@
 \end{equation*}
-\newline
-The same thing cannot be said about electric field however. It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-
+The same thing cannot be said about electric field however. 
+It can create force in any direction with respect to velocity. Therefore, we have the following equality;
 \begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
@@
 \end{equation}
-\newline
 Acceleration due to electric field can be simplified as;
@@
 \end{eqnarray*}
-
 Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-
 \begin{equation} \label{eq:acc_of_E_and_B}
@@
 
-\newpage
-\subsection{Leap Frog}
-Leapfrog is a method that is used to numarically intergenerate that are in the form of
+\section{Numerical Integration Methods}
 
-\begin{equation*}
-    \parDerivS{x}{t} = f(x)
-\end{equation*}
+\subsection{Leapfrog} \label{sec:leapfrog}
+The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
 
-It is also known as the Störmer-Verlet method, commonly used to numerically calculate the trejectory of particles. 
-The name comes from the fact that calculation of updated $\textbf{x}$ and $\textbf{v}$ are done in some order and calculated for different time slices. 
-The energy is approximately conserved during the calculation. 
-It is stable in oscillatory motion as long as the time-step $\Delta t$ is constant, and satisfies $\Delta t\leq 2/\omega$ \cite{leapfrog_osc}.
+\begin{equation}
+    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
+\end{equation}
+\newline
+The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
+The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
+It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
 The idea is straight forward; in the time interval $\Delta t$, 
-
 \begin{eqnarray}
@@
 For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-
 \begin{eqnarray} \label{eq:leapfrog}
@@
 
-Runge Kutta is another
+The Runge-Kutta method is another numerical method used to solve ordinary differential equations (ODEs) numerically (see $\fromeq{second-order-ODE}$).
+It's named after the German mathematicians Carl Runge and Martin Wilhelm Kutta.
+
+The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average of function evaluations at different points within each step. 
+This weighted average improves the accuracy of the approximation compared to simpler methods like Leapfrog (see $\textit{section \ref{sec:leapfrog}}$).
+% TODO: ADD GENERAL FORM OF RK HERE
+\newline
+The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4.
+The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
+
+% TODO: ADD RK4 HERE
 

### 2023-06-15 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
merge the sections

@@
 
-\subsubsection{Leap Frog}
-Leapfrog is a method that is used to numarically intergenerate that are in the form of
+\subsubsection{Leapfrog} \label{sec:leapfrog}
+The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
 
-\begin{equation*}
-    \ddot{x} = \derivS{x}{t} = f(x)
-\end{equation*}
-
-It is also known as the Störmer-Verlet method, commonly used to numerically calculate the trejectory of particles. 
-The name comes from the fact that calculation of updated $\textbf{x}$ and $\textbf{v}$ are done in some order and calculated for different time slices. 
-The energy is approximately conserved during the calculation. 
-It is stable in oscillatory motion as long as the time-step $\Delta t$ is constant, and satisfies $\Delta t\leq 2/\omega$ \cite{leapfrog_osc}.
+\begin{equation}
+    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
+\end{equation}
+\newline
+The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
+The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
+It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
 The idea is straight forward; in the time interval $\Delta t$, 
-
 \begin{eqnarray}
@@
 
-Runge Kutta is another numerical integration method that is
+The Runge-Kutta method is another numerical method used to solve ordinary differential equations (ODEs) numerically (see $\fromeq{second-order-ODE}$).
+It's named after the German mathematicians Carl Runge and Martin Wilhelm Kutta.
+
+The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average of function evaluations at different points within each step. 
+This weighted average improves the accuracy of the approximation compared to simpler methods like Leapfrog (see $\textit{section \ref{sec:leapfrog}}$).
+% TODO: ADD GENERAL FORM OF RK HERE
+\newline
+The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4.
+The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
+
+% TODO: ADD RK4 HERE
 

### 2023-06-24 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
automation scripts added for thesis

@@
 
-\section{Theory}
+%%%%%%
 
-\subsection{Numerical Integration Methods}
+\section{Numerical Integration Methods}
 
-\subsubsection{Leapfrog} \label{sec:leapfrog}
+\subsection{Leapfrog} \label{sec:leapfrog}
 The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
@@
 
-\subsubsection{Runge Kutta}
+\subsection{Runge Kutta}
 
@@
 
+%%%%%%
+
 \begin{thebibliography}{9}

### 2023-06-24 subsections/theory/rhodotron/rhodotron.tex
merge the sections
automation scripts added for thesis

@@
 
-\section{Theory}
+%%%%%%
 
-\subsection{Practical}
+\section{Practical}
 
-\subsubsection{Accelerating Cavity}
+\subsection{Accelerators}
+Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
+These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
+They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
 
-\subsubsection{}
+At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
+These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
+By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
+
+Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
+Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
+
+The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
+As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
+Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
+
+As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
+Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
+
+Particle accelerators are essential tools for scientific research.
+They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
+Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
+They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
+
+In summary, particle accelerators are complex scientific instruments that use electromagnetic fields to accelerate charged particles to high speeds and energies. 
+They enable scientists to investigate the fundamental nature of matter, unravel the mysteries of the universe, and apply their findings to various fields of research and practical applications.
+
+% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+
+\subsubsection{Key Concepts}
+
+\begin{itemize}
+    \item Phase Lag
+
+    This is the asdasd
+
+    \item XD
+    \item AW
+
+\end{itemize}
+
+\subsubsection{Acceleration Cavities}
+Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
+These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
+
+RF cavities are typically hollow metallic structures made of high-conductivity materials such as copper or niobium. 
+They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
+The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
+The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
+The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
+To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
+The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
+These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
+
+In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
+By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
+This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
+This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
+Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
+
+% TODO : ADD RF CAVITY PICTURE HERE
+
+\subsubsection{Steerer Magnets}
+Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
+They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator. 
+According to the Lorentz Force Law ( $\textit{Section \ref{sec:LorentzForce}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
+vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
+
+% TODO : ADD STEERER MAGNET PICTURE HERE
+
+\subsection{Rhodotron Accelerator}
+
+%%%%%%
 

### 2023-06-24 subsections/theory/simulation/simulation.tex
automation scripts added for thesis

--- 2023-06-11 subsections/theory/rhodotron/rhodotron.tex
@@
 
-\section{Theory}
+%%%%%%
 
-\subsection{Practical}
+\section{Simulation}
 
-\subsubsection{Accelerating Cavity}
+A simulation software is a computer program or tool that enables the creation and execution of 
+simulations to model and analyze real-world systems or processes. 
+It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
+providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
 
-\subsubsection{}
+Simulation software provides a virtual environment where users can define the parameters,
+variables, and rules of the system being simulated. The software then uses mathematical models, 
+algorithms, and computational techniques to simulate the behavior of the system over time.
+
+\subsection{}
+
+%%%%%%
 

### 2023-06-24 theory.tex
automation scripts added for thesis

--- 2023-06-15 mythesis.tex
@@
 
-% COVER PAGE
-\title{THESIS TITLE}
-\turkcebaslik{TEZ BAŞLIĞI}
-\degree{B.S., Program Name, Boğaziçi University, 2010\\
-	M.S., Program Name, Boğaziçi University, 2013}
-\author{Name Surname}
-\program{Program Name}
-\subyear{2019}
-
-% APPROVED BY PAGE
-\supervisor{Prof. Name Surname}
-%\cosuperi{Title and Name of Cosupervisor I}
-%\cosuperii{Title and Name of Cosupervisor II}
-\examineri{Assoc. Prof. Name Surname}
-\examinerii{Assist. Prof. Name Surname}
-\examineriii{Name Surname, Ph.D.}
-%\examineriv{}
-%\examinerv{}
-\dateofapproval{DD.MM.YYYY}
-
 % BEGIN OF DOCS
@@
 \pagenumbering{roman}
-\makemstitle % M.S. thesis
-\makeapprovalpage
-
-% ACK PAGE
-\begin{acknowledgements}
-Acknowledgements come here...
-\end{acknowledgements}
-
-% ABS PAGE
-\begin{abstract}
-One page abstract will come here.  
-\end{abstract}
-
-% OZET PAGE
-\begin{ozet}
-Bir sayfa uzunluğunda özet gelecektir.
-\end{ozet}
 
@@
 \tableofcontents
-\listoffigures
-\listoftables
 
-% LIST OF SYMBOLS PAGE
-\begin{symbols}
-% The title will be typeset as "LIST OF SYMBOLS".
-% Use a separate \sym command for each symbols definition.
-% First, Latin symbols in alphabetical order
-\sym{$a_{ij}$}{Description of $a_{ij}$}
-\sym{$\mathbf{A}$}{State transition matrix of a hidden Markov model}
-% 1 EMPTY LINE BETWEEN LATIN AND GREEK SYMBOLS GROUP!!!
-\sym{}{}
-% Then Greek symbols in alphabetical order
-\sym{$\alpha$}{Blending parameter \textit{or} scale}
-\sym{$\beta_t(i)$}{Backward variable}
-\sym{$\Theta$}{Parameter set}
-\sym{ }{}
-\end{symbols}
+\pagenumbering{arabic}
+
+%#####
+% START OF THEORY
+
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
 
@@
 
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-
-\newpage
 \chapter{THEORY}
 
-\section{Relation between momentum and acceleration}
+\section{Accelerating Charged Particles}
+
+\subsection{Relation between momentum and acceleration}
 In classical mechanics, Newton's second law defines momentum and states 
@@
 
-\section{Lorentz Force}
+\subsection{Lorentz Force}
 Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
@@
 
-\section{Relativistic Lorentz Force}
+\subsection{Relativistic Lorentz Force}
 Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
@@
 
-\section{Acceleration caused by lorentz force}
+\subsection{Acceleration caused by lorentz force}
 Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
@@
 \end{equation}
+
+\section{Practical}
+
+\subsection{Accelerators}
+Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
+These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
+They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
+
+At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
+These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
+By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
+
+Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
+Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
+
+The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
+As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
+Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
+
+As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
+Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
+
+Particle accelerators are essential tools for scientific research.
+They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
+Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
+They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
+
+In summary, particle accelerators are complex scientific instruments that use electromagnetic fields to accelerate charged particles to high speeds and energies. 
+They enable scientists to investigate the fundamental nature of matter, unravel the mysteries of the universe, and apply their findings to various fields of research and practical applications.
+
+% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+
+\subsubsection{Key Concepts}
+
+\begin{itemize}
+    \item Phase Lag
+
+    This is the asdasd
+
+    \item XD
+    \item AW
+
+\end{itemize}
+
+\subsubsection{Acceleration Cavities}
+Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
+These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
+
+RF cavities are typically hollow metallic structures made of high-conductivity materials such as copper or niobium. 
+They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
+The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
+The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
+The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
+To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
+The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
+These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
+
+In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
+By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
+This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
+This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
+Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
+
+% TODO : ADD RF CAVITY PICTURE HERE
+
+\subsubsection{Steerer Magnets}
+Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
+They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator. 
+According to the Lorentz Force Law ( $\textit{Section \ref{sec:LorentzForce}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
+vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
+
+% TODO : ADD STEERER MAGNET PICTURE HERE
+
+\subsection{Rhodotron Accelerator}
 
@@
 
-\begin{thebibliography}{9}
-\bibitem{leapfrog_osc}
-C. K. Birdsall and A. B. Langdon, \emph{Plasma Physics via Computer Simulations}, McGraw-Hill Book Company, 1985, p. 56.
-\end{thebibliography}
+\section{Simulation}
 
+A simulation software is a computer program or tool that enables the creation and execution of 
+simulations to model and analyze real-world systems or processes. 
+It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
+providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
+
+Simulation software provides a virtual environment where users can define the parameters,
+variables, and rules of the system being simulated. The software then uses mathematical models, 
+algorithms, and computational techniques to simulate the behavior of the system over time.
+
+\subsection{}
+
+% END OF THEORY
+%#####
 \end{document}

### 2023-07-02 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
runge kutta updated

@@
 \usepackage{tabu}
+\usepackage{subcaption}
 \usepackage[a4paper, total={6in, 8in}]{geometry}
@@
 \newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+
+\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
 
@@
 
-The Runge-Kutta method is another numerical method used to solve ordinary differential equations (ODEs) numerically (see $\fromeq{second-order-ODE}$).
-It's named after the German mathematicians Carl Runge and Martin Wilhelm Kutta.
+The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
+used to solve ordinary differential equations (ODEs) that are in the following form
 
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average of function evaluations at different points within each step. 
-This weighted average improves the accuracy of the approximation compared to simpler methods like Leapfrog (see $\textit{section \ref{sec:leapfrog}}$).
-% TODO: ADD GENERAL FORM OF RK HERE
-\newline
+\begin{equation} \label{eq:first-order-ODE}
+    \parDeriv{y}{x} = f(x, y)
+\end{equation}
+
+The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
+of function evaluations at different points within each step.
+
+\begin{equation} \label{eq:general-rk}
+    \begin{aligned}
+        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
+    \end{aligned}
+    \qquad
+    \begin{aligned}
+        x_{n+1} = x_n + \delta x 
+    \end{aligned}
+\end{equation}
+
+where
+
+\begin{eqnarray} \label{eq:general-rk-coef}
+    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
+\end{eqnarray}
+
+These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
+The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
+
+\begin{figure}[h!]
+    \[ 
+    \begin{array} 
+        {c|cccc}
+        0\\
+        c_1 & a_{21} \\
+        c_2 & a_{31} & a_{32}\\
+        \vdots& & \cdots& \\
+        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
+        \hline
+        & b_1 & b_2 &\cdots & b_m
+    \end{array}
+    \]
+    \caption{Butcher Tableau}
+    \label{fig:Butcher}
+\end{figure}
+
+The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
+
+\[ 
+    \begin{array} 
+        {c|cccc}
+        0\\
+        \hline
+        & 1
+    \end{array}
+\]
+
 The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
 The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
+Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
 
-% TODO: ADD RK4 HERE
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+        \[ 
+        \begin{array} 
+            {c|cccc}
+            0\\
+            1/2 & 1/2 \\
+            1/2 & 0 & 1/2 \\
+            1   & 0 & 0 & 1\\
+            \hline
+            & 1/6 & 1/3 & 1/3 & 1/6
+        \end{array}
+        \]  
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+        \[ 
+        \begin{array} 
+            {c|cccc}
+            0\\
+            1/3 & 1/3 \\
+            2/3 & -1/3 & 1 \\
+            1   & 1 & -1 & 1\\
+            \hline
+            & 1/8 & 3/8 & 3/8 & 1/8
+        \end{array}
+        \]  
+    \end{subfigure}
+    \caption{Butcher Tableau for RK4}
+    \label{fig:Butcher-RK4}
+\end{figure}
+
+The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
+Its main advantage is that its error coefficients are smaller than the other.
+But it costs more floating point operations per step.
+Resulting in slower calculations.
 

### 2023-07-02 theory.tex
runge kutta updated

@@
 \usepackage{notoccite}
+\usepackage{subcaption}
+\usepackage{tabu}
 
@@
 \newcommand{\crossProd}[2]{\vecthree{#1} \times \vecthree{#2}}
+
+\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
 
@@
 
+\newpage
 \section{Practical}
@@
 
+\newpage
 \section{Numerical Integration Methods}
@@
 
-The Runge-Kutta method is another numerical method used to solve ordinary differential equations (ODEs) numerically (see $\fromeq{second-order-ODE}$).
-It's named after the German mathematicians Carl Runge and Martin Wilhelm Kutta.
+The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
+used to solve ordinary differential equations (ODEs) that are in the following form
 
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average of function evaluations at different points within each step. 
-This weighted average improves the accuracy of the approximation compared to simpler methods like Leapfrog (see $\textit{section \ref{sec:leapfrog}}$).
-% TODO: ADD GENERAL FORM OF RK HERE
-\newline
+\begin{equation} \label{eq:first-order-ODE}
+    \parDeriv{y}{x} = f(x, y)
+\end{equation}
+
+The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
+of function evaluations at different points within each step.
+
+\begin{equation} \label{eq:general-rk}
+    \begin{aligned}
+        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
+    \end{aligned}
+    \qquad
+    \begin{aligned}
+        x_{n+1} = x_n + \delta x 
+    \end{aligned}
+\end{equation}
+
+where
+
+\begin{eqnarray} \label{eq:general-rk-coef}
+    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
+\end{eqnarray}
+
+These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
+The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
+
+\begin{figure}[h!]
+    \[ 
+    \begin{array} 
+        {c|cccc}
+        0\\
+        c_1 & a_{21} \\
+        c_2 & a_{31} & a_{32}\\
+        \vdots& & \cdots& \\
+        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
+        \hline
+        & b_1 & b_2 &\cdots & b_m
+    \end{array}
+    \]
+    \caption{Butcher Tableau}
+    \label{fig:Butcher}
+\end{figure}
+
+The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
+
+\[ 
+    \begin{array} 
+        {c|cccc}
+        0\\
+        \hline
+        & 1
+    \end{array}
+\]
+
 The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
 The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
+Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
 
-% TODO: ADD RK4 HERE
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}{}
+        \[ 
+        \begin{array} 
+            {c|cccc}
+            0\\
+            1/2 & 1/2 \\
+            1/2 & 0 & 1/2 \\
+            1   & 0 & 0 & 1\\
+            \hline
+            & 1/6 & 1/3 & 1/3 & 1/6
+        \end{array}
+        \]  
+    \end{subfigure} %
+    \centering
+    \begin{subfigure}{}
+        \[ 
+        \begin{array} 
+            {c|cccc}
+            0\\
+            1/3 & 1/3 \\
+            2/3 & -1/3 & 1 \\
+            1   & 1 & -1 & 1\\
+            \hline
+            & 1/8 & 3/8 & 3/8 & 1/8
+        \end{array}
+        \]  
+    \end{subfigure}
+    \caption{Butcher Tableau for RK4}
+    \label{fig:Butcher-RK4}
+\end{figure}
 
+The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
+Its main advantage is that its error coefficients are smaller than the other.
+But it costs more floating point operations per step.
+Resulting in slower calculations.
+
+\newpage
 \section{Simulation}

### 2023-07-03 subsections/theory/common/common_start_theory.tex
theory mostly done

--- 2023-06-15 mythesis.tex
@@
 \usepackage{multirow}
-\usepackage{subfigure}
 \usepackage{algorithm}
@@
 \usepackage{epstopdf}
-\usepackage{subfigure} % 
 \usepackage{amsmath}
 \usepackage{notoccite}
+\usepackage{subcaption}
+\usepackage{tabu}
 
@@
 
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
 
-\newpage
 \chapter{THEORY}
-
-\section{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines momentum and states 
-\begin{equation}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force.
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\section{Lorentz Force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\section{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\section{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta method is another numerical method used to solve ordinary differential equations (ODEs) numerically (see $\fromeq{second-order-ODE}$).
-It's named after the German mathematicians Carl Runge and Martin Wilhelm Kutta.
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average of function evaluations at different points within each step. 
-This weighted average improves the accuracy of the approximation compared to simpler methods like Leapfrog (see $\textit{section \ref{sec:leapfrog}}$).
-% TODO: ADD GENERAL FORM OF RK HERE
-\newline
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4.
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-
-% TODO: ADD RK4 HERE
-
-\begin{thebibliography}{9}
-\bibitem{leapfrog_osc}
-C. K. Birdsall and A. B. Langdon, \emph{Plasma Physics via Computer Simulations}, McGraw-Hill Book Company, 1985, p. 56.
-\end{thebibliography}
-
-\end{document}

### 2023-07-03 subsections/theory/common/theory_bib.tex
theory mostly done

\begin{thebibliography}{9}

    \bibitem{rhodo_pottier}
    Jacques Pottier,
    \emph{A new type of rf electron accelerator: The rhodotron},
    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
    Volumes 40–41, Part 2,
    1989,
    Pages 943-945,

    \bibitem{rhodo_prototype}
    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
    \emph{Rhodotron: an accelerator for industrial irradiation},
    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
    Volume 68, Issues 1–4,
    1992,
    Pages 92-95,A:

    \bibitem{rhodos}
    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.

    \bibitem{cpu_instruction_speed}
    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.

\end{thebibliography}

### 2023-07-03 subsections/theory/rhodotron/rhodotron.tex
theory mostly done

@@
 
-\section{Practical}
+\section{Particle Accelerators}
 
-\subsection{Accelerators}
 Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
@@
 
-In summary, particle accelerators are complex scientific instruments that use electromagnetic fields to accelerate charged particles to high speeds and energies. 
-They enable scientists to investigate the fundamental nature of matter, unravel the mysteries of the universe, and apply their findings to various fields of research and practical applications.
-
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
 
-\subsubsection{Key Concepts}
+\subsection{Key Concepts}
 
 \begin{itemize}
+    \item Phase Stability
     \item Phase Lag
-
-    This is the asdasd
-
-    \item XD
     \item AW
@@
 
-\subsubsection{Acceleration Cavities}
+\subsection{Acceleration Cavities}
 Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
@@
 
-RF cavities are typically hollow metallic structures made of high-conductivity materials such as copper or niobium. 
+RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
 They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
@@
 The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
+
 To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
@@
 
-\subsubsection{Steerer Magnets}
+\subsection{Steerer Magnets}
 Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
 They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:LorentzForce}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
+
+According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
 vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
@@
 
+Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
+First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
+
+The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
+
 %%%%%%
 
+\begin{thebibliography}{9}
+    \bibitem{rhodo_pottier}
+    Jacques Pottier,
+    \emph{A new type of rf electron accelerator: The rhodotron},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volumes 40–41, Part 2,
+    1989,
+    Pages 943-945,
+
+    \bibitem{rhodo_prototype}
+    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
+    \emph{Rhodotron: an accelerator for industrial irradiation},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volume 68, Issues 1–4,
+    1992,
+    Pages 92-95,A:
+
+    \bibitem{rhodos}
+    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
+\end{thebibliography}
+
 \end{document}

### 2023-07-03 subsections/theory/simulation/simulation.tex
theory mostly done

@@
 
+%----../../..++++.
+
 %%%%%%
@@
 Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical models, 
+variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
 algorithms, and computational techniques to simulate the behavior of the system over time.
 
-\subsection{}
+\subsection{Basic Consepts in Programming}
+
+\subsubsection{Clock Cycle}
+
+In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
+It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
+
+A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
+It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
+Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
+
+The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
+Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
+Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.9\textwidth]{../../../figures/cpu_instruction_speed.png}
+    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
+\end{figure}
+
+Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
+
+\subsubsection{Concurrency}
+
+Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
+It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
+
+Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
+This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
+True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
+
+Programs that implement concurrency using multiple cores executes more operations per clock cycle.
+However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
 
@@
 
+\begin{thebibliography}{9}
+    \bibitem{cpu_instruction_speed}
+    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775. 
+\end{thebibliography}
+
 \end{document}

### 2023-07-03 theory.tex
theory mostly done

@@
 \usepackage{epstopdf}
-\usepackage{subfigure} % 
 \usepackage{amsmath}
@@
 \subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines momentum and states 
-\begin{equation}
+In classical mechanics, Newton's second law defines force and states 
+\begin{equation} \label{eq:newton_second_law}
     \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
 \end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
+In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
 \begin{equation*}
@@
 \end{equation}
-It is clear that acceleration is not necessarily parallel to the force.
+It is clear that acceleration is not necessarily parallel to the force anymore.
 To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
@@
 \end{eqnarray*}
+We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
 \begin{equation} \label{eq:Frel_para_and_perp}
@@
 
-\subsection{Lorentz Force}
+\subsection{Lorentz Force} \label{sec:lorentz-force}
 Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
@@
 \end{equation}
-Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
+Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
 \newline
@@
     \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
+        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
     \end{aligned}
@@
 \newpage
-\section{Practical}
+\section{Particle Accelerators}
 
-\subsection{Accelerators}
 Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
@@
 \subsection{Rhodotron Accelerator}
+
+Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
+First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
+
+The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
 
@@
 \end{equation}
-
 where 
-
 \begin{eqnarray} \label{eq:general-rk-coef}
@@
 The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-
 \[ 
@@
     \centering
-    \begin{subfigure}{}
+    \begin{subfigure}{.5\textwidth}
         \[ 
@@
             1   & 0 & 0 & 1\\
-            \hline
+            \hlinevvmwa
             & 1/6 & 1/3 & 1/3 & 1/6
@@
         \]  
-    \end{subfigure} %
-    \centering
-    \begin{subfigure}{}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
         \[ 
@@
 Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical models, 
+variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
 algorithms, and computational techniques to simulate the behavior of the system over time.
 
-\subsection{}
+\subsection{Basic Consepts in Programming}
+
+\subsubsection{Clock Cycle}
+
+In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
+It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
+
+A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
+It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
+Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
+
+The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
+Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
+Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
+    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
+\end{figure}
+
+Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
+
+\subsubsection{Concurrency}
+
+Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
+It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
+
+Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
+This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
+True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
+
+Programs that implement concurrency using multiple cores executes more operations per clock cycle.
+However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
+
+\begin{thebibliography}{9}
+
+    \bibitem{rhodo_pottier}
+    Jacques Pottier,
+    \emph{A new type of rf electron accelerator: The rhodotron},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volumes 40–41, Part 2,
+    1989,
+    Pages 943-945,
+
+    \bibitem{rhodo_prototype}
+    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
+    \emph{Rhodotron: an accelerator for industrial irradiation},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volume 68, Issues 1–4,
+    1992,
+    Pages 92-95,A:
+
+    \bibitem{rhodos}
+    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
+
+    \bibitem{cpu_instruction_speed}
+    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
+
+\end{thebibliography}
 

### 2023-07-04 subsections/theory/rhodotron/rhodotron.tex
rhodo theory part almost complete

@@
 
+\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+
+%----../../..++++.
+
 %%%%%%
@@
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{A circular accelerator}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{A linear accelerator}
+\end{figure}
 
@@
     \item Phase Lag
-    \item AW
+    \item Shunt Impedance
 
@@
 Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-
 % TODO : ADD RF CAVITY PICTURE HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{A rf cavity used in KAHVELab}
+\end{figure}
 
@@
 % TODO : ADD STEERER MAGNET PICTURE HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{A steerer magnet used in KAHVELab}
+\end{figure}
 
@@
 The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
+RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
+
+\subsubsection{Cavity of a Rhodotron}
+
+Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
+Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
+% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{SUPERFISH simulation of a coaxial cavity}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{CST simulation of a coaxial cavity}
+\end{figure}
+
+With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
+This constraint helps with  phase stability and synchronization of the beam.
+
+In the table below, optimized characteristics of a rhodotron cavity can be observed. 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table1.png}
+    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
+    \label{fig:pottier_table1}
+\end{figure}
+
+Here, $p$ is the integer multiplier in the equation ($l=p\lambda \label{eq:lpl}$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
+$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
+
+Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
+\begin{equation}
+    \label{eq:W_gain_each_pass_pottier}
+    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
+\end{equation}
+
+Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
+
+Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table2.png}
+    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
+    \label{fig:pottier_table2}
+\end{figure}
+
+Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
+\begin{equation}
+    \label{eq:W_total_gain_pottier}
+    W \approx 2.3 \lambda^{1/4} P^{1/2} n
+\end{equation}
+
+\subsubsection{Acceleration cycle of Rhodotron}
+
+Electrons undergo four different stages during a single pass. 
+They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
+
+\begin{description}
+    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
+    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+\end{description}
+
+This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
+After desired amount of pass has been completed, the electrons exit the accelerator.
+
+This process is explained further in the following figures where $T$ is the period of the electric field.
+% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
+\end{figure}
 

### 2023-07-04 theory.tex
rhodo theory part almost complete

@@
 It is clear that acceleration is not necessarily parallel to the force anymore.
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
+
+To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
 \begin{equation} \label{eq:a_F_parallels}
@@
 \newpage
+
 \section{Particle Accelerators}
@@
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{A circular accelerator}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{A linear accelerator}
+\end{figure}
 
@@
 Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-
 % TODO : ADD RF CAVITY PICTURE HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{A rf cavity used in KAHVELab}
+\end{figure}
 
@@
 % TODO : ADD STEERER MAGNET PICTURE HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{A steerer magnet used in KAHVELab}
+\end{figure}
 
@@
 The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
+RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
+
+\subsubsection{Cavity of a Rhodotron}
+
+Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
+Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
+% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{SUPERFISH simulation of a coaxial cavity}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{CST simulation of a coaxial cavity}
+\end{figure}
+
+With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
+This constraint helps with  phase stability and synchronization of the beam.
+
+In the table below, optimized characteristics of a rhodotron cavity can be observed. 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
+    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
+    \label{fig:pottier_table1}
+\end{figure}
+
+Here, $p$ is the integer multiplier in the equation ($l=p\lambda \label{eq:lpl}$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
+$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
+
+Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
+\begin{equation}
+    \label{eq:W_gain_each_pass_pottier}
+    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
+\end{equation}
+
+Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
+
+Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
+    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
+    \label{fig:pottier_table2}
+\end{figure}
+
+Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
+\begin{equation}
+    \label{eq:W_total_gain_pottier}
+    W \approx 2.3 \lambda^{1/4} P^{1/2} n
+\end{equation}
+
+\subsubsection{Acceleration cycle of Rhodotron}
+
+Electrons undergo four different stages during a single pass. 
+They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
+
+\begin{description}
+    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
+    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+\end{description}
+
+This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
+After desired amount of pass has been completed, the electrons exit the accelerator.
+
+This process is explained further in the following figures where $T$ is the period of the electric field.
+% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
+\end{figure}
 
 \newpage
+
 \section{Numerical Integration Methods}
@@
             1   & 0 & 0 & 1\\
-            \hlinevvmwa
+            \hline
             & 1/6 & 1/3 & 1/3 & 1/6
@@
 \newpage
+
 \section{Simulation}
@@
 
+\newpage
+
 \begin{thebibliography}{9}

### 2023-07-09 subsections/common/common_end.tex
cavity design added

--- 2023-07-02 theory.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
-\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
-\usepackage{amsmath, amsthm} % Some extra symbols
-\usepackage[bottom]{footmisc}
-\usepackage{cite}
-\usepackage{graphicx}
-\usepackage{longtable}
-\usepackage{float}
-\usepackage{multirow}
-\usepackage{subfigure}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{array}
-\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
-\usepackage{epsfig}
-\usepackage{epstopdf}
-\usepackage{subfigure} % 
-\usepackage{amsmath}
-\usepackage{notoccite}
-\usepackage{subcaption}
-\usepackage{tabu}
+\begin{thebibliography}{9}
 
-\interdisplaylinepenalty=2500
-\hyphenation{lists} \makeatletter
+    \bibitem{rhodo_pottier}
+    Jacques Pottier,
+    \emph{A new type of rf electron accelerator: The rhodotron},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volumes 40–41, Part 2,
+    1989,
+    Pages 943-945,
 
-\newcommand{\field}[1]{\mathbb{#1} }
-\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
-\setlength\belowdisplayskip{5pt}}
-\newcommand{\eeq}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\defn}{\stackrel{\triangle}{=}}
-\newcommand{\nn}{\nonumber}
-\newcommand{\nnl}{\nonumber \\}
-\renewcommand{\theequation}{\arabic{equation}}
-\renewcommand{\labelenumi}{(\roman{enumi})}
+    \bibitem{rhodo_prototype}
+    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
+    \emph{Rhodotron: an accelerator for industrial irradiation},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volume 68, Issues 1–4,
+    1992,
+    Pages 92-95,A:
 
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
+    \bibitem{rhodos}
+    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
 
-\def\ifundefined{\@ifundefined}
-\def\bfat{\left[ \begin{array}}
-\def\emat{\end{array} \right]}
-\def\bfatt{\left\{ \begin{array}}
-\def\ematt{\end{array} \right.}
-\def\bset{\left\{ \begin{array}}
-\def\eset{\end{array} \right\}}
-\def\bpar{\left( \begin{array}}
-\def\epar{\end{array} \right)}
+    \bibitem{cpu_instruction_speed}
+    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
 
-\graphicspath{{figures/}} % Graphics will be here
+\end{thebibliography}
 
-\newtheorem{thm}{Theorem}[chapter]
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
-
-\numberwithin{equation}{chapter}
-
-% BEGIN OF DOCS
-\begin{document}
-\pagenumbering{roman}
-
-% CONTENTS AND LIST OF FIG AND TABLE PAGES
-\tableofcontents
-
-\pagenumbering{arabic}
-
-%#####
-% START OF THEORY
-
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-
-\newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
-\newcommand{\vecthree}[1]{\vec{#1}}
-
-\newcommand{\parDeriv}[2]{\frac{\partial #1}{\partial #2}}
-\newcommand{\parDerivS}[2]{\frac{\partial^2 #1}{\partial #2^2}}
-\newcommand{\derivS}[2]{\frac{d^2 #1}{d#2^2}}
-
-\newcommand{\dotProdBF}[2]{\vecthreeBF{#1} \cdot \vecthreeBF{#2}}
-\newcommand{\dotProd}[2]{\vecthree{#1} \cdot \vecthree{#2}}
-
-\newcommand{\crossProdBF}[2]{\vecthreeBF{#1} \times \vecthreeBF{#2}}
-\newcommand{\crossProd}[2]{\vecthree{#1} \times \vecthree{#2}}
-
-\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
-
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines momentum and states 
-\begin{equation}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force.
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-\section{Practical}
-
-\subsection{Accelerators}
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-In summary, particle accelerators are complex scientific instruments that use electromagnetic fields to accelerate charged particles to high speeds and energies. 
-They enable scientists to investigate the fundamental nature of matter, unravel the mysteries of the universe, and apply their findings to various fields of research and practical applications.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-
-\subsubsection{Key Concepts}
-
-\begin{itemize}
-    \item Phase Lag
-
-    This is the asdasd
-
-    \item XD
-    \item AW
-
-\end{itemize}
-
-\subsubsection{Acceleration Cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of high-conductivity materials such as copper or niobium. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-
-% TODO : ADD RF CAVITY PICTURE HERE
-
-\subsubsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator. 
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:LorentzForce}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-
-\subsection{Rhodotron Accelerator}
-
-\newpage
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-
-where
-
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure} %
-    \centering
-    \begin{subfigure}{}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{}
-
-% END OF THEORY
-%#####
 \end{document}

### 2023-07-09 subsections/design/cavity/cavity.tex
cavity design added

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{float}
\usepackage{wrapfig,lipsum}
\usepackage{svg}
\usepackage{mathtools}
\usepackage{tabu}
\usepackage{subcaption}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\begin{document}

\newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
\newcommand{\vecthree}[1]{\vec{#1}}

\newcommand{\parDeriv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\parDerivS}[2]{\frac{\partial^2 #1}{\partial #2^2}}
\newcommand{\derivS}[2]{\frac{d^2 #1}{d#2^2}}

\newcommand{\dotProdBF}[2]{\vecthreeBF{#1} \cdot \vecthreeBF{#2}}
\newcommand{\dotProd}[2]{\vecthree{#1} \cdot \vecthree{#2}}

\newcommand{\crossProdBF}[2]{\vecthreeBF{#1} \times \vecthreeBF{#2}}
\newcommand{\crossProd}[2]{\vecthree{#1} \times \vecthree{#2}}

\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}

\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}

%----../../..++++.

%%%%%%

\section{Cavity Design}

The first and the most important design parameter for a cavity is the operating RF frequency.
After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.

By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.

In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;

\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
    \begin{aligned}
        f_{107.5} = 107.5 \textrm{ MHz} \\
        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
        R_1 = \frac{R_2}{4} = 0.188 m \\
        h = \frac{\lambda}{2} = 1.394 m 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        f_{180} = 180 \textrm{ MHz} \\
        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
        R_1 = \frac{R_2}{4} = 0.113 m \\
        h = \frac{\lambda}{2} = 0.833 m 
    \end{aligned}
\end{eqnarray}

In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish107.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:107_simple_cavity_design}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/cst/cst107.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst180.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:180_simple_cavity_design}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst107_e.png}
      \caption{107.5 MHz}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.94\linewidth]{../../../figures/cst/cst180_e.png}
      \caption{180 MHz}
    \end{subfigure}
    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
    \label{fig:cst_simple_cavity_designs}
\end{figure}

As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/superfish/superfish107mod.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/superfish/superfish180mod.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{Poisson SUPERFISH field results of truncated cavities}
    \label{fig:107_180_modified_cavities_superfish}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst107mod.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst180mod.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{CST eigenmode results of truncated cavities}
    \label{fig:107_180_modified_cavities_cst_eigenmode}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst107mod_e.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.88\linewidth]{../../../figures/cst/cst180mod_e.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{CST electric field results of truncated cavities}
    \label{fig:107_180_modified_cavities_cst_field}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=0.97\linewidth]{../../../figures/superfish/superfish107_z.png}
      \caption{107.5 MHz unmodified}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=0.99\linewidth]{../../../figures/superfish/superfish180_z}
      \caption{180 MHz unmodified}
    \end{subfigure}
    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
    \label{fig:107_cavity_shunt_diff}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=0.95\linewidth]{../../../figures/superfish/superfish107mod_z.png}
      \caption{107.5 MHz truncated}
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180mod_z.png}
      \caption{180 MHz truncated}
    \end{subfigure}
    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
    \label{fig:180_cavity_shunt_diff}
\end{figure}

One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};

\begin{equation*}
    \begin{aligned}
        \Delta Z_{107.5}=2.5\%
    \end{aligned}
    \qquad
    \begin{aligned}
        \Delta Z_{180}=2.7\%
    \end{aligned}
\end{equation*}

%%%%%%

\end{document}

### 2023-07-09 msthesis.tex
thesis scripts added

--- 2023-07-04 theory.tex
@@
 
-%#####
-% START OF THEORY
-
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-
 \newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
@@
 
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+
 \newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
+% START OF THEORY
 
@@
 
-\subsection{Acceleration Cavities}
+\subsection{Acceleration Cavities} \label{sec:theory_cavities}
 Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
@@
 
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda \label{eq:lpl}$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
+Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
 $Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
@@
 
+% START OF DESIGN
+
+\chapter{DESIGN}
+
+\section{Cavity Design}
+
+The first and the most important design parameter for a cavity is the operating RF frequency.
+After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
+
+By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
+This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
+For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
+Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
+
+In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
+Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
+\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
+    \begin{aligned}
+        f_{107.5} = 107.5 \textrm{ MHz} \\
+        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
+        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
+        R_1 = \frac{R_2}{4} = 0.188 m \\
+        h = \frac{\lambda}{2} = 1.394 m 
+    \end{aligned}
+    \qquad\qquad
+    \begin{aligned}
+        f_{180} = 180 \textrm{ MHz} \\
+        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
+        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
+        R_1 = \frac{R_2}{4} = 0.113 m \\
+        h = \frac{\lambda}{2} = 0.833 m 
+    \end{aligned}
+\end{eqnarray}
+
+In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
+      \caption{107.5 MHz}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
+      \caption{180 MHz}
+    \end{subfigure}
+    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
+    \label{fig:107_simple_cavity_design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
+      \caption{107.5 MHz}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
+      \caption{180 MHz}
+    \end{subfigure}
+    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
+    \label{fig:180_simple_cavity_design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
+      \caption{107.5 MHz}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
+      \caption{180 MHz}
+    \end{subfigure}
+    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
+    \label{fig:cst_simple_cavity_designs}
+\end{figure}
+
+As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
+Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
+      \caption{107.5 MHz truncated}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
+      \caption{180 MHz truncated}
+    \end{subfigure}
+    \caption{Poisson SUPERFISH field results of truncated cavities}
+    \label{fig:107_180_modified_cavities_superfish}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
+      \caption{107.5 MHz truncated}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
+      \caption{180 MHz truncated}
+    \end{subfigure}
+    \caption{CST eigenmode results of truncated cavities}
+    \label{fig:107_180_modified_cavities_cst_eigenmode}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
+      \caption{107.5 MHz truncated}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
+      \caption{180 MHz truncated}
+    \end{subfigure}
+    \caption{CST electric field results of truncated cavities}
+    \label{fig:107_180_modified_cavities_cst_field}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
+      \caption{107.5 MHz unmodified}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
+      \caption{180 MHz unmodified}
+    \end{subfigure}
+    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
+    \label{fig:107_cavity_shunt_diff}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
+      \caption{107.5 MHz truncated}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
+      \caption{180 MHz truncated}
+    \end{subfigure}
+    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
+    \label{fig:180_cavity_shunt_diff}
+\end{figure}
+
+One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
+\begin{equation*}
+    \begin{aligned}
+        \Delta Z_{107.5}=2.5\%
+    \end{aligned}
+    \qquad
+    \begin{aligned}
+        \Delta Z_{180}=2.7\%
+    \end{aligned}
+\end{equation*}
+
+\newpage
+
 \begin{thebibliography}{9}
@@
 
-% END OF THEORY
-%#####
 \end{document}

### 2023-07-11 msthesis.tex
design finished, simulation started

@@
 \usepackage{tabu}
+\usepackage{minted}
+
+\usemintedstyle{xcode}
+\definecolor{bg}{rgb}{0.95,0.95,0.95}
 
@@
 \newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
 
@@
 \newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+
 \newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-% START OF THEORY
+\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+
+\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}% START OF THEORY
 
@@
 
-\subsubsection{Cavity of a Rhodotron}
+\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
 
@@
 
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
+Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
 \begin{equation}
     \label{eq:W_total_gain_pottier}
-    W \approx 2.3 \lambda^{1/4} P^{1/2} n
+    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
 \end{equation}
@@
 
-\section{Cavity Design}
+\section{Cavity Design} \label{sec:cavity_design}
 
@@
 
+\section{Magnet Design} \label{sec:magnet_design}
+Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
+Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
+Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
+      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
+      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
+    \end{subfigure}
+    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
+    \label{fig:magnet_design_illustrations}
+\end{figure}
+
+In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
+This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
+Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
+
+Two different approaches have been used to achieve phase stability.
+These approaches are discussed further in the following sections.
+
+\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
+
+First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
+
+To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
+As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
+In other words, total trajectory of synchronous particle needs to satisfy the following equality;
+\begin{equation*}
+    L_{pass} = n \lambda
+\end{equation*} 
+Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
+\begin{equation}
+    L_{pass} = \lambda
+\end{equation}
+
+\begin{figure}[H]    
+    \centering
+    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
+    \caption{Trejectory of a particle in single pass}
+    \label{fig:magnet_design}
+\end{figure}
+
+From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
+\begin{eqnarray}
+    L_{in} &=& 2R_2 \nonumber\\
+    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
+    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
+    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
+\end{eqnarray}
+
+After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
+Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
+
+\begin{eqnarray}
+    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
+    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
+    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
+    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
+    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
+    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
+\end{eqnarray}
+
+\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
+As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
+Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
+Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
+
+\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
+
+As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
+This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
+This scenario can happen when RF power is not sufficiently high.
+
+Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
+after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
+\begin{eqnarray*}
+    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
+    W_{total} &=& 394 keV \\
+    \beta_{40keV} &\approx& 0.374 \\
+    \beta_{394keV} &\approx& 0.825
+\end{eqnarray*}
+It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
+For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
+Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
+\begin{eqnarray*}
+    L_{pass} &=& K \\
+    L_{in} + L_{out} &=& K
+\end{eqnarray*}
+
+Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
+\begin{equation} \label{eq:mag_sweep_constraint}
+    L_{out} = K
+\end{equation}
+
+To start, an optimization criteria for the following pass such as
+\begin{itemize}
+    \item Ensure the phase stability of the synchronous electron
+    \item Maximize the energy gain of the synchronous electron
+    \item Minimize the energy spread of the beam
+    \item Minimize the phase lag spread of the beam
+    \item All of the above with decided weights
+\end{itemize}
+needs be selected.
+Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
+This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
+
+However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
+As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
+But the calculation times are too slow to be useful in this particular problem.
+\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
+
+\newpage
+
+\section{Initial Design at KAHVELab}
+
+A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
+After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
+    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
+    \label{fig:initial_design}
+\end{figure}
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
+      \caption{Axial cross section.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
+      \caption{Cross section at acceleration plane.}
+    \end{subfigure}
+    \caption{Initial design of the proposed rhodotron.}
+    \label{fig:initial_design_cross_section}
+\end{figure}
+The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
+    \end{subfigure}
+    \caption{Initial magnet design.}
+    \label{fig:initial_magnet_design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
+    \caption{Magnetic field in acceleration plate of initial magnet design.}
+    \label{fig:initial_magnet_design_B}
+\end{figure}
+
+\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
+
+After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
+    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
+    \label{fig:initial_three_magnet_design}
+\end{figure}
+
+These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $0.1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
+Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
+      \caption{One pass simulation of \fromfig{initial_design}}
+    \end{subfigure}
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
+      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
+    \end{subfigure}
+    \caption{$|r|$ vs $Energy$ simulation of initial design.}
+    \label{fig:initial_designs_PIC_phase_space_monitor}
+\end{figure}
+
+The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
+When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
+Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
+This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
+
+After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
+as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
+\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
+
+In KAHVELab, several improvements were made to these initial designs by \textit{Mr.
+Sinan ÖZ}.
+They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
+Improved designs can be seen in the figures below.
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
+    \end{subfigure}
+    \caption{Improved cavity design.}
+    \label{fig:improved_cavity_design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
+    \caption{Improved magnet design.}
+    \label{fig:improved_magnet_design}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
+    \end{subfigure}
+    \caption{Cross section and coils of improved magnet design.}
+    \label{fig:improved_magnet_design_cross_section}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
+    \caption{Magnetic field in acceleration plate of improved magnet design.}
+    \label{fig:improved_magnet_design_B}
+\end{figure}
+
+From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
+This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
+
+\newpage
+
+% START OF SIMULATION
+
+\chapter{SIMULATION}
+\newpage
+
+\newpage
+
+\appendix
+\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{\textwidth}
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            for(double i = 2; i < 9; i += dT_out){
+                t_dum += i;
+                double enow = gecis(r_pos, vel, Et, t_dum);
+                if( enow > maxE ){
+                  maxE = enow;
+                  t_opt = i;
+                }
+                t_dum = t;
+            }
+        \end{minted}
+    \end{subfigure} 
+    \\
+    \begin{subfigure}{\textwidth}
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            double gecis(double r_pos, double vel, double Et, double &t){
+                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
+                    vel = c*sqrt(Et*Et-E0*E0)/Et;
+                    double RelBeta  = vel/c;
+                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+
+                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
+
+                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
+
+                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
+                    vel=vel+acc*dT*ns;
+                    RelBeta  = vel/c;
+                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+                    Et=RelGamma*E0; 
+                }
+                return Et;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{$L_{out}$ Optimization For Single $e^-$}
+    \label{fig:lout_opt_single_e}
+\end{figure}
+
 \begin{thebibliography}{9}
@@
 
+    \bibitem{cite:rhodo_design}
+    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
+    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
+    9th International Particle Accelerator Conference,
+    2018
+
 \end{thebibliography}

### 2023-07-11 subsections/common/common_end.tex
design finished, simulation started

@@
+\appendix
+\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{\textwidth}
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            for(double i = 2; i < 9; i += dT_out){
+                t_dum += i;
+                double enow = gecis(r_pos, vel, Et, t_dum);
+                if( enow > maxE ){
+                  maxE = enow;
+                  t_opt = i;
+                }
+                t_dum = t;
+            }
+        \end{minted}
+    \end{subfigure} 
+    \\
+    \begin{subfigure}{\textwidth}
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            double gecis(double r_pos, double vel, double Et, double &t){
+                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
+                    vel = c*sqrt(Et*Et-E0*E0)/Et;
+                    double RelBeta  = vel/c;
+                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+
+                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
+
+                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
+
+                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
+                    vel=vel+acc*dT*ns;
+                    RelBeta  = vel/c;
+                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+                    Et=RelGamma*E0; 
+                }
+                return Et;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{$L_{out}$ Optimization For Single $e^-$}
+    \label{fig:lout_opt_single_e}
+\end{figure}
+
 \begin{thebibliography}{9}

### 2023-07-11 subsections/design.tex
design finished, simulation started

--- 2023-07-09 msthesis.tex
@@
 \newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-% START OF THEORY
 
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.3 \lambda^{1/4} P^{1/2} n
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
+%#####
 % START OF DESIGN
@@
 
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-\end{thebibliography}
-
+% END OF DESIGN
+%#####
 \end{document}

### 2023-07-11 subsections/design/first_design/first_design.tex
design finished, simulation started

--- 2023-07-04 theory.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
-\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
-\usepackage{amsmath, amsthm} % Some extra symbols
-\usepackage[bottom]{footmisc}
-\usepackage{cite}
+\documentclass{article}
+
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
-\usepackage{longtable}
+\usepackage{tikz}
 \usepackage{float}
-\usepackage{multirow}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{array}
-\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
-\usepackage{epsfig}
-\usepackage{epstopdf}
-\usepackage{amsmath}
-\usepackage{notoccite}
+\usepackage{wrapfig,lipsum}
+\usepackage{svg}
+\usepackage{mathtools}
+\usepackage{tabu}
 \usepackage{subcaption}
-\usepackage{tabu}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 
-\interdisplaylinepenalty=2500
-\hyphenation{lists} \makeatletter
-
-\newcommand{\field}[1]{\mathbb{#1} }
-\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
-\setlength\belowdisplayskip{5pt}}
-\newcommand{\eeq}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\defn}{\stackrel{\triangle}{=}}
-\newcommand{\nn}{\nonumber}
-\newcommand{\nnl}{\nonumber \\}
-\renewcommand{\theequation}{\arabic{equation}}
-\renewcommand{\labelenumi}{(\roman{enumi})}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\ifundefined{\@ifundefined}
-\def\bfat{\left[ \begin{array}}
-\def\emat{\end{array} \right]}
-\def\bfatt{\left\{ \begin{array}}
-\def\ematt{\end{array} \right.}
-\def\bset{\left\{ \begin{array}}
-\def\eset{\end{array} \right\}}
-\def\bpar{\left( \begin{array}}
-\def\epar{\end{array} \right)}
-
-\graphicspath{{figures/}} % Graphics will be here
-
-\newtheorem{thm}{Theorem}[chapter]
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
-
-\numberwithin{equation}{chapter}
-
-% BEGIN OF DOCS
 \begin{document}
-\pagenumbering{roman}
-
-% CONTENTS AND LIST OF FIG AND TABLE PAGES
-\tableofcontents
-
-\pagenumbering{arabic}
-
-%#####
-% START OF THEORY
-
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
 
@@
 
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+
 \newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
 
-\chapter{THEORY}
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
+\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
 
-\section{Accelerating Charged Particles}
+%----../../..++++.
 
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
+%%%%%%
 
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
+\section{Initial Design at KAHVELab}
 
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
+A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
+After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
 
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
 \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
+    \captionsetup{justification=centering}
+    \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
+    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
+    \label{fig:initial_design}
+\end{figure}
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_design3.png}
+      \caption{Axial cross section.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_design2.png}
+      \caption{Cross section at acceleration plane.}
+    \end{subfigure}
+    \caption{Initial design of the proposed rhodotron.}
+    \label{fig:initial_design_cross_section}
+\end{figure}
+The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_first_magnet_design1.png}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.92\linewidth]{../../../figures/cst/cst_first_magnet_design2.png}
+    \end{subfigure}
+    \caption{Initial magnet design.}
+    \label{fig:initial_magnet_design}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
+    \captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
+    \caption{Magnetic field in acceleration plate of initial magnet design.}
+    \label{fig:initial_magnet_design_B}
 \end{figure}
 
-\subsection{Key Concepts}
+\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
 
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
-
-\subsection{Acceleration Cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
+After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
 
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
+    \captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_design2.png}
+    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
+    \label{fig:initial_three_magnet_design}
+\end{figure}
+
+These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $0.1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
+Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{../../../figures/cst/cst_first_design4.png}
+      \caption{One pass simulation of \fromfig{initial_design}}
+    \end{subfigure}
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{../../../figures/cst/cst_second_design3.png}
+      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
+    \end{subfigure}
+    \caption{$|r|$ vs $Energy$ simulation of initial design.}
+    \label{fig:initial_designs_PIC_phase_space_monitor}
+\end{figure}
+
+The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
+When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
+Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
+This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
+
+After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
+as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
+\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
+
+In KAHVELab, several improvements were made to these initial designs by \textit{Mr.
+Sinan ÖZ}.
+They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
+Improved designs can be seen in the figures below.
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_sinan_cavity_design1.png}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.94\linewidth]{../../../figures/cst/cst_sinan_cavity_design2.png}
+    \end{subfigure}
+    \caption{Improved cavity design.}
+    \label{fig:improved_cavity_design}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
+    \captionsetup{justification=centering}
+    \includegraphics[width=.7\linewidth]{../../../figures/cst/cst_second_magnet_design1.png}
+    \caption{Improved magnet design.}
+    \label{fig:improved_magnet_design}
 \end{figure}
 
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
 \begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
     \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda \label{eq:lpl}$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
+    \begin{subfigure}{.5\textwidth}
       \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.3 \lambda^{1/4} P^{1/2} n
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
+      \includegraphics[width=.96\linewidth]{../../../figures/cst/cst_second_magnet_design2.png}
+    \end{subfigure}%
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{../../../figures/cst/cst_second_magnet_design3.png}
+    \end{subfigure}
+    \caption{Cross section and coils of improved magnet design.}
+    \label{fig:improved_magnet_design_cross_section}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
+    \captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_magnet_design4.png}
+    \caption{Magnetic field in acceleration plate of improved magnet design.}
+    \label{fig:improved_magnet_design_B}
 \end{figure}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
+From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
+This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
+%%%%%%
 
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-\end{thebibliography}
-
-% END OF THEORY
-%#####
 \end{document}

### 2023-07-11 subsections/design/magnet/magnet.tex
design finished, simulation started

--- 2023-07-04 theory.tex
@@
 
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+
 \newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
 
-\chapter{THEORY}
+%----../../..++++.
 
-\section{Accelerating Charged Particles}
+%%%%%%
 
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
+\section{Magnet Design} \label{sec:magnet_design}
+Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
+Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
+Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
+      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
+      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
+    \end{subfigure}
+    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
+    \label{fig:magnet_design_illustrations}
+\end{figure}
+
+In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
+This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
+Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
+
+Two different approaches have been used to achieve phase stability.
+These approaches are discussed further in the following sections.
+
+\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
+
+First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
+
+To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
+As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
+In other words, total trajectory of synchronous particle needs to satisfy the following equality;
+\begin{equation*}
+    L_{pass} = n \lambda
+\end{equation*} 
+Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
+\begin{equation}
+    L_{pass} = \lambda
 \end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
 
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
+    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
+    \caption{Trejectory of a particle in single pass}
+    \label{fig:magnet_design}
 \end{figure}
 
-\subsection{Key Concepts}
+From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
+\begin{eqnarray}
+    L_{in} &=& 2R_2 \nonumber\\
+    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
+    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
+    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
+\end{eqnarray}
 
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
+After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
+Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
 
-\end{itemize}
+\begin{eqnarray}
+    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
+    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
+    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
+    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
+    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
+    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
+\end{eqnarray}
 
-\subsection{Acceleration Cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
+\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
+As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
+Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
+Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
 
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
+\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
 
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
+As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
+This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
+This scenario can happen when RF power is not sufficiently high.
 
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
+Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
+after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
+\begin{eqnarray*}
+    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
+    W_{total} &=& 394 keV \\
+    \beta_{40keV} &\approx& 0.374 \\
+    \beta_{394keV} &\approx& 0.825
+\end{eqnarray*}
+It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
+For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
+Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
+\begin{eqnarray*}
+    L_{pass} &=& K \\
+    L_{in} + L_{out} &=& K
+\end{eqnarray*}
 
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda \label{eq:lpl}$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
+Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
+\begin{equation} \label{eq:mag_sweep_constraint}
+    L_{out} = K
 \end{equation}
 
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
+To start, an optimization criteria for the following pass such as
+\begin{itemize}
+    \item Ensure the phase stability of the synchronous electron
+    \item Maximize the energy gain of the synchronous electron
+    \item Minimize the energy spread of the beam
+    \item Minimize the phase lag spread of the beam
+    \item All of the above with decided weights
+\end{itemize}
+needs be selected.
+Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
+This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
 
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
+However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
+As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
+But the calculation times are too slow to be useful in this particular problem.
+\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
 
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.3 \lambda^{1/4} P^{1/2} n
-\end{equation}
+%%%%%%
 
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-\end{thebibliography}
-
-% END OF THEORY
-%#####
 \end{document}

### 2023-07-11 subsections/simulation/intermediate_versions/intermediate.tex
design finished, simulation started

--- 2023-07-04 theory.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
-\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
-\usepackage{amsmath, amsthm} % Some extra symbols
-\usepackage[bottom]{footmisc}
-\usepackage{cite}
+\documentclass{book}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
-\usepackage{longtable}
+\usepackage{tikz}
 \usepackage{float}
-\usepackage{multirow}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{array}
-\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
-\usepackage{epsfig}
-\usepackage{epstopdf}
-\usepackage{amsmath}
-\usepackage{notoccite}
+\usepackage{wrapfig,lipsum}
+\usepackage{svg}
+\usepackage{mathtools}
+\usepackage{tabu}
 \usepackage{subcaption}
-\usepackage{tabu}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage{minted}
 
-\interdisplaylinepenalty=2500
-\hyphenation{lists} \makeatletter
+\usemintedstyle{xcode}
 
-\newcommand{\field}[1]{\mathbb{#1} }
-\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
-\setlength\belowdisplayskip{5pt}}
-\newcommand{\eeq}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\defn}{\stackrel{\triangle}{=}}
-\newcommand{\nn}{\nonumber}
-\newcommand{\nnl}{\nonumber \\}
-\renewcommand{\theequation}{\arabic{equation}}
-\renewcommand{\labelenumi}{(\roman{enumi})}
+\definecolor{bg}{rgb}{0.95,0.95,0.95}
 
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\ifundefined{\@ifundefined}
-\def\bfat{\left[ \begin{array}}
-\def\emat{\end{array} \right]}
-\def\bfatt{\left\{ \begin{array}}
-\def\ematt{\end{array} \right.}
-\def\bset{\left\{ \begin{array}}
-\def\eset{\end{array} \right\}}
-\def\bpar{\left( \begin{array}}
-\def\epar{\end{array} \right)}
-
-\graphicspath{{figures/}} % Graphics will be here
-
-\newtheorem{thm}{Theorem}[chapter]
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
-
-\numberwithin{equation}{chapter}
-
-% BEGIN OF DOCS
 \begin{document}
-\pagenumbering{roman}
-
-% CONTENTS AND LIST OF FIG AND TABLE PAGES
-\tableofcontents
-
-\pagenumbering{arabic}
-
-%#####
-% START OF THEORY
-
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
 
@@
 
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+
 \newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
 
-\chapter{THEORY}
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
+\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
 
-\section{Accelerating Charged Particles}
+\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
 
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
+%----../../..++++.
 
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
+%%%%%%
+% Start of intermediate.tex
+\section{Intermediate Versions}
 
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
+\subsection{$L_{out}$ Optimization For Single $e^-$}
+Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
+First approach was to hang the $e^-$ outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
+Then sweep the $t_{out}$ parameter to find the optimal value.
+This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
 
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
+Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
 
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
+\subsection{From Single $e^-$ to Bunches}
+After successfully accelerating single $e^-$, next step was to implement bunches to approximate a real $e^-$ gun.
 
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
+%%%%%%
 
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+\appendix
+\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
 \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
+    \begin{subfigure}{\textwidth}
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            for(double i = 2; i < 9; i += dT_out){
+                t_dum += i;
+                double enow = gecis(r_pos, vel, Et, t_dum);
+                if( enow > maxE ){
+                  maxE = enow;
+                  t_opt = i;
+                }
+                t_dum = t;
+            }
+        \end{minted}
+    \end{subfigure} 
+    \\
+    \begin{subfigure}{\textwidth}
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            double gecis(double r_pos, double vel, double Et, double &t){
+                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
+                    vel = c*sqrt(Et*Et-E0*E0)/Et;
+                    double RelBeta  = vel/c;
+                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+
+                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
+
+                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
+
+                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
+                    vel=vel+acc*dT*ns;
+                    RelBeta  = vel/c;
+                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+                    Et=RelGamma*E0; 
+                }
+                return Et;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{$L_{out}$ Optimization For Single $e^-$}
+    \label{fig:lout_opt_single_e}
 \end{figure}
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
-
-\subsection{Acceleration Cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda \label{eq:lpl}$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.3 \lambda^{1/4} P^{1/2} n
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-\end{thebibliography}
-
-% END OF THEORY
-%#####
 \end{document}

### 2023-07-11 subsections/simulation/poc/poc.tex
design finished, simulation started

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{float}
\usepackage{wrapfig,lipsum}
\usepackage{svg}
\usepackage{mathtools}
\usepackage{tabu}
\usepackage{subcaption}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{minted}

\begin{document}

\newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
\newcommand{\vecthree}[1]{\vec{#1}}

\newcommand{\parDeriv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\parDerivS}[2]{\frac{\partial^2 #1}{\partial #2^2}}
\newcommand{\derivS}[2]{\frac{d^2 #1}{d#2^2}}

\newcommand{\dotProdBF}[2]{\vecthreeBF{#1} \cdot \vecthreeBF{#2}}
\newcommand{\dotProd}[2]{\vecthree{#1} \cdot \vecthree{#2}}

\newcommand{\crossProdBF}[2]{\vecthreeBF{#1} \times \vecthreeBF{#2}}
\newcommand{\crossProd}[2]{\vecthree{#1} \times \vecthree{#2}}

\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}

\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}

\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}

%----../../..++++.

%%%%%%
% Start of poc.tex
\section{Proof of Concept}
Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.

This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
\begin{itemize}
    \item Get electron energy $E_{in}$
    \item Get the RF field definitions
    \item Get the magnet design parameters if there is any
    \item Do following until the simulation time has ellapsed
    \begin{enumerate}
        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_y}
        \item Calculate new $E_t$
    \end{enumerate}
\end{itemize}

The implemenation of this logic can be observed in the following code block.
\begin{figure}[H]
    \begin{minted}[linenos=true]{c++}
        for (double t=0; t<SimuTime; t+=dT){
            double RelBeta  = v/c;
            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);

            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);

            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
            v = v + acc*dT*ns;

            RelBeta  = v/c;
            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
            Et=RelGamma*E0; 
        }
    \end{minted}
    \caption{Core logic loop of the POC}
    \label{fig:POC_core_logic}
\end{figure}

After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass in THE CAVITY, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
% 40 kW total power
% Emax = 0.96 in old, 2.08 in new version
% R1 = 0.1882
% R2 = 0.753
% f = 107.5
\begin{eqnarray}
    E_{Pottier} &=& 0.565 MeV \nonumber\\
    E_{CST} &=& 0.872 MeV \label{eq:poc_E_results}\\
    E_{POC} &=& 0.873 MeV \nonumber
\end{eqnarray}

As can be observed in \fromfig{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results.However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
Using a single software would make the process error prone. Their results, at the end of the day, depend on the physical and mathematical models they use.

After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software. This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
The development and improvement efforts are still ongoing.

During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested. The following sections in this chapter investigates their implementations further.

%%%%%%

-lout opt
-phlag opt
-going 3D
-implement actual magnets instead of relying on lout
-

\end{document}

### 2023-07-11 msthesis.tex
simulation chapter half way done

@@
 \usepackage{minted}
+\usepackage{xcolor}
 
@@
 
-\subsection{Rhodotron Accelerator}
+\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
 
@@
 \chapter{SIMULATION}
+% Start of poc.tex
+\section{Proof of Concept}
+Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
+
+This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
+Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
+\begin{itemize}
+    \item Get electron energy $E_{in}$
+    \item Get the RF field definitions
+    \item Get the magnet design parameters if there is any
+    \item Do following until the simulation time has ellapsed
+    \begin{enumerate}
+        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
+        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
+        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
+        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
+        \item Calculate new $E_t$
+    \end{enumerate}
+\end{itemize}
+
+The implemenation of this logic can be observed in the following code block.
+\begin{figure}[H]
+    \begin{minted}[linenos=true]{c++}
+        for (double t=0; t<SimuTime; t+=dT){
+            double RelBeta  = v/c;
+            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+
+            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
+            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
+
+            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
+            v = v + acc*dT*ns;
+
+            RelBeta  = v/c;
+            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+            Et=RelGamma*E0; 
+        }
+    \end{minted}
+    \caption{Core logic loop of the POC}
+    \label{fig:POC_core_logic}
+\end{figure}
+
+After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass in THE CAVITY, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
+% 40 kW total power
+% Emax = 0.96 in old, 2.08 in new version
+% R1 = 0.1882
+% R2 = 0.753
+% f = 107.5
+\begin{eqnarray}
+    E_{Pottier} &=& 0.565 MeV \nonumber\\
+    E_{CST} &=& 0.872 MeV \label{eq:poc_E_results}\\
+    E_{POC} &=& 0.873 MeV \nonumber
+\end{eqnarray}
+
+As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
+This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
+Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
+
+After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software.
+This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
+The development and improvement efforts are still ongoing.
+
+During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
+The following sections in this chapter investigates their implementations further.
+
 \newpage
 
+% Start of intermediate.tex
+\section{Intermediate Versions}
+
+\subsection{$L_{out}$ Optimization For Single $e^-$}
+Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
+First approach was to hang the $e^-$ outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
+Then sweep the $t_{out}$ parameter to find the optimal value.
+This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
+
+Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
+
+\subsection{$\phi_{lag}$ Optimization For Bunches}
+After successfully accelerating single $e^-$, particle bunches were implemented to approximate a real $e^-$ gun. 
+They were modeled as $N$ electrons fired from an $e^-$ gun at even time intervals.
+This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing $e^-$ gun design.
+
+Addition of bunches would immediately proven useful when finding optimal gun phase lag.
+$\phi_{lag}$ for a bunch was defined as the RF phase when the first $e^-$ of the bunch entered the cavity, it defines the starting time of the current pass.
+To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
+
+\begin{itemize}
+    \item $\mu E$: Average energy
+    \item $E_{RMS}$: Root mean square of energy
+    \item $r_{RMS}$: Root mean square of $e^-$ positions
+\end{itemize}
+
+Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{RMS}$ \& $r_{RMS}$. For the first pass, 
+$E_{RMS}$ and $r_{RMS}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{RMS}$ during simulation (\textit{see \fromfig{phlag_opt}}).
+For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
+
+\begin{figure}[H]
+    \centering
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+        int phase_opt(int phase_sweep_range){
+            double minrms = 1;
+            int opt_phase;
+            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+              Bunch bunch1(RFphase);
+              double t1 = 0;
+              bunch1.bunch_gecis_t(t1);
+              bunch1.reset_pos();
+
+              if( bunch1.E_rms() < minrms ){
+                minrms = bunch1.E_rms();
+                opt_phase = RFphase;
+              }
+            }
+            return opt_phase;
+        }
+    \end{minted}
+    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
+    \label{fig:phlag_opt}
+\end{figure}
+
+Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
+This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
+
+\subsection{$L_{out}$ Optimization For Bunches}
+
 \newpage
+
+% START OF APPENDIX
 
@@
 
+\begin{figure}[H]
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
+                double minrms = 1;
+                int opt_phase;
+                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+                    Bunch bunch1(RFphase);
+                    double t1 = 0;
+                    bunch1.bunch_gecis_t(t1);
+                    bunch1.reset_pos();
+
+                    for(int i = 0; i < Louts.size(); i++){
+                        bunch1.bunch_gecis_d(Louts[i]);
+                        bunch1.reset_pos();
+                    }
+
+                    if( bunch1.E_rms() < minrms ){
+                        minrms = bunch1.E_rms();
+                        opt_phase = RFphase;
+                    }
+                }
+                return opt_phase;
+            }
+        \end{minted}
+    \caption{$\phi_{lag}$ Optimization For Tnitial Bunch Design}
+    \label{fig:phlag_opt_n_pass}
+\end{figure}
+
+% END OF APPENDIX
+
+% START OF BIBLIOGRAPHY
+
 \begin{thebibliography}{9}
@@
 
+% END OF BIBLIOGRAPHY
+
 \end{document}

### 2023-07-11 subsections/common/common_end.tex
simulation chapter half way done

@@
+% START OF APPENDIX
+
 \appendix

### 2023-07-11 subsections/simulation/intermediate_versions/intermediate.tex
simulation chapter half way done

@@
 
-\subsection{From Single $e^-$ to Bunches}
-After successfully accelerating single $e^-$, next step was to implement bunches to approximate a real $e^-$ gun.
+\subsection{$\phi_{lag}$ Optimization For Bunches}
+After successfully accelerating single $e^-$, particle bunches were implemented to approximate a real $e^-$ gun. 
+They were modeled as $N$ electrons fired from an $e^-$ gun at even time intervals.
+This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing $e^-$ gun design.
+
+Addition of bunches would immediately proven useful when finding optimal gun phase lag.
+$\phi_{lag}$ for a bunch was defined as the RF phase when the first $e^-$ of the bunch entered the cavity, it defines the starting time of the current pass.
+To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
+
+\begin{itemize}
+    \item $\mu E$: Average energy
+    \item $E_{RMS}$: Root mean square of energy
+    \item $r_{RMS}$: Root mean square of $e^-$ positions
+\end{itemize}
+
+Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{RMS}$ \& $r_{RMS}$. For the first pass, 
+$E_{RMS}$ and $r_{RMS}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{RMS}$ during simulation (\textit{see \fromfig{phlag_opt}}).
+For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
+
+\begin{figure}[H]
+    \centering
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+        int phase_opt(int phase_sweep_range){
+            double minrms = 1;
+            int opt_phase;
+            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+              Bunch bunch1(RFphase);
+              double t1 = 0;
+              bunch1.bunch_gecis_t(t1);
+              bunch1.reset_pos();
+
+              if( bunch1.E_rms() < minrms ){
+                minrms = bunch1.E_rms();
+                opt_phase = RFphase;
+              }
+            }
+            return opt_phase;
+        }
+    \end{minted}
+    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
+    \label{fig:phlag_opt}
+\end{figure}
+
+Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
+This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
+
+\subsection{$L_{out}$ Optimization For Bunches}
 
@@
 
+\begin{figure}[H]
+        \centering
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
+                double minrms = 1;
+                int opt_phase;
+                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+                    Bunch bunch1(RFphase);
+                    double t1 = 0;
+                    bunch1.bunch_gecis_t(t1);
+                    bunch1.reset_pos();
+
+                    for(int i = 0; i < Louts.size(); i++){
+                        bunch1.bunch_gecis_d(Louts[i]);
+                        bunch1.reset_pos();
+                    }
+
+                    if( bunch1.E_rms() < minrms ){
+                        minrms = bunch1.E_rms();
+                        opt_phase = RFphase;
+                    }
+                }
+                return opt_phase;
+            }
+        \end{minted}
+    \caption{$\phi_{lag}$ Optimization For Tnitial Bunch Design}
+    \label{fig:phlag_opt_n_pass}
+\end{figure}
+
 \end{document}

### 2023-07-11 subsections/simulation/poc/poc.tex
simulation chapter half way done

@@
         \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_y}
+        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
         \item Calculate new $E_t$
@@
 
-As can be observed in \fromfig{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results.However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
+As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
 This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
-Using a single software would make the process error prone. Their results, at the end of the day, depend on the physical and mathematical models they use.
+Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
 

### 2023-07-11 testler.cpp

@@ -1,0 +1,40 @@
+
+int phase_opt(int phase_sweep_range){
+    double minrms = 1;
+    int opt_phase;
+    for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+      Bunch bunch1(RFphase);
+      double t1 = 0;
+      bunch1.bunch_gecis_t(t1);
+      bunch1.reset_pos();
+
+      if( bunch1.E_rms() < minrms ){
+        minrms = bunch1.E_rms();
+        opt_phase = RFphase;
+      }
+    }
+    return opt_phase;
+}
+
+
+int phase_opt(const vector<double>& Louts, int phase_sweep_range){
+    double minrms = 1;
+    int opt_phase;
+    for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+        Bunch bunch1(RFphase);
+        double t1 = 0;
+        bunch1.bunch_gecis_t(t1);
+        bunch1.reset_pos();
+
+        for(int i = 0; i < Louts.size(); i++){
+            bunch1.bunch_gecis_d(Louts[i]);
+            bunch1.reset_pos();
+        }
+            
+        if( bunch1.E_rms() < minrms ){
+            minrms = bunch1.E_rms();
+            opt_phase = RFphase;
+        }
+    }
+    return opt_phase;
+}

### 2023-07-12 msthesis.tex
simulation in 3d started

@@
 
-The implemenation of this logic can be observed in the following code block.
-\begin{figure}[H]
-    \begin{minted}[linenos=true]{c++}
+The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
+\begin{figure}[H]
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
         for (double t=0; t<SimuTime; t+=dT){
@@
 % f = 107.5
+\begin{figure}[H]
     \begin{eqnarray}
@@
     \end{eqnarray}
+    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
+\end{figure}
 
@@
 
-\subsection{$L_{out}$ Optimization For Single $e^-$}
+\subsection{$L_{out}$ Optimization For Single $\textbf{e}^-$}
 Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the $e^-$ outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
+First approach was to hang the $\textbf{e}^-$ outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
 Then sweep the $t_{out}$ parameter to find the optimal value.
@@
 \subsection{$\phi_{lag}$ Optimization For Bunches}
-After successfully accelerating single $e^-$, particle bunches were implemented to approximate a real $e^-$ gun. 
-They were modeled as $N$ electrons fired from an $e^-$ gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing $e^-$ gun design.
+After successfully accelerating single $\textbf{e}^-$, particle bunches were implemented to approximate a real $\textbf{e}^-$ gun. 
+They were modeled as $N$ electrons fired from an $\textbf{e}^-$ gun at even time intervals.
+This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing $\textbf{e}^-$ gun design.
 
 Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first $e^-$ of the bunch entered the cavity, it defines the starting time of the current pass.
+$\phi_{lag}$ for a bunch was defined as the RF phase when the first $\textbf{e}^-$ of the bunch entered the cavity, it defines the starting time of the current pass.
 To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
@@
     \item $\mu E$: Average energy
-    \item $E_{RMS}$: Root mean square of energy
-    \item $r_{RMS}$: Root mean square of $e^-$ positions
+    \item $E_{rms}$: Root mean square of energy
+    \item $R_{rms}$: Root mean square of $\textbf{e}^-$ positions
 \end{itemize}
 
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{RMS}$ \& $r_{RMS}$. For the first pass, 
-$E_{RMS}$ and $r_{RMS}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{RMS}$ during simulation (\textit{see \fromfig{phlag_opt}}).
+Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
+$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
 For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
@@
     \centering
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
         int phase_opt(int phase_sweep_range){
@@
 
-\subsection{$L_{out}$ Optimization For Bunches}
+After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
+$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
+Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
+
+\subsection{Simulation in 3D}
+After successfully implementing $\textbf{e}^-$ - $\vecthreeBF{E}$ interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
+Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction.
+The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
+
+Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
+For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary.
+
+Interaction logic for $\textbf{e}^-$ - $\vecthreeBF{E}$ and $\textbf{e}^-$ - $\vecthreeBF{B}$ in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+            vector3d CoaxialRFField::actOn(Electron& e){
+                vector3d Efield = getField(e.pos);                          // Calculate E vector
+                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
+                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \end{subfigure}
+
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+            vector3d MagneticField::actOn(Electron& e){
+                if (isInside(e.pos) == -1)
+                    return vector3d(0,0,0);
+                vector3d Bfield = getField(e.pos);                          // Calculate B vector
+                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
+                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{$\textbf{e}^-$ - $\textbf{EM}$ interaction logic from \fromeq{acc_of_E_and_B}}
+    \label{fig:3D_e_EM_interaction_first}
+\end{figure}
+
+Where \* and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
 
@@
     \centering
+    \captionsetup{justification=centering}
     \begin{subfigure}{\textwidth}
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
             for(double i = 2; i < 9; i += dT_out){
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\small]{c++}
             double gecis(double r_pos, double vel, double Et, double &t){
@@
     \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single $e^-$}
+    \caption{$L_{out}$ Optimization For Single $\textbf{e}^-$}
     \label{fig:lout_opt_single_e}
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+        \captionsetup{justification=centering}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
             int phase_opt(const vector<double>& Louts, int phase_sweep_range){
@@
 
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+            double vector3d::operator* (const vector3d& other){
+                double dot = 0;
+                dot += this->x * other.x;
+                dot += this->y * other.y;
+                dot += this->z * other.z;
+                return dot;
+            }
+        \end{minted}
+    \end{subfigure}
+
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+            vector3d vector3d::operator% (const vector3d& other){
+                double x_ = (this->y * other.z) - (this->z * other.y);
+                double y_ = (this->z * other.x) - (this->x * other.z);
+                double z_ = (this->x * other.y) - (this->y * other.x);
+                vector3d crossed(x_, y_, z_);
+                return crossed;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{* and \% operators of \textit{vector3d} class}
+    \label{fig:vector3d_dot_cross_product}
+\end{figure}
+
+\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        Optimal phase with the least RMS : -5
+
+        Simulation settings : 
+        ph = -5 deg, gt = 1 ns, enum = 1000
+        dT = 0.001 ns, dT_out = 0.01 ns
+
+        For the 1th magnet:
+        Optimum out path = 0.81044 m
+        Magnet guide = 0.25852 m
+        Rho = 0.088477 m
+        Drift time of the first electron in the bunch : 7.688 ns
+        Drift time of the last electron in the bunch : 7.487 ns
+        Max energy = 0.47581 MeV
+        RMS = 0.0058165 MeV
+
+        For the 2th magnet:
+        Optimum out path = 1.0833 m
+        Magnet guide = 0.37766 m
+        Rho = 0.098898 m
+        Drift time of the first electron in the bunch : 5.597 ns
+        Drift time of the last electron in the bunch : 5.617 ns
+        Max energy = 0.89172 MeV
+        RMS = 0.0099018 MeV
+
+        For the 3th magnet:
+        Optimum out path = 1.1705 m
+        Magnet guide = 0.41573 m
+        Rho = 0.10223 m
+        Drift time of the first electron in the bunch : 5.314 ns
+        Drift time of the last electron in the bunch : 5.325 ns
+        Max energy = 1.298 MeV
+        RMS = 0.013879 MeV
+
+        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
+
+        Total steps calculated : 12468052652
+        Simulation finished in : 632050015 us     ( 632.1 s )
+
+    \end{minted}
+\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
+\label{fig:lout_opt_1ns_Erms}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        Optimal phase with the least RMS : 0
+
+        Simulation settings : 
+        ph = 0 deg, gt = 0.8 ns, enum = 1000
+        dT = 0.001 ns, dT_out = 0.01 ns
+
+        For the 1th magnet:
+        Optimum out path = 0.80787 m
+        Magnet guide = 0.2574 m
+        Rho = 0.088379 m
+        Drift time of the first electron in the bunch : 7.629 ns
+        Drift time of the last electron in the bunch : 7.48 ns
+        Max energy = 0.47579 MeV
+        RMS = 0.0038689 MeV
+
+        For the 2th magnet:
+        Optimum out path = 1.0833 m
+        Magnet guide = 0.37765 m
+        Rho = 0.098898 m
+        Drift time of the first electron in the bunch : 5.589 ns
+        Drift time of the last electron in the bunch : 5.605 ns
+        Max energy = 0.89169 MeV
+        RMS = 0.0068848 MeV
+
+        For the 3th magnet:
+        Optimum out path = 1.1705 m
+        Magnet guide = 0.41573 m
+        Rho = 0.10223 m
+        Drift time of the first electron in the bunch : 5.311 ns
+        Drift time of the last electron in the bunch : 5.318 ns
+        Max energy = 1.298 MeV
+        RMS = 0.0096887 MeV
+
+        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
+
+        Total steps calculated : 12455378454
+        Simulation finished in : 631136046 us     ( 631.1 s )        
+    \end{minted}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\label{fig:lout_opt_08ns_Erms}
+\end{figure}
+
 % END OF APPENDIX

### 2023-07-12 subsections/common/common_end.tex
simulation in 3d started

@@
     \label{fig:phlag_opt_n_pass}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+            double vector3d::operator* (const vector3d& other){
+                double dot = 0;
+                dot += this->x * other.x;
+                dot += this->y * other.y;
+                dot += this->z * other.z;
+                return dot;
+            }
+        \end{minted}
+    \end{subfigure}
+
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+            vector3d vector3d::operator% (const vector3d& other){
+                double x_ = (this->y * other.z) - (this->z * other.y);
+                double y_ = (this->z * other.x) - (this->x * other.z);
+                double z_ = (this->x * other.y) - (this->y * other.x);
+                vector3d crossed(x_, y_, z_);
+                return crossed;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{* and \% operators of \textit{vector3d} class}
+    \label{fig:vector3d_dot_cross_product}
+\end{figure}
+
+\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        Optimal phase with the least RMS : -5
+
+        Simulation settings : 
+        ph = -5 deg, gt = 1 ns, enum = 1000
+        dT = 0.001 ns, dT_out = 0.01 ns
+
+        For the 1th magnet:
+        Optimum out path = 0.81044 m
+        Magnet guide = 0.25852 m
+        Rho = 0.088477 m
+        Drift time of the first electron in the bunch : 7.688 ns
+        Drift time of the last electron in the bunch : 7.487 ns
+        Max energy = 0.47581 MeV
+        RMS = 0.0058165 MeV
+
+        For the 2th magnet:
+        Optimum out path = 1.0833 m
+        Magnet guide = 0.37766 m
+        Rho = 0.098898 m
+        Drift time of the first electron in the bunch : 5.597 ns
+        Drift time of the last electron in the bunch : 5.617 ns
+        Max energy = 0.89172 MeV
+        RMS = 0.0099018 MeV
+
+        For the 3th magnet:
+        Optimum out path = 1.1705 m
+        Magnet guide = 0.41573 m
+        Rho = 0.10223 m
+        Drift time of the first electron in the bunch : 5.314 ns
+        Drift time of the last electron in the bunch : 5.325 ns
+        Max energy = 1.298 MeV
+        RMS = 0.013879 MeV
+
+        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
+
+        Total steps calculated : 12468052652
+        Simulation finished in : 632050015 us     ( 632.1 s )
+
+    \end{minted}
+\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
+\label{fig:lout_opt_1ns_Erms}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        Optimal phase with the least RMS : 0
+
+        Simulation settings : 
+        ph = 0 deg, gt = 0.8 ns, enum = 1000
+        dT = 0.001 ns, dT_out = 0.01 ns
+
+        For the 1th magnet:
+        Optimum out path = 0.80787 m
+        Magnet guide = 0.2574 m
+        Rho = 0.088379 m
+        Drift time of the first electron in the bunch : 7.629 ns
+        Drift time of the last electron in the bunch : 7.48 ns
+        Max energy = 0.47579 MeV
+        RMS = 0.0038689 MeV
+
+        For the 2th magnet:
+        Optimum out path = 1.0833 m
+        Magnet guide = 0.37765 m
+        Rho = 0.098898 m
+        Drift time of the first electron in the bunch : 5.589 ns
+        Drift time of the last electron in the bunch : 5.605 ns
+        Max energy = 0.89169 MeV
+        RMS = 0.0068848 MeV
+
+        For the 3th magnet:
+        Optimum out path = 1.1705 m
+        Magnet guide = 0.41573 m
+        Rho = 0.10223 m
+        Drift time of the first electron in the bunch : 5.311 ns
+        Drift time of the last electron in the bunch : 5.318 ns
+        Max energy = 1.298 MeV
+        RMS = 0.0096887 MeV
+
+        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
+
+        Total steps calculated : 12455378454
+        Simulation finished in : 631136046 us     ( 631.1 s )        
+    \end{minted}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\label{fig:lout_opt_08ns_Erms}
 \end{figure}

### 2023-07-12 subsections/simulation/intermediate_versions/intermediate.tex
simulation in 3d started

--- 2023-07-11 subsections/simulation/intermediate_versions/intermediate.tex
@@
 
-\subsection{From Single $e^-$ to Bunches}
-After successfully accelerating single $e^-$, next step was to implement bunches to approximate a real $e^-$ gun.
+\subsection{$\phi_{lag}$ Optimization For Bunches}
+After successfully accelerating single $\textbf{e}^-$, particle bunches were implemented to approximate a real $\textbf{e}^-$ gun. 
+They were modeled as $N$ electrons fired from an $\textbf{e}^-$ gun at even time intervals.
+This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing $\textbf{e}^-$ gun design.
+
+Addition of bunches would immediately proven useful when finding optimal gun phase lag.
+$\phi_{lag}$ for a bunch was defined as the RF phase when the first $\textbf{e}^-$ of the bunch entered the cavity, it defines the starting time of the current pass.
+To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
+
+\begin{itemize}
+    \item $\mu E$: Average energy
+    \item $E_{rms}$: Root mean square of energy
+    \item $R_{rms}$: Root mean square of $\textbf{e}^-$ positions
+\end{itemize}
+
+Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
+$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
+For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        int phase_opt(int phase_sweep_range){
+            double minrms = 1;
+            int opt_phase;
+            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+              Bunch bunch1(RFphase);
+              double t1 = 0;
+              bunch1.bunch_gecis_t(t1);
+              bunch1.reset_pos();
+
+              if( bunch1.E_rms() < minrms ){
+                minrms = bunch1.E_rms();
+                opt_phase = RFphase;
+              }
+            }
+            return opt_phase;
+        }
+    \end{minted}
+    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
+    \label{fig:phlag_opt}
+\end{figure}
+
+Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
+This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
+
+After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
+$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
+Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
+
+\subsection{Simulation in 3D}
+After successfully implementing $\textbf{e}^-$ - $\vecthreeBF{E}$ interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
+Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction.
+The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
+
+Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
+For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary.
+
+Interaction logic for $\textbf{e}^-$ - $\vecthreeBF{E}$ and $\textbf{e}^-$ - $\vecthreeBF{B}$ in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+            vector3d CoaxialRFField::actOn(Electron& e){
+                vector3d Efield = getField(e.pos);                          // Calculate E vector
+                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
+                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \end{subfigure}
+
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+            vector3d MagneticField::actOn(Electron& e){
+                if (isInside(e.pos) == -1)
+                    return vector3d(0,0,0);
+                vector3d Bfield = getField(e.pos);                          // Calculate B vector
+                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
+                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{$\textbf{e}^-$ - $\textbf{EM}$ interaction logic from \fromeq{acc_of_E_and_B}}
+    \label{fig:3D_e_EM_interaction_first}
+\end{figure}
+
+Where \* and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
 
@@
     \centering
+    \captionsetup{justification=centering}
     \begin{subfigure}{\textwidth}
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
             for(double i = 2; i < 9; i += dT_out){
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\footnotesize]{c++}
             double gecis(double r_pos, double vel, double Et, double &t){
@@
 
+\begin{figure}[H]
+        \centering
+        \captionsetup{justification=centering}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
+                double minrms = 1;
+                int opt_phase;
+                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
+                    Bunch bunch1(RFphase);
+                    double t1 = 0;
+                    bunch1.bunch_gecis_t(t1);
+                    bunch1.reset_pos();
+
+                    for(int i = 0; i < Louts.size(); i++){
+                        bunch1.bunch_gecis_d(Louts[i]);
+                        bunch1.reset_pos();
+                    }
+
+                    if( bunch1.E_rms() < minrms ){
+                        minrms = bunch1.E_rms();
+                        opt_phase = RFphase;
+                    }
+                }
+                return opt_phase;
+            }
+        \end{minted}
+    \caption{$\phi_{lag}$ Optimization For Tnitial Bunch Design}
+    \label{fig:phlag_opt_n_pass}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+            double vector3d::operator* (const vector3d& other){
+                double dot = 0;
+                dot += this->x * other.x;
+                dot += this->y * other.y;
+                dot += this->z * other.z;
+                return dot;
+            }
+        \end{minted}
+    \end{subfigure}
+
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+            vector3d vector3d::operator% (const vector3d& other){
+                double x_ = (this->y * other.z) - (this->z * other.y);
+                double y_ = (this->z * other.x) - (this->x * other.z);
+                double z_ = (this->x * other.y) - (this->y * other.x);
+                vector3d crossed(x_, y_, z_);
+                return crossed;
+            }
+        \end{minted}
+    \end{subfigure}
+    \caption{* and \% operators of \textit{vector3d} class}
+    \label{fig:vector3d_dot_cross_product}
+\end{figure}
+
+\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        Optimal phase with the least RMS : -5
+
+        Simulation settings : 
+        ph = -5 deg, gt = 1 ns, enum = 1000
+        dT = 0.001 ns, dT_out = 0.01 ns
+
+        For the 1th magnet:
+        Optimum out path = 0.81044 m
+        Magnet guide = 0.25852 m
+        Rho = 0.088477 m
+        Drift time of the first electron in the bunch : 7.688 ns
+        Drift time of the last electron in the bunch : 7.487 ns
+        Max energy = 0.47581 MeV
+        RMS = 0.0058165 MeV
+
+        For the 2th magnet:
+        Optimum out path = 1.0833 m
+        Magnet guide = 0.37766 m
+        Rho = 0.098898 m
+        Drift time of the first electron in the bunch : 5.597 ns
+        Drift time of the last electron in the bunch : 5.617 ns
+        Max energy = 0.89172 MeV
+        RMS = 0.0099018 MeV
+
+        For the 3th magnet:
+        Optimum out path = 1.1705 m
+        Magnet guide = 0.41573 m
+        Rho = 0.10223 m
+        Drift time of the first electron in the bunch : 5.314 ns
+        Drift time of the last electron in the bunch : 5.325 ns
+        Max energy = 1.298 MeV
+        RMS = 0.013879 MeV
+
+        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
+
+        Total steps calculated : 12468052652
+        Simulation finished in : 632050015 us     ( 632.1 s )
+
+    \end{minted}
+\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
+\label{fig:lout_opt_1ns_Erms}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        Optimal phase with the least RMS : 0
+
+        Simulation settings : 
+        ph = 0 deg, gt = 0.8 ns, enum = 1000
+        dT = 0.001 ns, dT_out = 0.01 ns
+
+        For the 1th magnet:
+        Optimum out path = 0.80787 m
+        Magnet guide = 0.2574 m
+        Rho = 0.088379 m
+        Drift time of the first electron in the bunch : 7.629 ns
+        Drift time of the last electron in the bunch : 7.48 ns
+        Max energy = 0.47579 MeV
+        RMS = 0.0038689 MeV
+
+        For the 2th magnet:
+        Optimum out path = 1.0833 m
+        Magnet guide = 0.37765 m
+        Rho = 0.098898 m
+        Drift time of the first electron in the bunch : 5.589 ns
+        Drift time of the last electron in the bunch : 5.605 ns
+        Max energy = 0.89169 MeV
+        RMS = 0.0068848 MeV
+
+        For the 3th magnet:
+        Optimum out path = 1.1705 m
+        Magnet guide = 0.41573 m
+        Rho = 0.10223 m
+        Drift time of the first electron in the bunch : 5.311 ns
+        Drift time of the last electron in the bunch : 5.318 ns
+        Max energy = 1.298 MeV
+        RMS = 0.0096887 MeV
+
+        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
+
+        Total steps calculated : 12455378454
+        Simulation finished in : 631136046 us     ( 631.1 s )        
+    \end{minted}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\label{fig:lout_opt_08ns_Erms}
+\end{figure}
+
 \end{document}

### 2023-07-12 subsections/simulation/poc/poc.tex
simulation in 3d started

@@
 
-The implemenation of this logic can be observed in the following code block.
+The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
 \begin{figure}[H]
-    \begin{minted}[linenos=true]{c++}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
         for (double t=0; t<SimuTime; t+=dT){

### 2023-07-16 msthesis.tex
multhtreading added GUI started

@@
 
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}% START OF THEORY
+\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
+
+\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
+\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}% START OF THEORY
 
@@
 
-\subsection{Runge Kutta}
+\subsection{Runge Kutta} \label{sec:rungekutta}
 
@@
 Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary.
+For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
 
@@
 
-Where \* and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+
+Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
+For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
+Rendered results could be stored as \textit{gif} animations. 
+Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
+        \caption*{Unsyncronized $\textbf{e}^-$ gun period, $T_g = 5ns$}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
+        \caption*{Syncronized $\textbf{e}^-$ gun period, $T_g = 9.3ns$}
+    \end{subfigure}
+    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
+    \label{fig:example_gnuplot_renders}
+\end{figure}
+
+\subsection{Acceleration in Magnetic Field}
+An issue regarding the $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction became apparent when energy gain during these interactions was observed.
+A setup simulation was implemented in which a bunch of 100$\textbf{e}^-$ at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
+Initial results at $dt=0.01$ns proved the suspicion of $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
+        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
+        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
+    \end{subfigure}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
+    \label{fig:mag_lf_render}
+\end{figure}
+
+Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
+Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for $\textbf{e}^-$ - \textbf{EM} interactions. 
+To test newer approaches, two additional version of  $\textbf{e}^-$ - \textbf{EM} interaction that are using \fromsec{rungekutta} were added.
+\subsubsection{RK4-1}
+First approach for integrating \fromsec{rungekutta} into $\textbf{e}^-$ - \textbf{EM} interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
+After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, $\textbf{e}^-$ would move and accelerate using the \textit{Leap-frog} method. 
+The idea was to produce more refined interaction results, leading to improved accuracy especially in $\textbf{e}^-$ - $\vecthreeBF{B}$.
+RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
+The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
+\subsubsection{RK4-2}
+Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
+Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
+
+These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison}.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:lf_rk1_rk2_comparison}
+\end{figure}
+
+The data from these tests can be found in \fromtabs{lf_rk1_rk2_Tsim}{lf_rk1_rk2_dE} of \fromapp{example_simulation_runs}. 
+As anticipated, \textit{Leap-frog} produced the fastest yet least accurate results, whereas \textit{RK4-2} method was proved to be the best performer for accuracy.
+When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
+\textit{RK4-2} provides around $41\%$ less energy gain in $\vecthreeBF{B}$ with respect to the next performer \textit{Leap-frog}.
+The tradeoff is the computational intensity mentioned in \fromsec{rungekutta}; \textit{Leap-frog} being around $47\%$ faster than $\textit{RK4-2}$.
+
+This relation is not linear however; \textit{RK4-2} is not as demanding in less computationally intensitive runs and able to keep up with \textit{Leap-frog} in execution times while increasing the accuracy difference from other methods,
+whereas \textit{Leap-frog} excels at simplicity, being able to use higher time resolution for given computational power. 
+Both methods can be used in different situations, therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
+\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
 
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             for(double i = 2; i < 9; i += dT_out){
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\small]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
             double gecis(double r_pos, double vel, double Et, double &t){
@@
         \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             int phase_opt(const vector<double>& Louts, int phase_sweep_range){
@@
         \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Tnitial Bunch Design}
+    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
     \label{fig:phlag_opt_n_pass}
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             double vector3d::operator* (const vector3d& other){
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\small]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d vector3d::operator% (const vector3d& other){
@@
     \label{fig:vector3d_dot_cross_product}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
+            vector3d relative = e_position - hs_position;       
+            // r/5 can be changed, use this for now                                
+            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
+                return true;                                                                 
+            }
+            return false;
+        }
+    \end{minted}
+\caption{Logic of is $\textbf{e}^-$ inside the shape of magnet}
+\label{fig:is_inside_halfsphere}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
+            if (B.isInside(pos) == -1){
+                return vector3d(0,0,0);
+            }
+            Electron2D e_dummy;
+            e_dummy.Et = Et;
+            e_dummy.pos = pos;
+            e_dummy.vel = vel;
+            double time_halved = time_interval*0.5;
+            // get k1                                       
+            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
+            vector3d k1 = F_m * e_dummy.gamma_inv();     
+            // get k2
+            e_dummy.move(time_halved);
+            e_dummy.accelerate(k1, time_halved);                                              
+            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
+            vector3d k2 = F_m * e_dummy.gamma_inv();    
+            // get k3
+            e_dummy.vel = vel;
+            e_dummy.accelerate(k2, time_halved);
+            vector3d k3 = F_m * e_dummy.gamma_inv();   
+            // get k4
+            e_dummy.vel = vel;
+            e_dummy.move(time_halved);
+            e_dummy.accelerate(k3, time_interval);                                           
+            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
+            vector3d k4 = F_m * e_dummy.gamma_inv();
+
+            return (k1 + k2*2 + k3*2 + k4)/6;
+        }
+    \end{minted}
+\caption{RK4-1 implemenation of $\textbf{e}^-$-$\vecthreeBF{B}$}
+\label{fig:rk1_B}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
+            vector3d run_kut_E = interactE_RK(E, time_interval);
+            vector3d run_kut_B = interactB_RK(B, time_interval);
+
+            vector3d acc = run_kut_E + run_kut_B;
+
+            move(acc, time_interval/2);
+            accelerate(acc, time_interval);
+            move(acc, time_interval/2);
+        }
+    \end{minted}
+\caption{RK4-1 implemenation of $\textbf{e}^-$-\textbf{EM}}
+\label{fig:rk1_EM}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
+            Electron2D e_dummy;
+            e_dummy.Et = Et;
+            e_dummy.pos = pos;
+            e_dummy.vel = vel;
+
+            // Calculate k1
+            vector3d acc_E = E.actOn(e_dummy);
+            vector3d acc_B = B.actOn(e_dummy);
+            vector3d acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
+
+            // Calculate k2
+            e_dummy.pos = (pos + pos_k1)*0.5;
+            e_dummy.vel = (vel + vel_k1)*0.5;
+            e_dummy.Et = e_dummy.gamma()*E0;
+            E.update(time + time_interval*0.5);
+
+            acc_E = E.actOn(e_dummy);
+            acc_B = B.actOn(e_dummy);
+            acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
+
+            // Calculate k3
+            e_dummy.pos = (pos + pos_k2)*0.5;
+            e_dummy.vel = (vel + vel_k2)*0.5;
+            e_dummy.Et = e_dummy.gamma()*E0;
+            E.update(time + time_interval*0.5);
+
+            acc_E = E.actOn(e_dummy);
+            acc_B = B.actOn(e_dummy);
+            acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
+
+            // Calculate k4
+            E.update(time + time_interval);
+
+            acc_E = E.actOn(e_dummy);
+            acc_B = B.actOn(e_dummy);
+            acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
+
+            E.update(time);
+            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
+            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
+            Et = gamma()*E0;
+    }
+    \end{minted}
+\caption{RK4-2 implemenation of $\textbf{e}^-$-\textbf{EM}}
+\label{fig:rk2_EM}
 \end{figure}
@@
 
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+    \hline
+        $dt$(ns) & $T_{sim LF}(s)$ & $T_{sim RK1}(s)$  & $T_{sim RK2}(s)$  & $\Delta T_{LF-RK2}$\\\hline
+        $10^{-2}$ & 4.14092 & 4.146 & 4.10945 & 0.77\% \\ \hline
+        $10^{-3}$ & 4.23817 & 4.61703 & 4.30225 & -1.51\% \\ \hline
+        $10^{-4}$ & 5.04679 & 8.93529 & 6.3065 & -24.96\% \\ \hline
+        $10^{-5}$ & 13.5135 & 51.9024 & 25.4279 & -88.17\%\\ \hline
+        $10^{-6}$ & 97.6229 & 486.378 & 217.704 & -123.01\% \\ \hline
+    \end{tabular}
+    \caption{$dt$ vs $T_{sim}$ of Leap-frog, RK4-1, RK4-2 \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:lf_rk1_rk2_Tsim}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+    \hline
+        $dt$(ns) & $\Delta E_{LF}$(MeV) & $\Delta E_{RK1}$(MeV)  & $\Delta E_{RK2}$(MeV)  & $\Delta E_{LF-RK2}$\\\hline
+        $10^{-2}$ & 2.78323 & 1.26503 & 1.04713 & 165.8\% \\ \hline
+        $10^{-3}$ & 0.11712 & 0.07469 & 0.06691 & 42.87\% \\ \hline
+        $10^{-4}$ & 0.01101 & 0.00716 & 0.00644 & 41.5\%  \\ \hline
+        $10^{-5}$ & 0.00109 & 0.00071 & 0.00064 & 41\% \\ \hline
+        $10^{-6}$ & 0.00011 & 0.00007 & 0.00006 & 45\% \\\hline
+    \end{tabular}
+    \caption{$dt$ vs $\Delta E$ of Leap-frog, RK4-1, RK4-2 \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:lf_rk1_rk2_dE}
+\end{table}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
+        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
+        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
+    \end{subfigure}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
+    \label{fig:mag_rk_render}
+\end{figure}
+
 % END OF APPENDIX
-
 % START OF BIBLIOGRAPHY

### 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
multhtreading added GUI started

@@
 \newcommand{\vecthree}[1]{\vec{#1}}
+\newcommand{\vecNum}[3]{(#1, #2, #3)}
 
@@
 \newcommand{\crossProd}[2]{\vecthree{#1} \times \vecthree{#2}}
+
+\newcommand{\e}{$\textbf{e}^-$}
+\newcommand{\egun}{$\textbf{e}^-$-gun}
+\newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
+\newcommand{\eE}{$\textbf{e}^-$ - $\vecthreeBF{E}$ }
+\newcommand{\eEM}{$\textbf{e}^-$ - \textbf{EM} }
+\newcommand{\ee}{$\textbf{e}^-$ - $\textbf{e}^-$ }
 
@@
 
+\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
+\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
+
 %----../../..++++.
@@
 
-\subsection{$L_{out}$ Optimization For Single $\textbf{e}^-$}
+\subsection{$L_{out}$ Optimization For Single \e}
 Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the $\textbf{e}^-$ outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
+First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
 Then sweep the $t_{out}$ parameter to find the optimal value.
@@
 \subsection{$\phi_{lag}$ Optimization For Bunches}
-After successfully accelerating single $\textbf{e}^-$, particle bunches were implemented to approximate a real $\textbf{e}^-$ gun. 
-They were modeled as $N$ electrons fired from an $\textbf{e}^-$ gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing $\textbf{e}^-$ gun design.
+After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
+They were modeled as $N$ electrons fired from an \e gun at even time intervals.
+This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.
 
 Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first $\textbf{e}^-$ of the bunch entered the cavity, it defines the starting time of the current pass.
+$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch entered the cavity, it defines the starting time of the current pass.
 To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
@@
     \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of $\textbf{e}^-$ positions
+    \item $R_{rms}$: Root mean square of \e positions
 \end{itemize}
@@
 \subsection{Simulation in 3D}
-After successfully implementing $\textbf{e}^-$ - $\vecthreeBF{E}$ interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction.
+After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
+Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
 The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
@@
 Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary.
+For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
 
-Interaction logic for $\textbf{e}^-$ - $\vecthreeBF{E}$ and $\textbf{e}^-$ - $\vecthreeBF{B}$ in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
+Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
 \begin{figure}[H]
@@
     \end{subfigure}
-    \caption{$\textbf{e}^-$ - $\textbf{EM}$ interaction logic from \fromeq{acc_of_E_and_B}}
+    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
     \label{fig:3D_e_EM_interaction_first}
@@
 
-Where \* and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+
+Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
+For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
+Rendered results could be stored as \textit{gif} animations. 
+Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/5ns_gnuplot.png}
+        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
+    \end{subfigure}
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}
+        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
+    \end{subfigure}
+    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
+    \label{fig:example_gnuplot_renders}
+\end{figure}
+
+\subsection{Acceleration in Magnetic Field}
+An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
+A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
+Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_001dt.png}
+        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
+    \end{subfigure}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_00001dt.png}
+        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
+    \end{subfigure}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
+    \label{fig:mag_lf_render}
+\end{figure}
+
+Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
+Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
+To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
+\subsubsection{RK4-1}
+First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
+After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
+The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
+RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
+The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
+\subsubsection{RK4-2}
+Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
+Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
+
+These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison}.
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-E.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-Tsim.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:lf_rk1_rk2_comparison}
+\end{figure}
+
+The data from these tests can be found in \fromtabs{lf_rk1_rk2_Tsim}{lf_rk1_rk2_dE} of \fromapp{example_simulation_runs}. 
+As anticipated, \textit{Leap-frog} produced the fastest yet least accurate results, whereas \textit{RK4-2} method was proved to be the best performer for accuracy.
+When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
+\textit{RK4-2} provides around $41\%$ less energy gain in $\vecthreeBF{B}$ with respect to the next performer \textit{Leap-frog}.
+The tradeoff is the computational intensity mentioned in \fromsec{rungekutta}; \textit{Leap-frog} being around $47\%$ faster than $\textit{RK4-2}$.
+
+This relation is not linear however; \textit{RK4-2} is not as demanding in less computationally intensitive runs and able to keep up with \textit{Leap-frog} in execution times while increasing the accuracy difference from other methods,
+whereas \textit{Leap-frog} excels at simplicity, being able to use higher time resolution for given computational power. 
+Both methods can be used in different situations, therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
+\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
+
+\subsection{Acceleration in Electric Field}
+After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
+
+As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
+Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.47\textwidth}
+        \centering
+        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_1.png}
+        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_2.png}
+        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
+    \end{subfigure}
+    \caption{Illustration of test setups.}
+\end{figure}
+
+In the first test, the beam would be injected into a static uniform electric field \\
+$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
+
+Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753, 0, 0} is
+\begin{eqnarray}
+    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
+             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
+             &=& 2.65616 \times 1.506 \\
+    \Delta V^1 &=& 4 MV \\
+    \Delta E^1 &=& 4 MeV \\
+    E_{exitTH}^1 &=& 5 MeV
+\end{eqnarray}
+
+In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
+$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
+\begin{eqnarray}
+    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
+                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
+                 &=& 5.31232 \times 0.753 \\
+    \Delta V^2   &=& 4 MV \\
+    \Delta E^2   &=& 4 MeV \\
+    E_{exitTH}^2 &=& 5 MeV
+\end{eqnarray}
+
+Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
+To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_par.png}
+        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
+    \end{subfigure}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_perp.png}
+        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
+    \end{subfigure}
+    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=0.5\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-E.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=0.5\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-Tsim.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
+    \label{fig:lf_rk2_par_stat_E_comparison}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=0.5\linewidth]{../../../figures/to_be_added.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=0.5\linewidth]{../../../figures/to_be_added.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
+    \label{fig:lf_rk2_perp_stat_E_comparison}
+\end{figure}
+
+\subsection{Multithreading}
+As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
+There have been a number of different approaches for implementation. 
+First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
+After the sizable refactoring done for 3D capabilities, this implementation was obselete.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/multh_arc.png}
+    \caption{An Illustration of the multithreading architecture.}
+    \label{fig:multh_illustration}
+\end{figure}
+
+For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
+The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{console_output_running}) 
+or communucating with the \textit{GUI} that will be disscussed in the next section.
+
+Focus of this section is the worker threads, also known as \eEM interaction threads.
+There were four competing architecture for these worker threads,
+\begin{enumerate}
+    \item Have a thread pool that calculates \eEM in a queue 
+    \item Assign a thread to each bunch
+    \item Assign random electrons to each thread and calculate \eEM with global time
+    \item Assign random electrons to each thread and calculate \eEM with local thread time
+\end{enumerate}
+
+\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
+
+\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
+
+\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
+
+\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
+This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
+However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
+
+Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
+This would lead to larger memory allocations and more time spent setting up simulations. 
+Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
+An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
+nevertheless, \textbf{Architecture 4} was chosed to be implemented.
+
+\subsection{Graphical User Interface}
+Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
+An exapmle of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
+This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
+For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
+This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
+
+The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \caption{An Illustration of first GUI design.}
+    \label{fig:gui_illustration}
+\end{figure}
+
+The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
+For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
+By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
 
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             for(double i = 2; i < 9; i += dT_out){
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\footnotesize]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
             double gecis(double r_pos, double vel, double Et, double &t){
@@
     \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single $\textbf{e}^-$}
+    \caption{$L_{out}$ Optimization For Single \e}
     \label{fig:lout_opt_single_e}
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             double vector3d::operator* (const vector3d& other){
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d vector3d::operator% (const vector3d& other){
@@
     \label{fig:vector3d_dot_cross_product}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
+            vector3d relative = e_position - hs_position;       
+            // r/5 can be changed, use this for now                                
+            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
+                return true;                                                                 
+            }
+            return false;
+        }
+    \end{minted}
+\caption{Logic of is \e inside the shape of magnet}
+\label{fig:is_inside_halfsphere}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
+            if (B.isInside(pos) == -1){
+                return vector3d(0,0,0);
+            }
+            Electron2D e_dummy;
+            e_dummy.Et = Et;
+            e_dummy.pos = pos;
+            e_dummy.vel = vel;
+            double time_halved = time_interval*0.5;
+            // get k1                                       
+            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
+            vector3d k1 = F_m * e_dummy.gamma_inv();     
+            // get k2
+            e_dummy.move(time_halved);
+            e_dummy.accelerate(k1, time_halved);                                              
+            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
+            vector3d k2 = F_m * e_dummy.gamma_inv();    
+            // get k3
+            e_dummy.vel = vel;
+            e_dummy.accelerate(k2, time_halved);
+            vector3d k3 = F_m * e_dummy.gamma_inv();   
+            // get k4
+            e_dummy.vel = vel;
+            e_dummy.move(time_halved);
+            e_dummy.accelerate(k3, time_interval);                                           
+            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
+            vector3d k4 = F_m * e_dummy.gamma_inv();
+
+            return (k1 + k2*2 + k3*2 + k4)/6;
+        }
+    \end{minted}
+\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
+\label{fig:rk1_B}
+\end{figure}
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
+            vector3d run_kut_E = interactE_RK(E, time_interval);
+            vector3d run_kut_B = interactB_RK(B, time_interval);
+
+            vector3d acc = run_kut_E + run_kut_B;
+
+            move(acc, time_interval/2);
+            accelerate(acc, time_interval);
+            move(acc, time_interval/2);
+        }
+    \end{minted}
+\caption{RK4-1 implemenation of \eEM}
+\label{fig:rk1_EM}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
+            Electron2D e_dummy;
+            e_dummy.Et = Et;
+            e_dummy.pos = pos;
+            e_dummy.vel = vel;
+
+            // Calculate k1
+            vector3d acc_E = E.actOn(e_dummy);
+            vector3d acc_B = B.actOn(e_dummy);
+            vector3d acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
+
+            // Calculate k2
+            e_dummy.pos = (pos + pos_k1)*0.5;
+            e_dummy.vel = (vel + vel_k1)*0.5;
+            e_dummy.Et = e_dummy.gamma()*E0;
+            E.update(time + time_interval*0.5);
+
+            acc_E = E.actOn(e_dummy);
+            acc_B = B.actOn(e_dummy);
+            acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
+
+            // Calculate k3
+            e_dummy.pos = (pos + pos_k2)*0.5;
+            e_dummy.vel = (vel + vel_k2)*0.5;
+            e_dummy.Et = e_dummy.gamma()*E0;
+            E.update(time + time_interval*0.5);
+
+            acc_E = E.actOn(e_dummy);
+            acc_B = B.actOn(e_dummy);
+            acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
+
+            // Calculate k4
+            E.update(time + time_interval);
+
+            acc_E = E.actOn(e_dummy);
+            acc_B = B.actOn(e_dummy);
+            acc = acc_E + acc_B;
+            e_dummy.move(time_interval);
+            e_dummy.accelerate(acc, time_interval);
+            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
+
+            E.update(time);
+            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
+            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
+            Et = gamma()*E0;
+    }
+    \end{minted}
+\caption{RK4-2 implemenation of \eEM}
+\label{fig:rk2_EM}
 \end{figure}
@@
 
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+    \hline
+        $dt$(ns) & $T_{sim LF}(s)$ & $T_{sim RK1}(s)$  & $T_{sim RK2}(s)$  & $\Delta T_{LF-RK2}$\\\hline
+        $10^{-2}$ & 4.14092 & 4.146 & 4.10945 & 0.77\% \\ \hline
+        $10^{-3}$ & 4.23817 & 4.61703 & 4.30225 & -1.51\% \\ \hline
+        $10^{-4}$ & 5.04679 & 8.93529 & 6.3065 & -24.96\% \\ \hline
+        $10^{-5}$ & 13.5135 & 51.9024 & 25.4279 & -88.17\%\\ \hline
+        $10^{-6}$ & 97.6229 & 486.378 & 217.704 & -123.01\% \\ \hline
+    \end{tabular}
+    \caption{$dt$ vs $T_{sim}$ of Leap-frog, RK4-1, RK4-2 \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:lf_rk1_rk2_Tsim}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+    \hline
+        $dt$(ns) & $\Delta E_{LF}$(MeV) & $\Delta E_{RK1}$(MeV)  & $\Delta E_{RK2}$(MeV)  & $\Delta E_{LF-RK2}$\\\hline
+        $10^{-2}$ & 2.78323 & 1.26503 & 1.04713 & 165.8\% \\ \hline
+        $10^{-3}$ & 0.11712 & 0.07469 & 0.06691 & 42.87\% \\ \hline
+        $10^{-4}$ & 0.01101 & 0.00716 & 0.00644 & 41.5\%  \\ \hline
+        $10^{-5}$ & 0.00109 & 0.00071 & 0.00064 & 41\% \\ \hline
+        $10^{-6}$ & 0.00011 & 0.00007 & 0.00006 & 45\% \\\hline
+    \end{tabular}
+    \caption{$dt$ vs $\Delta E$ of Leap-frog, RK4-1, RK4-2 \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:lf_rk1_rk2_dE}
+\end{table}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_rk_001dt.png}
+        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_rk_00001dt.png}
+        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
+    \end{subfigure}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
+    \label{fig:mag_rk_render}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
+        #            Rhodotron Simulation Configuration File
+        # ================================================================
+        #    M.Furkan Er                                     22/09/2022   
+        # ================================================================
+        #
+        # emax = Maximum electric field strength (MV/m)
+        # ein = Energy of electrons coming out of the gun (MeV)
+        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
+        # targeten = Max energy on the output gif (MeV)
+        # freq = Frequency of the RF field (MHz)
+        # phaselag = phase lag of the first electrons (degree)
+        # starttime = time to start firing the gun (ns)
+        # endtime = ns to run the simulation (ns)
+        # dt = time interval to do the calculations (ns)
+        # guntime = how long a gun pulse is (ns)
+        # gunperiod = time between two gun pulses (ns)
+        # enum = number of electrons to simulate in a bunch
+        # bunchnum = number of times the gun fires
+        # r1 = radius of the inner cylinder (m)
+        # r2 = radius of the outer cylinder (m)
+        # epath = path to store the electric field data
+        # bpath = path to store the magnetic field data
+        # cpath = path to store the settings
+        # ppath = path to store electron data
+        # multh = enable or disable multitheading
+        # thcount = set the maximum thread to be used
+        # magrotation = degrees of rotation to enter each magnet 
+        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
+        # output = output file name
+
+        # E FIELD CONFIGURATION 
+        emax=1.170
+        freq=107.3
+        phaselag=10.0
+        r1=0.1840
+        r2=0.7380
+
+        # B FIELD CONFIGURATION 
+        magrotation=5.0
+
+        # GUN CONFIGURATION 
+        einmean=0.040
+        einstd=0.0000
+        targeten=2.0
+        guntime=1.0
+        gunperiod=9.3
+        enum=50
+        bunchnum=1
+
+        # SIM CONFIGURATION 
+        starttime=0
+        endtime=10
+        dt=0.0000010000
+        epath=xy/rf.dat
+        bpath=xy/magnet.dat
+        cpath=xy/settings.dat
+        ppath=xy/paths/
+        multh=1
+        thcount=10     
+    \end{minted}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\label{fig:config_file}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
+        -- Simulation Configuration --
+        Emax : 0.96     MV/m
+        Freq : 107.5    MHz
+        Phase Lag : -5  degree
+        EndTime : 100   ns
+        dT : 0.0001     ns
+        guntime : 0.8   ns
+        gunperiod : 9.3 ns
+        enum : 100
+        bunchnum : 2
+        R1 : 0.188241   m
+        R2 : 0.752967   m
+        Magnet count :  5
+        Ein : 0.04      MeV
+        TargetE : 2.5   MeV
+        --------------------------------
+
+                     ...Simulation is running...
+        V_____________________________________________________V
+        [####################################                 ]
+    \end{minted}
+\caption{Example of console output while simulation is running.}
+\label{fig:console_output_running}
+\end{figure}
+
 \end{document}

### 2023-07-16 figures/analiz/root_draw.c

@@ -1,0 +1,64 @@
+{
+	//TGraph *gr1 = new TGraph("times_lf.txt", "%lg,%*lg,%lg");
+    TCanvas *c1 = new TCanvas();
+    c1->SetLogy();
+    c1->SetLogx();
+    c1->SetGridx();
+    c1->SetGridy();
+    TGraph *lf, *rk1, * rk2;
+
+    bool delE = false;
+
+    if(delE){
+        lf = new TGraph("data/lf_staticE_test_results.txt", "%lg %lg %*lg %*lg %*lg");   
+    }
+    else{
+        lf = new TGraphErrors("data/lf_staticE_test_results.txt", "%lg %*lg %*lg %lg %lg");   
+    }
+    lf->SetMarkerStyle(23);
+    lf->SetMarkerColor(kBlue);
+    lf->SetTitle("Leap-frog");
+/*
+    if(delE){
+        rk1 = new TGraph("rk1_test_results.txt", "%lg %lg %*lg");   
+    }
+    else{
+        rk1 = new TGraphErrors("rk1_test_results.txt", "%lg %*lg %lg %lg");   
+    }
+    rk1->SetMarkerStyle(22);
+    rk1->SetMarkerColor(kRed);
+    rk1->SetTitle("RK4-1");*/
+
+    if(delE){
+        rk2 = new TGraph("data/rk_staticE_test_results.txt", "%lg %lg %*lg %*lg %*lg");   
+    }
+    else{
+        rk2 = new TGraphErrors("data/rk_staticE_test_results.txt", "%lg %*lg %*lg %lg %lg");   
+    }
+    rk2->SetMarkerStyle(21);
+    rk2->SetMarkerColor(kRed);
+    rk2->SetTitle("RK4-2");
+    //plot->Draw("AP");
+    TMultiGraph *mg = new TMultiGraph();
+    mg->Add(lf, "lp");
+    //mg->Add(rk1, "cp");
+    mg->Add(rk2, "lp");
+    mg->GetXaxis()->SetTitle("dt(ns)");
+    mg->GetXaxis()->SetLimits(5e-7,1e-1);
+    if(delE){
+        mg->GetYaxis()->SetTitle("#DeltaE(MeV)");
+        mg->SetMaximum(0.13);
+        mg->SetMinimum(1e-6);
+    }
+    else{
+        mg->GetYaxis()->SetTitle("T_{SIM}(s)");
[…]

### 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
figures for acc in E & multithreading added

@@
     \centering
-    \begin{subfigure}{0.8\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
-        \includegraphics[width=0.5\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-E.png}
+        \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-E.png}
         \caption*{$dt$ vs $\Delta E$}
@@
 
-    \begin{subfigure}{0.8\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
-        \includegraphics[width=0.5\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-Tsim.png}
+        \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-Tsim.png}
         \caption*{$dt$ vs $T_{sim}$}
@@
     \centering
-    \begin{subfigure}{0.8\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
-        \includegraphics[width=0.5\linewidth]{../../../figures/to_be_added.png}
+        \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-E_3.png}
         \caption*{$dt$ vs $\Delta E$}
@@
 
-    \begin{subfigure}{0.8\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
-        \includegraphics[width=0.5\linewidth]{../../../figures/to_be_added.png}
+        \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
         \caption*{$dt$ vs $T_{sim}$}
@@
 Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An exapmle of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
+An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.

### 2023-07-16 msthesis.tex
mag acc revised

@@
 
-Interaction logic for $\textbf{e}^-$ - $\vecthreeBF{E}$ and $\textbf{e}^-$ - $\vecthreeBF{B}$ in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
+Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
 \begin{figure}[H]
@@
     \captionsetup{justification=centering}
-    \begin{subfigure}{0.48\textwidth}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
         \centering
         \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized $\textbf{e}^-$ gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
+        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
+    \end{subfigure}
+    \begin{subfigure}{0.9\textwidth}
         \centering
         \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized $\textbf{e}^-$ gun period, $T_g = 9.3ns$}
+        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
     \end{subfigure}
@@
 \subsection{Acceleration in Magnetic Field}
-An issue regarding the $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100$\textbf{e}^-$ at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
+An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
+A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
+Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
 
@@
     \captionsetup{justification=centering}
-    \begin{subfigure}{0.48\textwidth}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
+    \begin{subfigure}{0.8\textwidth}
         \centering
@@
 Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for $\textbf{e}^-$ - \textbf{EM} interactions. 
-To test newer approaches, two additional version of  $\textbf{e}^-$ - \textbf{EM} interaction that are using \fromsec{rungekutta} were added.
+Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
+To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
 \subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into $\textbf{e}^-$ - \textbf{EM} interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, $\textbf{e}^-$ would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in $\textbf{e}^-$ - $\vecthreeBF{B}$.
+First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
+After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
+The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
 RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
@@
         \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E.png}
+        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
         \caption*{$dt$ vs $\Delta E$}
@@
         \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim.png}
+        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
         \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on $\textbf{e}^-$ - $\vecthreeBF{B}$ interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{fig:lf_rk1_rk2_comparison}
@@
 
+\subsection{Acceleration in Electric Field}
+After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
+
+As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
+Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.47\textwidth}
+        \centering
+        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
+        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
+    \end{subfigure}
+    \begin{subfigure}{0.48\textwidth}
+        \centering
+        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
+        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
+    \end{subfigure}
+    \caption{Illustration of test setups.}
+\end{figure}
+
+In the first test, the beam would be injected into a static uniform electric field \\
+$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
+
+Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
+\begin{eqnarray}
+    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
+             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
+             &=& 2.65616 \times 1.506 \\
+    \Delta V^1 &=& 4 MV \\
+    \Delta E^1 &=& 4 MeV \\
+    E_{exitTH}^1 &=& 5 MeV
+\end{eqnarray}
+
+In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
+$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
+\begin{eqnarray}
+    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
+                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
+                 &=& 5.31232 \times 0.753 \\
+    \Delta V^2   &=& 4 MV \\
+    \Delta E^2   &=& 4 MeV \\
+    E_{exitTH}^2 &=& 5 MeV
+\end{eqnarray}
+
+Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
+To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
+        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
+    \end{subfigure}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
+        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
+    \end{subfigure}
+    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
+    \label{fig:lf_rk2_par_stat_E_comparison}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
+    \label{fig:lf_rk2_perp_stat_E_comparison}
+\end{figure}
+
+\subsection{Multithreading}
+As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
+There have been a number of different approaches for implementation. 
+First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
+After the sizable refactoring done for 3D capabilities, this implementation was obselete.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
+    \caption{An Illustration of the multithreading architecture.}
+    \label{fig:multh_illustration}
+\end{figure}
+
+For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
+The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{example_simulation_runs}) 
+or communucating with the \textit{GUI} that will be disscussed in the next section.
+
+Focus of this section is the worker threads, also known as \eEM interaction threads.
+There were four competing architecture for these worker threads,
+\begin{enumerate}
+    \item Have a thread pool that calculates \eEM in a queue 
+    \item Assign a thread to each bunch
+    \item Assign random electrons to each thread and calculate \eEM with global time
+    \item Assign random electrons to each thread and calculate \eEM with local thread time
+\end{enumerate}
+
+\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
+
+\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
+
+\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
+
+\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
+This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
+However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
+
+Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
+This would lead to larger memory allocations and more time spent setting up simulations. 
+Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
+An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
+nevertheless, \textbf{Architecture 4} was chosed to be implemented.
+
+\subsection{Graphical User Interface}
+Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
+An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
+This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
+For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
+This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
+
+The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \caption{An Illustration of first GUI design.}
+    \label{fig:gui_illustration}
+\end{figure}
+
+The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
+For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
+By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+
 \newpage
-
-% START OF APPENDIX
 
@@
     \end{minted}
-\caption{Logic of is $\textbf{e}^-$ inside the shape of magnet}
+\caption{Logic of is \e inside the shape of magnet}
 \label{fig:is_inside_halfsphere}
@@
     \end{minted}
-\caption{RK4-1 implemenation of $\textbf{e}^-$-$\vecthreeBF{B}$}
+\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
 \label{fig:rk1_B}
@@
     \end{minted}
-\caption{RK4-1 implemenation of $\textbf{e}^-$-\textbf{EM}}
+\caption{RK4-1 implemenation of \eEM}
 \label{fig:rk1_EM}
@@
     \end{minted}
-\caption{RK4-2 implemenation of $\textbf{e}^-$-\textbf{EM}}
+\caption{RK4-2 implemenation of \eEM}
 \label{fig:rk2_EM}
@@
 
-% END OF APPENDIX
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
+        #            Rhodotron Simulation Configuration File
+        # ================================================================
+        #    M.Furkan Er                                     22/09/2022   
+        # ================================================================
+        #
+        # emax = Maximum electric field strength (MV/m)
+        # ein = Energy of electrons coming out of the gun (MeV)
+        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
+        # targeten = Max energy on the output gif (MeV)
+        # freq = Frequency of the RF field (MHz)
+        # phaselag = phase lag of the first electrons (degree)
+        # starttime = time to start firing the gun (ns)
+        # endtime = ns to run the simulation (ns)
+        # dt = time interval to do the calculations (ns)
+        # guntime = how long a gun pulse is (ns)
+        # gunperiod = time between two gun pulses (ns)
+        # enum = number of electrons to simulate in a bunch
+        # bunchnum = number of times the gun fires
+        # r1 = radius of the inner cylinder (m)
+        # r2 = radius of the outer cylinder (m)
+        # epath = path to store the electric field data
+        # bpath = path to store the magnetic field data
+        # cpath = path to store the settings
+        # ppath = path to store electron data
+        # multh = enable or disable multitheading
+        # thcount = set the maximum thread to be used
+        # magrotation = degrees of rotation to enter each magnet 
+        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
+        # output = output file name
+
+        # E FIELD CONFIGURATION 
+        emax=1.170
+        freq=107.3
+        phaselag=10.0
+        r1=0.1840
+        r2=0.7380
+
+        # B FIELD CONFIGURATION 
+        magrotation=5.0
+
+        # GUN CONFIGURATION 
+        einmean=0.040
+        einstd=0.0000
+        targeten=2.0
+        guntime=1.0
+        gunperiod=9.3
+        enum=50
+        bunchnum=1
+
+        # SIM CONFIGURATION 
+        starttime=0
+        endtime=10
+        dt=0.0000010000
+        epath=xy/rf.dat
+        bpath=xy/magnet.dat
+        cpath=xy/settings.dat
+        ppath=xy/paths/
+        multh=1
+        thcount=10     
+    \end{minted}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\label{fig:config_file}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+        -- Simulation Configuration --
+        Emax : 0.96     MV/m
+        Freq : 107.5    MHz
+        Phase Lag : -5  degree
+        EndTime : 100   ns
+        dT : 0.0001     ns
+        guntime : 0.8   ns
+        gunperiod : 9.3 ns
+        enum : 100
+        bunchnum : 2
+        R1 : 0.188241   m
+        R2 : 0.752967   m
+        Magnet count :  5
+        Ein : 0.04      MeV
+        TargetE : 2.5   MeV
+        --------------------------------
+
+                     ...Simulation is running...
+        V_____________________________________________________V
+        [####################################                 ]
+    \end{minted}
+\caption{Example of console output while simulation is running.}
+\label{fig:console_output_running}
+\end{figure}
+
 % START OF BIBLIOGRAPHY

### 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
mag acc revised

@@
 \newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
 
@@
 
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison}.
+These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{other}.
+\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
+
+More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
+Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
+Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
 
@@
         \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-E.png}
+        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png}
         \caption*{$dt$ vs $\Delta E$}
@@
         \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-Tsim.png}
+        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png}
         \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:mag_lf_rk2_comparison}
 \end{figure}
 
-The data from these tests can be found in \fromtabs{lf_rk1_rk2_Tsim}{lf_rk1_rk2_dE} of \fromapp{example_simulation_runs}. 
-As anticipated, \textit{Leap-frog} produced the fastest yet least accurate results, whereas \textit{RK4-2} method was proved to be the best performer for accuracy.
+The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
+To investigate the data further, one can define a performance measurement, $F$.
+\begin{eqnarray*}
+    F &\propto& 1/T \\
+    F &\propto& 1/\Delta E 
+\end{eqnarray*}
+
 When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\textit{RK4-2} provides around $41\%$ less energy gain in $\vecthreeBF{B}$ with respect to the next performer \textit{Leap-frog}.
-The tradeoff is the computational intensity mentioned in \fromsec{rungekutta}; \textit{Leap-frog} being around $47\%$ faster than $\textit{RK4-2}$.
+\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
+    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
+    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
+    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
+    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
+    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
+    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
+    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
+\end{eqnarray}
 
-This relation is not linear however; \textit{RK4-2} is not as demanding in less computationally intensitive runs and able to keep up with \textit{Leap-frog} in execution times while increasing the accuracy difference from other methods,
-whereas \textit{Leap-frog} excels at simplicity, being able to use higher time resolution for given computational power. 
-Both methods can be used in different situations, therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
+Also, observing from the data,
+\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
+    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
+    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
+    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
+    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
+\end{eqnarray}
+Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
+\begin{equation}
+    F_{LF}/F_{RK} = 1.36 \pm 0.05
+\end{equation}
+
+Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
+\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
 \textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
@@
 
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753, 0, 0} is
+Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
 \begin{eqnarray}
@@
 
+Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
+\begin{eqnarray*}
+    \begin{aligned}
+        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
+        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
+        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
+        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
+    \end{aligned}
+    \qquad
+    \begin{aligned}
+        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
+        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
+        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
+        T_{RK}^2 &=& 34.93 \pm 0.39 s 
+    \end{aligned}
+\end{eqnarray*}
+
+\begin{eqnarray} \label{eq:f_lf_rk_1}
+    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
+    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
+    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
+\end{eqnarray}
+
+\begin{eqnarray} \label{eq:f_lf_rk_2}
+    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
+    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
+    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
+\end{eqnarray}
+
+\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
+This results can be tested further with obsering from the data (see TODO),
+
+\begin{eqnarray} \label{eq:f_lf_rk_3}
+    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
+    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
+    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
+    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
+\end{eqnarray}
+\begin{eqnarray} \label{eq:f_lf_rk_4}
+    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
+    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
+    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
+    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
+\end{eqnarray}
+
+The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
+the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
+
+\begin{equation}\label{eq:lf_rk_eE_relative_performance}
+    F_{LF}/F_{RK} = 2.11 \pm 0.03
+\end{equation}
+
+Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
+
 \subsection{Multithreading}
@@
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{console_output_running}) 
+The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{example_simulation_runs}) 
 or communucating with the \textit{GUI} that will be disscussed in the next section.
@@
 
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-        $dt$(ns) & $T_{sim LF}(s)$ & $T_{sim RK1}(s)$  & $T_{sim RK2}(s)$  & $\Delta T_{LF-RK2}$\\\hline
-        $10^{-2}$ & 4.14092 & 4.146 & 4.10945 & 0.77\% \\ \hline
-        $10^{-3}$ & 4.23817 & 4.61703 & 4.30225 & -1.51\% \\ \hline
-        $10^{-4}$ & 5.04679 & 8.93529 & 6.3065 & -24.96\% \\ \hline
-        $10^{-5}$ & 13.5135 & 51.9024 & 25.4279 & -88.17\%\\ \hline
-        $10^{-6}$ & 97.6229 & 486.378 & 217.704 & -123.01\% \\ \hline
-    \end{tabular}
-    \caption{$dt$ vs $T_{sim}$ of Leap-frog, RK4-1, RK4-2 \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_rk1_rk2_Tsim}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
-    \hline
-        $dt$(ns) & $\Delta E_{LF}$(MeV) & $\Delta E_{RK1}$(MeV)  & $\Delta E_{RK2}$(MeV)  & $\Delta E_{LF-RK2}$\\\hline
-        $10^{-2}$ & 2.78323 & 1.26503 & 1.04713 & 165.8\% \\ \hline
-        $10^{-3}$ & 0.11712 & 0.07469 & 0.06691 & 42.87\% \\ \hline
-        $10^{-4}$ & 0.01101 & 0.00716 & 0.00644 & 41.5\%  \\ \hline
-        $10^{-5}$ & 0.00109 & 0.00071 & 0.00064 & 41\% \\ \hline
-        $10^{-6}$ & 0.00011 & 0.00007 & 0.00006 & 45\% \\\hline
-    \end{tabular}
-    \caption{$dt$ vs $\Delta E$ of Leap-frog, RK4-1, RK4-2 \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_rk1_rk2_dE}
-\end{table}
-
 \begin{figure}[H]
@@
     \captionsetup{justification=centering}
-    \begin{subfigure}{0.48\textwidth}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
@@
     \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
         -- Simulation Configuration --
@@
 
+\chapter{Data and Graphs}\label{appendix:data_graph}
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
+        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
+        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
+        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
+        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
+        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
+        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
+        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
+        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
+        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
+        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
+        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
+        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
+        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
+        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
+        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
+        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
+        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
+        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
+        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
+        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
+    \end{tabular}
+    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:lf_mag_table}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
+        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
+        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
+        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
+        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
+        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
+        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
+        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
+        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
+        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
+        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
+        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
+        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
+        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
+        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
+        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
+        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
+        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
+        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
+        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
+        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
+    \end{tabular}
+    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:rk2_mag_table}
+\end{table}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-E_3.png}
+        \caption*{$dt$ vs $\Delta E$}
+    \end{subfigure}
+
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
+        \caption*{$dt$ vs $T_{sim}$}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:lf_rk1_rk2_comparison}
+\end{figure}
+
 \end{document}

### 2023-07-16 figures/analiz/root_draw.c

@@ -7,13 +7,13 @@
     c1->SetGridy();
     TGraph *lf, *rk1, * rk2;
 
-    bool delE = false;
+    bool delE = true;
 
     if(delE){
-        lf = new TGraph("data/lf_staticE_test_results.txt", "%lg %lg %*lg %*lg %*lg");   
+        lf = new TGraph("data/lf_mag_test_results.txt", "%lg %lg %*lg %*lg %*lg");   
     }
     else{
-        lf = new TGraphErrors("data/lf_staticE_test_results.txt", "%lg %*lg %*lg %lg %lg");   
+        lf = new TGraphErrors("data/lf_mag_test_results.txt", "%lg %*lg %*lg %lg %lg");   
     }
     lf->SetMarkerStyle(23);
     lf->SetMarkerColor(kBlue);
@@ -30,10 +30,10 @@
     rk1->SetTitle("RK4-1");*/
 
     if(delE){
-        rk2 = new TGraph("data/rk_staticE_test_results.txt", "%lg %lg %*lg %*lg %*lg");   
+        rk2 = new TGraph("data/rk_mag_test_results.txt", "%lg %lg %*lg %*lg %*lg");   
     }
     else{
-        rk2 = new TGraphErrors("data/rk_staticE_test_results.txt", "%lg %*lg %*lg %lg %lg");   
+        rk2 = new TGraphErrors("data/rk_mag_test_results.txt", "%lg %*lg %*lg %lg %lg");   
     }
     rk2->SetMarkerStyle(21);
     rk2->SetMarkerColor(kRed);
@@ -44,11 +44,11 @@
     //mg->Add(rk1, "cp");
     mg->Add(rk2, "lp");
     mg->GetXaxis()->SetTitle("dt(ns)");
-    mg->GetXaxis()->SetLimits(5e-7,1e-1);
+    mg->GetXaxis()->SetLimits(5e-7,2e-2);
     if(delE){
         mg->GetYaxis()->SetTitle("#DeltaE(MeV)");
-        mg->SetMaximum(0.13);
-        mg->SetMinimum(1e-6);
+        mg->SetMaximum(4);
+        mg->SetMinimum(5e-5);
     }
     else{
         mg->GetYaxis()->SetTitle("T_{SIM}(s)");

### 2023-07-16 msthesis.tex
GUI started

@@
 \newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}% START OF THEORY
+\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
+
+% START OF THEORY
 
@@
 
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison}.
+These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
+\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
+
+More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
+Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
+Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
 
@@
         \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
+        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
         \caption*{$dt$ vs $\Delta E$}
@@
         \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
+        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
         \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_rk1_rk2_Tsim}{lf_rk1_rk2_dE} of \fromapp{example_simulation_runs}. 
-As anticipated, \textit{Leap-frog} produced the fastest yet least accurate results, whereas \textit{RK4-2} method was proved to be the best performer for accuracy.
+    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:mag_lf_rk2_comparison}
+\end{figure}
+
+The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
+To investigate the data further, one can define a performance measurement, $F$.
+\begin{eqnarray*}
+    F &\propto& 1/T \\
+    F &\propto& 1/\Delta E 
+\end{eqnarray*}
+
 When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\textit{RK4-2} provides around $41\%$ less energy gain in $\vecthreeBF{B}$ with respect to the next performer \textit{Leap-frog}.
-The tradeoff is the computational intensity mentioned in \fromsec{rungekutta}; \textit{Leap-frog} being around $47\%$ faster than $\textit{RK4-2}$.
-
-This relation is not linear however; \textit{RK4-2} is not as demanding in less computationally intensitive runs and able to keep up with \textit{Leap-frog} in execution times while increasing the accuracy difference from other methods,
-whereas \textit{Leap-frog} excels at simplicity, being able to use higher time resolution for given computational power. 
-Both methods can be used in different situations, therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
+\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
+    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
+    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
+    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
+    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
+    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
+    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
+    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
+\end{eqnarray}
+
+Also, observing from the data,
+\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
+    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
+    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
+    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
+    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
+\end{eqnarray}
+Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
+\begin{equation}
+    F_{LF}/F_{RK} = 1.36 \pm 0.05
+\end{equation}
+
+Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
+\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
 \textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
@@
         \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-        \caption*{$dt$ vs $\Delta E$}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
@@
 \end{figure}
+
+Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
+\begin{eqnarray*}
+    \begin{aligned}
+        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
+        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
+        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
+        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
+    \end{aligned}
+    \qquad
+    \begin{aligned}
+        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
+        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
+        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
+        T_{RK}^2 &=& 34.93 \pm 0.39 s 
+    \end{aligned}
+\end{eqnarray*}
+
+\begin{eqnarray} \label{eq:f_lf_rk_1}
+    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
+    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
+    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
+\end{eqnarray}
+
+\begin{eqnarray} \label{eq:f_lf_rk_2}
+    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
+    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
+    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
+\end{eqnarray}
+
+\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
+This results can be tested further with obsering from the data (see TODO),
+
+\begin{eqnarray} \label{eq:f_lf_rk_3}
+    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
+    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
+    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
+    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
+\end{eqnarray}
+\begin{eqnarray} \label{eq:f_lf_rk_4}
+    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
+    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
+    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
+    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
+\end{eqnarray}
+
+The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
+the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
+
+\begin{equation}\label{eq:lf_rk_eE_relative_performance}
+    F_{LF}/F_{RK} = 2.11 \pm 0.03
+\end{equation}
+
+Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
 
@@
 
+\chapter{Data and Graphs}\label{appendix:data_graph}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
+    \end{subfigure}
+
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:lf_rk1_rk2_comparison}
+\end{figure}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
+        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
+        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
+        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
+        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
+        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
+        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
+        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
+        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
+        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
+        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
+        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
+        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
+        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
+        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
+        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
+        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
+        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
+        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
+        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
+        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
+    \end{tabular}
+    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:lf_mag_table}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
+        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
+        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
+        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
+        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
+        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
+        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
+        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
+        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
+        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
+        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
+        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
+        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
+        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
+        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
+        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
+        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
+        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
+        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
+        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
+        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
+    \end{tabular}
+    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{tab:rk2_mag_table}
+\end{table}
+
 % START OF BIBLIOGRAPHY

### 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
GUI started

@@
 
-\newcommand{\e}{$\textbf{e}^-$}
-\newcommand{\egun}{$\textbf{e}^-$-gun}
+\newcommand{\e}{$\textbf{e}^-$ }
+\newcommand{\egun}{$\textbf{e}^-$-gun }
 \newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
@@
 \newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
 
@@
 
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{other}.
+These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
 \textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
@@
         \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-        \caption*{$dt$ vs $\Delta E$}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
     \end{subfigure}
@@
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{example_simulation_runs}) 
+The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation 
+(see \fromfig{console_output_running} in \fromapp{example_simulation_runs} for example console notification, \fromfig{ui_thread} in \fromapp{intermediate_codes} for implemenation)
 or communucating with the \textit{GUI} that will be disscussed in the next section.
@@
 
+The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
+
 \subsection{Graphical User Interface}
@@
     \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of first GUI design.}
+    \caption{An Illustration of the first GUI design.}
     \label{fig:gui_illustration}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
+    \caption{The configuration frame of implementated first GUI design.}
+    \label{fig:gui_config}
 \end{figure}
@@
 By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+
+In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} 
+\begin{itemize}
+    \item[Configuration Frame] provides an interface for specifying, saving or loading a configuration.
+    \item[Simulation Frame] provides an interface for starting and managing the \textit{simulation engine}, displaying the progress of the simulation.
+    \item[Render Frame] provides an interface for rendering the results of a simulation.
+    \item[Analyze Frame] provides an interface for analyzing the results of a simulation.  
+    \item[Sweep Frame] provides an interface for parameter sweep functionality. 
+\end{itemize}
+
+\subsubsection{Configuration Frame}
+This frame consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
+
+\subsubsection{Simulation Frame}
+This frame spawns the \textit{simulation engine}, configures and starts the simulation. 
+It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
+    \caption{Simulate frame of \textit{GUI}.}
+    \label{fig:gui_simulate_1}
+\end{figure}
+
+\subsubsection{Render Frame}
+Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
+see a specific time frame, export as snapshot or animated gif file.
+
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
+    \end{subfigure} 
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
+    \end{subfigure} 
+    \caption{Render frame of \textit{GUI}.}
+    \label{fig:gui_render_1}
+\end{figure}
+
+\subsubsection{Analyze Frame}
+Analyze frame provides tools for analyzing and visualizing the simulation data. 
+In the current version \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
+This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
+
+\subsubsection{Sweep Frame}
 
@@
 \label{fig:rk2_EM}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void RhodotronSimulator::_runMT(){
+            gun.fireAllWithFireTimesMT();
+
+            MTEngine.setupPool(time_interval, start_time, end_time, gun, E_field, B_field, gun.thread_bunchs);
+
+            STEPS_TAKEN = 0;
+            simulation_time = start_time;
+            while (simulation_time < end_time + time_interval ){
+                if (STEPS_TAKEN % log_interval() == 0){
+                    E_field.update(simulation_time);
+                    logEfield(simulation_time, simulation_time + time_interval > end_time);
+                    notifyUI(MTEngine.getAverageTime());
+                }
+                simulation_time+=time_interval;
+                STEPS_TAKEN++;
+            }
+            bool end = false;
+            while (!end){
+                double time = MTEngine.getAverageTime();
+                notifyUI(time);
+                if ( time >= end_time ){
+                    end = true;
+                }
+                this_thread::yield();
+            }
+            MTEngine.join();
+
+        }
+    \end{minted}
+    \caption{Multithreading main-thread logic.}
+    \label{fig:_runMT}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void Gun::fireAllWithFireTimesMT(){
+            std::random_device rd;
+            std::mt19937 e2(rd());
+            std::normal_distribution<double> Edist(Ein, sEin);
+
+            for(_fired_bunch= 0; _fired_bunch < bunch_count; _fired_bunch++){
+                for(_fired_e_in_current_bunch= 0; _fired_e_in_current_bunch < e_per_bunch; _fired_e_in_current_bunch++){
+
+                    double E = (sEin == 0 ) ? Ein : Edist(e2);
+
+                    double fire_time = (ns_between_each_electron_fire * _fired_e_in_current_bunch) + _fired_bunch*gun_period;
+
+                    auto burrowed_e = bunchs[_fired_bunch].AddElectronGiveAddress(E, gunpos, gundir, fire_time);
+
+                    int thread_index = (_fired_e_in_current_bunch + _fired_bunch*e_per_bunch)%thread_bunchs.size();
+
+                    thread_bunchs[thread_index]->push_back(burrowed_e);
+                }
+            }
+        }
+    \end{minted}
+    \caption{Multithreading electron assign logic.}
+    \label{fig:fireAllWithFireTimesMT}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void MultiThreadEngine::setupPool( double _time_interval, double _start_time, double _end_time, Gun& gun, 
+            CoaxialRFField& RF, MagneticField& B, vector<shared_ptr<vector<shared_ptr<Electron2D>>>>& e_list){
+            threads.reserve(thread_count);
+
+            for(int i = 0; i < thread_count && i == threads.size(); i++){
+
+                child_notifier_mutexes.push_back(make_shared<mutex>());
+                child_times.push_back(make_shared<double>());
+
+                auto _E = RF.Copy();
+                auto _B = B.LightWeightCopy();
+                double time_between_fires = thread_count*gun.getGunActiveTime()/gun.getElectronsPerBunch();
+                double first_fire_time = i*gun.getGunActiveTime()/gun.getElectronsPerBunch();
+                ThreadArguments thread_arguments(i, _time_interval, _start_time, _end_time, &gun, _E, _B, e_list[i], first_fire_time, time_between_fires);
+                thread_arguments.parent_notifier_mutex = child_notifier_mutexes[i];
+                thread_arguments.current_thread_time = child_times[i];
+                threads.push_back(thread(threadLoop, thread_arguments));
+            }
+        }
+    \end{minted}
+    \caption{Multithreading worker-threads setup logic.}
+    \label{fig:setupPool}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void threadLoop(ThreadArguments thread_arguments){
+            uint64_t count = 0;
+
+            double sim_time = thread_arguments.start_time;
+
+            while(sim_time < thread_arguments.end_time + thread_arguments.time_interval){
+                thread_arguments.E->update(sim_time);
+                thread_arguments.i_args.time = sim_time;
+
+                if ( count % (unsigned long)(0.1/thread_arguments.time_interval) == 0){
+                    saveElectronInfoForSingleThread(thread_arguments.i_args);
+                    // Notifiy the main thread
+                    if(thread_arguments.parent_notifier_mutex->try_lock()){
+                        *thread_arguments.current_thread_time = sim_time;
+                        thread_arguments.parent_notifier_mutex->unlock();
+                    }
+                }
+
+                interactForSingleThread(thread_arguments.i_args);
+                // save electron info here
+                sim_time+= thread_arguments.time_interval;
+                count++;
+            }
+            thread_arguments.parent_notifier_mutex->lock();
+            *thread_arguments.current_thread_time = sim_time;
+            thread_arguments.parent_notifier_mutex->unlock();
+        }
+    \end{minted}
+    \caption{Multithreading worker-thread logic.}
+    \label{fig:threadLoop}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        void UIThreadWork(UIThreadArgs args){
+            int UI_WORK_PIECE = SIM_WORK_MASK;
+            if ( !args.isService ) {
+                UI_WORK_PIECE = 50;
+            }
+
+            double piece = (args.end_time - args.start_time)/UI_WORK_PIECE;
+
+            if ( !args.isService ) {
+                std::string sim_running_msg = "...Simulation is running...";
+                for(int i = 0; i < 26 - sim_running_msg.size()/2 ; i++){
+                    std::cout << " ";
+                }
+                std::cout << sim_running_msg <<"\n";
+            }
+
+            args.ui_mutex->lock();
+            double simtime = *(args.simulation_time);
+            args.ui_mutex->unlock();
+
+            if ( !args.isService ) {
+                std::cout << "V";
+                for(int i = 0; i < 51; i++){
+                    std::cout << "_";
+                }
+                std::cout << "V\n[" << std::flush;
+            }
+
+            int count = 0;
+            bool running = true;
+            while(running && (simtime < args.end_time || count < UI_WORK_PIECE )){
+                if( simtime > count * piece ){
+                    if ( !args.isService ) {
+                        std::cout << "#" << std::flush;
+                    }
+                    count++;
+                    args.state_mutex->lock();
+                    running = *args.state_ptr & SIM_RUNNING;
+                    *args.state_ptr = (*args.state_ptr & ~SIM_WORK_MASK) | (count & SIM_WORK_MASK);
+                    if (args.isService) write(args._fd, args.state_ptr, SIGNAL_SIZE);
+                    args.state_mutex->unlock();
+                }
+                std::this_thread::sleep_for(std::chrono::milliseconds(25));
+                args.ui_mutex->lock();
+                simtime = *(args.simulation_time);
+                args.ui_mutex->unlock();
+
+            }
+            if ( !args.isService ) {
+                std::cout << "#]\n\n" << std::flush;
+                std::cout << "     ...Simulation is finished successfully...\n\n" << std::flush;
+            }
+
+            args.state_mutex->lock();
+            *args.state_ptr |= SIM_RENDERING;
+            if ( args.isService ) write(args._fd, args.state_ptr, SIGNAL_SIZE);
+            args.state_mutex->unlock();
+        }
+    \end{minted}
+    \caption{UI-Console handler thread logic.}
+    \label{fig:ui_thread}
 \end{figure}
@@
     \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\caption{An example \textit{config.in} file.}
 \label{fig:config_file}
@@
 \chapter{Data and Graphs}\label{appendix:data_graph}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-E_3.png}
+    \end{subfigure}
+
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \label{fig:lf_rk1_rk2_comparison}
+\end{figure}
+
 \begin{table}[H]
@@
 
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-E_3.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
 \end{document}

### 2023-07-16 msthesis.tex
simulation draft complete

@@
 
-\subsection{$L_{out}$ Optimization For Single \e}
+\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
 Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
@@
 
-\subsection{$\phi_{lag}$ Optimization For Bunches}
+\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
 After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
@@
     \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of first GUI design.}
+    \caption{An Illustration of the first GUI design.}
     \label{fig:gui_illustration}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
+    \caption{The configuration frame of implementated first GUI design.}
+    \label{fig:gui_config}
 \end{figure}
@@
 By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+
+In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
+
+\subsubsection{Configuration Frame}
+This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
+
+\subsubsection{Simulation Frame}
+This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
+It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
+    \caption{Simulate frame of \textit{GUI}.}
+    \label{fig:gui_simulate_1}
+\end{figure}
+
+\subsubsection{Render Frame}
+Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
+see a specific time frame, export as snapshot or animated gif file.
+
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
+    \end{subfigure} 
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
+    \end{subfigure} 
+    \caption{Render frame of \textit{GUI}.}
+    \label{fig:gui_render_1}
+\end{figure}
+
+\subsubsection{Analyze Frame}
+Analyze frame provides tools for analyzing and visualizing the simulation data. 
+In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
+This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
+    \caption{Analyze frame of \textit{GUI} E distribution.}
+    \label{fig:gui_analyze_Edist}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
+    \end{subfigure} 
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
+    \end{subfigure} 
+    \caption{Analyze frame of \textit{GUI} E(t).}
+    \label{fig:gui_analyze_Et}
+\end{figure}
+
+\subsubsection{Sweep Frame}
+Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
+$\phi_{lag}$ sweep was the first parameter to be implemented. 
+It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
+This enables user with an already built accelerator to optimize \egun parameters quickly. 
+In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be observed in detail.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
+    \label{fig:gui_sweep_running}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
+    \label{fig:gui_sweep_muE}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
+    \label{fig:gui_sweep_sE}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
+    \label{fig:gui_sweep_sR}
+\end{figure}
+
+As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
+New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
 

### 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
simulation draft complete

@@
 
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} 
-\begin{itemize}
-    \item[Configuration Frame] provides an interface for specifying, saving or loading a configuration.
-    \item[Simulation Frame] provides an interface for starting and managing the \textit{simulation engine}, displaying the progress of the simulation.
-    \item[Render Frame] provides an interface for rendering the results of a simulation.
-    \item[Analyze Frame] provides an interface for analyzing the results of a simulation.  
-    \item[Sweep Frame] provides an interface for parameter sweep functionality. 
-\end{itemize}
+In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
 
 \subsubsection{Configuration Frame}
-This frame consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
 Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
@@
 \subsubsection{Simulation Frame}
-This frame spawns the \textit{simulation engine}, configures and starts the simulation. 
+This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
 It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
@@
     \centering
-    \includegraphics[width=0.5\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
     \caption{Simulate frame of \textit{GUI}.}
@@
         \centering
-        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
     \end{subfigure} 
@@
         \centering
-        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
     \end{subfigure} 
@@
 Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
+In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
 This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
+    \caption{Analyze frame of \textit{GUI} E distribution.}
+    \label{fig:gui_analyze_Edist}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \captionsetup{justification=centering}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_1.png}
+    \end{subfigure} 
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_2.png}
+    \end{subfigure} 
+    \caption{Analyze frame of \textit{GUI} E(t).}
+    \label{fig:gui_analyze_Et}
+\end{figure}
+
 \subsubsection{Sweep Frame}
+Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
+$\phi_{lag}$ sweep was the first parameter to be implemented. 
+It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
+This enables user with an already built accelerator to optimize \egun parameters quickly. 
+In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be observed in detail.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_running.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
+    \label{fig:gui_sweep_running}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
+    \label{fig:gui_sweep_muE}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
+    \label{fig:gui_sweep_sE}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sR.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
+    \label{fig:gui_sweep_sR}
+\end{figure}
+
+As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
+New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
 

### 2023-07-18 msthesis.tex
future work & production added

@@
 
-\subsection{Graphical User Interface}
+\newpage
+
+% Start of intermediate.tex
+\section{Graphical User Interface}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \caption{An Illustration of the first GUI design.}
+    \label{fig:gui_illustration}
+\end{figure}
+
 Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 
-\subsubsection{Configuration Frame}
+\subsection{Configuration Frame}
 This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
@@
 
-\subsubsection{Simulation Frame}
+\subsection{Simulation Frame}
 This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
 It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
     \caption{Simulate frame of \textit{GUI}.}
@@
 
-\subsubsection{Render Frame}
+\subsection{Render Frame}
 Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
 see a specific time frame, export as snapshot or animated gif file.
+Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
 
@@
     \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
-    \end{subfigure} 
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
-    \end{subfigure} 
     \caption{Render frame of \textit{GUI}.}
@@
 
-\subsubsection{Analyze Frame}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
+    \caption{Render frame of \textit{GUI}.}
+    \label{fig:gui_render_2}
+\end{figure}
+
+\subsection{Analyze Frame}
 Analyze frame provides tools for analyzing and visualizing the simulation data. 
@@
 This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
+In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
 
@@
     \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
-    \end{subfigure} 
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
-    \end{subfigure} 
     \caption{Analyze frame of \textit{GUI} E(t).}
@@
 
-\subsubsection{Sweep Frame}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
+    \caption{Analyze frame of \textit{GUI} E(t).}
+    \label{fig:gui_analyze_Et2}
+\end{figure}
+
+\subsection{Sweep Frame}
 Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
@@
 This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be observed in detail.
+In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
 
@@
 New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
+
+\newpage
+
+% START OF PRODUCTION
+
+\chapter{PRODUCTION}
+% Start of final.tex
+\section{Final Design}
+
+\newpage
+
+% Start of techd.tex
+\section{Technical Drawing}
+
+\newpage
+
+% Start of mani.tex
+\section{Manifacturing}
+
+\newpage
+
+% Start of rf.tex
+\section{RF Supply}
+
+\newpage
+
+% START OF FUTURE_WORK
+
+\chapter{FUTURE WORK}
 

### 2023-07-18 subsections/future/future_work.tex
future work & production added

--- 2023-07-16 msthesis.tex
@@
 \usepackage{tabu}
-\usepackage{minted}
-\usepackage{xcolor}
-
-\usemintedstyle{xcode}
-\definecolor{bg}{rgb}{0.95,0.95,0.95}
 
@@
 \newcommand{\vecthree}[1]{\vec{#1}}
-\newcommand{\vecNum}[3]{(#1, #2, #3)}
 
@@
 
-\newcommand{\e}{$\textbf{e}^-$}
-\newcommand{\egun}{$\textbf{e}^-$-gun}
-\newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
-\newcommand{\eE}{$\textbf{e}^-$ - $\vecthreeBF{E}$ }
-\newcommand{\eEM}{$\textbf{e}^-$ - \textbf{EM} }
-\newcommand{\ee}{$\textbf{e}^-$ - $\textbf{e}^-$ }
-
 \newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
@@
 \newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
 
@@
 
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
+%%%%%%
+% START OF FUTURE_WORK
 
-\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
+\chapter{FUTURE WORK}
 
-% START OF THEORY
-
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta} \label{sec:rungekutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
-% START OF DESIGN
-
-\chapter{DESIGN}
-
-\section{Cavity Design} \label{sec:cavity_design}
-
-The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
-
-By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
-This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
-For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
-    \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
-    \end{aligned}
-\end{eqnarray}
-
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:107_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:180_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:cst_simple_cavity_designs}
-\end{figure}
-
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson SUPERFISH field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_superfish}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST eigenmode results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_eigenmode}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST electric field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_field}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
-      \caption{107.5 MHz unmodified}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
-      \caption{180 MHz unmodified}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
-    \label{fig:107_cavity_shunt_diff}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
-    \label{fig:180_cavity_shunt_diff}
-\end{figure}
-
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
-    \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta Z_{180}=2.7\%
-    \end{aligned}
-\end{equation*}
-
-\newpage
-
-\section{Magnet Design} \label{sec:magnet_design}
-Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
-Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
-Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
-    \label{fig:magnet_design_illustrations}
-\end{figure}
-
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
-
-Two different approaches have been used to achieve phase stability.
-These approaches are discussed further in the following sections.
-
-\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
-
-First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
-
-To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
-As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
-    L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
-
-\begin{figure}[H]    
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
-    \label{fig:magnet_design}
-\end{figure}
-
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
-
-After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
-Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
-\begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
-
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
-Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
-Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
-
-\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
-
-As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
-This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
-This scenario can happen when RF power is not sufficiently high.
-
-Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
-after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
-It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
-For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
-Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
-
-Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
-
-To start, an optimization criteria for the following pass such as
-\begin{itemize}
-    \item Ensure the phase stability of the synchronous electron
-    \item Maximize the energy gain of the synchronous electron
-    \item Minimize the energy spread of the beam
-    \item Minimize the phase lag spread of the beam
-    \item All of the above with decided weights
-\end{itemize}
-needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
-This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
-
-However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
-
-\newpage
-
-\section{Initial Design at KAHVELab}
-
-A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
-After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
-    \label{fig:initial_design}
-\end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
-      \caption{Axial cross section.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
-      \caption{Cross section at acceleration plane.}
-    \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
-    \label{fig:initial_design_cross_section}
-\end{figure}
-The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
-    \end{subfigure}
-    \caption{Initial magnet design.}
-    \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
-    \label{fig:initial_three_magnet_design}
-\end{figure}
-
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $0.1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
-Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
-
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
-
-In KAHVELab, several improvements were made to these initial designs by \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
-Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
-    \end{subfigure}
-    \caption{Improved cavity design.}
-    \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \caption{Improved magnet design.}
-    \label{fig:improved_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
-    \end{subfigure}
-    \caption{Cross section and coils of improved magnet design.}
-    \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \caption{Magnetic field in acceleration plate of improved magnet design.}
-    \label{fig:improved_magnet_design_B}
-\end{figure}
-
-From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
-This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
-
-\newpage
-
-% START OF SIMULATION
-
-\chapter{SIMULATION}
-% Start of poc.tex
-\section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
-\begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
-    \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
-    \end{enumerate}
-\end{itemize}
-
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \caption{Core logic loop of the POC}
-    \label{fig:POC_core_logic}
-\end{figure}
-
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass in THE CAVITY, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
-Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
-
-After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
-The development and improvement efforts are still ongoing.
-
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
-The following sections in this chapter investigates their implementations further.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e}
-Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-Then sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch entered the cavity, it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see TODO),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{example_simulation_runs}) 
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-\subsection{Graphical User Interface}
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
-
-\newpage
-
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
-\end{figure}
-
-\begin{figure}[H]
-        \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
-\end{figure}
-
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
-
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-% START OF BIBLIOGRAPHY
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-    \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018
-
-\end{thebibliography}
-
-% END OF BIBLIOGRAPHY
+%%%%%%
 

### 2023-07-18 subsections/production/manifacturing/mani.tex
future work & production added

--- 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
@@
 \usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{minted}
-
-\usemintedstyle{xcode}
 
@@
 %%%%%%
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e}
-Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-Then sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch entered the cavity, it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{other}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{../../../figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see TODO),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{example_simulation_runs}) 
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-\subsection{Graphical User Interface}
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+% Start of mani.tex
+\section{Manifacturing}
 
@@
 
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
-\end{figure}
-
-\begin{figure}[H]
-        \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
-\end{figure}
-
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
-
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-E_3.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
 \end{document}

### 2023-07-18 subsections/simulation/gui/gui.tex
future work & production added

--- 2023-07-16 msthesis.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
-\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
-\usepackage{amsmath, amsthm} % Some extra symbols
-\usepackage[bottom]{footmisc}
-\usepackage{cite}
+\documentclass{book}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
-\usepackage{longtable}
+\usepackage{tikz}
 \usepackage{float}
-\usepackage{multirow}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{array}
-\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
-\usepackage{epsfig}
-\usepackage{epstopdf}
-\usepackage{amsmath}
-\usepackage{notoccite}
+\usepackage{wrapfig,lipsum}
+\usepackage{svg}
+\usepackage{mathtools}
+\usepackage{tabu}
 \usepackage{subcaption}
-\usepackage{tabu}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 \usepackage{minted}
-\usepackage{xcolor}
 
 \usemintedstyle{xcode}
+
 \definecolor{bg}{rgb}{0.95,0.95,0.95}
 
-\interdisplaylinepenalty=2500
-\hyphenation{lists} \makeatletter
-
-\newcommand{\field}[1]{\mathbb{#1} }
-\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
-\setlength\belowdisplayskip{5pt}}
-\newcommand{\eeq}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\defn}{\stackrel{\triangle}{=}}
-\newcommand{\nn}{\nonumber}
-\newcommand{\nnl}{\nonumber \\}
-\renewcommand{\theequation}{\arabic{equation}}
-\renewcommand{\labelenumi}{(\roman{enumi})}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\ifundefined{\@ifundefined}
-\def\bfat{\left[ \begin{array}}
-\def\emat{\end{array} \right]}
-\def\bfatt{\left\{ \begin{array}}
-\def\ematt{\end{array} \right.}
-\def\bset{\left\{ \begin{array}}
-\def\eset{\end{array} \right\}}
-\def\bpar{\left( \begin{array}}
-\def\epar{\end{array} \right)}
-
-\graphicspath{{figures/}} % Graphics will be here
-
-\newtheorem{thm}{Theorem}[chapter]
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
-
-\numberwithin{equation}{chapter}
-
-% BEGIN OF DOCS
 \begin{document}
-\pagenumbering{roman}
-
-% CONTENTS AND LIST OF FIG AND TABLE PAGES
-\tableofcontents
-
-\pagenumbering{arabic}
 
@@
 
-% START OF THEORY
+%----../../..++++.
 
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
+%%%%%%
+% Start of intermediate.tex
+\section{Graphical User Interface}
 
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \caption{An Illustration of the first GUI design.}
+    \label{fig:gui_illustration}
 \end{figure}
 
-\subsection{Key Concepts}
-
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta} \label{sec:rungekutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
-% START OF DESIGN
-
-\chapter{DESIGN}
-
-\section{Cavity Design} \label{sec:cavity_design}
-
-The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
-
-By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
-This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
-For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
-    \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
-    \end{aligned}
-\end{eqnarray}
-
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:107_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:180_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:cst_simple_cavity_designs}
-\end{figure}
-
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson SUPERFISH field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_superfish}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST eigenmode results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_eigenmode}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST electric field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_field}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
-      \caption{107.5 MHz unmodified}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
-      \caption{180 MHz unmodified}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
-    \label{fig:107_cavity_shunt_diff}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
-    \label{fig:180_cavity_shunt_diff}
-\end{figure}
-
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
-    \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta Z_{180}=2.7\%
-    \end{aligned}
-\end{equation*}
-
-\newpage
-
-\section{Magnet Design} \label{sec:magnet_design}
-Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
-Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
-Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
-    \label{fig:magnet_design_illustrations}
-\end{figure}
-
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
-
-Two different approaches have been used to achieve phase stability.
-These approaches are discussed further in the following sections.
-
-\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
-
-First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
-
-To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
-As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
-    L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
-
-\begin{figure}[H]    
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
-    \label{fig:magnet_design}
-\end{figure}
-
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
-
-After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
-Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
-\begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
-
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
-Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
-Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
-
-\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
-
-As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
-This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
-This scenario can happen when RF power is not sufficiently high.
-
-Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
-after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
-It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
-For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
-Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
-
-Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
-
-To start, an optimization criteria for the following pass such as
-\begin{itemize}
-    \item Ensure the phase stability of the synchronous electron
-    \item Maximize the energy gain of the synchronous electron
-    \item Minimize the energy spread of the beam
-    \item Minimize the phase lag spread of the beam
-    \item All of the above with decided weights
-\end{itemize}
-needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
-This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
-
-However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
-
-\newpage
-
-\section{Initial Design at KAHVELab}
-
-A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
-After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
-    \label{fig:initial_design}
-\end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
-      \caption{Axial cross section.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
-      \caption{Cross section at acceleration plane.}
-    \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
-    \label{fig:initial_design_cross_section}
-\end{figure}
-The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
-    \end{subfigure}
-    \caption{Initial magnet design.}
-    \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
-    \label{fig:initial_three_magnet_design}
-\end{figure}
-
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $0.1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
-Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
-
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
-
-In KAHVELab, several improvements were made to these initial designs by \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
-Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
-    \end{subfigure}
-    \caption{Improved cavity design.}
-    \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \caption{Improved magnet design.}
-    \label{fig:improved_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
-    \end{subfigure}
-    \caption{Cross section and coils of improved magnet design.}
-    \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \caption{Magnetic field in acceleration plate of improved magnet design.}
-    \label{fig:improved_magnet_design_B}
-\end{figure}
-
-From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
-This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
-
-\newpage
-
-% START OF SIMULATION
-
-\chapter{SIMULATION}
-% Start of poc.tex
-\section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
-\begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
-    \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
-    \end{enumerate}
-\end{itemize}
-
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \caption{Core logic loop of the POC}
-    \label{fig:POC_core_logic}
-\end{figure}
-
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass in THE CAVITY, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
-Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
-
-After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
-The development and improvement efforts are still ongoing.
-
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
-The following sections in this chapter investigates their implementations further.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e}
-Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-Then sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch entered the cavity, it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see TODO),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation (see \fromfig{console_output_running} in \fromapp{example_simulation_runs}) 
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-\subsection{Graphical User Interface}
 Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of first GUI design.}
-    \label{fig:gui_illustration}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
+    \caption{The configuration frame of implementated first GUI design.}
+    \label{fig:gui_config}
 \end{figure}
@@
 
-\newpage
+In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
 
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
+\subsection{Configuration Frame}
+This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
+
+\subsection{Simulation Frame}
+This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
+It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
+
+\begin{figure}
     \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
+    \caption{Simulate frame of \textit{GUI}.}
+    \label{fig:gui_simulate_1}
 \end{figure}
 
-\begin{figure}[H]
+\subsection{Render Frame}
+Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
+see a specific time frame, export as snapshot or animated gif file.
+Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
+
+\begin{figure}
     \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
+    \caption{Render frame of \textit{GUI}.}
+    \label{fig:gui_render_1}
 \end{figure}
 
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
+    \caption{Render frame of \textit{GUI}.}
+    \label{fig:gui_render_2}
 \end{figure}
 
-\begin{figure}[H]
+\subsection{Analyze Frame}
+Analyze frame provides tools for analyzing and visualizing the simulation data. 
+In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
+This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
+In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
+
+\begin{figure}
     \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
+    \caption{Analyze frame of \textit{GUI} E distribution.}
+    \label{fig:gui_analyze_Edist}
 \end{figure}
 
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_1.png}
+    \caption{Analyze frame of \textit{GUI} E(t).}
+    \label{fig:gui_analyze_Et}
 \end{figure}
 
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_2.png}
+    \caption{Analyze frame of \textit{GUI} E(t).}
+    \label{fig:gui_analyze_Et2}
 \end{figure}
 
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
+\subsection{Sweep Frame}
+Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
+$\phi_{lag}$ sweep was the first parameter to be implemented. 
+It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
+This enables user with an already built accelerator to optimize \egun parameters quickly. 
+In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
 
-\begin{figure}[H]
+\begin{figure}
     \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_running.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
+    \label{fig:gui_sweep_running}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
+    \label{fig:gui_sweep_muE}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
+    \label{fig:gui_sweep_sE}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sR.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
+    \label{fig:gui_sweep_sR}
 \end{figure}
 
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
+As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
+New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
 
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-% START OF BIBLIOGRAPHY
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-    \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018
-
-\end{thebibliography}
-
-% END OF BIBLIOGRAPHY
+%%%%%%
 

### 2023-07-18 subsections/simulation/intermediate_versions/intermediate.tex
future work & production added

--- 2023-07-16 subsections/simulation/intermediate_versions/intermediate.tex
@@
 The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
-
-\subsection{Graphical User Interface}
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
-    \caption{The configuration frame of implementated first GUI design.}
-    \label{fig:gui_config}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
-
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} 
-\begin{itemize}
-    \item[Configuration Frame] provides an interface for specifying, saving or loading a configuration.
-    \item[Simulation Frame] provides an interface for starting and managing the \textit{simulation engine}, displaying the progress of the simulation.
-    \item[Render Frame] provides an interface for rendering the results of a simulation.
-    \item[Analyze Frame] provides an interface for analyzing the results of a simulation.  
-    \item[Sweep Frame] provides an interface for parameter sweep functionality. 
-\end{itemize}
-
-\subsubsection{Configuration Frame}
-This frame consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\subsubsection{Simulation Frame}
-This frame spawns the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
-
-\subsubsection{Render Frame}
-Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
-see a specific time frame, export as snapshot or animated gif file.
-
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
-    \end{subfigure} 
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[angle=270,origin=c,width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
-    \end{subfigure} 
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_1}
-\end{figure}
-
-\subsubsection{Analyze Frame}
-Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
-This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-
-\subsubsection{Sweep Frame}
 

### 2023-08-05 subsections/production/manifacturing/mani.tex
production added

@@
 
+Manifacturing of the rhodotron cavity has been ongoing, planned to be completed in the following months.
+
+The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet.
+
+Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
+These sheets were then pressed to achieve the shapes of the parts. 
+Several flanges were then machined, including
+\begin{itemize}
+    \item $4.5$in EIA RF flange for RF input
+    \item ISO100-KF vacuum connector flanges for vacuum pumps
+    \item ISO-63 KF flange for probe insertion
+    \item KF40 flanges for beam line vacuum gauges
+\end{itemize}
+
+After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
+304 stainless steel sheet bars of different sizes were then added by 
+TIG welding to achieve pressure resistance.
+
+Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
+This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
+which would be removed after the heat treatment.
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
+      \caption{Bottom part of the cavity while polishing.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
+      \caption{Top part of the cavity after polishing.}
+    \end{subfigure}
+    \caption{Polishing of the inner surface of cavity.}
+    \label{fig:manif_polishing}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
+      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
+      \caption{Bottom part of the cavity with the beam line assembled.}
+    \end{subfigure}
+    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
+    \label{fig:manif_toroidal_sheets}
+\end{figure}
+
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.8\linewidth]{../../../figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
+    \caption{Welded sheet bars.}
+\end{figure}
+
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.7\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
+    \caption{Middle part of the cavity containing the beam line.}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
+      \caption{Welding sheet bars.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
+      \caption{Welding toroidal sheets.}
+    \end{subfigure}
+    \caption{TIG welding.}
+    \label{fig:manif_welding}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
+    \end{subfigure}
+    \caption{Assembled cavity as the current stage.}
+    \label{fig:manif_assembled}
+\end{figure}
+
 %%%%%%

### 2023-08-05 subsections/production/technical_drawings/techd.tex
future work & production added
production added

--- 2023-07-18 subsections/production/manifacturing/mani.tex
@@
 %%%%%%
-% Start of mani.tex
-\section{Manifacturing}
+% Start of techd.tex
+\section{Technical Drawing}
+
+Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\linewidth]{../../../figures/teknikcizim/altgovdeteknikresim.pdf}
+    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
+    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{../../../figures/teknikcizim/Rho-A1.1.00.pdf}
+    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{../../../figures/teknikcizim/Rho-A1.2.00.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
 

### 2023-08-06 msthesis.tex
tools added

@@
 \newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
+
+% START OF intro.tex
+
+\chapter{INTRODUCTION}
+
+\newpage
 
@@
 
+Threads utilize \textit{mutexes}, short for "mutual exclusion," 
+to synchronize and manage access to shared resources 
+in a multi-threaded or multi-process environment.
+
+\subsubsection{Object Oriented Programming}
+
+Object-Oriented Programming (OOP) is a programming paradigm that revolves around the concept of objects. 
+Definition called class serves as a blueprint that defines the structure and behavior of objects. 
+Each object encapsulates both data, and the functions that manipulate that data. 
+This encapsulation promotes modular code design and enhances data security by controlling access to the object's internal state.
+
+In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
+\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
+By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
+
+\newpage
+
+% START OF tools.tex
+
+\chapter{TOOLS}
+
+\section{Poisson Superfish}
+Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
+for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
+It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
+
+\section{CST Studio Suite}
+CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
+It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
+The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
+
+\section{ROOT}
+ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
+visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
+like the Large Hadron Collider (LHC). It has become an essential tool in particle physics research, 
+and it's used by physicists around the world to analyze and interpret data.
+
+\section{gnuplot}
+GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs. 
+It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
+to represent and analyze data in a graphical format.
+
 \newpage
@@
 % Start of final.tex
-\section{Final Design}
+\section{Final Design} \label{sec:final_design}
+
+As discussed before, production efforts of a rhodotron type accelerator is still ongoing in KAHVELab.
+This accelerator will be used at $f=107.5$MHz $P=50-100$kW. 
+In the following figures, rendered visuals of the final design by \textit{Mr. Sinan Öz} can be observed.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
+    \caption{Rhodotron in KAHVELab}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
+    \caption{Rhodotron cavity and \e gun}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
+    \caption{Vertical cross section of the beam injection line}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
+    \caption{Cross section of the acceleration plane}
+\end{figure}
 
@@
 
+Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\linewidth]{./figures/teknikcizim/altgovdeteknikresim.pdf}
+    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
+    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
+    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.2.00.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
+
 \newpage
@@
 
+Manifacturing of the rhodotron cavity has been ongoing, planned to be completed in the following months.
+
+The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet.
+
+Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
+These sheets were then pressed to achieve the shapes of the parts. 
+Several flanges were then machined, including
+\begin{itemize}
+    \item $4.5$in EIA RF flange for RF input
+    \item ISO100-KF vacuum connector flanges for vacuum pumps
+    \item ISO-63 KF flange for probe insertion
+    \item KF40 flanges for beam line vacuum gauges
+\end{itemize}
+
+After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
+304 stainless steel sheet bars of different sizes were then added by 
+TIG welding to achieve pressure resistance.
+
+Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
+This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
+which would be removed after the heat treatment.
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
+      \caption{Bottom part of the cavity while polishing.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
+      \caption{Top part of the cavity after polishing.}
+    \end{subfigure}
+    \caption{Polishing of the inner surface of cavity.}
+    \label{fig:manif_polishing}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
+      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
+      \caption{Bottom part of the cavity with the beam line assembled.}
+    \end{subfigure}
+    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
+    \label{fig:manif_toroidal_sheets}
+\end{figure}
+
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
+    \caption{Welded sheet bars.}
+\end{figure}
+
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
+    \caption{Middle part of the cavity containing the beam line.}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
+      \caption{Welding sheet bars.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
+      \caption{Welding toroidal sheets.}
+    \end{subfigure}
+    \caption{TIG welding.}
+    \label{fig:manif_welding}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
+    \end{subfigure}
+    \caption{Assembled cavity as the current stage.}
+    \label{fig:manif_assembled}
+\end{figure}
+
 \newpage
@@
 % Start of rf.tex
-\section{RF Supply}
+% \section{RF Supply}
 
@@
 \chapter{FUTURE WORK}
+
+At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
+Present bottleneck is the fabrication of the cavity.
+
+\section{Cavity}
+The cavity manufacturing process is in its concluding stages.
+The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
+After the heat treatment operation, 
+the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
+
+\section{Magnets}
+Magnet production was decided to be kept on hold in the early stages of the project, 
+due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
+and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
+The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.
+
+\section{Rhodotron Simulation}
+
+\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
+several improvements and new feature implementations are underway in the mean time. 
+They include the following;
+\begin{figure}[H]
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Electric and magnetic field import
+            \item Field generator module to directly produce field files from specified cavity
+            \item Synchrotron radiation calculations to determine radiation and energy loss
+            \item \ee interactions
+            \item Redesign of the GUI
+            \item 3D render in GUI
+        \end{itemize}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Refactoring of the \eEM interaction and logging to improve performance
+            \item Refactoring of the GUI Render Frame to improve render speed
+            \item Refactoring the magnet class to introduce field leaks
+            \item Extention of analysis tools in Analyze Frame
+            \item $L_{out}$ sweep in Sweep Frame
+        \end{itemize}
+    \end{subfigure}
+\end{figure}
+
+\section{Conclusion}
+
+In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
+before the cavity production is completed and the performance is compared with the predictions of the tool;
+however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
+lead to the inference that this tool holds promise.
 

### 2023-08-06 subsections/future/future_work.tex
tools added

@@
 \documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
-\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
 \usepackage{amsmath, amsthm} % Some extra symbols
@@
 
+\newcommand{\e}{$\textbf{e}^-$ }
+\newcommand{\egun}{$\textbf{e}^-$-gun }
+\newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
+\newcommand{\eE}{$\textbf{e}^-$ - $\vecthreeBF{E}$ }
+\newcommand{\eEM}{$\textbf{e}^-$ - \textbf{EM} }
+\newcommand{\ee}{$\textbf{e}^-$ - $\textbf{e}^-$ }
+
 %%%%%%
@@
 
+At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
+Present bottleneck is the fabrication of the cavity.
+
+\section{Cavity}
+The cavity manufacturing process is in its concluding stages.
+The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
+After the heat treatment operation, 
+the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
+
+\section{Magnets}
+Magnet production was decided to be kept on hold in the early stages of the project, 
+due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
+and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
+The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.
+
+\section{Rhodotron Simulation}
+
+\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
+several improvements and new feature implementations are underway in the mean time. 
+They include the following;
+\begin{figure}[H]
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Electric and magnetic field import
+            \item Field generator module to directly produce field files from specified cavity
+            \item Synchrotron radiation calculations to determine radiation and energy loss
+            \item \ee interactions
+            \item Redesign of the GUI
+            \item 3D render in GUI
+        \end{itemize}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Refactoring of the \eEM interaction and logging to improve performance
+            \item Refactoring of the GUI Render Frame to improve render speed
+            \item Refactoring the magnet class to introduce field leaks
+            \item Extention of analysis tools in Analyze Frame
+            \item $L_{out}$ sweep in Sweep Frame
+        \end{itemize}
+    \end{subfigure}
+\end{figure}
+
+\section{Conclusion}
+
+In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
+before the cavity production is completed and the performance is compared with the predictions of the tool;
+however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
+lead to the inference that this tool holds promise.
 %%%%%%

### 2023-08-06 subsections/theory/rhodotron/rhodotron.tex
simulation chapter half way done
tools added

@@
 
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
+\subsection{Bending Magnets}
+Bending magnets, also known as dipole magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
 They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
@@
     \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
+    \caption{A bending magnet used in KAHVELab}
 \end{figure}
 
-\subsection{Rhodotron Accelerator}
+\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
 
@@
 
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
+The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and bending magnets surrounding it.
 RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.

### 2023-08-06 subsections/theory/simulation/simulation.tex
tools added

@@
 
+Threads utilize \textit{mutexes}, short for "mutual exclusion," 
+to synchronize and manage access to shared resources 
+in a multi-threaded or multi-process environment.
+
+\subsubsection{Object Oriented Programming}
+
+Object-Oriented Programming (OOP) is a programming paradigm that revolves around the concept of objects. 
+Definition called class serves as a blueprint that defines the structure and behavior of objects. 
+Each object encapsulates both data, and the functions that manipulate that data. 
+This encapsulation promotes modular code design and enhances data security by controlling access to the object's internal state.
+
+In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
+\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
+By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
+
 %%%%%%

### 2023-08-06 subsections/tools/tools.tex
tools added

--- 2023-07-16 msthesis.tex
@@
 
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+
+\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
+\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+
 \newcommand{\e}{$\textbf{e}^-$ }
@@
 
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
+%%%%%%
+% START OF tools.tex
 
-\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
-\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
-\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
+\chapter{TOOLS}
 
-\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+\section{Poisson Superfish}
+Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
+for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
+It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
 
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
+\section{CST Studio Suite}
+CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
+It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
+The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
 
-\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
+\section{ROOT}
+ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
+visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
+like the Large Hadron Collider (LHC). It has become an essential tool in particle physics research, 
+and it's used by physicists around the world to analyze and interpret data.
 
-% START OF THEORY
+\section{gnuplot}
+GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs. 
+It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
+to represent and analyze data in a graphical format.
 
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and steerer magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta} \label{sec:rungekutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle.
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-\newpage
-
-% START OF DESIGN
-
-\chapter{DESIGN}
-
-\section{Cavity Design} \label{sec:cavity_design}
-
-The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
-
-By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
-This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
-For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
-    \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
-    \end{aligned}
-\end{eqnarray}
-
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:107_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:180_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:cst_simple_cavity_designs}
-\end{figure}
-
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson SUPERFISH field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_superfish}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST eigenmode results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_eigenmode}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST electric field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_field}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
-      \caption{107.5 MHz unmodified}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
-      \caption{180 MHz unmodified}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
-    \label{fig:107_cavity_shunt_diff}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
-    \label{fig:180_cavity_shunt_diff}
-\end{figure}
-
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
-    \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta Z_{180}=2.7\%
-    \end{aligned}
-\end{equation*}
-
-\newpage
-
-\section{Magnet Design} \label{sec:magnet_design}
-Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
-Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
-Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
-    \label{fig:magnet_design_illustrations}
-\end{figure}
-
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
-
-Two different approaches have been used to achieve phase stability.
-These approaches are discussed further in the following sections.
-
-\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
-
-First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
-
-To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
-As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
-    L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
-
-\begin{figure}[H]    
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
-    \label{fig:magnet_design}
-\end{figure}
-
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
-
-After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
-Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
-\begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
-
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
-Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
-Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
-
-\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
-
-As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
-This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
-This scenario can happen when RF power is not sufficiently high.
-
-Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
-after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
-It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
-For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
-Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
-
-Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
-
-To start, an optimization criteria for the following pass such as
-\begin{itemize}
-    \item Ensure the phase stability of the synchronous electron
-    \item Maximize the energy gain of the synchronous electron
-    \item Minimize the energy spread of the beam
-    \item Minimize the phase lag spread of the beam
-    \item All of the above with decided weights
-\end{itemize}
-needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
-This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
-
-However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
-
-\newpage
-
-\section{Initial Design at KAHVELab}
-
-A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
-After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
-    \label{fig:initial_design}
-\end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
-      \caption{Axial cross section.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
-      \caption{Cross section at acceleration plane.}
-    \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
-    \label{fig:initial_design_cross_section}
-\end{figure}
-The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
-    \end{subfigure}
-    \caption{Initial magnet design.}
-    \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
-    \label{fig:initial_three_magnet_design}
-\end{figure}
-
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $0.1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
-Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
-
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
-
-In KAHVELab, several improvements were made to these initial designs by \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
-Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
-    \end{subfigure}
-    \caption{Improved cavity design.}
-    \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \caption{Improved magnet design.}
-    \label{fig:improved_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
-    \end{subfigure}
-    \caption{Cross section and coils of improved magnet design.}
-    \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \caption{Magnetic field in acceleration plate of improved magnet design.}
-    \label{fig:improved_magnet_design_B}
-\end{figure}
-
-From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
-This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
-
-\newpage
-
-% START OF SIMULATION
-
-\chapter{SIMULATION}
-% Start of poc.tex
-\section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
-\begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
-    \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
-    \end{enumerate}
-\end{itemize}
-
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \caption{Core logic loop of the POC}
-    \label{fig:POC_core_logic}
-\end{figure}
-
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass in THE CAVITY, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
-Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
-
-After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
-The development and improvement efforts are still ongoing.
-
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
-The following sections in this chapter investigates their implementations further.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
-Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-Then sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch entered the cavity, it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see TODO),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation 
-(see \fromfig{console_output_running} in \fromapp{example_simulation_runs} for example console notification, \fromfig{ui_thread} in \fromapp{intermediate_codes} for implemenation)
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
-
-\subsection{Graphical User Interface}
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
-    \caption{The configuration frame of implementated first GUI design.}
-    \label{fig:gui_config}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
-
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
-
-\subsubsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\subsubsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
-
-\subsubsection{Render Frame}
-Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
-see a specific time frame, export as snapshot or animated gif file.
-
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
-    \end{subfigure} 
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
-    \end{subfigure} 
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_1}
-\end{figure}
-
-\subsubsection{Analyze Frame}
-Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
-This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
-    \caption{Analyze frame of \textit{GUI} E distribution.}
-    \label{fig:gui_analyze_Edist}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
-    \end{subfigure} 
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
-    \end{subfigure} 
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et}
-\end{figure}
-
-\subsubsection{Sweep Frame}
-Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
-$\phi_{lag}$ sweep was the first parameter to be implemented. 
-It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
-This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be observed in detail.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
-    \label{fig:gui_sweep_running}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
-    \label{fig:gui_sweep_muE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
-    \label{fig:gui_sweep_sE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
-    \label{fig:gui_sweep_sR}
-\end{figure}
-
-As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
-New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
-
-\newpage
-
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
-\end{figure}
-
-\begin{figure}[H]
-        \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void RhodotronSimulator::_runMT(){
-            gun.fireAllWithFireTimesMT();
-
-            MTEngine.setupPool(time_interval, start_time, end_time, gun, E_field, B_field, gun.thread_bunchs);
-
-            STEPS_TAKEN = 0;
-            simulation_time = start_time;
-            while (simulation_time < end_time + time_interval ){
-                if (STEPS_TAKEN % log_interval() == 0){
-                    E_field.update(simulation_time);
-                    logEfield(simulation_time, simulation_time + time_interval > end_time);
-                    notifyUI(MTEngine.getAverageTime());
-                }
-                simulation_time+=time_interval;
-                STEPS_TAKEN++;
-            }
-            bool end = false;
-            while (!end){
-                double time = MTEngine.getAverageTime();
-                notifyUI(time);
-                if ( time >= end_time ){
-                    end = true;
-                }
-                this_thread::yield();
-            }
-            MTEngine.join();
-
-        }
-    \end{minted}
-    \caption{Multithreading main-thread logic.}
-    \label{fig:_runMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Gun::fireAllWithFireTimesMT(){
-            std::random_device rd;
-            std::mt19937 e2(rd());
-            std::normal_distribution<double> Edist(Ein, sEin);
-
-            for(_fired_bunch= 0; _fired_bunch < bunch_count; _fired_bunch++){
-                for(_fired_e_in_current_bunch= 0; _fired_e_in_current_bunch < e_per_bunch; _fired_e_in_current_bunch++){
-
-                    double E = (sEin == 0 ) ? Ein : Edist(e2);
-
-                    double fire_time = (ns_between_each_electron_fire * _fired_e_in_current_bunch) + _fired_bunch*gun_period;
-
-                    auto burrowed_e = bunchs[_fired_bunch].AddElectronGiveAddress(E, gunpos, gundir, fire_time);
-
-                    int thread_index = (_fired_e_in_current_bunch + _fired_bunch*e_per_bunch)%thread_bunchs.size();
-
-                    thread_bunchs[thread_index]->push_back(burrowed_e);
-                }
-            }
-        }
-    \end{minted}
-    \caption{Multithreading electron assign logic.}
-    \label{fig:fireAllWithFireTimesMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void MultiThreadEngine::setupPool( double _time_interval, double _start_time, double _end_time, Gun& gun, 
-            CoaxialRFField& RF, MagneticField& B, vector<shared_ptr<vector<shared_ptr<Electron2D>>>>& e_list){
-            threads.reserve(thread_count);
-
-            for(int i = 0; i < thread_count && i == threads.size(); i++){
-
-                child_notifier_mutexes.push_back(make_shared<mutex>());
-                child_times.push_back(make_shared<double>());
-
-                auto _E = RF.Copy();
-                auto _B = B.LightWeightCopy();
-                double time_between_fires = thread_count*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                double first_fire_time = i*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                ThreadArguments thread_arguments(i, _time_interval, _start_time, _end_time, &gun, _E, _B, e_list[i], first_fire_time, time_between_fires);
-                thread_arguments.parent_notifier_mutex = child_notifier_mutexes[i];
-                thread_arguments.current_thread_time = child_times[i];
-                threads.push_back(thread(threadLoop, thread_arguments));
-            }
-        }
-    \end{minted}
-    \caption{Multithreading worker-threads setup logic.}
-    \label{fig:setupPool}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void threadLoop(ThreadArguments thread_arguments){
-            uint64_t count = 0;
-
-            double sim_time = thread_arguments.start_time;
-
-            while(sim_time < thread_arguments.end_time + thread_arguments.time_interval){
-                thread_arguments.E->update(sim_time);
-                thread_arguments.i_args.time = sim_time;
-
-                if ( count % (unsigned long)(0.1/thread_arguments.time_interval) == 0){
-                    saveElectronInfoForSingleThread(thread_arguments.i_args);
-                    // Notifiy the main thread
-                    if(thread_arguments.parent_notifier_mutex->try_lock()){
-                        *thread_arguments.current_thread_time = sim_time;
-                        thread_arguments.parent_notifier_mutex->unlock();
-                    }
-                }
-
-                interactForSingleThread(thread_arguments.i_args);
-                // save electron info here
-                sim_time+= thread_arguments.time_interval;
-                count++;
-            }
-            thread_arguments.parent_notifier_mutex->lock();
-            *thread_arguments.current_thread_time = sim_time;
-            thread_arguments.parent_notifier_mutex->unlock();
-        }
-    \end{minted}
-    \caption{Multithreading worker-thread logic.}
-    \label{fig:threadLoop}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void UIThreadWork(UIThreadArgs args){
-            int UI_WORK_PIECE = SIM_WORK_MASK;
-            if ( !args.isService ) {
-                UI_WORK_PIECE = 50;
-            }
-
-            double piece = (args.end_time - args.start_time)/UI_WORK_PIECE;
-
-            if ( !args.isService ) {
-                std::string sim_running_msg = "...Simulation is running...";
-                for(int i = 0; i < 26 - sim_running_msg.size()/2 ; i++){
-                    std::cout << " ";
-                }
-                std::cout << sim_running_msg <<"\n";
-            }
-
-            args.ui_mutex->lock();
-            double simtime = *(args.simulation_time);
-            args.ui_mutex->unlock();
-
-            if ( !args.isService ) {
-                std::cout << "V";
-                for(int i = 0; i < 51; i++){
-                    std::cout << "_";
-                }
-                std::cout << "V\n[" << std::flush;
-            }
-
-            int count = 0;
-            bool running = true;
-            while(running && (simtime < args.end_time || count < UI_WORK_PIECE )){
-                if( simtime > count * piece ){
-                    if ( !args.isService ) {
-                        std::cout << "#" << std::flush;
-                    }
-                    count++;
-                    args.state_mutex->lock();
-                    running = *args.state_ptr & SIM_RUNNING;
-                    *args.state_ptr = (*args.state_ptr & ~SIM_WORK_MASK) | (count & SIM_WORK_MASK);
-                    if (args.isService) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-                    args.state_mutex->unlock();
-                }
-                std::this_thread::sleep_for(std::chrono::milliseconds(25));
-                args.ui_mutex->lock();
-                simtime = *(args.simulation_time);
-                args.ui_mutex->unlock();
-
-            }
-            if ( !args.isService ) {
-                std::cout << "#]\n\n" << std::flush;
-                std::cout << "     ...Simulation is finished successfully...\n\n" << std::flush;
-            }
-
-            args.state_mutex->lock();
-            *args.state_ptr |= SIM_RENDERING;
-            if ( args.isService ) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-            args.state_mutex->unlock();
-        }
-    \end{minted}
-    \caption{UI-Console handler thread logic.}
-    \label{fig:ui_thread}
-\end{figure}
-
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
-
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{An example \textit{config.in} file.}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-% START OF BIBLIOGRAPHY
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-    \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018
-
-\end{thebibliography}
-
-% END OF BIBLIOGRAPHY
+%%%%%%
 

### 2023-08-06 theory.tex
tools added

--- 2023-07-02 theory.tex
@@
 % START OF THEORY
-
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-
 \newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
 \newcommand{\vecthree}[1]{\vec{#1}}
+\newcommand{\vecNum}[3]{(#1, #2, #3)}
 
@@
 
+\newcommand{\e}{$\textbf{e}^-$ }
+\newcommand{\egun}{$\textbf{e}^-$-gun }
+\newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
+\newcommand{\eE}{$\textbf{e}^-$ - $\vecthreeBF{E}$ }
+\newcommand{\eEM}{$\textbf{e}^-$ - \textbf{EM} }
+\newcommand{\ee}{$\textbf{e}^-$ - $\textbf{e}^-$ }
+
+\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
+
 \newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
+
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
+\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+
+\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
+
+\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
+\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
 
@@
 
-\section{Accelerating Charged Particles}
+% START OF PRODUCTION
 
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines momentum and states 
-\begin{equation}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force.
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
+\chapter{PRODUCTION}
+% Start of final.tex
+\section{Final Design} \label{sec:final_design}
 
-\subsection{Lorentz Force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
+As discussed before, production efforts of a rhodotron type accelerator is still ongoing in KAHVELab.
+This accelerator will be used at $f=107.5$MHz $P=50-100$kW. 
+In the following figures, rendered visuals of the final design from a CAD software can be observed.
 
 \newpage
-\section{Practical}
 
-\subsection{Accelerators}
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
+% Start of techd.tex
+\section{Technical Drawing}
 
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
+Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
 
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\linewidth]{./figures/teknikcizim/altgovdeteknikresim.pdf}
+    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
 
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
+    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
 
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
+    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
 
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.2.00.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
 
-In summary, particle accelerators are complex scientific instruments that use electromagnetic fields to accelerate charged particles to high speeds and energies. 
-They enable scientists to investigate the fundamental nature of matter, unravel the mysteries of the universe, and apply their findings to various fields of research and practical applications.
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
+\end{figure}
 
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+\newpage
 
-\subsubsection{Key Concepts}
+% Start of mani.tex
+\section{Manifacturing}
 
+Manifacturing of the rhodotron cavity has been ongoing, planned to be completed in the following months.
+
+The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet.
+
+Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
+These sheets were then pressed to achieve the shapes of the parts. 
+Several flanges were then machined, including
 \begin{itemize}
-    \item Phase Lag
-
-    This is the asdasd
-
-    \item XD
-    \item AW
-
+    \item $4.5$in EIA RF flange for RF input
+    \item ISO100-KF vacuum connector flanges for vacuum pumps
+    \item ISO-63 KF flange for probe insertion
+    \item KF40 flanges for beam line vacuum gauges
 \end{itemize}
 
-\subsubsection{Acceleration Cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
+After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
+304 stainless steel sheet bars of different sizes were then added by 
+TIG welding to achieve pressure resistance.
 
-RF cavities are typically hollow metallic structures made of high-conductivity materials such as copper or niobium. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
+Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
+This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
+which would be removed after the heat treatment.
 
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
+      \caption{Bottom part of the cavity while polishing.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
+      \caption{Top part of the cavity after polishing.}
+    \end{subfigure}
+    \caption{Polishing of the inner surface of cavity.}
+    \label{fig:manif_polishing}
+\end{figure}
 
-% TODO : ADD RF CAVITY PICTURE HERE
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
+      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
+      \caption{Bottom part of the cavity with the beam line assembled.}
+    \end{subfigure}
+    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
+    \label{fig:manif_toroidal_sheets}
+\end{figure}
 
-\subsubsection{Steerer Magnets}
-Steerer magnets, also known as dipole magnets or bending magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator. 
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:LorentzForce}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
+    \caption{Welded sheet bars.}
+\end{figure}
 
-% TODO : ADD STEERER MAGNET PICTURE HERE
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
+    \caption{Middle part of the cavity containing the beam line.}
+\end{figure}
 
-\subsection{Rhodotron Accelerator}
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
+      \caption{Welding sheet bars.}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
+      \caption{Welding toroidal sheets.}
+    \end{subfigure}
+    \caption{TIG welding.}
+    \label{fig:manif_welding}
+\end{figure}
+
+\begin{figure}
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
+    \end{subfigure}%
+    \centering
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
+    \end{subfigure}
+    \caption{Assembled cavity as the current stage.}
+    \label{fig:manif_assembled}
+\end{figure}
 
 \newpage
-\section{Numerical Integration Methods}
 
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-
-where
-
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure} %
-    \centering
-    \begin{subfigure}{}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{}
+% Start of rf.tex
+\section{RF Supply}
 

### 2023-08-07 msthesis.tex
statE raw data added

@@
 \newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
+\newcommand{\fromfigsix}[6]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
 
@@
 \newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
+\newcommand{\fromtabf}[4]{\textit{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}}
 
@@
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+
 \begin{figure}[H]
@@
     \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear accelerator}
+    \caption{A linear proton accelerator in KAHVELab}
 \end{figure}
@@
 
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
-
-\end{itemize}
+\subsubsection{Resonance Frequency}
+Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
+It is determined by the physical dimensions and the speed of light in the cavity's medium. 
+In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
+\begin{equation}
+    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
+    \label{eq:f_r_rec}
+\end{equation}
+Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
+
+\subsubsection{Bunch}
+Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
+
+\subsubsection{Phase Stability}
+Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
+It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
+which is crucial for achieving efficient particle acceleration. 
+Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
+ensuring that they receive the correct energy boosts and interact predictably with detectors. 
+Deviations in phase stability can lead to particle loss and decreased beam quality.
+
+\subsubsection{Phase Lag}
+Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
+It describes the difference in phase angles within their respective cycles, between two signals.
+
+\subsubsection{Shunt Impedance}
+The shunt impedance of an RF accelerator is a measure of the efficiency 
+at which the accelerator can transform the supplied RF power into acceleration.
 
@@
     \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A steerer magnet used in KAHVELab}
+    \caption{A bending magnet used in KAHVELab}
 \end{figure}
@@
 Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
+% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
 
@@
     \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
+See \fromfig{rhod_cycle_1}
+    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.See \fromfig{rhod_cycle_2}
     \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+See \fromfig{rhod_cycle_3}
     \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+See \fromfig{rhod_cycle_4}
 \end{description}
 
-This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
+This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
 After desired amount of pass has been completed, the electrons exit the accelerator.
@@
 This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{./figures/illustrations/rhod1.pdf}
     \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \label{fig:rhod_cycle_1}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{./figures/illustrations/rhod2.pdf}
     \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \label{fig:rhod_cycle_2}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{./figures/illustrations/rhod3.pdf}
     \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
+    \label{fig:rhod_cycle_3}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{./figures/illustrations/rhod4.pdf}
     \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
+    \label{fig:rhod_cycle_4}
 \end{figure}
@@
 
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $0.1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
+These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
 Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
@@
 
-In KAHVELab, several improvements were made to these initial designs by \textit{Mr.
+In KAHVELab, several improvements were made to these initial designs together with \textit{Mr.
 Sinan ÖZ}.
@@
 
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass in THE CAVITY, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
+After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
 % 40 kW total power
@@
 As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
-Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
-
-After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software.
+This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+Since using a single software would have made the process error prone.
+
+After the results obtained from \textit{POC} were found to be promising, a decision was made to develop a more robust simulation software.
 This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
@@
 \subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
-Initial step of improving $POC$ towards $Rhodotron Simulation$ was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
+Initial step of improving \textit{POC} towards \textit{Rhodotron Simulation} was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
 First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-Then sweep the $t_{out}$ parameter to find the optimal value.
+One can sweep the $t_{out}$ parameter to find the optimal value.
 This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
@@
 They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsing \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal gun phase lag.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch entered the cavity, it defines the starting time of the current pass.
+This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
+
+Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
+$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
 To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
@@
 Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, early implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as $ROOT$.
+$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
+For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}.
 
@@
 $\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
+Two example runs from this intermediate build can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
 
@@
 Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of $OOP$, details of which can be seen in \fromapp{intermediate_codes}.
+The refactoring effort included proper implementation of \textit{OOP}, details of which can be seen in \fromfigsix{e_class}{bunch_class}{gun_class}{sim_class}{rhodosim_class}{rf_class} of \fromapp{intermediate_codes}.
 
@@
 An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired to a uniform magnetic field of $0.1$T placed in $x>0.05$m.
+A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired into a uniform magnetic field of $0.1$T located in $x>0.05$m.
 Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
@@
 
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable because time and computing power. 
+Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
 Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
@@
 \textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see TODO),
+This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph}),
 
@@
     \label{fig:ui_thread}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        class Electron{
+            std::vector<ElectronLog> log;
+            uint64_t index;
+            double Et;
+            vector3d pos;
+            vector3d vel;
+            double fire_time;
+        public:
+            Electron();
+            Electron(double Ein, vector3d position, vector3d direction, double _fire_time = 0);
+            ~Electron();
+
+            void setEin(double E_in);
+            void print_electron_info();
+
+            void move(double dt);
+            void move(const vector3d& acc, double dt);
+            void move(const vector3d& acc, const vector3d& jerk, double dt);
+            void accelerate(const vector3d& acc, double dt);
+            void accelerate(const vector3d& acc, const vector3d& jerk, double dt);
+
+            void interactLF(RFField& E, MagneticField& B, double time_interval);
+            void interactRK(RFField& E, MagneticField& B, double time_interval);
+            void interactRK(RFField& E, MagneticField& B, const double time, double time_interval);
+            void interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval);
+
+            vector3d interactE_RK(const RFField& E, double time_interval);
+            vector3d interactB_RK(const MagneticField& B, double time_interval);
+
+            void saveInfo(double t);
+            void setLogSize(size_t size);
+            void loge(DataStorage& path);
+            const vector<ElectronLog>& getLog();
+
+            double vel();
+            double beta();
+            double beta2();
+            double gamma();
+            double gamma_inv();
+        };
+    \end{minted}
+    \caption{Electron class definition}
+    \label{fig:e_class}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        class Bunch{
+        private:
+            int e_count = 0;
+            int index_fastest = 0;
+            double max_energy = 0;
+            double entry_time = 0;
+            double E_in = 0.04;
+
+            vector<Bunch> subBunchs;
+            vector<shared_ptr<Electron>> e;
+        public:
+            Bunch(unsigned int num_of_electrons, double Ein, vector3d gunpos, vector3d gundir, double gun_ns);
+            Bunch();
+            ~Bunch();
+
+            void saveInfo(double time);
+
+            Electron& getFastest();
+
+            void AddElectron(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
+
+            shared_ptr<Electron> AddElectronGiveAddress(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
+
+            void setEntryTime(double entry_time);
+            void setEin(double E_in);
+            void setNSLen(double len);
+
+            uint32_t get_e_count();
+            double getEin();
+            double E_ave();
+            double E_rms();
+
+            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
+
+            void divide(unsigned int num);
+            void concat();
+            Bunch& subBunch(unsigned int index);
+            vector<Bunch*> subBunchPtr();
+
+            void reset();
+
+            void print_bunch_info();
+            void print_summary();
+
+            void logPaths(vector<DataStorage>& pathStorage, std::string header);
+        };
+    \end{minted}
+    \caption{Bunch class definition}
+    \label{fig:bunch_class}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        class Gun{
+            double Ein;
+            double sEin;
+            double gun_period;
+            double gun_active_time;
+            double ns_between_each_electron_fire;
+
+            vector3d gunpos;
+            vector3d gundir = vector3d(1,0,0);
+
+            uint64_t bunch_count = 0;
+            uint64_t e_per_bunch = 1;
+
+            uint32_t _fired_bunch = 0;
+            uint32_t _fired_e_in_current_bunch = 0;
+            bool _firing = false;
+
+            bool _mt_enabled = false;
+            uint32_t _child_thread_count = 0;
+
+            vector<Bunch> bunchs;
+
+            mutex _gun_mutex; 
+            vector<shared_ptr<vector<shared_ptr<Electron>>>> thread_bunchs;
+
+            void setNSLen(double len);
+        public:
+            Gun();
+            Gun(double Ein, double gun_active_time, double pulse_interval, vector3d gunpos);
+            ~Gun();
+            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
+
+            void fireIfActive(double time);
+            void fireAllWithFireTimesMT();
+
+            void addBunch(unsigned int num_of_electrons, double Ein);
+
+            void setGunActiveTime(double gt);
+            double getGunActiveTime(){return gun_active_time;}
+            void setGunInterval(double guninterval);
+            void setGunPos(vector3d gun_pos);
+            void setGunDir(vector3d gun_dir);
+            void setEin(double Ein) ;
+            void setEinStd(double EinStd) ;
+            void setNumberOfElectrons(uint64_t e_num);
+            void getElectronsPerBunch(){return e_per_bunch;}
+            void setNumberOfBunchs(uint64_t b_num);
+            void enableMT(uint32_t thread_count);
+
+            void saveInfo(double time);
+            void logPaths(vector<vector<DataStorage> >& pathsStorage, std::string pathsPath, std::string header);
+        };
+    \end{minted}
+    \caption{Gun class definition}
+    \label{fig:gun_class}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        class Simulator{        // E in MV/m,   En in MeV,   B in T,    t in ns
+        protected:
+            Gun gun;
+            double Emax; double freq = 107.5; double phase_lag = 0; 
+            DataStorage EfieldStorage; DataStorage BfieldStorage;
+            vector<vector<DataStorage>> pathsStorage;
+            std::string configPath;
+            std::string pathsPath;
+            std::string EfieldLogHeader;
+            std::string BfieldLogHeader;
+            std::string eLogHeader;
+
+            double simulation_time = 0;
+            double dummy_time = 0;
+            double start_time = 0;
+            double end_time = 45;   
+            double time_interval = 0.0001;
+            uint64_t STEPS_TAKEN = 0;
+            double GUN_ACTIVE_TIME = 1;         
+            double GUN_PERIOD = 9.3;
+            uint64_t NUM_OF_ELECTRONS = 1;
+            uint64_t NUM_OF_BUNCHS = 1;
+            double Ein = 0.04;
+            double EinStd = 0;
+            vector3d gunPosition;
+            vector3d gunDirection = vector3d(1,0,0);
+
+            shared_ptr<mutex> ui_mutex;
+            UIHandler ui_handler;
+            shared_ptr<mutex> state_mutex;
+            uint8_t state = 0x0;
+
+            MultiThreadEngine MTEngine;
+            unsigned int MAX_THREAD_COUNT = 1;
+            bool MULTI_THREAD = false;
+        public:
+            Simulator();
+            ~Simulator(){}
+
+            void enableMultiThreading(unsigned int thread_count);
+            void setdT(double dT);
+            void setEin(double E_in);
+            void setEinStd(double Ein_Std);
+            void setNumberofElectrons(uint64_t num_of_electrons);
+            void setNumberofBunchs(uint64_t num_of_bunchs);
+            void setStartTime(double starttime);
+            void setEndTime(double end_time);
+            void setGunActiveTime(double gun_ns);
+            void setGunPeriod(double pi);
+            void setGunPosition(vector3d pos);
+            void setGunDirection(vector3d dir);
+            void setRFPath(std::string path);
+            void setBPath(std::string path);
+            void setPathsPath(std::string path);
+            void setConfigPath(std::string path);
+
+            virtual void run();
+            void openLogs();
+            void closeLogs();
+            virtual void getConfig(Configuration& config) = 0;
+            virtual void logEfield(double time, bool) = 0;
+            virtual void logBfield() = 0;
+            void logPaths();
+            shared_ptr<mutex> getUIMutex();
+        };
+    \end{minted}
+    \caption{Simulator class definition}
+    \label{fig:sim_class}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        class RhodotronSimulator : public Simulator{
+        private:
+            double R1;
+            double R2;
+            CoaxialRFField E_field;
+            MagneticField B_field;
+
+            void _runMT();
+            void _runST();
+        public:
+            RhodotronSimulator(double phase_lag);
+            RhodotronSimulator(Configuration& config);
+
+            void StartUIHandler();
+            void StopUIHandler();
+            void DeclareService(std::string pipe_name);
+
+            void setFreq(double frequency);
+            void setPhaseLag(double phase_lag);
+            void setEmax(double E_max);
+            void setR1(double r1);
+            void setR2(double r2);
+            void addMagnet(double B, double r, vector3d position);
+            void addMagnet(Magnet m);
+
+            void updateSimulation();
+            void getConfig(Configuration& config);
+            void logEfield(double time, bool end);
+            void logBfield();
+
+            void run();
+            void notifyUI(double time);
+
+            void setState(uint8_t state_);
+        };
+    \end{minted}
+    \caption{RhodotronSimulator class definition}
+    \label{fig:rhodosim_class}
+\end{figure}
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+            class RFField{
+            protected:
+                double E;                       // MV/m
+                double E_max = 0;               // MV/m
+                double frequency = 107.5;       // MHz
+                double phase_lag = 0;           // degree
+            public:
+                RFField();
+                RFField(double phase_lag);
+                virtual ~RFField() {}
+
+                virtual vector3d getField(vector3d position);              
+                virtual double getField(double R);
+                virtual int log(DataStorage& rf, double time, bool end = false);
+                vector3d actOn(Electron& e);    
+                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);
+
+                double getE() {return E;}
+                void setEmax(double E_max) {this->E_max = E_max; update(0);}
+                void setFreq(double freq){ frequency = freq;}
+                void setPhaseLag(double phaselag){ phase_lag = phaselag; update(0);}
+                virtual void update(double time);
+            };
+        \end{minted}
+    \end{subfigure}
+
+    \begin{subfigure}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+            class CoaxialRFField : public RFField{
+            private:
+                double r1 = 0.188;                         // m
+                double r2 = 0.753;                         // m
+                double E_max_pos = r1;                     // m
+                std::vector<CoaxialRFField*> _childs;
+                double E_radial(double R) const;
+            public:
+                CoaxialRFField();
+                CoaxialRFField(double phase_lag);
+                ~CoaxialRFField() override;
+                void setR1(double r1);
+                void setR2(double r2);
+                void setEmaxPos(double Emaxpos);
+
+                vector3d getField(vector3d position) const override;
+                double getField(double R) const override;
+                vector3d actOn(Electron& e);
+                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);    
+                void update(double time) override;
+
+                int log(DataStorage& rf, double time, bool end = false) override;
+
+                std::shared_ptr<CoaxialRFField> Copy();
+                void split(uint32_t amount_of_child);
+                CoaxialRFField* child(uint32_t index);
+            };
+        \end{minted}
+    \end{subfigure}
+    \caption{CoaxialRFField class definition}
+    \label{fig:rf_class}
 \end{figure}
@@
 
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+    5.00E-02 & 0.114422     & 0.028398 & 0.009294 \\
+    1.00E-02 & 0.019233     & 0.036245 & 0.002182 \\
+    1.00E-03 & 0.002141     & 0.147979 & 0.00125  \\
+    9.00E-04 & 0.001749     & 0.172161 & 0.00794  \\
+    8.00E-04 & 0.001516     & 0.184629 & 0.004359 \\
+    7.00E-04 & 0.00152      & 0.20445  & 0.001919 \\
+    6.00E-04 & 0.001049     & 0.234947 & 0.004416 \\
+    5.00E-04 & 0.000974     & 0.278938 & 0.010969 \\
+    4.00E-04 & 0.0009       & 0.336847 & 0.003028 \\
+    3.00E-04 & 0.000587     & 0.441771 & 0.005859 \\
+    2.00E-04 & 0.000433     & 0.652066 & 0.006637 \\
+    1.00E-04 & 0.0002       & 1.280059 & 0.016027 \\
+    9.00E-05 & 0.000145     & 1.41908  & 0.013122 \\
+    8.00E-05 & 0.000153     & 1.592492 & 0.011332 \\
+    7.00E-05 & 0.000162     & 1.806561 & 0.009931 \\
+    6.00E-05 & 0.000123     & 2.103571 & 0.011143 \\
+    5.00E-05 & 0.000084     & 2.515006 & 0.01393  \\
+    4.00E-05 & 0.000092     & 3.140471 & 0.014138 \\
+    3.00E-05 & 0.000053     & 4.158715 & 0.009474 \\
+    2.00E-05 & 0.000045     & 6.231734 & 0.015236 \\
+    1.00E-05 & 0.000022     & 12.39871 & 0.039575 \\
+    1.00E-06 & 0.000003     & 123.318  & 0.299559
+    \end{tabular}
+    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
+    \label{tab:lf_statE_table}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+        5.00E-02 & 0.055355     & 0.031054 & 0.003281 \\
+        1.00E-02 & 0.009868     & 0.063656 & 0.000893 \\
+        1.00E-03 & 0.001141     & 0.435864 & 0.005332 \\
+        9.00E-04 & 0.001325     & 0.478216 & 0.00595  \\
+        8.00E-04 & 0.001112     & 0.533789 & 0.003897 \\
+        7.00E-04 & 0.000705     & 0.60586  & 0.005441 \\
+        6.00E-04 & 0.000687     & 0.703851 & 0.009447 \\
+        5.00E-04 & 0.000474     & 0.840173 & 0.00913  \\
+        4.00E-04 & 0.00046      & 1.039166 & 0.005874 \\
+        3.00E-04 & 0.000456     & 1.378822 & 0.007995 \\
+        2.00E-04 & 0.000207     & 2.045464 & 0.008499 \\
+        1.00E-04 & 0.000127     & 4.052472 & 0.014711 \\
+        9.00E-05 & 0.000091     & 4.500401 & 0.015404 \\
+        8.00E-05 & 0.000124     & 5.048922 & 0.014392 \\
+        7.00E-05 & 0.000062     & 5.773208 & 0.031443 \\
+        6.00E-05 & 0.000057     & 6.726501 & 0.020609 \\
+        5.00E-05 & 0.00006      & 8.045931 & 0.014246 \\
+        4.00E-05 & 0.000039     & 10.04809 & 0.012756 \\
+        3.00E-05 & 0.000045     & 13.39669 & 0.028057 \\
+        2.00E-05 & 0.000023     & 20.03889 & 0.006436 \\
+        1.00E-05 & 0.000016     & 40.0818  & 0.120627 \\
+        1.00E-06 & 0.000003     & 400.2421 & 0.554172
+    \end{tabular}
+    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
+    \label{tab:rk2_statE_table}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+    5.00E-02 & 0.986005     & 0.030314 & 0.009209 \\
+    1.00E-02 & 0.154314     & 0.036833 & 0.004068 \\
+    1.00E-03 & 0.01476      & 0.131783 & 0.002352 \\
+    9.00E-04 & 0.013618     & 0.150984 & 0.005618 \\
+    8.00E-04 & 0.011863     & 0.161336 & 0.003117 \\
+    7.00E-04 & 0.010109     & 0.179693 & 0.002658 \\
+    6.00E-04 & 0.009277     & 0.205356 & 0.002912 \\
+    5.00E-04 & 0.007527     & 0.242352 & 0.003093 \\
+    4.00E-04 & 0.006084     & 0.294269 & 0.001551 \\
+    3.00E-04 & 0.00449      & 0.383982 & 0.001711 \\
+    2.00E-04 & 0.002897     & 0.563762 & 0.004214 \\
+    1.00E-04 & 0.001458     & 1.101252 & 0.008064 \\
+    9.00E-05 & 0.001376     & 1.229321 & 0.0089   \\
+    8.00E-05 & 0.001232     & 1.381441 & 0.01057  \\
+    7.00E-05 & 0.001027     & 1.574994 & 0.011933 \\
+    6.00E-05 & 0.000853     & 1.833183 & 0.006065 \\
+    5.00E-05 & 0.00074      & 2.184948 & 0.013416 \\
+    4.00E-05 & 0.000596     & 2.72503  & 0.016356 \\
+    3.00E-05 & 0.000467     & 3.617576 & 0.017581 \\
+    2.00E-05 & 0.000308     & 5.394629 & 0.027885 \\
+    1.00E-05 & 0.00015      & 10.75182 & 0.03301  \\
+    1.00E-06 & 0.000017     & 106.9198 & 0.373175
+    \end{tabular}
+    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
+    \label{tab:lf_statE90_table}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
+        5.00E-02 & 0.587777     & 0.034741 & 0.012735 \\
+        1.00E-02 & 0.09943      & 0.059945 & 0.001318 \\
+        1.00E-03 & 0.009987     & 0.38199  & 0.005941 \\
+        9.00E-04 & 0.007946     & 0.417119 & 0.005683 \\
+        8.00E-04 & 0.007999     & 0.466052 & 0.006398 \\
+        7.00E-04 & 0.006732     & 0.525791 & 0.003782 \\
+        6.00E-04 & 0.005541     & 0.612876 & 0.007114 \\
+        5.00E-04 & 0.005022     & 0.732091 & 0.012129 \\
+        4.00E-04 & 0.004031     & 0.906845 & 0.012156 \\
+        3.00E-04 & 0.002779     & 1.199367 & 0.014536 \\
+        2.00E-04 & 0.001897     & 1.782653 & 0.016993 \\
+        1.00E-04 & 0.000895     & 3.52464  & 0.029778 \\
+        9.00E-05 & 0.000858     & 3.916115 & 0.041066 \\
+        8.00E-05 & 0.000731     & 4.409459 & 0.040828 \\
+        7.00E-05 & 0.00066      & 5.012686 & 0.042727 \\
+        6.00E-05 & 0.000561     & 5.851793 & 0.038488 \\
+        5.00E-05 & 0.000471     & 7.002315 & 0.046152 \\
+        4.00E-05 & 0.000363     & 8.747954 & 0.063936 \\
+        3.00E-05 & 0.000264     & 11.64305 & 0.091404 \\
+        2.00E-05 & 0.000184     & 17.44533 & 0.123198 \\
+        1.00E-05 & 0.000093     & 34.93332 & 0.391012 \\
+        1.00E-06 & 0.000011     & 348.494  & 3.237203
+    \end{tabular}
+    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
+    \label{tab:rk2_statE90_table}
+\end{table}
 % START OF BIBLIOGRAPHY

### 2023-08-07 subsections/simulation/poc/poc.tex
statE raw data added

@@
 As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on $CST$.
-Using a single software would have made the process error prone. Their results, at the end of the day, depend heavily on the physical and mathematical models they use.
+This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+Since using a single software would have made the process error prone.
 
-After the promising results obtained from \textit{POC}, the decision was made to develop a more robust simulation software.
+After the results obtained from \textit{POC} were found to be promising, a decision was made to develop a more robust simulation software.
 This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.

### 2023-08-07 subsections/theory/rhodotron/rhodotron.tex
statE raw data added

@@
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{A circular accelerator}
-\end{figure}
 
@@
     \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{A linear accelerator}
+    \caption{A linear proton accelerator in KAHVELab}
 \end{figure}
@@
 
-\begin{itemize}
-    \item Phase Stability
-    \item Phase Lag
-    \item Shunt Impedance
+\subsubsection{Resonance Frequency}
+Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
+It is determined by the physical dimensions and the speed of light in the cavity's medium. 
+In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
+\begin{equation}
+    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
+    \label{eq:f_r_rec}
+\end{equation}
+Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
 
-\end{itemize}
+\subsubsection{Bunch}
+Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
+
+\subsubsection{Phase Stability}
+Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
+It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
+which is crucial for achieving efficient particle acceleration. 
+Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
+ensuring that they receive the correct energy boosts and interact predictably with detectors. 
+Deviations in phase stability can lead to particle loss and decreased beam quality.
+
+\subsubsection{Phase Lag}
+Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
+It describes the difference in phase angles within their respective cycles, between two signals.
+
+\subsubsection{Shunt Impedance}
+The shunt impedance of an RF accelerator is a measure of the efficiency 
+at which the accelerator can transform the supplied RF power into acceleration.
 
@@
 Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{SUPERFISH simulation of a coaxial cavity}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{CST simulation of a coaxial cavity}
-\end{figure}
+% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
 
@@
 This process is explained further in the following figures where $T$ is the period of the electric field.
-% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
 \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod1.pdf}
     \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
+    \label{fig:rhod_cycle_1}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod2.pdf}
     \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
+    \label{fig:rhod_cycle_2}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod3.pdf}
     \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
+    \label{fig:rhod_cycle_3}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
+    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod4.pdf}
     \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
+    \label{fig:rhod_cycle_4}
 \end{figure}

### 2023-08-07 testler.cpp

@@ -38,3 +38,317 @@ int phase_opt(const vector<double>& Louts, int phase_sweep_range){
     }
     return opt_phase;
 }
+
+
+
+class Electron{
+    std::vector<ElectronLog> log;
+    uint64_t index;
+    double Et;
+    vector3d pos;
+    vector3d vel;
+    double fire_time;
+public:
+    Electron();
+    Electron(double Ein, vector3d position, vector3d direction, double _fire_time = 0);
+    ~Electron();
+
+    void setEin(double E_in);
+    void print_electron_info();
+
+    void move(double dt);
+    void move(const vector3d& acc, double dt);
+    void move(const vector3d& acc, const vector3d& jerk, double dt);
+    void accelerate(const vector3d& acc, double dt);
+    void accelerate(const vector3d& acc, const vector3d& jerk, double dt);
+    
+    void interactLF(RFField& E, MagneticField& B, double time_interval);
+    void interactRK(RFField& E, MagneticField& B, double time_interval);
+    void interactRK(RFField& E, MagneticField& B, const double time, double time_interval);
+    void interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval);
+
+    vector3d interactE_RK(const RFField& E, double time_interval);
+    vector3d interactB_RK(const MagneticField& B, double time_interval);
+
+    void saveInfo(double t);
+    void setLogSize(size_t size);
+    void loge(DataStorage& path);
+    const vector<ElectronLog>& getLog();
+
+    double vel();
+    double beta();
+    double beta2();
+    double gamma();
+    double gamma_inv();
+};
+
+class Bunch{
+private:
+    int e_count = 0;
+    int index_fastest = 0;
+    double max_energy = 0;
+    double entry_time = 0;
+    double E_in = 0.04;
+
+    vector<Bunch> subBunchs;
+    vector<shared_ptr<Electron>> e;
+
+public:
+
+    Bunch(unsigned int num_of_electrons, double Ein, vector3d gunpos, vector3d gundir, double gun_ns);
+    Bunch();
+
+    void saveInfo(double time);
+
+    Electron& getFastest();
+
+    void AddElectron(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
+
+    shared_ptr<Electron> AddElectronGiveAddress(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
+
[…]

### 2023-08-07 msthesis.tex
başlık eklendi

@@
 
+% COVER PAGE
+\title{DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS}
+\turkcebaslik{RHODOTRON TİPİ ELEKTRON HIZLANDIRICILARI İÇİN TASARIM VE SİMÜLASYON YAZILIMI}
+\degree{B.S., Physics, Boğaziçi University, 2020}
+\author{Muhammet Furkan Er}
+\program{M.S. Physics}
+\subyear{2023}
+
+% APPROVED BY PAGE
+\supervisor{Prof. Veysi Erkcan Özcan}
+\cosuperi{Gökhan Ünel, Ph.D.}
+%\cosuperii{Title and Name of Cosupervisor II}
+\examineri{Prof. Erhan Gülmez}
+\examinerii{Bora Işıldak , Ph.D.}
+%\examineriv{}
+%\examinerv{}
+\dateofapproval{DD.MM.YYYY}
+
 % BEGIN OF DOCS
@@
 \pagenumbering{roman}
+\makemstitle % M.S. thesis
+\makeapprovalpage
+
+% ACK PAGE
+\begin{acknowledgements}
+Acknowledgements come here...
+\end{acknowledgements}
+
+% ABS PAGE
+\begin{abstract}
+One page abstract will come here.  
+\end{abstract}
+
+% OZET PAGE
+\begin{ozet}
+Bir sayfa uzunluğunda özet gelecektir.
+\end{ozet}
 
@@
 \tableofcontents
+\listoffigures
+\listoftables
 
@@
 \newcommand{\fromtabf}[4]{\textit{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}}
-
-% START OF intro.tex
-
-\chapter{INTRODUCTION}
-
-\newpage
 
@@
 Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
 \begin{equation} \label{eq:lf}
@@
 \end{equation}
-\newline
 where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
@@
 Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
 
@@
 They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-
 \begin{figure}[H]
@@
 \end{figure}
-
 \subsection{Key Concepts}
@@
 vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
 % TODO : ADD STEERER MAGNET PICTURE HERE
@@
 \end{figure}
-
 Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
@@
 \end{equation}
-
 Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
@@
 \end{figure}
-
 Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
@@
 \end{figure}
-
 \begin{figure}[H]
@@
 The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
 \begin{equation}
@@
 \end{eqnarray}
-
 For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
@@
 \end{eqnarray}
-
 This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
@@
 used to solve ordinary differential equations (ODEs) that are in the following form
-
 \begin{equation} \label{eq:first-order-ODE}
@@
 \end{equation}
-
 The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
 of function evaluations at different points within each step.
-
 \begin{equation} \label{eq:general-rk}
@@
 \end{eqnarray}
-
 These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
 The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
 \begin{figure}[h!]
@@
 \end{figure}
-
 The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
@@
 \]
-
 The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
@@
 Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
 \begin{figure}[h!]
@@
 \end{figure}
-
 The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
@@
 
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
+\section{Basic Consepts in Programming}
+
+\subsection{Clock Cycle}
 
@@
 Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
 \begin{figure}[h!]
@@
 \end{figure}
-
 Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
 
-\subsubsection{Concurrency}
+\subsection{Concurrency}
 
@@
 
-\subsubsection{Object Oriented Programming}
+\subsection{Object Oriented Programming}
 
@@
 \end{eqnarray}
-
 In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
 Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
@@
 Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
@@
 \end{figure}
-
 From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
@@
 \end{eqnarray}
-
 After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
 Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
 \begin{eqnarray}
@@
 \end{eqnarray}
-
 \textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
@@
 \end{eqnarray*}
-
 Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
@@
 \end{equation}
-
 To start, an optimization criteria for the following pass such as
@@
 After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
 \begin{figure}[H]
@@
 The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 \fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
@@
 After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
 \begin{figure}[H]
@@
 \end{figure}
-
 These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
 Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
@@
 \end{figure}
-
 From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
@@
 \end{itemize}
-
 The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
@@
 \end{figure}
-
 After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
@@
 \end{figure}
-
 As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
@@
 To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
 \begin{itemize}
@@
 \end{itemize}
-
 Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
@@
 For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
-
 \begin{figure}[H]
@@
 \end{figure}
-
 Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
@@
 \end{figure}
-
 Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
@@
 Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
 \begin{figure}[H]
@@
 Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
+\begin{figure}
     \captionsetup[subfigure]{justification=centering}
@@
 \end{figure}
-
 Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
@@
 Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
+\begin{figure}
     \captionsetup[subfigure]{justification=centering}
@@
 \end{figure}
-
 The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
@@
 \end{eqnarray*}
-
 When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
@@
 \end{eqnarray}
-
 Also, observing from the data,
@@
 \end{equation}
-
 Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
@@
 Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV. 
-
 \begin{figure}[H]
@@
 \end{figure}
-
 In the first test, the beam would be injected into a static uniform electric field \\
@@
 \end{eqnarray}
-
 In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
@@
 \end{eqnarray}
-
 Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
 To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
 \begin{figure}[H]
@@
 \end{figure}
-
 Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
@@
 \end{eqnarray}
-
 \textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
 This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph}),
-
 \begin{eqnarray} \label{eq:f_lf_rk_3}
@@
 \end{eqnarray}
-
 The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
 the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
 \begin{equation}\label{eq:lf_rk_eE_relative_performance}
@@
 \end{equation}
-
 Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
@@
 After the sizable refactoring done for 3D capabilities, this implementation was obselete. 
-
 \begin{figure}[H]
@@
 \end{figure}
-
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
@@
 \end{enumerate}
-
 \textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
@@
 \end{figure}
-
 Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
@@
 The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
 \begin{figure}[h]
@@
 \end{figure}
-
 The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
@@
 Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
-
 \begin{figure}
@@
 Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
-
 \begin{figure}
@@
 In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
-
 \begin{figure}
@@
 In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
-
 \begin{figure}
@@
 \end{figure}
-
 As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
@@
 In the following figures, rendered visuals of the final design by \textit{Mr. Sinan Öz} can be observed.
-
 \begin{figure}[H]
@@
 \section{Technical Drawing}
-
 Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
-
 \begin{figure}[H]
@@
 \end{itemize}
-
 After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
@@
 which would be removed after the heat treatment.
-
 \begin{figure}
@@
     dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.114422     & 0.028398 & 0.009294 \\
-    1.00E-02 & 0.019233     & 0.036245 & 0.002182 \\
-    1.00E-03 & 0.002141     & 0.147979 & 0.00125  \\
-    9.00E-04 & 0.001749     & 0.172161 & 0.00794  \\
-    8.00E-04 & 0.001516     & 0.184629 & 0.004359 \\
-    7.00E-04 & 0.00152      & 0.20445  & 0.001919 \\
-    6.00E-04 & 0.001049     & 0.234947 & 0.004416 \\
-    5.00E-04 & 0.000974     & 0.278938 & 0.010969 \\
-    4.00E-04 & 0.0009       & 0.336847 & 0.003028 \\
-    3.00E-04 & 0.000587     & 0.441771 & 0.005859 \\
-    2.00E-04 & 0.000433     & 0.652066 & 0.006637 \\
-    1.00E-04 & 0.0002       & 1.280059 & 0.016027 \\
-    9.00E-05 & 0.000145     & 1.41908  & 0.013122 \\
-    8.00E-05 & 0.000153     & 1.592492 & 0.011332 \\
-    7.00E-05 & 0.000162     & 1.806561 & 0.009931 \\
-    6.00E-05 & 0.000123     & 2.103571 & 0.011143 \\
-    5.00E-05 & 0.000084     & 2.515006 & 0.01393  \\
-    4.00E-05 & 0.000092     & 3.140471 & 0.014138 \\
-    3.00E-05 & 0.000053     & 4.158715 & 0.009474 \\
-    2.00E-05 & 0.000045     & 6.231734 & 0.015236 \\
-    1.00E-05 & 0.000022     & 12.39871 & 0.039575 \\
-    1.00E-06 & 0.000003     & 123.318  & 0.299559
+    5.00E-02 & 0.114422     & 0.028398 & 0.009294 \\\hline
+    1.00E-02 & 0.019233     & 0.036245 & 0.002182 \\\hline
+    1.00E-03 & 0.002141     & 0.147979 & 0.00125  \\\hline
+    9.00E-04 & 0.001749     & 0.172161 & 0.00794  \\\hline
+    8.00E-04 & 0.001516     & 0.184629 & 0.004359 \\\hline
+    7.00E-04 & 0.00152      & 0.20445  & 0.001919 \\\hline
+    6.00E-04 & 0.001049     & 0.234947 & 0.004416 \\\hline
+    5.00E-04 & 0.000974     & 0.278938 & 0.010969 \\\hline
+    4.00E-04 & 0.0009       & 0.336847 & 0.003028 \\\hline
+    3.00E-04 & 0.000587     & 0.441771 & 0.005859 \\\hline
+    2.00E-04 & 0.000433     & 0.652066 & 0.006637 \\\hline
+    1.00E-04 & 0.0002       & 1.280059 & 0.016027 \\\hline
+    9.00E-05 & 0.000145     & 1.41908  & 0.013122 \\\hline
+    8.00E-05 & 0.000153     & 1.592492 & 0.011332 \\\hline
+    7.00E-05 & 0.000162     & 1.806561 & 0.009931 \\\hline
+    6.00E-05 & 0.000123     & 2.103571 & 0.011143 \\\hline
+    5.00E-05 & 0.000084     & 2.515006 & 0.01393  \\\hline
+    4.00E-05 & 0.000092     & 3.140471 & 0.014138 \\\hline
+    3.00E-05 & 0.000053     & 4.158715 & 0.009474 \\\hline
+    2.00E-05 & 0.000045     & 6.231734 & 0.015236 \\\hline
+    1.00E-05 & 0.000022     & 12.39871 & 0.039575 \\\hline
+    1.00E-06 & 0.000003     & 123.318  & 0.299559 \\\hline
     \end{tabular}
@@
     dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.055355     & 0.031054 & 0.003281 \\
-        1.00E-02 & 0.009868     & 0.063656 & 0.000893 \\
-        1.00E-03 & 0.001141     & 0.435864 & 0.005332 \\
-        9.00E-04 & 0.001325     & 0.478216 & 0.00595  \\
-        8.00E-04 & 0.001112     & 0.533789 & 0.003897 \\
-        7.00E-04 & 0.000705     & 0.60586  & 0.005441 \\
-        6.00E-04 & 0.000687     & 0.703851 & 0.009447 \\
-        5.00E-04 & 0.000474     & 0.840173 & 0.00913  \\
-        4.00E-04 & 0.00046      & 1.039166 & 0.005874 \\
-        3.00E-04 & 0.000456     & 1.378822 & 0.007995 \\
-        2.00E-04 & 0.000207     & 2.045464 & 0.008499 \\
-        1.00E-04 & 0.000127     & 4.052472 & 0.014711 \\
-        9.00E-05 & 0.000091     & 4.500401 & 0.015404 \\
-        8.00E-05 & 0.000124     & 5.048922 & 0.014392 \\
-        7.00E-05 & 0.000062     & 5.773208 & 0.031443 \\
-        6.00E-05 & 0.000057     & 6.726501 & 0.020609 \\
-        5.00E-05 & 0.00006      & 8.045931 & 0.014246 \\
-        4.00E-05 & 0.000039     & 10.04809 & 0.012756 \\
-        3.00E-05 & 0.000045     & 13.39669 & 0.028057 \\
-        2.00E-05 & 0.000023     & 20.03889 & 0.006436 \\
-        1.00E-05 & 0.000016     & 40.0818  & 0.120627 \\
-        1.00E-06 & 0.000003     & 400.2421 & 0.554172
+        5.00E-02 & 0.055355     & 0.031054 & 0.003281 \\\hline
+        1.00E-02 & 0.009868     & 0.063656 & 0.000893 \\\hline
+        1.00E-03 & 0.001141     & 0.435864 & 0.005332 \\\hline
+        9.00E-04 & 0.001325     & 0.478216 & 0.00595  \\\hline
+        8.00E-04 & 0.001112     & 0.533789 & 0.003897 \\\hline
+        7.00E-04 & 0.000705     & 0.60586  & 0.005441 \\\hline
+        6.00E-04 & 0.000687     & 0.703851 & 0.009447 \\\hline
+        5.00E-04 & 0.000474     & 0.840173 & 0.00913  \\\hline
+        4.00E-04 & 0.00046      & 1.039166 & 0.005874 \\\hline
+        3.00E-04 & 0.000456     & 1.378822 & 0.007995 \\\hline
+        2.00E-04 & 0.000207     & 2.045464 & 0.008499 \\\hline
+        1.00E-04 & 0.000127     & 4.052472 & 0.014711 \\\hline
+        9.00E-05 & 0.000091     & 4.500401 & 0.015404 \\\hline
+        8.00E-05 & 0.000124     & 5.048922 & 0.014392 \\\hline
+        7.00E-05 & 0.000062     & 5.773208 & 0.031443 \\\hline
+        6.00E-05 & 0.000057     & 6.726501 & 0.020609 \\\hline
+        5.00E-05 & 0.00006      & 8.045931 & 0.014246 \\\hline
+        4.00E-05 & 0.000039     & 10.04809 & 0.012756 \\\hline
+        3.00E-05 & 0.000045     & 13.39669 & 0.028057 \\\hline
+        2.00E-05 & 0.000023     & 20.03889 & 0.006436 \\\hline
+        1.00E-05 & 0.000016     & 40.0818  & 0.120627 \\\hline
+        1.00E-06 & 0.000003     & 400.2421 & 0.554172 \\\hline 
     \end{tabular}
@@
     dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.986005     & 0.030314 & 0.009209 \\
-    1.00E-02 & 0.154314     & 0.036833 & 0.004068 \\
-    1.00E-03 & 0.01476      & 0.131783 & 0.002352 \\
-    9.00E-04 & 0.013618     & 0.150984 & 0.005618 \\
-    8.00E-04 & 0.011863     & 0.161336 & 0.003117 \\
-    7.00E-04 & 0.010109     & 0.179693 & 0.002658 \\
-    6.00E-04 & 0.009277     & 0.205356 & 0.002912 \\
-    5.00E-04 & 0.007527     & 0.242352 & 0.003093 \\
-    4.00E-04 & 0.006084     & 0.294269 & 0.001551 \\
-    3.00E-04 & 0.00449      & 0.383982 & 0.001711 \\
-    2.00E-04 & 0.002897     & 0.563762 & 0.004214 \\
-    1.00E-04 & 0.001458     & 1.101252 & 0.008064 \\
-    9.00E-05 & 0.001376     & 1.229321 & 0.0089   \\
-    8.00E-05 & 0.001232     & 1.381441 & 0.01057  \\
-    7.00E-05 & 0.001027     & 1.574994 & 0.011933 \\
-    6.00E-05 & 0.000853     & 1.833183 & 0.006065 \\
-    5.00E-05 & 0.00074      & 2.184948 & 0.013416 \\
-    4.00E-05 & 0.000596     & 2.72503  & 0.016356 \\
-    3.00E-05 & 0.000467     & 3.617576 & 0.017581 \\
-    2.00E-05 & 0.000308     & 5.394629 & 0.027885 \\
-    1.00E-05 & 0.00015      & 10.75182 & 0.03301  \\
-    1.00E-06 & 0.000017     & 106.9198 & 0.373175
+    5.00E-02 & 0.986005     & 0.030314 & 0.009209 \\\hline
+    1.00E-02 & 0.154314     & 0.036833 & 0.004068 \\\hline
+    1.00E-03 & 0.01476      & 0.131783 & 0.002352 \\\hline
+    9.00E-04 & 0.013618     & 0.150984 & 0.005618 \\\hline
+    8.00E-04 & 0.011863     & 0.161336 & 0.003117 \\\hline
+    7.00E-04 & 0.010109     & 0.179693 & 0.002658 \\\hline
+    6.00E-04 & 0.009277     & 0.205356 & 0.002912 \\\hline
+    5.00E-04 & 0.007527     & 0.242352 & 0.003093 \\\hline
+    4.00E-04 & 0.006084     & 0.294269 & 0.001551 \\\hline
+    3.00E-04 & 0.00449      & 0.383982 & 0.001711 \\\hline
+    2.00E-04 & 0.002897     & 0.563762 & 0.004214 \\\hline
+    1.00E-04 & 0.001458     & 1.101252 & 0.008064 \\\hline
+    9.00E-05 & 0.001376     & 1.229321 & 0.0089   \\\hline
+    8.00E-05 & 0.001232     & 1.381441 & 0.01057  \\\hline
+    7.00E-05 & 0.001027     & 1.574994 & 0.011933 \\\hline
+    6.00E-05 & 0.000853     & 1.833183 & 0.006065 \\\hline
+    5.00E-05 & 0.00074      & 2.184948 & 0.013416 \\\hline
+    4.00E-05 & 0.000596     & 2.72503  & 0.016356 \\\hline
+    3.00E-05 & 0.000467     & 3.617576 & 0.017581 \\\hline
+    2.00E-05 & 0.000308     & 5.394629 & 0.027885 \\\hline
+    1.00E-05 & 0.00015      & 10.75182 & 0.03301  \\\hline
+    1.00E-06 & 0.000017     & 106.9198 & 0.373175 \\\hline
     \end{tabular}
@@
     dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.587777     & 0.034741 & 0.012735 \\
-        1.00E-02 & 0.09943      & 0.059945 & 0.001318 \\
-        1.00E-03 & 0.009987     & 0.38199  & 0.005941 \\
-        9.00E-04 & 0.007946     & 0.417119 & 0.005683 \\
-        8.00E-04 & 0.007999     & 0.466052 & 0.006398 \\
-        7.00E-04 & 0.006732     & 0.525791 & 0.003782 \\
-        6.00E-04 & 0.005541     & 0.612876 & 0.007114 \\
-        5.00E-04 & 0.005022     & 0.732091 & 0.012129 \\
-        4.00E-04 & 0.004031     & 0.906845 & 0.012156 \\
-        3.00E-04 & 0.002779     & 1.199367 & 0.014536 \\
-        2.00E-04 & 0.001897     & 1.782653 & 0.016993 \\
-        1.00E-04 & 0.000895     & 3.52464  & 0.029778 \\
-        9.00E-05 & 0.000858     & 3.916115 & 0.041066 \\
-        8.00E-05 & 0.000731     & 4.409459 & 0.040828 \\
-        7.00E-05 & 0.00066      & 5.012686 & 0.042727 \\
-        6.00E-05 & 0.000561     & 5.851793 & 0.038488 \\
-        5.00E-05 & 0.000471     & 7.002315 & 0.046152 \\
-        4.00E-05 & 0.000363     & 8.747954 & 0.063936 \\
-        3.00E-05 & 0.000264     & 11.64305 & 0.091404 \\
-        2.00E-05 & 0.000184     & 17.44533 & 0.123198 \\
-        1.00E-05 & 0.000093     & 34.93332 & 0.391012 \\
-        1.00E-06 & 0.000011     & 348.494  & 3.237203
+        5.00E-02 & 0.587777     & 0.034741 & 0.012735 \\\hline
+        1.00E-02 & 0.09943      & 0.059945 & 0.001318 \\\hline
+        1.00E-03 & 0.009987     & 0.38199  & 0.005941 \\\hline
+        9.00E-04 & 0.007946     & 0.417119 & 0.005683 \\\hline
+        8.00E-04 & 0.007999     & 0.466052 & 0.006398 \\\hline
+        7.00E-04 & 0.006732     & 0.525791 & 0.003782 \\\hline
+        6.00E-04 & 0.005541     & 0.612876 & 0.007114 \\\hline
+        5.00E-04 & 0.005022     & 0.732091 & 0.012129 \\\hline
+        4.00E-04 & 0.004031     & 0.906845 & 0.012156 \\\hline
+        3.00E-04 & 0.002779     & 1.199367 & 0.014536 \\\hline
+        2.00E-04 & 0.001897     & 1.782653 & 0.016993 \\\hline
+        1.00E-04 & 0.000895     & 3.52464  & 0.029778 \\\hline
+        9.00E-05 & 0.000858     & 3.916115 & 0.041066 \\\hline
+        8.00E-05 & 0.000731     & 4.409459 & 0.040828 \\\hline
+        7.00E-05 & 0.00066      & 5.012686 & 0.042727 \\\hline
+        6.00E-05 & 0.000561     & 5.851793 & 0.038488 \\\hline
+        5.00E-05 & 0.000471     & 7.002315 & 0.046152 \\\hline
+        4.00E-05 & 0.000363     & 8.747954 & 0.063936 \\\hline
+        3.00E-05 & 0.000264     & 11.64305 & 0.091404 \\\hline
+        2.00E-05 & 0.000184     & 17.44533 & 0.123198 \\\hline
+        1.00E-05 & 0.000093     & 34.93332 & 0.391012 \\\hline
+        1.00E-06 & 0.000011     & 348.494  & 3.237203 \\\hline
     \end{tabular}

### 2023-08-07 subsections/design/cavity/cavity.tex
thesis scripts added
design finished, simulation started
başlık eklendi

@@
 Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-
 \begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
@@
 \end{figure}
-
 One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-
 \begin{equation*}

### 2023-08-07 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
theory mostly done
multhtreading added GUI started
başlık eklendi

@@
 \end{eqnarray}
-
 This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
 
-\subsection{Runge Kutta}
+\subsection{Runge Kutta} \label{sec:rungekutta}
 
@@
 \end{figure}
-
 The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-
 \[ 

### 2023-08-17 msthesis.tex
changes from Erkcan & Gokhan hocas

@@
 \supervisor{Prof. Veysi Erkcan Özcan}
-\cosuperi{Gökhan Ünel, Ph.D.}
+\cosuperi{Assoc. Prof. Gökhan Ünel}
 %\cosuperii{Title and Name of Cosupervisor II}
-\examineri{Prof. Erhan Gülmez}
-\examinerii{Bora Işıldak , Ph.D.}
+\examineri{Asst. Prof. Bora Akgün}
+\examinerii{Assoc. Prof. Bora Işıldak}
 %\examineriv{}
@@
 \begin{abstract}
-One page abstract will come here.  
+    The focus of this study is to design and optimize rose-pattle-type electron accelerators; a new simulation tool called \textit{Rhodotron Simulation} has been developed for this purpose.
+    A coaxial cavity with an operating frequency of $107.5$ MHz is currently being manufactured in the Kandilli Detector Accelerator and Instrumentation Laboratory (KAHVELab).
+    This new tool's capabilities will be tested with the cavity and will be used to design complementary bending magnets for reaching $1-5$ MeV beam energy.
 \end{abstract}
@@
 \begin{ozet}
-Bir sayfa uzunluğunda özet gelecektir.
+Bu çalışma, gül yaprağı tipi elektron hızlandırıcıları tasarlamak ve optimize etmek üzerine odaklanmaktadır. 
+Bu amaçla \textit{Rhodotron Simulation} adında yeni bir benzetim uygulaması geliştirilmiş, $107.5$ MHz hedef frekansında çalışmak üzere tasarlanmış bir koaksiyal kavitesinin üretimi, Kandilli Algıç Hızlandırıcı ve Enstrümentasyon Laboratuvarı'nda devam etmektedir.
+Yeni benzetim uygulaması, kabiliyetleri üretilen kavite ile test edildikten sonra bükme mıknatısları tasarım ve optimizasyonunda $1-5$ MeV demet enerjisine ulaşmak için kullanılacaktır.
 \end{ozet}
@@
 \listoftables
+
+% LIST OF SYMBOLS PAGE
+\begin{symbols}
+    % The title will be typeset as "LIST OF SYMBOLS".
+    % Use a separate \sym command for each symbols definition.
+    % First, Latin symbols in alphabetical order
+    \sym{$\vec{a}$}{Acceleration}
+    \sym{\textbf{$\vec{B}$}}{Magnetic field}
+    \sym{c}{Speed of light in vacuum}
+    \sym{E}{Energy}
+    \sym{\textbf{$\vec{E}$}}{Electric field}
+    \sym{f}{Frequency}
+    \sym{$\vec{F}$}{Force}
+    \sym{$\vec{p}$}{Momentum}
+    \sym{$\vec{r}$}{Position}
+    \sym{t}{Time}
+    \sym{T}{Period}
+    \sym{$\vec{v}$}{Velocity}
+    \sym{Z}{Shunt Impedance}
+    % 1 EMPTY LINE BETWEEN LATIN AND GREEK SYMBOLS GROUP!!!
+    \sym{}{}
+    % Then Greek symbols in alphabetical order
+    \sym{$\gamma$}{Lorentz Factor}
+    \sym{$\beta$}{Beta Factor}
+    \sym{$\phi_{lag}$}{Phase Lag}
+
+    \sym{$\mu X$}{Mean Value of X}
+    \sym{$\sigma X$}{Standard Deviation of X}
+    \sym{}{}
+\end{symbols}
+
+% LIST OF ABBREV PAGE
+\begin{abbreviations}
+    % Abbreviations in alphabetical order
+   \sym{2D}{One Dimensional}
+   \sym{2D}{Two Dimensional}
+   \sym{3D}{Three Dimensional}
+   \sym{eV}{Electron Volt}
+   \sym{Hz}{Hertz}
+   \sym{KAHVELab}{Kandilli Detector Accelerator and \\Instrumentation Laboratory}
+   \sym{Linac}{Linear Particle Accelerator}
+   \sym{ODE}{Ordinary Differential Equation}
+   \sym{RF}{Radio Frequency}
+   \sym{s}{Second}
+   \sym{T}{Tesla}
+   \sym{V}{Volt}
+
+\end{abbreviations}
 
@@
 
+\newcommand{\fromch}[1]{\textit{chapter \ref{ch:#1}}}
+
 \newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
@@
 
-% START OF THEORY
-
-\chapter{THEORY}
+% START OF INTRODUCTION AND THEORY
+
+\chapter{INTRODUCTION AND THEORY}
+
+Particle accelerators are essential tools for scientific research.
+They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
+Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and more recently the Higgs boson. 
+They also facilitate the production of high-intensity particle beams for applications in industrial processes. A conservative estimate puts the number of industrial high-current electron
+accelerators to be in the thousands, worldwide.
+
+MeV-level electron beams, both as is and as X-Ray sources, are especially useful for industrial and medical applications. 
+For example, high-energy beams (5–10 MeV) are used in medical accelerators and provide services such as medical device sterilization and food irradiation;
+with medium energy devices (400 keV–5 MeV) wires, cables and tires are improved, factory flue gases or wastewater can be treated.
+Although most of the industrial electron accelerators operating at MeV-level are linear accelerators at the moment, due to their compact nature, circular accelerators have been gaining prominence.
+
+Rose-pattle accelerator is a type of circular accelerator suitable for producing electron beams at MeV-level energy. 
+It that was developed in 1989 and was named \textit{Rhodotron} \cite{rhodo_pottier}. This name was trademarked by \textit{IBA Group} in the following years.
 
@@
 \subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
+In classical mechanics, Newton's second law defines force, $\vecthreeBF{F}$, and states 
 \begin{equation} \label{eq:newton_second_law}
@@
 \end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
+where $\vecthreeBF{p}$ is the momentum, $m\vecthreeBF{v}$ of the particle.
+In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor:
+\begin{equation}
+    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = = \frac{1}{\sqrt{1-\beta^2}}
+            = \frac{1}{\sqrt{1- (\dotProd{v}{v})/ c^2}} =  \frac{1}{\sqrt{1- \dotProd{\beta}{\beta}}}
+\end{equation}
+Considering these two statements, we can find the relation between momentum and acceleration as follows:
+\begin{eqnarray}
     \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
@@
     \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
+\end{eqnarray}
+thus,
 \begin{equation} \label{eq:Frel}
@@
 
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
+To start separating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
 \begin{equation} \label{eq:a_F_parallels}
@@
 \end{equation}
-\begin{eqnarray*}
+\begin{eqnarray}
     \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
                                 &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
+\end{eqnarray}
 Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
+\begin{equation}
     \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
+\end{equation}
+inserting this into \fromeq{a_F_parallels},
 \begin{eqnarray}
@@
 Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
+\begin{eqnarray}
     \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
@@
                     &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
+\end{eqnarray}
+We finally have two separate equations which are in similar form with \fromeq{newton_second_law}.
 \begin{equation} \label{eq:Frel_para_and_perp}
@@
 \end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
+where $ \partial \tau = \partial t / \gamma $ and greek letters are Lorentz indices,
 \begin{equation}
@@
 \end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
+where $W$ is the energy of the particle and $\gamma$ is the Lorentz factor mentioned in the previous section.
 
@@
 
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
+\subsection{Acceleration caused by Lorentz force}
+Due to the nature of the cross product, Lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
 Therefore the acceleration of the magnetic field is straightforward
@@
 \end{equation}
-
-\newpage
+where $\vecthreeBF{a}_{E}$ consists of two components in the direction of $\vecthreeBF{E}$ and $\vecthreeBF{v}$.
+The component in the direction of $\vecthreeBF{v}$ depends on the $\dotProdBF{E}{v}$, 
+resulting in $\vecthreeBF{a}_{E} || \vecthreeBF{E}$ if $\vecthreeBF{E} \perp \vecthreeBF{v}$.
 
@@
 At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
+These fields are generated by intricate arrangements of electromagnets and RF (radiofrequency) cavities within the accelerator structure. 
+By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, thus to high energies.
 
@@
 The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
+As they progress through the accelerator, they are subjected to electric fields that accelerate them, while magnetic fields guide their trajectories.
+Focusing elements, such as solenoid, dipole or quadrupole magnets, ensure the particles remain tightly controlled.
 
@@
 Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
 % TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear proton accelerator in KAHVELab}
+    \includegraphics[width=.9\textwidth]{./figures/kahvelab_linac.png}
+    \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
+    \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
+    \caption{An RF cavity used in KAHVELab}
 \end{figure}
@@
 vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A bending magnet used in KAHVELab}
-\end{figure}
 
@@
 
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
+Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in 1989 \cite{rhodo_pottier}. 
+First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. It is named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
 
 The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and bending magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
+RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron injector.
+
+\subsubsection{Acceleration cycle of Rhodotron}
+
+Electrons undergo four different stages during a single pass. 
+They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
+
+\begin{description}
+    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+(\fromfig{rhod_cycle_1})
+    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed. (\fromfig{rhod_cycle_2})
+    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+(\fromfig{rhod_cycle_3})
+    \item[Recirculating Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+(\fromfig{rhod_cycle_4})
+\end{description}
+
+This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
+After the desired amount of cycles, also called passes, has been completed, the electrons exit the accelerator.
+
+This process is explained further in the \fromfigf{rhod_cycle_1}{rhod_cycle_2}{rhod_cycle_3}{rhod_cycle_4} where $T$ is the period of the electric field.
 
@@
     \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
+    W_1 = Z_{sp}^{1/2} P^{1/2} \cos \phi  
 \end{equation}
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
+where $P$ is the dissipated power, $\phi$ is the phase lag, typically taken as $15^\circ$ \cite{rhodo_pottier}.
 
@@
 \end{figure}
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
+Total energy gain after $n$ passes, $W$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
 \begin{equation}
@@
 
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-See \fromfig{rhod_cycle_1}
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.See \fromfig{rhod_cycle_2}
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-See \fromfig{rhod_cycle_3}
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-See \fromfig{rhod_cycle_4}
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
 \begin{figure}[H]
@@
 
+\section{Basic Concepts in Programming}
+
+\subsection{Clock Cycle}
+
+In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
+It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
+
+A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
+It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
+Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
+
+The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
+Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
+Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
+    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
+\end{figure}
+Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
+
+Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
+
+\subsection{Concurrency}
+
+Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
+It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
+
+Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
+This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
+True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
+
+Programs that implement concurrency using multiple cores executes more operations per clock cycle. 
+However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
+
+Threads utilize \textit{mutexes}, short for "mutual exclusion," 
+to synchronize and manage access to shared resources 
+in a multi-threaded or multi-process environment.
+
+\subsection{Object Oriented Programming}
+
+Object-Oriented Programming (OOP) is a programming paradigm that revolves around the concept of objects. 
+Definition called class serves as a blueprint that defines the structure and behavior of objects. 
+Each object encapsulates both data, and the functions that manipulate that data. 
+This encapsulation promotes modular code design and enhances data security by controlling access to the object's internal state.
+
+In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
+\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
+By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
+
 \newpage
 
-\section{Numerical Integration Methods}
+% START OF common_start_tools.tex
+
+\chapter{TOOLS}
+
+For the purpose of designing, enhancing, and optimizing particle accelerators, certain tools can be employed. 
+The following sections will explore several of the software and algorithms that were put to use.
+
+\section{Simulation}
+A simulation software is a computer program or tool that enables the creation and execution of 
+simulations to model and analyze real-world systems or processes. 
+It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
+providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
+
+Simulation software provides a virtual environment where users can define the parameters,
+variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
+algorithms, and computational techniques to simulate the behavior of the system over time.
+
+% START OF available.tex
+
+\section{Available Tools}
+
+\subsection{Poisson Superfish}
+Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
+for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments \cite{poi-sup}.
+It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
+
+\subsection{CST Studio Suite}
+CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
+It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
+The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
+
+\subsection{ROOT}
+ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
+visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
+like the Large Hadron Collider (LHC) \cite{root}. It has become an essential tool in particle physics research, 
+and it's used by physicists around the world to analyze and interpret data.
+
+\subsection{gnuplot}
+GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs  \cite{gnuplot}. 
+It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
+to represent and analyze data in a graphical format.
+
+\section{Algorithms}
 
@@
 
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
+The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta \cite{runge} \cite{kutta}, family of numerical methods
 used to solve ordinary differential equations (ODEs) that are in the following form
@@
 
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\section{Basic Consepts in Programming}
-
-\subsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle. 
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-Threads utilize \textit{mutexes}, short for "mutual exclusion," 
-to synchronize and manage access to shared resources 
-in a multi-threaded or multi-process environment.
-
-\subsection{Object Oriented Programming}
-
-Object-Oriented Programming (OOP) is a programming paradigm that revolves around the concept of objects. 
-Definition called class serves as a blueprint that defines the structure and behavior of objects. 
-Each object encapsulates both data, and the functions that manipulate that data. 
-This encapsulation promotes modular code design and enhances data security by controlling access to the object's internal state.
-
-In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
-\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
-By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
-
-\newpage
-
-% START OF tools.tex
-
-\chapter{TOOLS}
-
-\section{Poisson Superfish}
-Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
-for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
-It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
-
-\section{CST Studio Suite}
-CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
-It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
-The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
-
-\section{ROOT}
-ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
-visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
-like the Large Hadron Collider (LHC). It has become an essential tool in particle physics research, 
-and it's used by physicists around the world to analyze and interpret data.
-
-\section{gnuplot}
-GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs. 
-It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
-to represent and analyze data in a graphical format.
-
-\newpage
-
 % START OF DESIGN
@@
 \chapter{DESIGN}
+
+In this chapter, the primary design factors of rhodotron-type accelerators are examined, along with an exploration of the design created within the \textit{KAHVELab}. 
+Rhodotron-type accelerators are composed of two principal components: a coaxial acceleration cavity and recirculating magnets. 
+The cavity's design is of utmost significance for attaining resonance and improving beam-RF interactions, while the magnet design focuses on preserving the beam's phase stability.
 
@@
 
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
+In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and it will be the focus of all further calculations.
+Using $f_{RF}=107.5$ MHz \& $f_{RF}=180$ MHz for comparison:
 \begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
@@
 
-\newpage
-
 \section{Magnet Design} \label{sec:magnet_design}
@@
       \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
     \end{subfigure}%
@@
       \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
+    \end{subfigure}
+    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}}
     \label{fig:magnet_design_illustrations}
@@
 This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
+Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass.
 
@@
 As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
+In other words, total trajectory of synchronous particle needs to satisfy the following equality:
+\begin{equation}
     L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
+\end{equation} 
+Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice:
 \begin{equation}
@@
 \end{figure}
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
+From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
+$L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
+    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
+    \rho &=&  \tan (\gamma) (R_2 + d + L) \nonumber\\
+    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
+    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda \nonumber\\
+    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}} \label{eq:magnet_rho_constraint} \\
+    L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 \label{eq:magnet_L_constraint}
 \end{eqnarray}
@@
 
-\newpage
-
 \section{Initial Design at KAHVELab}
@@
 A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
+Frequency was selected to benefit from the RF power supply units at hand.
 After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
@@
 
-In KAHVELab, several improvements were made to these initial designs together with \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
+Several improvements were made to KAHVELab Rhodotron initial designs \cite{sinan}.
+These include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
 Improved designs can be seen in the figures below.
@@
 
-\chapter{SIMULATION}
+\chapter{SIMULATION} \label{ch:simulation}
+
+After considering the lack of design and simulation software available for \textit{Rhodotron-type} accelerators, 
+together with the energy gain disagreement between \textit{CST Studio} and the calculations of \textit{J. Pottier} in \fromeq{W_gain_each_pass_pottier},
+the need for a custom built tool became apparent. A simple 1D proof of concept was quickly implemented for this purpose.
 % Start of poc.tex
 \section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
+The POC worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
 Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
@@
 
-\newpage
-
 % Start of intermediate.tex
@@
 Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
+For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (\fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
 
@@
 \end{figure}
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+Where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
 
@@
 To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
+Results from these tests can be observed in \fromfig{lf_rk2_perp_stat_E_comparison} and \fromfig{lf_rk2_par_stat_E_comparison} of \fromapp{data_graph}.
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.9\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
@@
     \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
 \end{figure}
@@
 It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
+Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
 
@@
 see a specific time frame, export as snapshot or animated gif file.
-Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
+Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
 \begin{figure}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_2}
-\end{figure}
-
 \subsection{Analyze Frame}
 Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
+In the current version, \textbf{E} distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
 This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
+In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
 \begin{figure}
     \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
     \caption{Analyze frame of \textit{GUI} E distribution.}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et2}
-\end{figure}
-
 \subsection{Sweep Frame}
@@
 $\phi_{lag}$ sweep was the first parameter to be implemented.
-It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
+
+It takes the range of sweep, draws $\phi_{lag}$ vs $\mu E$, $\phi_{lag}$ vs $\sigma E$ and $\phi_{lag}$ vs $\sigma R$ mentioned in \fromsec{philag_sweep}.
 This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
+In the \fromfigf{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_running}{gui_sweep_sR} of \fromapp{supp}, this frame can be inspected in detail.
+
 \begin{figure}
     \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
-    \label{fig:gui_sweep_running}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
@@
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
-    \label{fig:gui_sweep_sR}
-\end{figure}
+
 As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
@@
 \chapter{PRODUCTION}
+
+As discussed before, production efforts of a \textit{Rhodotron-type} accelerator are still ongoing in KAHVELab.
+This accelerator will be used at $f=107.5$MHz $P=50-100$kW to achieve beams with the energy range of $1-5$MeV.
 % Start of final.tex
 \section{Final Design} \label{sec:final_design}
-
-As discussed before, production efforts of a rhodotron type accelerator is still ongoing in KAHVELab.
-This accelerator will be used at $f=107.5$MHz $P=50-100$kW. 
-In the following figures, rendered visuals of the final design by \textit{Mr. Sinan Öz} can be observed.
+In the following figures, rendered visuals of the final design can be observed \cite{sinan}.
 \begin{figure}[H]
@@
 
-\newpage
-
 % Start of techd.tex
 \section{Technical Drawing}
-Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1\linewidth]{./figures/teknikcizim/altgovdeteknikresim.pdf}
-    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
+Technical drawings of the design mentioned in \fromsec{final_design} can be found in \fromfigs{techd_rhod}{techd_mid}, \fromfig{techd_up} of \fromapp{supp}.
 \begin{figure}
@@
     \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
-    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
+    \caption{Technical drawing of the rhodotron cavity. \cite{sinan}}
+    \label{fig:techd_rhod}
 \end{figure}
@@
     \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
-    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.2.00.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
     \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\newpage
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \cite{sinan}}
+    \label{fig:techd_mid}
+\end{figure}
 
@@
 
-\newpage
-
 % Start of rf.tex
@@
 
-\chapter{FUTURE WORK}
-
+\chapter{CONCLUSION}
 At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
@@
 
-\section{Cavity}
-The cavity manufacturing process is in its concluding stages.
+\section{Future Work}
+Regarding the cavity manufacturing process, it is in the concluding stages.
 The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
@@
 
-\section{Magnets}
-Magnet production was decided to be kept on hold in the early stages of the project, 
+As far as the magnets concerned, it was decided to be kept on hold in the early stages of the project, 
 due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
@@
 
-\section{Rhodotron Simulation}
-
-\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
+\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
 several improvements and new feature implementations are underway in the mean time. 
@@
 \end{figure}
-
-\section{Conclusion}
-
-In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
+After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
+Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunuties.
+
+\section{Discussion}
+In conclusion, a new computational \eEM interaction simulation and analysis tool that focuses on designing and improving \textit{Rhodotron-type} accelerators has been successfully developed; 
+a \textit{Rhodotron-type} accelerator with an operating frequency of $107.5$ MHz and a target energy of $1-5$ MeV has been designed and is currently being manufactured.
+
+The software features a robust GUI that is capable of rendering and analyzing simulation results.
+Leap-frog and Runge-Kutta numerical methods have been implemented for initial speed and accuracy tests.
+The real-world performance and accuracy of this new tool, on the other hand, cannot be tested
 before the cavity production is completed and the performance is compared with the predictions of the tool;
-however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
-lead to the inference that this tool holds promise.
+however, the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
+lead to the inference that it holds promise.
 
@@
 
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
+    \end{subfigure}
+
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
+    \end{subfigure}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
+    \label{fig:lf_rk2_par_stat_E_comparison}
+\end{figure}
+
 \begin{table}[H]
@@
 \end{table}
+
+\chapter{Supporting Figures} \label{appendix:supp}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
+    \caption{Technical drawing of upper part of the cavity. \cite{sinan}}
+    \label{fig:techd_up}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
+    \caption{Simulate frame of \textit{GUI}.}
+    \label{fig:gui_simulate_1}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
+    \caption{Render frame of \textit{GUI}.}
+    \label{fig:gui_render_2}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
+    \caption{Analyze frame of \textit{GUI} E(t).}
+    \label{fig:gui_analyze_Et2}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
+    \label{fig:gui_sweep_running}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
+    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
+    \label{fig:gui_sweep_sR}
+\end{figure}
 % START OF BIBLIOGRAPHY
@@
 
+    \bibitem{runge}
+    Runge, Carl David Tolmé (1895), \emph{Über die numerische Auflösung von Differentialgleichungen}, Mathematische Annalen, Springer, 46 (2): 167–178.
+
+    \bibitem{kutta}
+    Kutta, Wilhelm (1901), \emph{Beitrag zur näherungsweisen Integration totaler Differentialgleichungen}, Zeitschrift für Mathematik und Physik, 46: 435–453.
+
     \bibitem{cite:rhodo_design}
@@
 
+    \bibitem{sinan}
+    Privite communication, Sinan ÖZ
+
+    \bibitem{gnuplot}
+    Williams, T. and Kelley, C. (2020). Gnuplot 5.4: An Interactive
+    Plotting Program. URL http://gnuplot.info.
+
+    \bibitem{root}
+    Rene Brun and Fons Rademakers, ROOT - An Object Oriented Data Analysis Framework,
+    Proceedings AIHENP'96 Workshop, Lausanne, Sep. 1996,
+    Nucl. Inst. \& Meth. in Phys. Res. A 389 (1997) 81-86.
+    See also "ROOT" [software], Release v6.20/04, 01/04/2020,
+    (https://zenodo.org/record/3895855).
+
+    \bibitem{poi-sup}
+    J. H. Billen and L. M. Young, “Poisson Superfish,” LA-UR-96-1834.
+
+    \bibitem{kahvelab_linac}
+    A. Adıgüzel, S. Açıksöz, A. Çağlar, H. Çetinkaya, Ş. Esen, D. Halis, A. Hamparsunoğlu, T.B. İlhan, A. Kılıçgedik, O. Koçer, S. Oğur, S. Öz, A. Özbey, V.E. Özcan and N.G. Ünel
+    \emph{Ion source and LEBT of KAHVELab proton beamline},
+    Journal of Instrumentation,
+    Volume 18, January 2023
+
 \end{thebibliography}

### 2023-08-17 subsections/design/magnet/magnet.tex
changes from Erkcan & Gokhan hocas

@@
       \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
     \end{subfigure}%
@@
       \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
     \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
+    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}}
     \label{fig:magnet_design_illustrations}

### 2023-08-17 subsections/future/future_work.tex
changes from Erkcan & Gokhan hocas

@@
 \end{figure}
+After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
+Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunuties.
 
-\section{Conclusion}
+\section{Discussion}
+In conclusion, a new computational \eEM interaction simulation and analysis tool that focuses on designing and improving \textit{Rhodotron-type} accelerators has been successfully developed; 
+a \textit{Rhodotron-type} accelerator with an operating frequency of $107.5$ MHz and a target energy of $1-5$ MeV has been designed and is currently being manufactured.
 
-In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
+The software features a robust GUI that is capable of rendering and analyzing simulation results.
+Leap-frog and Runge-Kutta numerical methods have been implemented for initial speed and accuracy tests.
+The real-world performance and accuracy of this new tool, on the other hand, cannot be tested
 before the cavity production is completed and the performance is compared with the predictions of the tool;
-however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
-lead to the inference that this tool holds promise.
+however, the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
+lead to the inference that it holds promise.
 %%%%%%

### 2023-08-17 subsections/production/technical_drawings/techd.tex
başlık eklendi
changes from Erkcan & Gokhan hocas

--- 2023-07-18 subsections/production/manifacturing/mani.tex
@@
 %%%%%%
-% Start of mani.tex
-\section{Manifacturing}
+% Start of techd.tex
+\section{Technical Drawing}
+Technical drawings of the design mentioned in \fromsec{final_design} can be found in \fromfigs{techd_rhod}{techd_mid}, \fromfig{techd_up} of \fromapp{supp}.
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.98\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
+    \caption{Technical drawing of the rhodotron cavity. \cite{sinan}}
+    \label{fig:techd_rhod}
+\end{figure}
 
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line. \cite{sinan}}
+    \label{fig:techd_mid}
+\end{figure}
 %%%%%%

### 2023-08-17 subsections/simulation/gui/gui.tex
changes from Erkcan & Gokhan hocas

@@
 It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
+Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
 
@@
 
+\subsection{Analyze Frame}
+Analyze frame provides tools for analyzing and visualizing the simulation data. 
+In the current version, \textbf{E} distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
+This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
+In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
 \begin{figure}
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_2.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_2}
-\end{figure}
-
-\subsection{Analyze Frame}
-Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
-This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
     \caption{Analyze frame of \textit{GUI} E distribution.}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_2.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et2}
-\end{figure}
-
 \subsection{Sweep Frame}
@@
 $\phi_{lag}$ sweep was the first parameter to be implemented.
-It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
+
+It takes the range of sweep, draws $\phi_{lag}$ vs $\mu E$, $\phi_{lag}$ vs $\sigma E$ and $\phi_{lag}$ vs $\sigma R$ mentioned in \fromsec{philag_sweep}.
 This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
+In the \fromfigf{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_running}{gui_sweep_sR} of \fromapp{supp}, this frame can be inspected in detail.
+
 \begin{figure}
     \centering
-    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
-    \label{fig:gui_sweep_running}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
@@
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_sweep_sR.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
-    \label{fig:gui_sweep_sR}
-\end{figure}
+
 As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.

### 2023-08-17 subsections/simulation/intermediate_versions/intermediate.tex
changes from Erkcan & Gokhan hocas

@@
     \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{../../../figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
 \end{figure}

### 2023-08-17 subsections/simulation/poc/poc.tex
changes from Erkcan & Gokhan hocas

@@
 \section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
+The POC worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
 Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;

### 2023-08-17 subsections/theory/common/common_start_theory.tex
changes from Erkcan & Gokhan hocas

@@
 \pagenumbering{arabic}
-
-%#####
-% START OF THEORY
-
 \newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
@@
 
-\chapter{THEORY}
+%#####
+% START OF INTRODUCTION AND THEORY
+
+\chapter{INTRODUCTION AND THEORY}
+
+Particle accelerators are essential tools for scientific research.
+They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
+Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and more recently the Higgs boson. 
+They also facilitate the production of high-intensity particle beams for applications in industrial processes. A conservative estimate puts the number of industrial high-current electron
+accelerators to be in the thousands, worldwide.
+
+MeV-level electron beams, both as is and as X-Ray sources, are especially useful for industrial and medical applications. 
+For example, high-energy beams (5–10 MeV) are used in medical accelerators and provide services such as medical device sterilization and food irradiation;
+with medium energy devices (400 keV–5 MeV) wires, cables and tires are improved, factory flue gases or wastewater can be treated.
+Although most of the industrial electron accelerators operating at MeV-level are linear accelerators at the moment, due to their compact nature, circular accelerators have been gaining prominence.
+
+Rose-pattle accelerator is a type of circular accelerator suitable for producing electron beams at MeV-level energy. 
+It that was developed in 1989 and was named \textit{Rhodotron} \cite{rhodo_pottier}. This name was trademarked by \textit{IBA Group} in the following years.

### 2023-08-17 subsections/theory/programming/programming.tex
changes from Erkcan & Gokhan hocas

--- 2023-08-07 msthesis.tex
@@
-\documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
-\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
-\usepackage{amsmath, amsthm} % Some extra symbols
-\usepackage[bottom]{footmisc}
-\usepackage{cite}
+\documentclass{article}
+
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
-\usepackage{longtable}
+\usepackage{tikz}
 \usepackage{float}
-\usepackage{multirow}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{array}
-\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
-\usepackage{epsfig}
-\usepackage{epstopdf}
-\usepackage{amsmath}
-\usepackage{notoccite}
-\usepackage{subcaption}
+\usepackage{wrapfig,lipsum}
+\usepackage{svg}
+\usepackage{mathtools}
 \usepackage{tabu}
-\usepackage{minted}
-\usepackage{xcolor}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 
-\usemintedstyle{xcode}
-\definecolor{bg}{rgb}{0.95,0.95,0.95}
-
-\interdisplaylinepenalty=2500
-\hyphenation{lists} \makeatletter
-
-\newcommand{\field}[1]{\mathbb{#1} }
-\newcommand{\beq}{\begin{equation} \setlength\abovedisplayskip{5pt} 
-\setlength\belowdisplayskip{5pt}}
-\newcommand{\eeq}{\end{equation}}
-\newcommand{\bea}{\begin{eqnarray}}
-\newcommand{\eea}{\end{eqnarray}}
-\newcommand{\defn}{\stackrel{\triangle}{=}}
-\newcommand{\nn}{\nonumber}
-\newcommand{\nnl}{\nonumber \\}
-\renewcommand{\theequation}{\arabic{equation}}
-\renewcommand{\labelenumi}{(\roman{enumi})}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\def\ifundefined{\@ifundefined}
-\def\bfat{\left[ \begin{array}}
-\def\emat{\end{array} \right]}
-\def\bfatt{\left\{ \begin{array}}
-\def\ematt{\end{array} \right.}
-\def\bset{\left\{ \begin{array}}
-\def\eset{\end{array} \right\}}
-\def\bpar{\left( \begin{array}}
-\def\epar{\end{array} \right)}
-
-\graphicspath{{figures/}} % Graphics will be here
-
-\newtheorem{thm}{Theorem}[chapter]
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
-
-\numberwithin{equation}{chapter}
-
-% BEGIN OF DOCS
 \begin{document}
-\pagenumbering{roman}
-
-% CONTENTS AND LIST OF FIG AND TABLE PAGES
-\tableofcontents
-
-\pagenumbering{arabic}
 
@@
 
-\newcommand{\e}{$\textbf{e}^-$ }
-\newcommand{\egun}{$\textbf{e}^-$-gun }
-\newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
-\newcommand{\eE}{$\textbf{e}^-$ - $\vecthreeBF{E}$ }
-\newcommand{\eEM}{$\textbf{e}^-$ - \textbf{EM} }
-\newcommand{\ee}{$\textbf{e}^-$ - $\textbf{e}^-$ }
-
 \newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
 \newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
 
-\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
-\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
-\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
-\newcommand{\fromfigsix}[6]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
+\newcommand{\fromch}[1]{\textit{chapter \ref{ch:#1}}}
 
-\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+%----../../..++++.
 
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
+%%%%%%
 
-\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
-\newcommand{\fromtabf}[4]{\textit{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}}
+\section{Basic Concepts in Programming}
 
-% START OF intro.tex
-
-\chapter{INTRODUCTION}
-
-\newpage
-
-% START OF THEORY
-
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear proton accelerator in KAHVELab}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\subsubsection{Resonance Frequency}
-Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
-It is determined by the physical dimensions and the speed of light in the cavity's medium. 
-In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
-\begin{equation}
-    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
-    \label{eq:f_r_rec}
-\end{equation}
-Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
-
-\subsubsection{Bunch}
-Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
-
-\subsubsection{Phase Stability}
-Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
-It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
-which is crucial for achieving efficient particle acceleration. 
-Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
-ensuring that they receive the correct energy boosts and interact predictably with detectors. 
-Deviations in phase stability can lead to particle loss and decreased beam quality.
-
-\subsubsection{Phase Lag}
-Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
-It describes the difference in phase angles within their respective cycles, between two signals.
-
-\subsubsection{Shunt Impedance}
-The shunt impedance of an RF accelerator is a measure of the efficiency 
-at which the accelerator can transform the supplied RF power into acceleration.
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Bending Magnets}
-Bending magnets, also known as dipole magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A bending magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and bending magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-See \fromfig{rhod_cycle_1}
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.See \fromfig{rhod_cycle_2}
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-See \fromfig{rhod_cycle_3}
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-See \fromfig{rhod_cycle_4}
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod1.pdf}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_1}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod2.pdf}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_2}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod3.pdf}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_3}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod4.pdf}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_4}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta} \label{sec:rungekutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
+\subsection{Clock Cycle}
 
@@
 Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
 \begin{figure}[h!]
     \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
+    \includegraphics[width=.9\textwidth]{../../../figures/cpu_instruction_speed.png}
     \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
 \end{figure}
-
 Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
 
-\subsubsection{Concurrency}
+Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
+
+\subsection{Concurrency}
 
@@
 
-\newpage
-
-% START OF tools.tex
-
-\chapter{TOOLS}
-
-\section{Poisson Superfish}
-Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
-for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
-It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
-
-\section{CST Studio Suite}
-CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
-It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
-The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
-
-\section{ROOT}
-ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
-visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
-like the Large Hadron Collider (LHC). It has become an essential tool in particle physics research, 
-and it's used by physicists around the world to analyze and interpret data.
-
-\section{gnuplot}
-GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs. 
-It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
-to represent and analyze data in a graphical format.
-
-\newpage
-
-% START OF DESIGN
-
-\chapter{DESIGN}
-
-\section{Cavity Design} \label{sec:cavity_design}
-
-The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
-
-By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
-This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
-For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
-    \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
-    \end{aligned}
-\end{eqnarray}
-
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:107_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:180_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:cst_simple_cavity_designs}
-\end{figure}
-
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson SUPERFISH field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_superfish}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST eigenmode results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_eigenmode}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST electric field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_field}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
-      \caption{107.5 MHz unmodified}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
-      \caption{180 MHz unmodified}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
-    \label{fig:107_cavity_shunt_diff}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
-    \label{fig:180_cavity_shunt_diff}
-\end{figure}
-
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
-    \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta Z_{180}=2.7\%
-    \end{aligned}
-\end{equation*}
-
-\newpage
-
-\section{Magnet Design} \label{sec:magnet_design}
-Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
-Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
-Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
-    \label{fig:magnet_design_illustrations}
-\end{figure}
-
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
-
-Two different approaches have been used to achieve phase stability.
-These approaches are discussed further in the following sections.
-
-\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
-
-First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
-
-To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
-As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
-    L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
-
-\begin{figure}[H]    
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
-    \label{fig:magnet_design}
-\end{figure}
-
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
-
-After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
-Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
-\begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
-
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
-Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
-Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
-
-\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
-
-As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
-This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
-This scenario can happen when RF power is not sufficiently high.
-
-Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
-after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
-It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
-For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
-Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
-
-Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
-
-To start, an optimization criteria for the following pass such as
-\begin{itemize}
-    \item Ensure the phase stability of the synchronous electron
-    \item Maximize the energy gain of the synchronous electron
-    \item Minimize the energy spread of the beam
-    \item Minimize the phase lag spread of the beam
-    \item All of the above with decided weights
-\end{itemize}
-needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
-This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
-
-However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
-
-\newpage
-
-\section{Initial Design at KAHVELab}
-
-A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
-After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
-    \label{fig:initial_design}
-\end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
-      \caption{Axial cross section.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
-      \caption{Cross section at acceleration plane.}
-    \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
-    \label{fig:initial_design_cross_section}
-\end{figure}
-The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
-    \end{subfigure}
-    \caption{Initial magnet design.}
-    \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
-    \label{fig:initial_three_magnet_design}
-\end{figure}
-
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
-Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
-
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
-
-In KAHVELab, several improvements were made to these initial designs together with \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
-Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
-    \end{subfigure}
-    \caption{Improved cavity design.}
-    \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \caption{Improved magnet design.}
-    \label{fig:improved_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
-    \end{subfigure}
-    \caption{Cross section and coils of improved magnet design.}
-    \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \caption{Magnetic field in acceleration plate of improved magnet design.}
-    \label{fig:improved_magnet_design_B}
-\end{figure}
-
-From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
-This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
-
-\newpage
-
-% START OF SIMULATION
-
-\chapter{SIMULATION}
-% Start of poc.tex
-\section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
-\begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
-    \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
-    \end{enumerate}
-\end{itemize}
-
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \caption{Core logic loop of the POC}
-    \label{fig:POC_core_logic}
-\end{figure}
-
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
-Since using a single software would have made the process error prone.
-
-After the results obtained from \textit{POC} were found to be promising, a decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
-The development and improvement efforts are still ongoing.
-
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
-The following sections in this chapter investigates their implementations further.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
-Initial step of improving \textit{POC} towards \textit{Rhodotron Simulation} was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-One can sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs from this intermediate build can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of \textit{OOP}, details of which can be seen in \fromfigsix{e_class}{bunch_class}{gun_class}{sim_class}{rhodosim_class}{rf_class} of \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired into a uniform magnetic field of $0.1$T located in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph}),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation 
-(see \fromfig{console_output_running} in \fromapp{example_simulation_runs} for example console notification, \fromfig{ui_thread} in \fromapp{intermediate_codes} for implemenation)
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Graphical User Interface}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
-    \caption{The configuration frame of implementated first GUI design.}
-    \label{fig:gui_config}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
-
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
-
-\subsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\subsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
-
-\subsection{Render Frame}
-Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
-see a specific time frame, export as snapshot or animated gif file.
-Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_1}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_2}
-\end{figure}
-
-\subsection{Analyze Frame}
-Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
-This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
-    \caption{Analyze frame of \textit{GUI} E distribution.}
-    \label{fig:gui_analyze_Edist}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et2}
-\end{figure}
-
-\subsection{Sweep Frame}
-Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
-$\phi_{lag}$ sweep was the first parameter to be implemented. 
-It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
-This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
-    \label{fig:gui_sweep_running}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
-    \label{fig:gui_sweep_muE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
-    \label{fig:gui_sweep_sE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
-    \label{fig:gui_sweep_sR}
-\end{figure}
-
-As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
-New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
-
-\newpage
-
-% START OF PRODUCTION
-
-\chapter{PRODUCTION}
-% Start of final.tex
-\section{Final Design} \label{sec:final_design}
-
-As discussed before, production efforts of a rhodotron type accelerator is still ongoing in KAHVELab.
-This accelerator will be used at $f=107.5$MHz $P=50-100$kW. 
-In the following figures, rendered visuals of the final design by \textit{Mr. Sinan Öz} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
-    \caption{Rhodotron in KAHVELab}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
-    \caption{Rhodotron cavity and \e gun}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
-    \caption{Vertical cross section of the beam injection line}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
-    \caption{Cross section of the acceleration plane}
-\end{figure}
-
-\newpage
-
-% Start of techd.tex
-\section{Technical Drawing}
-
-Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1\linewidth]{./figures/teknikcizim/altgovdeteknikresim.pdf}
-    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
-    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
-    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.2.00.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\newpage
-
-% Start of mani.tex
-\section{Manifacturing}
-
-Manifacturing of the rhodotron cavity has been ongoing, planned to be completed in the following months.
-
-The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet.
-
-Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
-These sheets were then pressed to achieve the shapes of the parts. 
-Several flanges were then machined, including
-\begin{itemize}
-    \item $4.5$in EIA RF flange for RF input
-    \item ISO100-KF vacuum connector flanges for vacuum pumps
-    \item ISO-63 KF flange for probe insertion
-    \item KF40 flanges for beam line vacuum gauges
-\end{itemize}
-
-After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
-304 stainless steel sheet bars of different sizes were then added by 
-TIG welding to achieve pressure resistance.
-
-Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
-This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
-which would be removed after the heat treatment.
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
-      \caption{Bottom part of the cavity while polishing.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
-      \caption{Top part of the cavity after polishing.}
-    \end{subfigure}
-    \caption{Polishing of the inner surface of cavity.}
-    \label{fig:manif_polishing}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
-      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
-      \caption{Bottom part of the cavity with the beam line assembled.}
-    \end{subfigure}
-    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
-    \label{fig:manif_toroidal_sheets}
-\end{figure}
-
-\begin{figure}
-    \captionsetup{justification=centering}
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
-    \caption{Welded sheet bars.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup{justification=centering}
-    \centering
-    \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
-    \caption{Middle part of the cavity containing the beam line.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
-      \caption{Welding sheet bars.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
-      \caption{Welding toroidal sheets.}
-    \end{subfigure}
-    \caption{TIG welding.}
-    \label{fig:manif_welding}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
-    \end{subfigure}
-    \caption{Assembled cavity as the current stage.}
-    \label{fig:manif_assembled}
-\end{figure}
-
-\newpage
-
-% Start of rf.tex
-% \section{RF Supply}
-
-\newpage
-
-% START OF FUTURE_WORK
-
-\chapter{FUTURE WORK}
-
-At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
-Present bottleneck is the fabrication of the cavity.
-
-\section{Cavity}
-The cavity manufacturing process is in its concluding stages.
-The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
-After the heat treatment operation, 
-the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
-
-\section{Magnets}
-Magnet production was decided to be kept on hold in the early stages of the project, 
-due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
-and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
-The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.
-
-\section{Rhodotron Simulation}
-
-\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
-several improvements and new feature implementations are underway in the mean time. 
-They include the following;
-\begin{figure}[H]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{itemize}
-            \item Electric and magnetic field import
-            \item Field generator module to directly produce field files from specified cavity
-            \item Synchrotron radiation calculations to determine radiation and energy loss
-            \item \ee interactions
-            \item Redesign of the GUI
-            \item 3D render in GUI
-        \end{itemize}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{itemize}
-            \item Refactoring of the \eEM interaction and logging to improve performance
-            \item Refactoring of the GUI Render Frame to improve render speed
-            \item Refactoring the magnet class to introduce field leaks
-            \item Extention of analysis tools in Analyze Frame
-            \item $L_{out}$ sweep in Sweep Frame
-        \end{itemize}
-    \end{subfigure}
-\end{figure}
-
-\section{Conclusion}
-
-In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
-before the cavity production is completed and the performance is compared with the predictions of the tool;
-however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
-lead to the inference that this tool holds promise.
-
-\newpage
-
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
-\end{figure}
-
-\begin{figure}[H]
-        \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void RhodotronSimulator::_runMT(){
-            gun.fireAllWithFireTimesMT();
-
-            MTEngine.setupPool(time_interval, start_time, end_time, gun, E_field, B_field, gun.thread_bunchs);
-
-            STEPS_TAKEN = 0;
-            simulation_time = start_time;
-            while (simulation_time < end_time + time_interval ){
-                if (STEPS_TAKEN % log_interval() == 0){
-                    E_field.update(simulation_time);
-                    logEfield(simulation_time, simulation_time + time_interval > end_time);
-                    notifyUI(MTEngine.getAverageTime());
-                }
-                simulation_time+=time_interval;
-                STEPS_TAKEN++;
-            }
-            bool end = false;
-            while (!end){
-                double time = MTEngine.getAverageTime();
-                notifyUI(time);
-                if ( time >= end_time ){
-                    end = true;
-                }
-                this_thread::yield();
-            }
-            MTEngine.join();
-
-        }
-    \end{minted}
-    \caption{Multithreading main-thread logic.}
-    \label{fig:_runMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Gun::fireAllWithFireTimesMT(){
-            std::random_device rd;
-            std::mt19937 e2(rd());
-            std::normal_distribution<double> Edist(Ein, sEin);
-
-            for(_fired_bunch= 0; _fired_bunch < bunch_count; _fired_bunch++){
-                for(_fired_e_in_current_bunch= 0; _fired_e_in_current_bunch < e_per_bunch; _fired_e_in_current_bunch++){
-
-                    double E = (sEin == 0 ) ? Ein : Edist(e2);
-
-                    double fire_time = (ns_between_each_electron_fire * _fired_e_in_current_bunch) + _fired_bunch*gun_period;
-
-                    auto burrowed_e = bunchs[_fired_bunch].AddElectronGiveAddress(E, gunpos, gundir, fire_time);
-
-                    int thread_index = (_fired_e_in_current_bunch + _fired_bunch*e_per_bunch)%thread_bunchs.size();
-
-                    thread_bunchs[thread_index]->push_back(burrowed_e);
-                }
-            }
-        }
-    \end{minted}
-    \caption{Multithreading electron assign logic.}
-    \label{fig:fireAllWithFireTimesMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void MultiThreadEngine::setupPool( double _time_interval, double _start_time, double _end_time, Gun& gun, 
-            CoaxialRFField& RF, MagneticField& B, vector<shared_ptr<vector<shared_ptr<Electron2D>>>>& e_list){
-            threads.reserve(thread_count);
-
-            for(int i = 0; i < thread_count && i == threads.size(); i++){
-
-                child_notifier_mutexes.push_back(make_shared<mutex>());
-                child_times.push_back(make_shared<double>());
-
-                auto _E = RF.Copy();
-                auto _B = B.LightWeightCopy();
-                double time_between_fires = thread_count*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                double first_fire_time = i*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                ThreadArguments thread_arguments(i, _time_interval, _start_time, _end_time, &gun, _E, _B, e_list[i], first_fire_time, time_between_fires);
-                thread_arguments.parent_notifier_mutex = child_notifier_mutexes[i];
-                thread_arguments.current_thread_time = child_times[i];
-                threads.push_back(thread(threadLoop, thread_arguments));
-            }
-        }
-    \end{minted}
-    \caption{Multithreading worker-threads setup logic.}
-    \label{fig:setupPool}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void threadLoop(ThreadArguments thread_arguments){
-            uint64_t count = 0;
-
-            double sim_time = thread_arguments.start_time;
-
-            while(sim_time < thread_arguments.end_time + thread_arguments.time_interval){
-                thread_arguments.E->update(sim_time);
-                thread_arguments.i_args.time = sim_time;
-
-                if ( count % (unsigned long)(0.1/thread_arguments.time_interval) == 0){
-                    saveElectronInfoForSingleThread(thread_arguments.i_args);
-                    // Notifiy the main thread
-                    if(thread_arguments.parent_notifier_mutex->try_lock()){
-                        *thread_arguments.current_thread_time = sim_time;
-                        thread_arguments.parent_notifier_mutex->unlock();
-                    }
-                }
-
-                interactForSingleThread(thread_arguments.i_args);
-                // save electron info here
-                sim_time+= thread_arguments.time_interval;
-                count++;
-            }
-            thread_arguments.parent_notifier_mutex->lock();
-            *thread_arguments.current_thread_time = sim_time;
-            thread_arguments.parent_notifier_mutex->unlock();
-        }
-    \end{minted}
-    \caption{Multithreading worker-thread logic.}
-    \label{fig:threadLoop}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void UIThreadWork(UIThreadArgs args){
-            int UI_WORK_PIECE = SIM_WORK_MASK;
-            if ( !args.isService ) {
-                UI_WORK_PIECE = 50;
-            }
-
-            double piece = (args.end_time - args.start_time)/UI_WORK_PIECE;
-
-            if ( !args.isService ) {
-                std::string sim_running_msg = "...Simulation is running...";
-                for(int i = 0; i < 26 - sim_running_msg.size()/2 ; i++){
-                    std::cout << " ";
-                }
-                std::cout << sim_running_msg <<"\n";
-            }
-
-            args.ui_mutex->lock();
-            double simtime = *(args.simulation_time);
-            args.ui_mutex->unlock();
-
-            if ( !args.isService ) {
-                std::cout << "V";
-                for(int i = 0; i < 51; i++){
-                    std::cout << "_";
-                }
-                std::cout << "V\n[" << std::flush;
-            }
-
-            int count = 0;
-            bool running = true;
-            while(running && (simtime < args.end_time || count < UI_WORK_PIECE )){
-                if( simtime > count * piece ){
-                    if ( !args.isService ) {
-                        std::cout << "#" << std::flush;
-                    }
-                    count++;
-                    args.state_mutex->lock();
-                    running = *args.state_ptr & SIM_RUNNING;
-                    *args.state_ptr = (*args.state_ptr & ~SIM_WORK_MASK) | (count & SIM_WORK_MASK);
-                    if (args.isService) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-                    args.state_mutex->unlock();
-                }
-                std::this_thread::sleep_for(std::chrono::milliseconds(25));
-                args.ui_mutex->lock();
-                simtime = *(args.simulation_time);
-                args.ui_mutex->unlock();
-
-            }
-            if ( !args.isService ) {
-                std::cout << "#]\n\n" << std::flush;
-                std::cout << "     ...Simulation is finished successfully...\n\n" << std::flush;
-            }
-
-            args.state_mutex->lock();
-            *args.state_ptr |= SIM_RENDERING;
-            if ( args.isService ) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-            args.state_mutex->unlock();
-        }
-    \end{minted}
-    \caption{UI-Console handler thread logic.}
-    \label{fig:ui_thread}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Electron{
-            std::vector<ElectronLog> log;
-            uint64_t index;
-            double Et;
-            vector3d pos;
-            vector3d vel;
-            double fire_time;
-        public:
-            Electron();
-            Electron(double Ein, vector3d position, vector3d direction, double _fire_time = 0);
-            ~Electron();
-
-            void setEin(double E_in);
-            void print_electron_info();
-
-            void move(double dt);
-            void move(const vector3d& acc, double dt);
-            void move(const vector3d& acc, const vector3d& jerk, double dt);
-            void accelerate(const vector3d& acc, double dt);
-            void accelerate(const vector3d& acc, const vector3d& jerk, double dt);
-
-            void interactLF(RFField& E, MagneticField& B, double time_interval);
-            void interactRK(RFField& E, MagneticField& B, double time_interval);
-            void interactRK(RFField& E, MagneticField& B, const double time, double time_interval);
-            void interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval);
-
-            vector3d interactE_RK(const RFField& E, double time_interval);
-            vector3d interactB_RK(const MagneticField& B, double time_interval);
-
-            void saveInfo(double t);
-            void setLogSize(size_t size);
-            void loge(DataStorage& path);
-            const vector<ElectronLog>& getLog();
-
-            double vel();
-            double beta();
-            double beta2();
-            double gamma();
-            double gamma_inv();
-        };
-    \end{minted}
-    \caption{Electron class definition}
-    \label{fig:e_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Bunch{
-        private:
-            int e_count = 0;
-            int index_fastest = 0;
-            double max_energy = 0;
-            double entry_time = 0;
-            double E_in = 0.04;
-
-            vector<Bunch> subBunchs;
-            vector<shared_ptr<Electron>> e;
-        public:
-            Bunch(unsigned int num_of_electrons, double Ein, vector3d gunpos, vector3d gundir, double gun_ns);
-            Bunch();
-            ~Bunch();
-
-            void saveInfo(double time);
-
-            Electron& getFastest();
-
-            void AddElectron(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
-
-            shared_ptr<Electron> AddElectronGiveAddress(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
-
-            void setEntryTime(double entry_time);
-            void setEin(double E_in);
-            void setNSLen(double len);
-
-            uint32_t get_e_count();
-            double getEin();
-            double E_ave();
-            double E_rms();
-
-            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
-
-            void divide(unsigned int num);
-            void concat();
-            Bunch& subBunch(unsigned int index);
-            vector<Bunch*> subBunchPtr();
-
-            void reset();
-
-            void print_bunch_info();
-            void print_summary();
-
-            void logPaths(vector<DataStorage>& pathStorage, std::string header);
-        };
-    \end{minted}
-    \caption{Bunch class definition}
-    \label{fig:bunch_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Gun{
-            double Ein;
-            double sEin;
-            double gun_period;
-            double gun_active_time;
-            double ns_between_each_electron_fire;
-
-            vector3d gunpos;
-            vector3d gundir = vector3d(1,0,0);
-
-            uint64_t bunch_count = 0;
-            uint64_t e_per_bunch = 1;
-
-            uint32_t _fired_bunch = 0;
-            uint32_t _fired_e_in_current_bunch = 0;
-            bool _firing = false;
-
-            bool _mt_enabled = false;
-            uint32_t _child_thread_count = 0;
-
-            vector<Bunch> bunchs;
-
-            mutex _gun_mutex; 
-            vector<shared_ptr<vector<shared_ptr<Electron>>>> thread_bunchs;
-
-            void setNSLen(double len);
-        public:
-            Gun();
-            Gun(double Ein, double gun_active_time, double pulse_interval, vector3d gunpos);
-            ~Gun();
-            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
-
-            void fireIfActive(double time);
-            void fireAllWithFireTimesMT();
-
-            void addBunch(unsigned int num_of_electrons, double Ein);
-
-            void setGunActiveTime(double gt);
-            double getGunActiveTime(){return gun_active_time;}
-            void setGunInterval(double guninterval);
-            void setGunPos(vector3d gun_pos);
-            void setGunDir(vector3d gun_dir);
-            void setEin(double Ein) ;
-            void setEinStd(double EinStd) ;
-            void setNumberOfElectrons(uint64_t e_num);
-            void getElectronsPerBunch(){return e_per_bunch;}
-            void setNumberOfBunchs(uint64_t b_num);
-            void enableMT(uint32_t thread_count);
-
-            void saveInfo(double time);
-            void logPaths(vector<vector<DataStorage> >& pathsStorage, std::string pathsPath, std::string header);
-        };
-    \end{minted}
-    \caption{Gun class definition}
-    \label{fig:gun_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Simulator{        // E in MV/m,   En in MeV,   B in T,    t in ns
-        protected:
-            Gun gun;
-            double Emax; double freq = 107.5; double phase_lag = 0; 
-            DataStorage EfieldStorage; DataStorage BfieldStorage;
-            vector<vector<DataStorage>> pathsStorage;
-            std::string configPath;
-            std::string pathsPath;
-            std::string EfieldLogHeader;
-            std::string BfieldLogHeader;
-            std::string eLogHeader;
-
-            double simulation_time = 0;
-            double dummy_time = 0;
-            double start_time = 0;
-            double end_time = 45;   
-            double time_interval = 0.0001;
-            uint64_t STEPS_TAKEN = 0;
-            double GUN_ACTIVE_TIME = 1;         
-            double GUN_PERIOD = 9.3;
-            uint64_t NUM_OF_ELECTRONS = 1;
-            uint64_t NUM_OF_BUNCHS = 1;
-            double Ein = 0.04;
-            double EinStd = 0;
-            vector3d gunPosition;
-            vector3d gunDirection = vector3d(1,0,0);
-
-            shared_ptr<mutex> ui_mutex;
-            UIHandler ui_handler;
-            shared_ptr<mutex> state_mutex;
-            uint8_t state = 0x0;
-
-            MultiThreadEngine MTEngine;
-            unsigned int MAX_THREAD_COUNT = 1;
-            bool MULTI_THREAD = false;
-        public:
-            Simulator();
-            ~Simulator(){}
-
-            void enableMultiThreading(unsigned int thread_count);
-            void setdT(double dT);
-            void setEin(double E_in);
-            void setEinStd(double Ein_Std);
-            void setNumberofElectrons(uint64_t num_of_electrons);
-            void setNumberofBunchs(uint64_t num_of_bunchs);
-            void setStartTime(double starttime);
-            void setEndTime(double end_time);
-            void setGunActiveTime(double gun_ns);
-            void setGunPeriod(double pi);
-            void setGunPosition(vector3d pos);
-            void setGunDirection(vector3d dir);
-            void setRFPath(std::string path);
-            void setBPath(std::string path);
-            void setPathsPath(std::string path);
-            void setConfigPath(std::string path);
-
-            virtual void run();
-            void openLogs();
-            void closeLogs();
-            virtual void getConfig(Configuration& config) = 0;
-            virtual void logEfield(double time, bool) = 0;
-            virtual void logBfield() = 0;
-            void logPaths();
-            shared_ptr<mutex> getUIMutex();
-        };
-    \end{minted}
-    \caption{Simulator class definition}
-    \label{fig:sim_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class RhodotronSimulator : public Simulator{
-        private:
-            double R1;
-            double R2;
-            CoaxialRFField E_field;
-            MagneticField B_field;
-
-            void _runMT();
-            void _runST();
-        public:
-            RhodotronSimulator(double phase_lag);
-            RhodotronSimulator(Configuration& config);
-
-            void StartUIHandler();
-            void StopUIHandler();
-            void DeclareService(std::string pipe_name);
-
-            void setFreq(double frequency);
-            void setPhaseLag(double phase_lag);
-            void setEmax(double E_max);
-            void setR1(double r1);
-            void setR2(double r2);
-            void addMagnet(double B, double r, vector3d position);
-            void addMagnet(Magnet m);
-
-            void updateSimulation();
-            void getConfig(Configuration& config);
-            void logEfield(double time, bool end);
-            void logBfield();
-
-            void run();
-            void notifyUI(double time);
-
-            void setState(uint8_t state_);
-        };
-    \end{minted}
-    \caption{RhodotronSimulator class definition}
-    \label{fig:rhodosim_class}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-            class RFField{
-            protected:
-                double E;                       // MV/m
-                double E_max = 0;               // MV/m
-                double frequency = 107.5;       // MHz
-                double phase_lag = 0;           // degree
-            public:
-                RFField();
-                RFField(double phase_lag);
-                virtual ~RFField() {}
-
-                virtual vector3d getField(vector3d position);              
-                virtual double getField(double R);
-                virtual int log(DataStorage& rf, double time, bool end = false);
-                vector3d actOn(Electron& e);    
-                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);
-
-                double getE() {return E;}
-                void setEmax(double E_max) {this->E_max = E_max; update(0);}
-                void setFreq(double freq){ frequency = freq;}
-                void setPhaseLag(double phaselag){ phase_lag = phaselag; update(0);}
-                virtual void update(double time);
-            };
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-            class CoaxialRFField : public RFField{
-            private:
-                double r1 = 0.188;                         // m
-                double r2 = 0.753;                         // m
-                double E_max_pos = r1;                     // m
-                std::vector<CoaxialRFField*> _childs;
-                double E_radial(double R) const;
-            public:
-                CoaxialRFField();
-                CoaxialRFField(double phase_lag);
-                ~CoaxialRFField() override;
-                void setR1(double r1);
-                void setR2(double r2);
-                void setEmaxPos(double Emaxpos);
-
-                vector3d getField(vector3d position) const override;
-                double getField(double R) const override;
-                vector3d actOn(Electron& e);
-                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);    
-                void update(double time) override;
-
-                int log(DataStorage& rf, double time, bool end = false) override;
-
-                std::shared_ptr<CoaxialRFField> Copy();
-                void split(uint32_t amount_of_child);
-                CoaxialRFField* child(uint32_t index);
-            };
-        \end{minted}
-    \end{subfigure}
-    \caption{CoaxialRFField class definition}
-    \label{fig:rf_class}
-\end{figure}
-
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
-
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{An example \textit{config.in} file.}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.114422     & 0.028398 & 0.009294 \\
-    1.00E-02 & 0.019233     & 0.036245 & 0.002182 \\
-    1.00E-03 & 0.002141     & 0.147979 & 0.00125  \\
-    9.00E-04 & 0.001749     & 0.172161 & 0.00794  \\
-    8.00E-04 & 0.001516     & 0.184629 & 0.004359 \\
-    7.00E-04 & 0.00152      & 0.20445  & 0.001919 \\
-    6.00E-04 & 0.001049     & 0.234947 & 0.004416 \\
-    5.00E-04 & 0.000974     & 0.278938 & 0.010969 \\
-    4.00E-04 & 0.0009       & 0.336847 & 0.003028 \\
-    3.00E-04 & 0.000587     & 0.441771 & 0.005859 \\
-    2.00E-04 & 0.000433     & 0.652066 & 0.006637 \\
-    1.00E-04 & 0.0002       & 1.280059 & 0.016027 \\
-    9.00E-05 & 0.000145     & 1.41908  & 0.013122 \\
-    8.00E-05 & 0.000153     & 1.592492 & 0.011332 \\
-    7.00E-05 & 0.000162     & 1.806561 & 0.009931 \\
-    6.00E-05 & 0.000123     & 2.103571 & 0.011143 \\
-    5.00E-05 & 0.000084     & 2.515006 & 0.01393  \\
-    4.00E-05 & 0.000092     & 3.140471 & 0.014138 \\
-    3.00E-05 & 0.000053     & 4.158715 & 0.009474 \\
-    2.00E-05 & 0.000045     & 6.231734 & 0.015236 \\
-    1.00E-05 & 0.000022     & 12.39871 & 0.039575 \\
-    1.00E-06 & 0.000003     & 123.318  & 0.299559
-    \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:lf_statE_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.055355     & 0.031054 & 0.003281 \\
-        1.00E-02 & 0.009868     & 0.063656 & 0.000893 \\
-        1.00E-03 & 0.001141     & 0.435864 & 0.005332 \\
-        9.00E-04 & 0.001325     & 0.478216 & 0.00595  \\
-        8.00E-04 & 0.001112     & 0.533789 & 0.003897 \\
-        7.00E-04 & 0.000705     & 0.60586  & 0.005441 \\
-        6.00E-04 & 0.000687     & 0.703851 & 0.009447 \\
-        5.00E-04 & 0.000474     & 0.840173 & 0.00913  \\
-        4.00E-04 & 0.00046      & 1.039166 & 0.005874 \\
-        3.00E-04 & 0.000456     & 1.378822 & 0.007995 \\
-        2.00E-04 & 0.000207     & 2.045464 & 0.008499 \\
-        1.00E-04 & 0.000127     & 4.052472 & 0.014711 \\
-        9.00E-05 & 0.000091     & 4.500401 & 0.015404 \\
-        8.00E-05 & 0.000124     & 5.048922 & 0.014392 \\
-        7.00E-05 & 0.000062     & 5.773208 & 0.031443 \\
-        6.00E-05 & 0.000057     & 6.726501 & 0.020609 \\
-        5.00E-05 & 0.00006      & 8.045931 & 0.014246 \\
-        4.00E-05 & 0.000039     & 10.04809 & 0.012756 \\
-        3.00E-05 & 0.000045     & 13.39669 & 0.028057 \\
-        2.00E-05 & 0.000023     & 20.03889 & 0.006436 \\
-        1.00E-05 & 0.000016     & 40.0818  & 0.120627 \\
-        1.00E-06 & 0.000003     & 400.2421 & 0.554172
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:rk2_statE_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.986005     & 0.030314 & 0.009209 \\
-    1.00E-02 & 0.154314     & 0.036833 & 0.004068 \\
-    1.00E-03 & 0.01476      & 0.131783 & 0.002352 \\
-    9.00E-04 & 0.013618     & 0.150984 & 0.005618 \\
-    8.00E-04 & 0.011863     & 0.161336 & 0.003117 \\
-    7.00E-04 & 0.010109     & 0.179693 & 0.002658 \\
-    6.00E-04 & 0.009277     & 0.205356 & 0.002912 \\
-    5.00E-04 & 0.007527     & 0.242352 & 0.003093 \\
-    4.00E-04 & 0.006084     & 0.294269 & 0.001551 \\
-    3.00E-04 & 0.00449      & 0.383982 & 0.001711 \\
-    2.00E-04 & 0.002897     & 0.563762 & 0.004214 \\
-    1.00E-04 & 0.001458     & 1.101252 & 0.008064 \\
-    9.00E-05 & 0.001376     & 1.229321 & 0.0089   \\
-    8.00E-05 & 0.001232     & 1.381441 & 0.01057  \\
-    7.00E-05 & 0.001027     & 1.574994 & 0.011933 \\
-    6.00E-05 & 0.000853     & 1.833183 & 0.006065 \\
-    5.00E-05 & 0.00074      & 2.184948 & 0.013416 \\
-    4.00E-05 & 0.000596     & 2.72503  & 0.016356 \\
-    3.00E-05 & 0.000467     & 3.617576 & 0.017581 \\
-    2.00E-05 & 0.000308     & 5.394629 & 0.027885 \\
-    1.00E-05 & 0.00015      & 10.75182 & 0.03301  \\
-    1.00E-06 & 0.000017     & 106.9198 & 0.373175
-    \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:lf_statE90_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.587777     & 0.034741 & 0.012735 \\
-        1.00E-02 & 0.09943      & 0.059945 & 0.001318 \\
-        1.00E-03 & 0.009987     & 0.38199  & 0.005941 \\
-        9.00E-04 & 0.007946     & 0.417119 & 0.005683 \\
-        8.00E-04 & 0.007999     & 0.466052 & 0.006398 \\
-        7.00E-04 & 0.006732     & 0.525791 & 0.003782 \\
-        6.00E-04 & 0.005541     & 0.612876 & 0.007114 \\
-        5.00E-04 & 0.005022     & 0.732091 & 0.012129 \\
-        4.00E-04 & 0.004031     & 0.906845 & 0.012156 \\
-        3.00E-04 & 0.002779     & 1.199367 & 0.014536 \\
-        2.00E-04 & 0.001897     & 1.782653 & 0.016993 \\
-        1.00E-04 & 0.000895     & 3.52464  & 0.029778 \\
-        9.00E-05 & 0.000858     & 3.916115 & 0.041066 \\
-        8.00E-05 & 0.000731     & 4.409459 & 0.040828 \\
-        7.00E-05 & 0.00066      & 5.012686 & 0.042727 \\
-        6.00E-05 & 0.000561     & 5.851793 & 0.038488 \\
-        5.00E-05 & 0.000471     & 7.002315 & 0.046152 \\
-        4.00E-05 & 0.000363     & 8.747954 & 0.063936 \\
-        3.00E-05 & 0.000264     & 11.64305 & 0.091404 \\
-        2.00E-05 & 0.000184     & 17.44533 & 0.123198 \\
-        1.00E-05 & 0.000093     & 34.93332 & 0.391012 \\
-        1.00E-06 & 0.000011     & 348.494  & 3.237203
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:rk2_statE90_table}
-\end{table}
-% START OF BIBLIOGRAPHY
+%%%%%%
 
 \begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
     \bibitem{cpu_instruction_speed}
     Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775. 
-
-    \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018
-
 \end{thebibliography}
 
-% END OF BIBLIOGRAPHY
-
 \end{document}

### 2023-08-17 subsections/theory/rhodotron/rhodotron.tex
changes from Erkcan & Gokhan hocas

@@
 \newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
+\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
 
@@
     \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{A linear proton accelerator in KAHVELab}
+    \includegraphics[width=.9\textwidth]{../../../figures/kahvelab_linac.png}
+    \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
+    \includegraphics[width=.75\textwidth]{../../../figures/pill_box.jpeg}
+    \caption{An RF cavity used in KAHVELab}
 \end{figure}
@@
 vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
-    \caption{A bending magnet used in KAHVELab}
-\end{figure}
 

### 2023-08-17 subsections/tools/available/available.tex
changes from Erkcan & Gokhan hocas

--- 2023-08-07 msthesis.tex
@@
 
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
+%%%%%%
+% START OF available.tex
 
-\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
-\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
-\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
-\newcommand{\fromfigsix}[6]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
+\section{Available Tools}
 
-\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
-
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
-
-\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
-\newcommand{\fromtabf}[4]{\textit{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}}
-
-% START OF intro.tex
-
-\chapter{INTRODUCTION}
-
-\newpage
-
-% START OF THEORY
-
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear proton accelerator in KAHVELab}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\subsubsection{Resonance Frequency}
-Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
-It is determined by the physical dimensions and the speed of light in the cavity's medium. 
-In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
-\begin{equation}
-    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
-    \label{eq:f_r_rec}
-\end{equation}
-Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
-
-\subsubsection{Bunch}
-Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
-
-\subsubsection{Phase Stability}
-Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
-It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
-which is crucial for achieving efficient particle acceleration. 
-Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
-ensuring that they receive the correct energy boosts and interact predictably with detectors. 
-Deviations in phase stability can lead to particle loss and decreased beam quality.
-
-\subsubsection{Phase Lag}
-Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
-It describes the difference in phase angles within their respective cycles, between two signals.
-
-\subsubsection{Shunt Impedance}
-The shunt impedance of an RF accelerator is a measure of the efficiency 
-at which the accelerator can transform the supplied RF power into acceleration.
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Bending Magnets}
-Bending magnets, also known as dipole magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A bending magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and bending magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-See \fromfig{rhod_cycle_1}
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.See \fromfig{rhod_cycle_2}
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-See \fromfig{rhod_cycle_3}
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-See \fromfig{rhod_cycle_4}
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod1.pdf}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_1}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod2.pdf}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_2}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod3.pdf}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_3}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod4.pdf}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_4}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta} \label{sec:rungekutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
-
-\section{Simulation}
-
-A simulation software is a computer program or tool that enables the creation and execution of 
-simulations to model and analyze real-world systems or processes. 
-It allows users to replicate the behavior, interactions, and outcomes of the system or process under study, 
-providing insights and predictions that can be valuable for decision-making, optimization, or understanding complex phenomena.
-
-Simulation software provides a virtual environment where users can define the parameters,
-variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
-algorithms, and computational techniques to simulate the behavior of the system over time.
-
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle. 
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-Threads utilize \textit{mutexes}, short for "mutual exclusion," 
-to synchronize and manage access to shared resources 
-in a multi-threaded or multi-process environment.
-
-\subsubsection{Object Oriented Programming}
-
-Object-Oriented Programming (OOP) is a programming paradigm that revolves around the concept of objects. 
-Definition called class serves as a blueprint that defines the structure and behavior of objects. 
-Each object encapsulates both data, and the functions that manipulate that data. 
-This encapsulation promotes modular code design and enhances data security by controlling access to the object's internal state.
-
-In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
-\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
-By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
-
-\newpage
-
-% START OF tools.tex
-
-\chapter{TOOLS}
-
-\section{Poisson Superfish}
+\subsection{Poisson Superfish}
 Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
-for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
+for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments \cite{poi-sup}.
 It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
 
-\section{CST Studio Suite}
+\subsection{CST Studio Suite}
 CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
@@
 
-\section{ROOT}
+\subsection{ROOT}
 ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
 visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
-like the Large Hadron Collider (LHC). It has become an essential tool in particle physics research, 
+like the Large Hadron Collider (LHC) \cite{root}. It has become an essential tool in particle physics research, 
 and it's used by physicists around the world to analyze and interpret data.
 
-\section{gnuplot}
-GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs. 
+\subsection{gnuplot}
+GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs  \cite{gnuplot}. 
 It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
@@
 
-\newpage
-
-% START OF DESIGN
-
-\chapter{DESIGN}
-
-\section{Cavity Design} \label{sec:cavity_design}
-
-The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
-
-By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
-This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
-For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
-    \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
-    \end{aligned}
-\end{eqnarray}
-
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:107_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:180_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:cst_simple_cavity_designs}
-\end{figure}
-
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson SUPERFISH field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_superfish}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST eigenmode results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_eigenmode}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST electric field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_field}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
-      \caption{107.5 MHz unmodified}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
-      \caption{180 MHz unmodified}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
-    \label{fig:107_cavity_shunt_diff}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
-    \label{fig:180_cavity_shunt_diff}
-\end{figure}
-
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
-    \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta Z_{180}=2.7\%
-    \end{aligned}
-\end{equation*}
-
-\newpage
-
-\section{Magnet Design} \label{sec:magnet_design}
-Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
-Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
-Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
-    \label{fig:magnet_design_illustrations}
-\end{figure}
-
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
-
-Two different approaches have been used to achieve phase stability.
-These approaches are discussed further in the following sections.
-
-\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
-
-First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
-
-To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
-As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
-    L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
-
-\begin{figure}[H]    
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
-    \label{fig:magnet_design}
-\end{figure}
-
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
-
-After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
-Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
-\begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
-
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
-Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
-Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
-
-\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
-
-As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
-This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
-This scenario can happen when RF power is not sufficiently high.
-
-Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
-after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
-It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
-For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
-Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
-
-Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
-
-To start, an optimization criteria for the following pass such as
-\begin{itemize}
-    \item Ensure the phase stability of the synchronous electron
-    \item Maximize the energy gain of the synchronous electron
-    \item Minimize the energy spread of the beam
-    \item Minimize the phase lag spread of the beam
-    \item All of the above with decided weights
-\end{itemize}
-needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
-This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
-
-However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
-
-\newpage
-
-\section{Initial Design at KAHVELab}
-
-A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
-After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
-    \label{fig:initial_design}
-\end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
-      \caption{Axial cross section.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
-      \caption{Cross section at acceleration plane.}
-    \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
-    \label{fig:initial_design_cross_section}
-\end{figure}
-The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
-    \end{subfigure}
-    \caption{Initial magnet design.}
-    \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
-    \label{fig:initial_three_magnet_design}
-\end{figure}
-
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
-Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
-
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
-
-In KAHVELab, several improvements were made to these initial designs together with \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
-Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
-    \end{subfigure}
-    \caption{Improved cavity design.}
-    \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \caption{Improved magnet design.}
-    \label{fig:improved_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
-    \end{subfigure}
-    \caption{Cross section and coils of improved magnet design.}
-    \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \caption{Magnetic field in acceleration plate of improved magnet design.}
-    \label{fig:improved_magnet_design_B}
-\end{figure}
-
-From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
-This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
-
-\newpage
-
-% START OF SIMULATION
-
-\chapter{SIMULATION}
-% Start of poc.tex
-\section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
-\begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
-    \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
-    \end{enumerate}
-\end{itemize}
-
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \caption{Core logic loop of the POC}
-    \label{fig:POC_core_logic}
-\end{figure}
-
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
-Since using a single software would have made the process error prone.
-
-After the results obtained from \textit{POC} were found to be promising, a decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
-The development and improvement efforts are still ongoing.
-
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
-The following sections in this chapter investigates their implementations further.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
-Initial step of improving \textit{POC} towards \textit{Rhodotron Simulation} was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-One can sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs from this intermediate build can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of \textit{OOP}, details of which can be seen in \fromfigsix{e_class}{bunch_class}{gun_class}{sim_class}{rhodosim_class}{rf_class} of \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired into a uniform magnetic field of $0.1$T located in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph}),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation 
-(see \fromfig{console_output_running} in \fromapp{example_simulation_runs} for example console notification, \fromfig{ui_thread} in \fromapp{intermediate_codes} for implemenation)
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Graphical User Interface}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
-    \caption{The configuration frame of implementated first GUI design.}
-    \label{fig:gui_config}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
-
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
-
-\subsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\subsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
-
-\subsection{Render Frame}
-Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
-see a specific time frame, export as snapshot or animated gif file.
-Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_1}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_2}
-\end{figure}
-
-\subsection{Analyze Frame}
-Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
-This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
-    \caption{Analyze frame of \textit{GUI} E distribution.}
-    \label{fig:gui_analyze_Edist}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et2}
-\end{figure}
-
-\subsection{Sweep Frame}
-Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
-$\phi_{lag}$ sweep was the first parameter to be implemented. 
-It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
-This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
-    \label{fig:gui_sweep_running}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
-    \label{fig:gui_sweep_muE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
-    \label{fig:gui_sweep_sE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
-    \label{fig:gui_sweep_sR}
-\end{figure}
-
-As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
-New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
-
-\newpage
-
-% START OF PRODUCTION
-
-\chapter{PRODUCTION}
-% Start of final.tex
-\section{Final Design} \label{sec:final_design}
-
-As discussed before, production efforts of a rhodotron type accelerator is still ongoing in KAHVELab.
-This accelerator will be used at $f=107.5$MHz $P=50-100$kW. 
-In the following figures, rendered visuals of the final design by \textit{Mr. Sinan Öz} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
-    \caption{Rhodotron in KAHVELab}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
-    \caption{Rhodotron cavity and \e gun}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
-    \caption{Vertical cross section of the beam injection line}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
-    \caption{Cross section of the acceleration plane}
-\end{figure}
-
-\newpage
-
-% Start of techd.tex
-\section{Technical Drawing}
-
-Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1\linewidth]{./figures/teknikcizim/altgovdeteknikresim.pdf}
-    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
-    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
-    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.2.00.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\newpage
-
-% Start of mani.tex
-\section{Manifacturing}
-
-Manifacturing of the rhodotron cavity has been ongoing, planned to be completed in the following months.
-
-The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet.
-
-Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
-These sheets were then pressed to achieve the shapes of the parts. 
-Several flanges were then machined, including
-\begin{itemize}
-    \item $4.5$in EIA RF flange for RF input
-    \item ISO100-KF vacuum connector flanges for vacuum pumps
-    \item ISO-63 KF flange for probe insertion
-    \item KF40 flanges for beam line vacuum gauges
-\end{itemize}
-
-After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
-304 stainless steel sheet bars of different sizes were then added by 
-TIG welding to achieve pressure resistance.
-
-Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
-This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
-which would be removed after the heat treatment.
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
-      \caption{Bottom part of the cavity while polishing.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
-      \caption{Top part of the cavity after polishing.}
-    \end{subfigure}
-    \caption{Polishing of the inner surface of cavity.}
-    \label{fig:manif_polishing}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
-      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
-      \caption{Bottom part of the cavity with the beam line assembled.}
-    \end{subfigure}
-    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
-    \label{fig:manif_toroidal_sheets}
-\end{figure}
-
-\begin{figure}
-    \captionsetup{justification=centering}
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
-    \caption{Welded sheet bars.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup{justification=centering}
-    \centering
-    \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
-    \caption{Middle part of the cavity containing the beam line.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
-      \caption{Welding sheet bars.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
-      \caption{Welding toroidal sheets.}
-    \end{subfigure}
-    \caption{TIG welding.}
-    \label{fig:manif_welding}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
-    \end{subfigure}
-    \caption{Assembled cavity as the current stage.}
-    \label{fig:manif_assembled}
-\end{figure}
-
-\newpage
-
-% Start of rf.tex
-% \section{RF Supply}
-
-\newpage
-
-% START OF FUTURE_WORK
-
-\chapter{FUTURE WORK}
-
-At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
-Present bottleneck is the fabrication of the cavity.
-
-\section{Cavity}
-The cavity manufacturing process is in its concluding stages.
-The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
-After the heat treatment operation, 
-the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
-
-\section{Magnets}
-Magnet production was decided to be kept on hold in the early stages of the project, 
-due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
-and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
-The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.
-
-\section{Rhodotron Simulation}
-
-\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
-several improvements and new feature implementations are underway in the mean time. 
-They include the following;
-\begin{figure}[H]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{itemize}
-            \item Electric and magnetic field import
-            \item Field generator module to directly produce field files from specified cavity
-            \item Synchrotron radiation calculations to determine radiation and energy loss
-            \item \ee interactions
-            \item Redesign of the GUI
-            \item 3D render in GUI
-        \end{itemize}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{itemize}
-            \item Refactoring of the \eEM interaction and logging to improve performance
-            \item Refactoring of the GUI Render Frame to improve render speed
-            \item Refactoring the magnet class to introduce field leaks
-            \item Extention of analysis tools in Analyze Frame
-            \item $L_{out}$ sweep in Sweep Frame
-        \end{itemize}
-    \end{subfigure}
-\end{figure}
-
-\section{Conclusion}
-
-In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
-before the cavity production is completed and the performance is compared with the predictions of the tool;
-however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
-lead to the inference that this tool holds promise.
-
-\newpage
-
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
-\end{figure}
-
-\begin{figure}[H]
-        \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void RhodotronSimulator::_runMT(){
-            gun.fireAllWithFireTimesMT();
-
-            MTEngine.setupPool(time_interval, start_time, end_time, gun, E_field, B_field, gun.thread_bunchs);
-
-            STEPS_TAKEN = 0;
-            simulation_time = start_time;
-            while (simulation_time < end_time + time_interval ){
-                if (STEPS_TAKEN % log_interval() == 0){
-                    E_field.update(simulation_time);
-                    logEfield(simulation_time, simulation_time + time_interval > end_time);
-                    notifyUI(MTEngine.getAverageTime());
-                }
-                simulation_time+=time_interval;
-                STEPS_TAKEN++;
-            }
-            bool end = false;
-            while (!end){
-                double time = MTEngine.getAverageTime();
-                notifyUI(time);
-                if ( time >= end_time ){
-                    end = true;
-                }
-                this_thread::yield();
-            }
-            MTEngine.join();
-
-        }
-    \end{minted}
-    \caption{Multithreading main-thread logic.}
-    \label{fig:_runMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Gun::fireAllWithFireTimesMT(){
-            std::random_device rd;
-            std::mt19937 e2(rd());
-            std::normal_distribution<double> Edist(Ein, sEin);
-
-            for(_fired_bunch= 0; _fired_bunch < bunch_count; _fired_bunch++){
-                for(_fired_e_in_current_bunch= 0; _fired_e_in_current_bunch < e_per_bunch; _fired_e_in_current_bunch++){
-
-                    double E = (sEin == 0 ) ? Ein : Edist(e2);
-
-                    double fire_time = (ns_between_each_electron_fire * _fired_e_in_current_bunch) + _fired_bunch*gun_period;
-
-                    auto burrowed_e = bunchs[_fired_bunch].AddElectronGiveAddress(E, gunpos, gundir, fire_time);
-
-                    int thread_index = (_fired_e_in_current_bunch + _fired_bunch*e_per_bunch)%thread_bunchs.size();
-
-                    thread_bunchs[thread_index]->push_back(burrowed_e);
-                }
-            }
-        }
-    \end{minted}
-    \caption{Multithreading electron assign logic.}
-    \label{fig:fireAllWithFireTimesMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void MultiThreadEngine::setupPool( double _time_interval, double _start_time, double _end_time, Gun& gun, 
-            CoaxialRFField& RF, MagneticField& B, vector<shared_ptr<vector<shared_ptr<Electron2D>>>>& e_list){
-            threads.reserve(thread_count);
-
-            for(int i = 0; i < thread_count && i == threads.size(); i++){
-
-                child_notifier_mutexes.push_back(make_shared<mutex>());
-                child_times.push_back(make_shared<double>());
-
-                auto _E = RF.Copy();
-                auto _B = B.LightWeightCopy();
-                double time_between_fires = thread_count*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                double first_fire_time = i*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                ThreadArguments thread_arguments(i, _time_interval, _start_time, _end_time, &gun, _E, _B, e_list[i], first_fire_time, time_between_fires);
-                thread_arguments.parent_notifier_mutex = child_notifier_mutexes[i];
-                thread_arguments.current_thread_time = child_times[i];
-                threads.push_back(thread(threadLoop, thread_arguments));
-            }
-        }
-    \end{minted}
-    \caption{Multithreading worker-threads setup logic.}
-    \label{fig:setupPool}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void threadLoop(ThreadArguments thread_arguments){
-            uint64_t count = 0;
-
-            double sim_time = thread_arguments.start_time;
-
-            while(sim_time < thread_arguments.end_time + thread_arguments.time_interval){
-                thread_arguments.E->update(sim_time);
-                thread_arguments.i_args.time = sim_time;
-
-                if ( count % (unsigned long)(0.1/thread_arguments.time_interval) == 0){
-                    saveElectronInfoForSingleThread(thread_arguments.i_args);
-                    // Notifiy the main thread
-                    if(thread_arguments.parent_notifier_mutex->try_lock()){
-                        *thread_arguments.current_thread_time = sim_time;
-                        thread_arguments.parent_notifier_mutex->unlock();
-                    }
-                }
-
-                interactForSingleThread(thread_arguments.i_args);
-                // save electron info here
-                sim_time+= thread_arguments.time_interval;
-                count++;
-            }
-            thread_arguments.parent_notifier_mutex->lock();
-            *thread_arguments.current_thread_time = sim_time;
-            thread_arguments.parent_notifier_mutex->unlock();
-        }
-    \end{minted}
-    \caption{Multithreading worker-thread logic.}
-    \label{fig:threadLoop}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void UIThreadWork(UIThreadArgs args){
-            int UI_WORK_PIECE = SIM_WORK_MASK;
-            if ( !args.isService ) {
-                UI_WORK_PIECE = 50;
-            }
-
-            double piece = (args.end_time - args.start_time)/UI_WORK_PIECE;
-
-            if ( !args.isService ) {
-                std::string sim_running_msg = "...Simulation is running...";
-                for(int i = 0; i < 26 - sim_running_msg.size()/2 ; i++){
-                    std::cout << " ";
-                }
-                std::cout << sim_running_msg <<"\n";
-            }
-
-            args.ui_mutex->lock();
-            double simtime = *(args.simulation_time);
-            args.ui_mutex->unlock();
-
-            if ( !args.isService ) {
-                std::cout << "V";
-                for(int i = 0; i < 51; i++){
-                    std::cout << "_";
-                }
-                std::cout << "V\n[" << std::flush;
-            }
-
-            int count = 0;
-            bool running = true;
-            while(running && (simtime < args.end_time || count < UI_WORK_PIECE )){
-                if( simtime > count * piece ){
-                    if ( !args.isService ) {
-                        std::cout << "#" << std::flush;
-                    }
-                    count++;
-                    args.state_mutex->lock();
-                    running = *args.state_ptr & SIM_RUNNING;
-                    *args.state_ptr = (*args.state_ptr & ~SIM_WORK_MASK) | (count & SIM_WORK_MASK);
-                    if (args.isService) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-                    args.state_mutex->unlock();
-                }
-                std::this_thread::sleep_for(std::chrono::milliseconds(25));
-                args.ui_mutex->lock();
-                simtime = *(args.simulation_time);
-                args.ui_mutex->unlock();
-
-            }
-            if ( !args.isService ) {
-                std::cout << "#]\n\n" << std::flush;
-                std::cout << "     ...Simulation is finished successfully...\n\n" << std::flush;
-            }
-
-            args.state_mutex->lock();
-            *args.state_ptr |= SIM_RENDERING;
-            if ( args.isService ) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-            args.state_mutex->unlock();
-        }
-    \end{minted}
-    \caption{UI-Console handler thread logic.}
-    \label{fig:ui_thread}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Electron{
-            std::vector<ElectronLog> log;
-            uint64_t index;
-            double Et;
-            vector3d pos;
-            vector3d vel;
-            double fire_time;
-        public:
-            Electron();
-            Electron(double Ein, vector3d position, vector3d direction, double _fire_time = 0);
-            ~Electron();
-
-            void setEin(double E_in);
-            void print_electron_info();
-
-            void move(double dt);
-            void move(const vector3d& acc, double dt);
-            void move(const vector3d& acc, const vector3d& jerk, double dt);
-            void accelerate(const vector3d& acc, double dt);
-            void accelerate(const vector3d& acc, const vector3d& jerk, double dt);
-
-            void interactLF(RFField& E, MagneticField& B, double time_interval);
-            void interactRK(RFField& E, MagneticField& B, double time_interval);
-            void interactRK(RFField& E, MagneticField& B, const double time, double time_interval);
-            void interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval);
-
-            vector3d interactE_RK(const RFField& E, double time_interval);
-            vector3d interactB_RK(const MagneticField& B, double time_interval);
-
-            void saveInfo(double t);
-            void setLogSize(size_t size);
-            void loge(DataStorage& path);
-            const vector<ElectronLog>& getLog();
-
-            double vel();
-            double beta();
-            double beta2();
-            double gamma();
-            double gamma_inv();
-        };
-    \end{minted}
-    \caption{Electron class definition}
-    \label{fig:e_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Bunch{
-        private:
-            int e_count = 0;
-            int index_fastest = 0;
-            double max_energy = 0;
-            double entry_time = 0;
-            double E_in = 0.04;
-
-            vector<Bunch> subBunchs;
-            vector<shared_ptr<Electron>> e;
-        public:
-            Bunch(unsigned int num_of_electrons, double Ein, vector3d gunpos, vector3d gundir, double gun_ns);
-            Bunch();
-            ~Bunch();
-
-            void saveInfo(double time);
-
-            Electron& getFastest();
-
-            void AddElectron(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
-
-            shared_ptr<Electron> AddElectronGiveAddress(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
-
-            void setEntryTime(double entry_time);
-            void setEin(double E_in);
-            void setNSLen(double len);
-
-            uint32_t get_e_count();
-            double getEin();
-            double E_ave();
-            double E_rms();
-
-            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
-
-            void divide(unsigned int num);
-            void concat();
-            Bunch& subBunch(unsigned int index);
-            vector<Bunch*> subBunchPtr();
-
-            void reset();
-
-            void print_bunch_info();
-            void print_summary();
-
-            void logPaths(vector<DataStorage>& pathStorage, std::string header);
-        };
-    \end{minted}
-    \caption{Bunch class definition}
-    \label{fig:bunch_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Gun{
-            double Ein;
-            double sEin;
-            double gun_period;
-            double gun_active_time;
-            double ns_between_each_electron_fire;
-
-            vector3d gunpos;
-            vector3d gundir = vector3d(1,0,0);
-
-            uint64_t bunch_count = 0;
-            uint64_t e_per_bunch = 1;
-
-            uint32_t _fired_bunch = 0;
-            uint32_t _fired_e_in_current_bunch = 0;
-            bool _firing = false;
-
-            bool _mt_enabled = false;
-            uint32_t _child_thread_count = 0;
-
-            vector<Bunch> bunchs;
-
-            mutex _gun_mutex; 
-            vector<shared_ptr<vector<shared_ptr<Electron>>>> thread_bunchs;
-
-            void setNSLen(double len);
-        public:
-            Gun();
-            Gun(double Ein, double gun_active_time, double pulse_interval, vector3d gunpos);
-            ~Gun();
-            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
-
-            void fireIfActive(double time);
-            void fireAllWithFireTimesMT();
-
-            void addBunch(unsigned int num_of_electrons, double Ein);
-
-            void setGunActiveTime(double gt);
-            double getGunActiveTime(){return gun_active_time;}
-            void setGunInterval(double guninterval);
-            void setGunPos(vector3d gun_pos);
-            void setGunDir(vector3d gun_dir);
-            void setEin(double Ein) ;
-            void setEinStd(double EinStd) ;
-            void setNumberOfElectrons(uint64_t e_num);
-            void getElectronsPerBunch(){return e_per_bunch;}
-            void setNumberOfBunchs(uint64_t b_num);
-            void enableMT(uint32_t thread_count);
-
-            void saveInfo(double time);
-            void logPaths(vector<vector<DataStorage> >& pathsStorage, std::string pathsPath, std::string header);
-        };
-    \end{minted}
-    \caption{Gun class definition}
-    \label{fig:gun_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Simulator{        // E in MV/m,   En in MeV,   B in T,    t in ns
-        protected:
-            Gun gun;
-            double Emax; double freq = 107.5; double phase_lag = 0; 
-            DataStorage EfieldStorage; DataStorage BfieldStorage;
-            vector<vector<DataStorage>> pathsStorage;
-            std::string configPath;
-            std::string pathsPath;
-            std::string EfieldLogHeader;
-            std::string BfieldLogHeader;
-            std::string eLogHeader;
-
-            double simulation_time = 0;
-            double dummy_time = 0;
-            double start_time = 0;
-            double end_time = 45;   
-            double time_interval = 0.0001;
-            uint64_t STEPS_TAKEN = 0;
-            double GUN_ACTIVE_TIME = 1;         
-            double GUN_PERIOD = 9.3;
-            uint64_t NUM_OF_ELECTRONS = 1;
-            uint64_t NUM_OF_BUNCHS = 1;
-            double Ein = 0.04;
-            double EinStd = 0;
-            vector3d gunPosition;
-            vector3d gunDirection = vector3d(1,0,0);
-
-            shared_ptr<mutex> ui_mutex;
-            UIHandler ui_handler;
-            shared_ptr<mutex> state_mutex;
-            uint8_t state = 0x0;
-
-            MultiThreadEngine MTEngine;
-            unsigned int MAX_THREAD_COUNT = 1;
-            bool MULTI_THREAD = false;
-        public:
-            Simulator();
-            ~Simulator(){}
-
-            void enableMultiThreading(unsigned int thread_count);
-            void setdT(double dT);
-            void setEin(double E_in);
-            void setEinStd(double Ein_Std);
-            void setNumberofElectrons(uint64_t num_of_electrons);
-            void setNumberofBunchs(uint64_t num_of_bunchs);
-            void setStartTime(double starttime);
-            void setEndTime(double end_time);
-            void setGunActiveTime(double gun_ns);
-            void setGunPeriod(double pi);
-            void setGunPosition(vector3d pos);
-            void setGunDirection(vector3d dir);
-            void setRFPath(std::string path);
-            void setBPath(std::string path);
-            void setPathsPath(std::string path);
-            void setConfigPath(std::string path);
-
-            virtual void run();
-            void openLogs();
-            void closeLogs();
-            virtual void getConfig(Configuration& config) = 0;
-            virtual void logEfield(double time, bool) = 0;
-            virtual void logBfield() = 0;
-            void logPaths();
-            shared_ptr<mutex> getUIMutex();
-        };
-    \end{minted}
-    \caption{Simulator class definition}
-    \label{fig:sim_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class RhodotronSimulator : public Simulator{
-        private:
-            double R1;
-            double R2;
-            CoaxialRFField E_field;
-            MagneticField B_field;
-
-            void _runMT();
-            void _runST();
-        public:
-            RhodotronSimulator(double phase_lag);
-            RhodotronSimulator(Configuration& config);
-
-            void StartUIHandler();
-            void StopUIHandler();
-            void DeclareService(std::string pipe_name);
-
-            void setFreq(double frequency);
-            void setPhaseLag(double phase_lag);
-            void setEmax(double E_max);
-            void setR1(double r1);
-            void setR2(double r2);
-            void addMagnet(double B, double r, vector3d position);
-            void addMagnet(Magnet m);
-
-            void updateSimulation();
-            void getConfig(Configuration& config);
-            void logEfield(double time, bool end);
-            void logBfield();
-
-            void run();
-            void notifyUI(double time);
-
-            void setState(uint8_t state_);
-        };
-    \end{minted}
-    \caption{RhodotronSimulator class definition}
-    \label{fig:rhodosim_class}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-            class RFField{
-            protected:
-                double E;                       // MV/m
-                double E_max = 0;               // MV/m
-                double frequency = 107.5;       // MHz
-                double phase_lag = 0;           // degree
-            public:
-                RFField();
-                RFField(double phase_lag);
-                virtual ~RFField() {}
-
-                virtual vector3d getField(vector3d position);              
-                virtual double getField(double R);
-                virtual int log(DataStorage& rf, double time, bool end = false);
-                vector3d actOn(Electron& e);    
-                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);
-
-                double getE() {return E;}
-                void setEmax(double E_max) {this->E_max = E_max; update(0);}
-                void setFreq(double freq){ frequency = freq;}
-                void setPhaseLag(double phaselag){ phase_lag = phaselag; update(0);}
-                virtual void update(double time);
-            };
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-            class CoaxialRFField : public RFField{
-            private:
-                double r1 = 0.188;                         // m
-                double r2 = 0.753;                         // m
-                double E_max_pos = r1;                     // m
-                std::vector<CoaxialRFField*> _childs;
-                double E_radial(double R) const;
-            public:
-                CoaxialRFField();
-                CoaxialRFField(double phase_lag);
-                ~CoaxialRFField() override;
-                void setR1(double r1);
-                void setR2(double r2);
-                void setEmaxPos(double Emaxpos);
-
-                vector3d getField(vector3d position) const override;
-                double getField(double R) const override;
-                vector3d actOn(Electron& e);
-                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);    
-                void update(double time) override;
-
-                int log(DataStorage& rf, double time, bool end = false) override;
-
-                std::shared_ptr<CoaxialRFField> Copy();
-                void split(uint32_t amount_of_child);
-                CoaxialRFField* child(uint32_t index);
-            };
-        \end{minted}
-    \end{subfigure}
-    \caption{CoaxialRFField class definition}
-    \label{fig:rf_class}
-\end{figure}
-
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
-
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{An example \textit{config.in} file.}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.114422     & 0.028398 & 0.009294 \\
-    1.00E-02 & 0.019233     & 0.036245 & 0.002182 \\
-    1.00E-03 & 0.002141     & 0.147979 & 0.00125  \\
-    9.00E-04 & 0.001749     & 0.172161 & 0.00794  \\
-    8.00E-04 & 0.001516     & 0.184629 & 0.004359 \\
-    7.00E-04 & 0.00152      & 0.20445  & 0.001919 \\
-    6.00E-04 & 0.001049     & 0.234947 & 0.004416 \\
-    5.00E-04 & 0.000974     & 0.278938 & 0.010969 \\
-    4.00E-04 & 0.0009       & 0.336847 & 0.003028 \\
-    3.00E-04 & 0.000587     & 0.441771 & 0.005859 \\
-    2.00E-04 & 0.000433     & 0.652066 & 0.006637 \\
-    1.00E-04 & 0.0002       & 1.280059 & 0.016027 \\
-    9.00E-05 & 0.000145     & 1.41908  & 0.013122 \\
-    8.00E-05 & 0.000153     & 1.592492 & 0.011332 \\
-    7.00E-05 & 0.000162     & 1.806561 & 0.009931 \\
-    6.00E-05 & 0.000123     & 2.103571 & 0.011143 \\
-    5.00E-05 & 0.000084     & 2.515006 & 0.01393  \\
-    4.00E-05 & 0.000092     & 3.140471 & 0.014138 \\
-    3.00E-05 & 0.000053     & 4.158715 & 0.009474 \\
-    2.00E-05 & 0.000045     & 6.231734 & 0.015236 \\
-    1.00E-05 & 0.000022     & 12.39871 & 0.039575 \\
-    1.00E-06 & 0.000003     & 123.318  & 0.299559
-    \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:lf_statE_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.055355     & 0.031054 & 0.003281 \\
-        1.00E-02 & 0.009868     & 0.063656 & 0.000893 \\
-        1.00E-03 & 0.001141     & 0.435864 & 0.005332 \\
-        9.00E-04 & 0.001325     & 0.478216 & 0.00595  \\
-        8.00E-04 & 0.001112     & 0.533789 & 0.003897 \\
-        7.00E-04 & 0.000705     & 0.60586  & 0.005441 \\
-        6.00E-04 & 0.000687     & 0.703851 & 0.009447 \\
-        5.00E-04 & 0.000474     & 0.840173 & 0.00913  \\
-        4.00E-04 & 0.00046      & 1.039166 & 0.005874 \\
-        3.00E-04 & 0.000456     & 1.378822 & 0.007995 \\
-        2.00E-04 & 0.000207     & 2.045464 & 0.008499 \\
-        1.00E-04 & 0.000127     & 4.052472 & 0.014711 \\
-        9.00E-05 & 0.000091     & 4.500401 & 0.015404 \\
-        8.00E-05 & 0.000124     & 5.048922 & 0.014392 \\
-        7.00E-05 & 0.000062     & 5.773208 & 0.031443 \\
-        6.00E-05 & 0.000057     & 6.726501 & 0.020609 \\
-        5.00E-05 & 0.00006      & 8.045931 & 0.014246 \\
-        4.00E-05 & 0.000039     & 10.04809 & 0.012756 \\
-        3.00E-05 & 0.000045     & 13.39669 & 0.028057 \\
-        2.00E-05 & 0.000023     & 20.03889 & 0.006436 \\
-        1.00E-05 & 0.000016     & 40.0818  & 0.120627 \\
-        1.00E-06 & 0.000003     & 400.2421 & 0.554172
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:rk2_statE_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.986005     & 0.030314 & 0.009209 \\
-    1.00E-02 & 0.154314     & 0.036833 & 0.004068 \\
-    1.00E-03 & 0.01476      & 0.131783 & 0.002352 \\
-    9.00E-04 & 0.013618     & 0.150984 & 0.005618 \\
-    8.00E-04 & 0.011863     & 0.161336 & 0.003117 \\
-    7.00E-04 & 0.010109     & 0.179693 & 0.002658 \\
-    6.00E-04 & 0.009277     & 0.205356 & 0.002912 \\
-    5.00E-04 & 0.007527     & 0.242352 & 0.003093 \\
-    4.00E-04 & 0.006084     & 0.294269 & 0.001551 \\
-    3.00E-04 & 0.00449      & 0.383982 & 0.001711 \\
-    2.00E-04 & 0.002897     & 0.563762 & 0.004214 \\
-    1.00E-04 & 0.001458     & 1.101252 & 0.008064 \\
-    9.00E-05 & 0.001376     & 1.229321 & 0.0089   \\
-    8.00E-05 & 0.001232     & 1.381441 & 0.01057  \\
-    7.00E-05 & 0.001027     & 1.574994 & 0.011933 \\
-    6.00E-05 & 0.000853     & 1.833183 & 0.006065 \\
-    5.00E-05 & 0.00074      & 2.184948 & 0.013416 \\
-    4.00E-05 & 0.000596     & 2.72503  & 0.016356 \\
-    3.00E-05 & 0.000467     & 3.617576 & 0.017581 \\
-    2.00E-05 & 0.000308     & 5.394629 & 0.027885 \\
-    1.00E-05 & 0.00015      & 10.75182 & 0.03301  \\
-    1.00E-06 & 0.000017     & 106.9198 & 0.373175
-    \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:lf_statE90_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.587777     & 0.034741 & 0.012735 \\
-        1.00E-02 & 0.09943      & 0.059945 & 0.001318 \\
-        1.00E-03 & 0.009987     & 0.38199  & 0.005941 \\
-        9.00E-04 & 0.007946     & 0.417119 & 0.005683 \\
-        8.00E-04 & 0.007999     & 0.466052 & 0.006398 \\
-        7.00E-04 & 0.006732     & 0.525791 & 0.003782 \\
-        6.00E-04 & 0.005541     & 0.612876 & 0.007114 \\
-        5.00E-04 & 0.005022     & 0.732091 & 0.012129 \\
-        4.00E-04 & 0.004031     & 0.906845 & 0.012156 \\
-        3.00E-04 & 0.002779     & 1.199367 & 0.014536 \\
-        2.00E-04 & 0.001897     & 1.782653 & 0.016993 \\
-        1.00E-04 & 0.000895     & 3.52464  & 0.029778 \\
-        9.00E-05 & 0.000858     & 3.916115 & 0.041066 \\
-        8.00E-05 & 0.000731     & 4.409459 & 0.040828 \\
-        7.00E-05 & 0.00066      & 5.012686 & 0.042727 \\
-        6.00E-05 & 0.000561     & 5.851793 & 0.038488 \\
-        5.00E-05 & 0.000471     & 7.002315 & 0.046152 \\
-        4.00E-05 & 0.000363     & 8.747954 & 0.063936 \\
-        3.00E-05 & 0.000264     & 11.64305 & 0.091404 \\
-        2.00E-05 & 0.000184     & 17.44533 & 0.123198 \\
-        1.00E-05 & 0.000093     & 34.93332 & 0.391012 \\
-        1.00E-06 & 0.000011     & 348.494  & 3.237203
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:rk2_statE90_table}
-\end{table}
-% START OF BIBLIOGRAPHY
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
-
-    \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018
-
-\end{thebibliography}
-
-% END OF BIBLIOGRAPHY
+%%%%%%
 

### 2023-08-17 subsections/tools/numericalmethods/leap-frog-runge-kutta.tex
changes from Erkcan & Gokhan hocas

--- 2023-08-07 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
@@
 
-\section{Numerical Integration Methods}
+\section{Algorithms}
 

### 2023-08-17 subsections/tools/simulation/simulation.tex
changes from Erkcan & Gokhan hocas

--- 2023-08-07 msthesis.tex
@@
 
-\newcommand{\e}{$\textbf{e}^-$ }
-\newcommand{\egun}{$\textbf{e}^-$-gun }
-\newcommand{\eB}{$\textbf{e}^-$ - $\vecthreeBF{B}$ }
-\newcommand{\eE}{$\textbf{e}^-$ - $\vecthreeBF{E}$ }
-\newcommand{\eEM}{$\textbf{e}^-$ - \textbf{EM} }
-\newcommand{\ee}{$\textbf{e}^-$ - $\textbf{e}^-$ }
-
 \newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
 \newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
 
-\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
-\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
-\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
-\newcommand{\fromfigsix}[6]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
+\newcommand{\fromch}[1]{\textit{chapter \ref{ch:#1}}}
 
-\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+%----../../..++++.
 
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
-
-\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
-\newcommand{\fromtabf}[4]{\textit{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}}
-
-% START OF intro.tex
-
-\chapter{INTRODUCTION}
-
-\newpage
-
-% START OF THEORY
-
-\chapter{THEORY}
-
-\section{Accelerating Charged Particles}
-
-\subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force and states 
-\begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
-\end{equation}
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
-\begin{equation*}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
-\end{equation*}
-Considering these two statements, we can find the relation between momentum and acceleration as follows
-\begin{eqnarray*}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
-\end{eqnarray*}
-\begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
-\end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
-\begin{equation} \label{eq:a_F_parallels}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
-    \end{aligned}
-\end{equation}
-\begin{eqnarray*}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
-\end{eqnarray*}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
-\begin{equation*}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation*}
-Inserting this
-\begin{eqnarray}
-    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
-\begin{eqnarray*}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
-\end{eqnarray*}
-We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
-\begin{equation} \label{eq:Frel_para_and_perp}
-    \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
-    \end{aligned}
-\end{equation}
-
-\subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
-\newline
-\begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
-\end{equation}
-\newline
-where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.
-
-\subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
-\begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
-\end{equation}
-Where $ \partial \tau = \partial t / \gamma $,
-\begin{equation}
-    \begin{aligned}
-        p^{\mu} = 
-        \begin{bmatrix}
-            W/c \\
-            p_x         \\
-            p_y \\
-            p_z
-        \end{bmatrix}    
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        F^{\mu\nu} = 
-        \begin{bmatrix}
-                0       & -E_x/c   & -E_y/c    & -E_z/c \\
-                E_x/c   &   0      & -B_z      & B_y     \\
-                E_y/c   &   B_z    &  0        & -B_x     \\
-                E_z/c   &   -B_y   & B_x       & 0   
-        \end{bmatrix} 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        u_{\nu} = \gamma
-        \begin{bmatrix}
-                 c \\
-                -v_x \\
-                -v_y \\
-                -v_z \\
-        \end{bmatrix} 
-    \end{aligned}
-\end{equation}
-Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
-\newline
-
-For $ \mu = 0 $, we have the time component of the equation;
-\begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
-\end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
-\begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
-\end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
-
-\subsection{Acceleration caused by lorentz force}
-Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
-\begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
-\end{equation*}
-The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
-\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
-    \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
-    \end{aligned}    
-\end{equation}
-Acceleration due to electric field can be simplified as;
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
-\end{eqnarray*}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
-\begin{equation} \label{eq:acc_of_E_and_B}
-    \begin{aligned}
-        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
-    \qquad \qquad
-    \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
-    \end{aligned}
-\end{equation}
-
-\newpage
-
-\section{Particle Accelerators}
-
-Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
-These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
-They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.
-
-At their core, particle accelerators utilize electromagnetic fields to impart energy to particles and control their trajectories. 
-These fields are generated by intricate arrangements of magnets and RF (radiofrequency) cavities within the accelerator structure. 
-By precisely controlling these fields, accelerators can propel particles to speeds close to the speed of light, enabling them to acquire high energies.
-
-Accelerators can be categorized into two main types: linear accelerators (linacs) and circular accelerators. 
-Linacs accelerate particles in a straight line, while circular accelerators use magnetic fields to bend the particle trajectory into a circular path.
-
-The acceleration process in accelerators involves multiple stages. Initially, particles are injected into the accelerator at a relatively low energy. 
-As they progress through the accelerator, they are subjected to alternating electric fields that accelerate them, while magnetic fields guide their trajectories.
-Focusing elements, such as magnetic lenses or quadrupole magnets, ensure the particles remain tightly controlled.
-
-As particles gain energy in the accelerator, they approach relativistic speeds, where relativistic effects become significant. 
-Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-
-Particle accelerators are essential tools for scientific research.
-They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics.
-Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
-They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
-
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A linear proton accelerator in KAHVELab}
-\end{figure}
-
-\subsection{Key Concepts}
-
-\subsubsection{Resonance Frequency}
-Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
-It is determined by the physical dimensions and the speed of light in the cavity's medium. 
-In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
-\begin{equation}
-    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
-    \label{eq:f_r_rec}
-\end{equation}
-Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
-
-\subsubsection{Bunch}
-Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
-
-\subsubsection{Phase Stability}
-Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
-It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
-which is crucial for achieving efficient particle acceleration. 
-Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
-ensuring that they receive the correct energy boosts and interact predictably with detectors. 
-Deviations in phase stability can lead to particle loss and decreased beam quality.
-
-\subsubsection{Phase Lag}
-Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
-It describes the difference in phase angles within their respective cycles, between two signals.
-
-\subsubsection{Shunt Impedance}
-The shunt impedance of an RF accelerator is a measure of the efficiency 
-at which the accelerator can transform the supplied RF power into acceleration.
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A rf cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Bending Magnets}
-Bending magnets, also known as dipole magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
-
-% TODO : ADD STEERER MAGNET PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{./figures/to_be_added.png}
-    \caption{A bending magnet used in KAHVELab}
-\end{figure}
-
-\subsection{Rhodotron Accelerator} \label{sec:theory_rhodo}
-
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in his publication \textit{A new type of rf electron accelerator:The Rhodotron} in 1989 \cite{rhodo_pottier}.
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. Its named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
-
-The design of a rhodotron mainly consists of a coaxial cylindrical RF cavity and bending magnets surrounding it.
-RF cavity is fed by an external RF source, accelerating the electrons entering from an attached electron gun.
-
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
-Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
-This constraint helps with  phase stability and synchronization of the beam.
-
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
-    \label{fig:pottier_table1}
-\end{figure}
-
-Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
-\end{equation}
-
-Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
-    \label{fig:pottier_table2}
-\end{figure}
-
-Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
-\begin{equation}
-    \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
-
-\subsubsection{Acceleration cycle of Rhodotron}
-
-Electrons undergo four different stages during a single pass. 
-They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-See \fromfig{rhod_cycle_1}
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.See \fromfig{rhod_cycle_2}
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-See \fromfig{rhod_cycle_3}
-    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-See \fromfig{rhod_cycle_4}
-\end{description}
-
-This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
-After desired amount of pass has been completed, the electrons exit the accelerator.
-
-This process is explained further in the following figures where $T$ is the period of the electric field.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod1.pdf}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_1}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod2.pdf}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_2}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod3.pdf}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_3}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod4.pdf}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
-    \label{fig:rhod_cycle_4}
-\end{figure}
-
-\newpage
-
-\section{Numerical Integration Methods}
-
-\subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
-The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
-It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
-The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
-This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
-
-\subsection{Runge Kutta} \label{sec:rungekutta}
-
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
-The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
-    \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        x_{n+1} = x_n + \delta x 
-    \end{aligned}
-\end{equation}
-where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
-\begin{figure}[h!]
-    \[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        c_1 & a_{21} \\
-        c_2 & a_{31} & a_{32}\\
-        \vdots& & \cdots& \\
-        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
-        \hline
-        & b_1 & b_2 &\cdots & b_m
-    \end{array}
-    \]
-    \caption{Butcher Tableau}
-    \label{fig:Butcher}
-\end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-\[ 
-    \begin{array} 
-        {c|cccc}
-        0\\
-        \hline
-        & 1
-    \end{array}
-\]
-
-The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
-The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/2 & 1/2 \\
-            1/2 & 0 & 1/2 \\
-            1   & 0 & 0 & 1\\
-            \hline
-            & 1/6 & 1/3 & 1/3 & 1/6
-        \end{array}
-        \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-        \[ 
-        \begin{array} 
-            {c|cccc}
-            0\\
-            1/3 & 1/3 \\
-            2/3 & -1/3 & 1 \\
-            1   & 1 & -1 & 1\\
-            \hline
-            & 1/8 & 3/8 & 3/8 & 1/8
-        \end{array}
-        \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
-    \label{fig:Butcher-RK4}
-\end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
-
-\newpage
+%%%%%%
 
 \section{Simulation}
-
 A simulation software is a computer program or tool that enables the creation and execution of 
@@
 
-\subsection{Basic Consepts in Programming}
-
-\subsubsection{Clock Cycle}
-
-In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
-It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).
-
-A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
-It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
-Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.
-
-The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
-Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
-Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
-
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
-\subsubsection{Concurrency}
-
-Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously.
-It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.
-
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
-This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
-True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.
-
-Programs that implement concurrency using multiple cores executes more operations per clock cycle. 
-However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.
-
-Threads utilize \textit{mutexes}, short for "mutual exclusion," 
-to synchronize and manage access to shared resources 
-in a multi-threaded or multi-process environment.
-
-\subsubsection{Object Oriented Programming}
-
-Object-Oriented Programming (OOP) is a programming paradigm that revolves around the concept of objects. 
-Definition called class serves as a blueprint that defines the structure and behavior of objects. 
-Each object encapsulates both data, and the functions that manipulate that data. 
-This encapsulation promotes modular code design and enhances data security by controlling access to the object's internal state.
-
-In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
-\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
-By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
-
-\newpage
-
-% START OF tools.tex
-
-\chapter{TOOLS}
-
-\section{Poisson Superfish}
-Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
-for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
-It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
-
-\section{CST Studio Suite}
-CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
-It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
-The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
-
-\section{ROOT}
-ROOT is a widely used open-source software framework developed by CERN (European Organization for Nuclear Research) for data analysis,
-visualization, and storage in the field of high-energy physics, particularly in experiments conducted at particle accelerators 
-like the Large Hadron Collider (LHC). It has become an essential tool in particle physics research, 
-and it's used by physicists around the world to analyze and interpret data.
-
-\section{gnuplot}
-GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs. 
-It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
-to represent and analyze data in a graphical format.
-
-\newpage
-
-% START OF DESIGN
-
-\chapter{DESIGN}
-
-\section{Cavity Design} \label{sec:cavity_design}
-
-The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
-
-By following the cylinderical design mentioned in \fromsec{theory_rhodo}, the only main design parameter remaining is the height of the cylindrical cavity.
-This parameter can be found using the constraint mentioned in \fromsec{theory_cavities}; the fact that operating RF frequency must be equal to resonant frequency of the cavity.
-For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
-In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and \textit{it will be the focus of all further calculations.}
-Using $f_{RF}=107.5$ MHz, $f_{RF}=180$;
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
-    \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
-    \end{aligned}
-    \qquad\qquad
-    \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
-    \end{aligned}
-\end{eqnarray}
-
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:107_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst107.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:180_simple_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107_e.png}
-      \caption{107.5 MHz}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst180_e.png}
-      \caption{180 MHz}
-    \end{subfigure}
-    \caption{CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}}
-    \label{fig:cst_simple_cavity_designs}
-\end{figure}
-
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/superfish/superfish180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson SUPERFISH field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_superfish}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst180mod.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST eigenmode results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_eigenmode}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst107mod_e.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.88\linewidth]{./figures/cst/cst180mod_e.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{CST electric field results of truncated cavities}
-    \label{fig:107_180_modified_cavities_cst_field}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
-      \caption{107.5 MHz unmodified}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
-      \caption{180 MHz unmodified}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
-    \label{fig:107_cavity_shunt_diff}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
-      \caption{107.5 MHz truncated}
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
-      \caption{180 MHz truncated}
-    \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
-    \label{fig:180_cavity_shunt_diff}
-\end{figure}
-
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
-    \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta Z_{180}=2.7\%
-    \end{aligned}
-\end{equation*}
-
-\newpage
-
-\section{Magnet Design} \label{sec:magnet_design}
-Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
-Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
-Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/Ltot.png}
-      \caption{Geometry of the outside trajectory \\ of a rhodotron \cite{cite:rhodo_design}}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/design/tt300_mag.png}
-      \caption{Modeling of the outside trajectory \\ of a rhodotron (TT300) \cite{cite:rhodo_design}}
-    \end{subfigure}
-    \caption{From "Design and Simulation Tools for the \\ High-Intensity Industrial Rhodotron Electron Accelerator," \\by W.Kleeven, M.Abs, J.Brison, E.Forton, J.Hubert and J.Van de Walle}
-    \label{fig:magnet_design_illustrations}
-\end{figure}
-
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the cavity should be precisely tuned to maximize acceleration in the succeeding pass.
-
-Two different approaches have been used to achieve phase stability.
-These approaches are discussed further in the following sections.
-
-\subsection{$n\lambda$ Technique} \label{sec:n_L_technique}
-
-First approach for phase stability considiration assumes that from the start of the current pass, $\beta_{avg} \approx 1$ for a synchronous particle.
-
-To maintain the phase synchronization, a particle that started the current pass at $t=0$, should start the next pass at $t=nT$, where $n$ is an integer and $T$ is the period of RF field inside cavity.
-As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality;
-\begin{equation*}
-    L_{pass} = n \lambda
-\end{equation*} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice.
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
-
-\begin{figure}[H]    
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
-    \label{fig:magnet_design}
-\end{figure}
-
-From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, $L$ is the length of the magnet guide, $d$ is the thickness of the cavity wall;
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
-
-After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
-Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-
-\begin{eqnarray}
-    tan(\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  tan(\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& tan(\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + tan(\gamma)(\pi + 2\gamma)) &=&  tan(\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{tan(\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{tan(\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
-
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
-Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
-Considering the importance of $\gamma$ for maximum number of possible passes, it will be used as the free magnet design variable in the further discussions.
-
-\subsection{$L_{out}$ Parameter Sweep} \label{sec:parameter_sweep}
-
-As mentioned previously in \fromsec{n_L_technique}, \fromeq{magnet_lambda_constraint} assumes that the particles are fast enough so that $\Delta t_{pass} \approx n T$. 
-This assumption is not guaranteed however, especially in the first few passes if the particles are not accelerated enough. 
-This scenario can happen when RF power is not sufficiently high.
-
-Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
-after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
-It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
-For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
-Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
-
-Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
-
-To start, an optimization criteria for the following pass such as
-\begin{itemize}
-    \item Ensure the phase stability of the synchronous electron
-    \item Maximize the energy gain of the synchronous electron
-    \item Minimize the energy spread of the beam
-    \item Minimize the phase lag spread of the beam
-    \item All of the above with decided weights
-\end{itemize}
-needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
-This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
-
-However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
-
-\newpage
-
-\section{Initial Design at KAHVELab}
-
-A rhodotron with operation frequency of $107.5$ MHz was decided to be built at KAHVELab. 
-After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
-    \label{fig:initial_design}
-\end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_design3.png}
-      \caption{Axial cross section.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_design2.png}
-      \caption{Cross section at acceleration plane.}
-    \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
-    \label{fig:initial_design_cross_section}
-\end{figure}
-The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_first_magnet_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.92\linewidth]{./figures/cst/cst_first_magnet_design2.png}
-    \end{subfigure}
-    \caption{Initial magnet design.}
-    \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
-    \label{fig:initial_three_magnet_design}
-\end{figure}
-
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
-Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
-
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
-
-In KAHVELab, several improvements were made to these initial designs together with \textit{Mr.
-Sinan ÖZ}.
-They include curved edges on cavity which reduce the power loss on cavity walls, and redesigned iron casing on magnets for ease of production and maintenance.
-Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_sinan_cavity_design1.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.94\linewidth]{./figures/cst/cst_sinan_cavity_design2.png}
-    \end{subfigure}
-    \caption{Improved cavity design.}
-    \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \caption{Improved magnet design.}
-    \label{fig:improved_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/cst/cst_second_magnet_design2.png}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.9\linewidth]{./figures/cst/cst_second_magnet_design3.png}
-    \end{subfigure}
-    \caption{Cross section and coils of improved magnet design.}
-    \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \caption{Magnetic field in acceleration plate of improved magnet design.}
-    \label{fig:improved_magnet_design_B}
-\end{figure}
-
-From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
-This reduction helps containing the spread of entering beam, decreasing the amount of focusing needed further into trajectory.
-
-\newpage
-
-% START OF SIMULATION
-
-\chapter{SIMULATION}
-% Start of poc.tex
-\section{Proof of Concept}
-Once the need for a custom built tool for designing and simulating a Rhodotron type accelerator was apparent, a simple 1D proof of concept was implemented.
-
-This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
-\begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
-    \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
-    \end{enumerate}
-\end{itemize}
-
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \caption{Core logic loop of the POC}
-    \label{fig:POC_core_logic}
-\end{figure}
-
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
-Since using a single software would have made the process error prone.
-
-After the results obtained from \textit{POC} were found to be promising, a decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
-The development and improvement efforts are still ongoing.
-
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
-The following sections in this chapter investigates their implementations further.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Intermediate Versions}
-
-\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
-Initial step of improving \textit{POC} towards \textit{Rhodotron Simulation} was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
-First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
-One can sweep the $t_{out}$ parameter to find the optimal value.
-This simple implementation can be found in \fromfig{lout_opt_single_e} of \fromapp{intermediate_codes}.
-
-Although the results from this optimization sweep were promising after they were simulated with $CST$, simulating one particle would not be sufficiently useful for designing a magnet.
-
-\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
-After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
-They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
-
-Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
-$\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
-
-\begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
-\end{itemize}
-
-Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}.
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        int phase_opt(int phase_sweep_range){
-            double minrms = 1;
-            int opt_phase;
-            for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-              Bunch bunch1(RFphase);
-              double t1 = 0;
-              bunch1.bunch_gecis_t(t1);
-              bunch1.reset_pos();
-
-              if( bunch1.E_rms() < minrms ){
-                minrms = bunch1.E_rms();
-                opt_phase = RFphase;
-              }
-            }
-            return opt_phase;
-        }
-    \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt}
-\end{figure}
-
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
-This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
-
-After the bunch and $\phi_{lag}$ sweep implementations, $L_{out}$ sweep was also updated to minimize $E_{rms}$.
-$\rho$ and $L$ calculations, using \fromeqs{magnet_rho_constraint}{magnet_L_constraint}, were also integrated.
-Two example runs from this intermediate build can be found in \fromfigs{lout_opt_1ns_Erms}{lout_opt_08ns_Erms} of \fromapp{example_simulation_runs}.
-
-\subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
-Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of \textit{OOP}, details of which can be seen in \fromfigsix{e_class}{bunch_class}{gun_class}{sim_class}{rhodosim_class}{rf_class} of \fromapp{intermediate_codes}.
-
-Magnets were modeled as major segments of a circle, defined with $\vecthreeBF{r}_{mag}$, $\textbf{R}$ and $|\textbf{B}|$. 
-For the initial implementation, $\vecthreeBF{B}$ assumed to be uniform and has no leaks outside the magnet boundary (See \fromfig{is_inside_halfsphere} in \fromapp{intermediate_codes}).
-
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d CoaxialRFField::actOn(Electron& e){
-                vector3d Efield = getField(e.pos);                          // Calculate E vector
-                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
-                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                          // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
-    \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-
-Where * and \% are, dot-product and cross-product respectably. (See \fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/5ns_gnuplot.png}
-        \caption*{Unsyncronized \e gun period, $T_g = 5ns$}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/9_3ns_gnuplot.png}
-        \caption*{Syncronized \e gun period, $T_g = 9.3ns$}
-    \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
-    \label{fig:example_gnuplot_renders}
-\end{figure}
-
-\subsection{Acceleration in Magnetic Field}
-An issue regarding the \eB interaction became apparent when energy gain during these interactions was observed.
-A setup simulation was implemented in which a bunch of 100\e at $1$MeV was fired into a uniform magnetic field of $0.1$T located in $x>0.05$m.
-Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=2.783$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_lf_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.011$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
-    \label{fig:mag_lf_render}
-\end{figure}
-
-Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
-To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
-The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
-The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
-
-These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-E.png}
-        \caption*{$dt$ vs $\Delta E$}
-    \end{subfigure}
-
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png}
-        \caption*{$dt$ vs $T_{sim}$}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:mag_lf_rk2_comparison}
-\end{figure}
-
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
-
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
-
-\subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
-
-As test setups, two simulation confgurations were made. They aimed to test the accuracy of acceleration of a beam in parallel and perpendicular static uniform electric fields.
-Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_1.png}
-        \caption*{Setup-1 parallel $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \begin{subfigure}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{./figures/illustrations/statE_2.png}
-        \caption*{Setup-2, perpendicular $\vecthreeBF{E}$ field}
-    \end{subfigure}
-    \caption{Illustration of test setups.}
-\end{figure}
-
-In the first test, the beam would be injected into a static uniform electric field \\
-$\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
-$\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
-
-Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
-To also measure the variance in simulation completion times, $T_{sim}$, set of $10$ runs were completed at the configuration for each $dt$ value.
-
-\begin{figure}[H]
-    \centering
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_par.png}
-        \caption*{Setup-1, $\textbf{V}_{\parallel}$=4MV}
-    \end{subfigure}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/statE_perp.png}
-        \caption*{Setup-2, $\textbf{V}_{\perp}$=4MV}
-    \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_par_stat_E_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
-    \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
-    \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
-    \end{aligned}
-    \qquad
-    \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
-    \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph}),
-
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
-
-The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
-
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
-
-\subsection{Multithreading}
-As already mentioned before, multithreading implementation efforts were ongoing since right after the start of this project. 
-There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
-After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
-
-For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
-The UI-Console thread would handle incoming and outgoing communication, notifying the user about the status of simulation 
-(see \fromfig{console_output_running} in \fromapp{example_simulation_runs} for example console notification, \fromfig{ui_thread} in \fromapp{intermediate_codes} for implemenation)
-or communucating with the \textit{GUI} that will be disscussed in the next section.
-
-Focus of this section is the worker threads, also known as \eEM interaction threads.
-There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
-This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
-However, this architecture can cause issues if \ee interactions were decided to be implemented in the future.
-
-Another caveat is that a copy operation of $\vecthreeBF{E}$ and $\vecthreeBF{B}$ objects for each worker thread would be needed.
-This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
-
-The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
-
-\newpage
-
-% Start of intermediate.tex
-\section{Graphical User Interface}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
-This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
-    \caption{The configuration frame of implementated first GUI design.}
-    \label{fig:gui_config}
-\end{figure}
-
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
-
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
-
-\subsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\subsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
-
-\subsection{Render Frame}
-Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
-see a specific time frame, export as snapshot or animated gif file.
-Two example renders can be seen in \fromfigs{gui_render_1}{gui_render_2}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_1}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
-    \caption{Render frame of \textit{GUI}.}
-    \label{fig:gui_render_2}
-\end{figure}
-
-\subsection{Analyze Frame}
-Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf(E)(t) graph of each electron are implementated into this frame.
-This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfigs{gui_analyze_Et}{gui_analyze_Et2}, \textit{Analyze Frame} plotting \textbf(E)(t) graphs can be observed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
-    \caption{Analyze frame of \textit{GUI} E distribution.}
-    \label{fig:gui_analyze_Edist}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
-    \label{fig:gui_analyze_Et2}
-\end{figure}
-
-\subsection{Sweep Frame}
-Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
-$\phi_{lag}$ sweep was the first parameter to be implemented. 
-It takes the range of sweep, draws $\phi_{lag} vs \mu E$, $\phi_{lag} vs \sigma E$ and $\phi_{lag} vs \sigma R$ mentioned in \fromsec{philag_sweep}.
-This enables user with an already built accelerator to optimize \egun parameters quickly. 
-In the following \fromfigf{gui_sweep_running}{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_sR}, this frame can be inspected in detail.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
-    \label{fig:gui_sweep_running}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
-    \label{fig:gui_sweep_muE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
-    \label{fig:gui_sweep_sE}
-\end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
-    \label{fig:gui_sweep_sR}
-\end{figure}
-
-As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
-New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
-
-\newpage
-
-% START OF PRODUCTION
-
-\chapter{PRODUCTION}
-% Start of final.tex
-\section{Final Design} \label{sec:final_design}
-
-As discussed before, production efforts of a rhodotron type accelerator is still ongoing in KAHVELab.
-This accelerator will be used at $f=107.5$MHz $P=50-100$kW. 
-In the following figures, rendered visuals of the final design by \textit{Mr. Sinan Öz} can be observed.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
-    \caption{Rhodotron in KAHVELab}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
-    \caption{Rhodotron cavity and \e gun}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
-    \caption{Vertical cross section of the beam injection line}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
-    \caption{Cross section of the acceleration plane}
-\end{figure}
-
-\newpage
-
-% Start of techd.tex
-\section{Technical Drawing}
-
-Technical drawings of the design mentioned in \fromsec{final_design} can be found in following figures:
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1\linewidth]{./figures/teknikcizim/altgovdeteknikresim.pdf}
-    \caption{Technical drawing of bottom part cross section of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
-    \caption{Technical drawing of the rhodotron cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
-    \caption{Technical drawing of upper part of the cavity. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.2.00.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \\ Courtesy of Mr. Sinan Öz}
-\end{figure}
-
-\newpage
-
-% Start of mani.tex
-\section{Manifacturing}
-
-Manifacturing of the rhodotron cavity has been ongoing, planned to be completed in the following months.
-
-The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet.
-
-Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
-These sheets were then pressed to achieve the shapes of the parts. 
-Several flanges were then machined, including
-\begin{itemize}
-    \item $4.5$in EIA RF flange for RF input
-    \item ISO100-KF vacuum connector flanges for vacuum pumps
-    \item ISO-63 KF flange for probe insertion
-    \item KF40 flanges for beam line vacuum gauges
-\end{itemize}
-
-After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
-304 stainless steel sheet bars of different sizes were then added by 
-TIG welding to achieve pressure resistance.
-
-Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
-This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
-which would be removed after the heat treatment.
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
-      \caption{Bottom part of the cavity while polishing.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
-      \caption{Top part of the cavity after polishing.}
-    \end{subfigure}
-    \caption{Polishing of the inner surface of cavity.}
-    \label{fig:manif_polishing}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
-      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
-      \caption{Bottom part of the cavity with the beam line assembled.}
-    \end{subfigure}
-    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
-    \label{fig:manif_toroidal_sheets}
-\end{figure}
-
-\begin{figure}
-    \captionsetup{justification=centering}
-    \centering
-    \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
-    \caption{Welded sheet bars.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup{justification=centering}
-    \centering
-    \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
-    \caption{Middle part of the cavity containing the beam line.}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
-      \caption{Welding sheet bars.}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
-      \caption{Welding toroidal sheets.}
-    \end{subfigure}
-    \caption{TIG welding.}
-    \label{fig:manif_welding}
-\end{figure}
-
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
-    \end{subfigure}%
-    \centering
-    \begin{subfigure}{.5\textwidth}
-      \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
-    \end{subfigure}
-    \caption{Assembled cavity as the current stage.}
-    \label{fig:manif_assembled}
-\end{figure}
-
-\newpage
-
-% Start of rf.tex
-% \section{RF Supply}
-
-\newpage
-
-% START OF FUTURE_WORK
-
-\chapter{FUTURE WORK}
-
-At the time of publication, production efforts of a new rhodotron type electron accelerator are currently continuing in KAHVELab. 
-Present bottleneck is the fabrication of the cavity.
-
-\section{Cavity}
-The cavity manufacturing process is in its concluding stages.
-The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
-After the heat treatment operation, 
-the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
-
-\section{Magnets}
-Magnet production was decided to be kept on hold in the early stages of the project, 
-due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
-and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
-The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.
-
-\section{Rhodotron Simulation}
-
-\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manifactured; 
-several improvements and new feature implementations are underway in the mean time. 
-They include the following;
-\begin{figure}[H]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{itemize}
-            \item Electric and magnetic field import
-            \item Field generator module to directly produce field files from specified cavity
-            \item Synchrotron radiation calculations to determine radiation and energy loss
-            \item \ee interactions
-            \item Redesign of the GUI
-            \item 3D render in GUI
-        \end{itemize}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{itemize}
-            \item Refactoring of the \eEM interaction and logging to improve performance
-            \item Refactoring of the GUI Render Frame to improve render speed
-            \item Refactoring the magnet class to introduce field leaks
-            \item Extention of analysis tools in Analyze Frame
-            \item $L_{out}$ sweep in Sweep Frame
-        \end{itemize}
-    \end{subfigure}
-\end{figure}
-
-\section{Conclusion}
-
-In conclusion, the performance and the accuracy of this new tool, \textit{Rhodotron Simulation}, cannot be determined
-before the cavity production is completed and the performance is compared with the predictions of the tool;
-however the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
-lead to the inference that this tool holds promise.
-
-\newpage
-
-\appendix
-\chapter{Intermediate Codes} \label{appendix:intermediate_codes}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            for(double i = 2; i < 9; i += dT_out){
-                t_dum += i;
-                double enow = gecis(r_pos, vel, Et, t_dum);
-                if( enow > maxE ){
-                  maxE = enow;
-                  t_opt = i;
-                }
-                t_dum = t;
-            }
-        \end{minted}
-    \end{subfigure} 
-    \\
-    \begin{subfigure}{\textwidth}
-        \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
-            double gecis(double r_pos, double vel, double Et, double &t){
-                for(; r_pos >= -R2 && r_pos <= R2 ; t+=dT){
-                    vel = c*sqrt(Et*Et-E0*E0)/Et;
-                    double RelBeta  = vel/c;
-                    double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-                    double ef=Eradial(r_pos*1000,t,RFphase*deg_to_rad);
-
-                    double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-                    r_pos = r_pos + vel * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-                    vel=vel+acc*dT*ns;
-                    RelBeta  = vel/c;
-                    RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-                    Et=RelGamma*E0; 
-                }
-                return Et;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
-    \label{fig:lout_opt_single_e}
-\end{figure}
-
-\begin{figure}[H]
-        \centering
-        \captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            int phase_opt(const vector<double>& Louts, int phase_sweep_range){
-                double minrms = 1;
-                int opt_phase;
-                for(int RFphase = -phase_sweep_range; RFphase <= phase_sweep_range; RFphase++){
-                    Bunch bunch1(RFphase);
-                    double t1 = 0;
-                    bunch1.bunch_gecis_t(t1);
-                    bunch1.reset_pos();
-
-                    for(int i = 0; i < Louts.size(); i++){
-                        bunch1.bunch_gecis_d(Louts[i]);
-                        bunch1.reset_pos();
-                    }
-
-                    if( bunch1.E_rms() < minrms ){
-                        minrms = bunch1.E_rms();
-                        opt_phase = RFphase;
-                    }
-                }
-                return opt_phase;
-            }
-        \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
-    \label{fig:phlag_opt_n_pass}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            double vector3d::operator* (const vector3d& other){
-                double dot = 0;
-                dot += this->x * other.x;
-                dot += this->y * other.y;
-                dot += this->z * other.z;
-                return dot;
-            }
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-            vector3d vector3d::operator% (const vector3d& other){
-                double x_ = (this->y * other.z) - (this->z * other.y);
-                double y_ = (this->z * other.x) - (this->x * other.z);
-                double z_ = (this->x * other.y) - (this->y * other.x);
-                vector3d crossed(x_, y_, z_);
-                return crossed;
-            }
-        \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
-    \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
-\label{fig:is_inside_halfsphere}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
-            if (B.isInside(pos) == -1){
-                return vector3d(0,0,0);
-            }
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-            double time_halved = time_interval*0.5;
-            // get k1                                       
-            vector3d F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                       
-            vector3d k1 = F_m * e_dummy.gamma_inv();     
-            // get k2
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k1, time_halved);                                              
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;                                               
-            vector3d k2 = F_m * e_dummy.gamma_inv();    
-            // get k3
-            e_dummy.vel = vel;
-            e_dummy.accelerate(k2, time_halved);
-            vector3d k3 = F_m * e_dummy.gamma_inv();   
-            // get k4
-            e_dummy.vel = vel;
-            e_dummy.move(time_halved);
-            e_dummy.accelerate(k3, time_interval);                                           
-            F_m = (e_dummy.vel % B.getField(pos))*eQMratio;  
-            vector3d k4 = F_m * e_dummy.gamma_inv();
-
-            return (k1 + k2*2 + k3*2 + k4)/6;
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
-\label{fig:rk1_B}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
-            vector3d run_kut_E = interactE_RK(E, time_interval);
-            vector3d run_kut_B = interactB_RK(B, time_interval);
-
-            vector3d acc = run_kut_E + run_kut_B;
-
-            move(acc, time_interval/2);
-            accelerate(acc, time_interval);
-            move(acc, time_interval/2);
-        }
-    \end{minted}
-\caption{RK4-1 implemenation of \eEM}
-\label{fig:rk1_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
-            Electron2D e_dummy;
-            e_dummy.Et = Et;
-            e_dummy.pos = pos;
-            e_dummy.vel = vel;
-
-            // Calculate k1
-            vector3d acc_E = E.actOn(e_dummy);
-            vector3d acc_B = B.actOn(e_dummy);
-            vector3d acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k1 = e_dummy.pos, vel_k1 = e_dummy.vel;
-
-            // Calculate k2
-            e_dummy.pos = (pos + pos_k1)*0.5;
-            e_dummy.vel = (vel + vel_k1)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k2 = e_dummy.pos, vel_k2 = e_dummy.vel;
-
-            // Calculate k3
-            e_dummy.pos = (pos + pos_k2)*0.5;
-            e_dummy.vel = (vel + vel_k2)*0.5;
-            e_dummy.Et = e_dummy.gamma()*E0;
-            E.update(time + time_interval*0.5);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k3 = e_dummy.pos, vel_k3 = e_dummy.vel;
-
-            // Calculate k4
-            E.update(time + time_interval);
-
-            acc_E = E.actOn(e_dummy);
-            acc_B = B.actOn(e_dummy);
-            acc = acc_E + acc_B;
-            e_dummy.move(time_interval);
-            e_dummy.accelerate(acc, time_interval);
-            vector3d pos_k4 = e_dummy.pos, vel_k4 = e_dummy.vel;
-
-            E.update(time);
-            pos = (pos_k1 + pos_k2*2 + pos_k3*2 + pos_k4)/6;
-            vel = (vel_k1 + vel_k2*2 + vel_k3*2 + vel_k4)/6;
-            Et = gamma()*E0;
-    }
-    \end{minted}
-\caption{RK4-2 implemenation of \eEM}
-\label{fig:rk2_EM}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void RhodotronSimulator::_runMT(){
-            gun.fireAllWithFireTimesMT();
-
-            MTEngine.setupPool(time_interval, start_time, end_time, gun, E_field, B_field, gun.thread_bunchs);
-
-            STEPS_TAKEN = 0;
-            simulation_time = start_time;
-            while (simulation_time < end_time + time_interval ){
-                if (STEPS_TAKEN % log_interval() == 0){
-                    E_field.update(simulation_time);
-                    logEfield(simulation_time, simulation_time + time_interval > end_time);
-                    notifyUI(MTEngine.getAverageTime());
-                }
-                simulation_time+=time_interval;
-                STEPS_TAKEN++;
-            }
-            bool end = false;
-            while (!end){
-                double time = MTEngine.getAverageTime();
-                notifyUI(time);
-                if ( time >= end_time ){
-                    end = true;
-                }
-                this_thread::yield();
-            }
-            MTEngine.join();
-
-        }
-    \end{minted}
-    \caption{Multithreading main-thread logic.}
-    \label{fig:_runMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void Gun::fireAllWithFireTimesMT(){
-            std::random_device rd;
-            std::mt19937 e2(rd());
-            std::normal_distribution<double> Edist(Ein, sEin);
-
-            for(_fired_bunch= 0; _fired_bunch < bunch_count; _fired_bunch++){
-                for(_fired_e_in_current_bunch= 0; _fired_e_in_current_bunch < e_per_bunch; _fired_e_in_current_bunch++){
-
-                    double E = (sEin == 0 ) ? Ein : Edist(e2);
-
-                    double fire_time = (ns_between_each_electron_fire * _fired_e_in_current_bunch) + _fired_bunch*gun_period;
-
-                    auto burrowed_e = bunchs[_fired_bunch].AddElectronGiveAddress(E, gunpos, gundir, fire_time);
-
-                    int thread_index = (_fired_e_in_current_bunch + _fired_bunch*e_per_bunch)%thread_bunchs.size();
-
-                    thread_bunchs[thread_index]->push_back(burrowed_e);
-                }
-            }
-        }
-    \end{minted}
-    \caption{Multithreading electron assign logic.}
-    \label{fig:fireAllWithFireTimesMT}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void MultiThreadEngine::setupPool( double _time_interval, double _start_time, double _end_time, Gun& gun, 
-            CoaxialRFField& RF, MagneticField& B, vector<shared_ptr<vector<shared_ptr<Electron2D>>>>& e_list){
-            threads.reserve(thread_count);
-
-            for(int i = 0; i < thread_count && i == threads.size(); i++){
-
-                child_notifier_mutexes.push_back(make_shared<mutex>());
-                child_times.push_back(make_shared<double>());
-
-                auto _E = RF.Copy();
-                auto _B = B.LightWeightCopy();
-                double time_between_fires = thread_count*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                double first_fire_time = i*gun.getGunActiveTime()/gun.getElectronsPerBunch();
-                ThreadArguments thread_arguments(i, _time_interval, _start_time, _end_time, &gun, _E, _B, e_list[i], first_fire_time, time_between_fires);
-                thread_arguments.parent_notifier_mutex = child_notifier_mutexes[i];
-                thread_arguments.current_thread_time = child_times[i];
-                threads.push_back(thread(threadLoop, thread_arguments));
-            }
-        }
-    \end{minted}
-    \caption{Multithreading worker-threads setup logic.}
-    \label{fig:setupPool}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void threadLoop(ThreadArguments thread_arguments){
-            uint64_t count = 0;
-
-            double sim_time = thread_arguments.start_time;
-
-            while(sim_time < thread_arguments.end_time + thread_arguments.time_interval){
-                thread_arguments.E->update(sim_time);
-                thread_arguments.i_args.time = sim_time;
-
-                if ( count % (unsigned long)(0.1/thread_arguments.time_interval) == 0){
-                    saveElectronInfoForSingleThread(thread_arguments.i_args);
-                    // Notifiy the main thread
-                    if(thread_arguments.parent_notifier_mutex->try_lock()){
-                        *thread_arguments.current_thread_time = sim_time;
-                        thread_arguments.parent_notifier_mutex->unlock();
-                    }
-                }
-
-                interactForSingleThread(thread_arguments.i_args);
-                // save electron info here
-                sim_time+= thread_arguments.time_interval;
-                count++;
-            }
-            thread_arguments.parent_notifier_mutex->lock();
-            *thread_arguments.current_thread_time = sim_time;
-            thread_arguments.parent_notifier_mutex->unlock();
-        }
-    \end{minted}
-    \caption{Multithreading worker-thread logic.}
-    \label{fig:threadLoop}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        void UIThreadWork(UIThreadArgs args){
-            int UI_WORK_PIECE = SIM_WORK_MASK;
-            if ( !args.isService ) {
-                UI_WORK_PIECE = 50;
-            }
-
-            double piece = (args.end_time - args.start_time)/UI_WORK_PIECE;
-
-            if ( !args.isService ) {
-                std::string sim_running_msg = "...Simulation is running...";
-                for(int i = 0; i < 26 - sim_running_msg.size()/2 ; i++){
-                    std::cout << " ";
-                }
-                std::cout << sim_running_msg <<"\n";
-            }
-
-            args.ui_mutex->lock();
-            double simtime = *(args.simulation_time);
-            args.ui_mutex->unlock();
-
-            if ( !args.isService ) {
-                std::cout << "V";
-                for(int i = 0; i < 51; i++){
-                    std::cout << "_";
-                }
-                std::cout << "V\n[" << std::flush;
-            }
-
-            int count = 0;
-            bool running = true;
-            while(running && (simtime < args.end_time || count < UI_WORK_PIECE )){
-                if( simtime > count * piece ){
-                    if ( !args.isService ) {
-                        std::cout << "#" << std::flush;
-                    }
-                    count++;
-                    args.state_mutex->lock();
-                    running = *args.state_ptr & SIM_RUNNING;
-                    *args.state_ptr = (*args.state_ptr & ~SIM_WORK_MASK) | (count & SIM_WORK_MASK);
-                    if (args.isService) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-                    args.state_mutex->unlock();
-                }
-                std::this_thread::sleep_for(std::chrono::milliseconds(25));
-                args.ui_mutex->lock();
-                simtime = *(args.simulation_time);
-                args.ui_mutex->unlock();
-
-            }
-            if ( !args.isService ) {
-                std::cout << "#]\n\n" << std::flush;
-                std::cout << "     ...Simulation is finished successfully...\n\n" << std::flush;
-            }
-
-            args.state_mutex->lock();
-            *args.state_ptr |= SIM_RENDERING;
-            if ( args.isService ) write(args._fd, args.state_ptr, SIGNAL_SIZE);
-            args.state_mutex->unlock();
-        }
-    \end{minted}
-    \caption{UI-Console handler thread logic.}
-    \label{fig:ui_thread}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Electron{
-            std::vector<ElectronLog> log;
-            uint64_t index;
-            double Et;
-            vector3d pos;
-            vector3d vel;
-            double fire_time;
-        public:
-            Electron();
-            Electron(double Ein, vector3d position, vector3d direction, double _fire_time = 0);
-            ~Electron();
-
-            void setEin(double E_in);
-            void print_electron_info();
-
-            void move(double dt);
-            void move(const vector3d& acc, double dt);
-            void move(const vector3d& acc, const vector3d& jerk, double dt);
-            void accelerate(const vector3d& acc, double dt);
-            void accelerate(const vector3d& acc, const vector3d& jerk, double dt);
-
-            void interactLF(RFField& E, MagneticField& B, double time_interval);
-            void interactRK(RFField& E, MagneticField& B, double time_interval);
-            void interactRK(RFField& E, MagneticField& B, const double time, double time_interval);
-            void interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval);
-
-            vector3d interactE_RK(const RFField& E, double time_interval);
-            vector3d interactB_RK(const MagneticField& B, double time_interval);
-
-            void saveInfo(double t);
-            void setLogSize(size_t size);
-            void loge(DataStorage& path);
-            const vector<ElectronLog>& getLog();
-
-            double vel();
-            double beta();
-            double beta2();
-            double gamma();
-            double gamma_inv();
-        };
-    \end{minted}
-    \caption{Electron class definition}
-    \label{fig:e_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Bunch{
-        private:
-            int e_count = 0;
-            int index_fastest = 0;
-            double max_energy = 0;
-            double entry_time = 0;
-            double E_in = 0.04;
-
-            vector<Bunch> subBunchs;
-            vector<shared_ptr<Electron>> e;
-        public:
-            Bunch(unsigned int num_of_electrons, double Ein, vector3d gunpos, vector3d gundir, double gun_ns);
-            Bunch();
-            ~Bunch();
-
-            void saveInfo(double time);
-
-            Electron& getFastest();
-
-            void AddElectron(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
-
-            shared_ptr<Electron> AddElectronGiveAddress(double Ein, const vector3d& gunpos, const vector3d& gundir, double fire_time);
-
-            void setEntryTime(double entry_time);
-            void setEin(double E_in);
-            void setNSLen(double len);
-
-            uint32_t get_e_count();
-            double getEin();
-            double E_ave();
-            double E_rms();
-
-            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
-
-            void divide(unsigned int num);
-            void concat();
-            Bunch& subBunch(unsigned int index);
-            vector<Bunch*> subBunchPtr();
-
-            void reset();
-
-            void print_bunch_info();
-            void print_summary();
-
-            void logPaths(vector<DataStorage>& pathStorage, std::string header);
-        };
-    \end{minted}
-    \caption{Bunch class definition}
-    \label{fig:bunch_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Gun{
-            double Ein;
-            double sEin;
-            double gun_period;
-            double gun_active_time;
-            double ns_between_each_electron_fire;
-
-            vector3d gunpos;
-            vector3d gundir = vector3d(1,0,0);
-
-            uint64_t bunch_count = 0;
-            uint64_t e_per_bunch = 1;
-
-            uint32_t _fired_bunch = 0;
-            uint32_t _fired_e_in_current_bunch = 0;
-            bool _firing = false;
-
-            bool _mt_enabled = false;
-            uint32_t _child_thread_count = 0;
-
-            vector<Bunch> bunchs;
-
-            mutex _gun_mutex; 
-            vector<shared_ptr<vector<shared_ptr<Electron>>>> thread_bunchs;
-
-            void setNSLen(double len);
-        public:
-            Gun();
-            Gun(double Ein, double gun_active_time, double pulse_interval, vector3d gunpos);
-            ~Gun();
-            void interact(RFField& E, MagneticField& B, const double time, double time_interval);
-
-            void fireIfActive(double time);
-            void fireAllWithFireTimesMT();
-
-            void addBunch(unsigned int num_of_electrons, double Ein);
-
-            void setGunActiveTime(double gt);
-            double getGunActiveTime(){return gun_active_time;}
-            void setGunInterval(double guninterval);
-            void setGunPos(vector3d gun_pos);
-            void setGunDir(vector3d gun_dir);
-            void setEin(double Ein) ;
-            void setEinStd(double EinStd) ;
-            void setNumberOfElectrons(uint64_t e_num);
-            void getElectronsPerBunch(){return e_per_bunch;}
-            void setNumberOfBunchs(uint64_t b_num);
-            void enableMT(uint32_t thread_count);
-
-            void saveInfo(double time);
-            void logPaths(vector<vector<DataStorage> >& pathsStorage, std::string pathsPath, std::string header);
-        };
-    \end{minted}
-    \caption{Gun class definition}
-    \label{fig:gun_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class Simulator{        // E in MV/m,   En in MeV,   B in T,    t in ns
-        protected:
-            Gun gun;
-            double Emax; double freq = 107.5; double phase_lag = 0; 
-            DataStorage EfieldStorage; DataStorage BfieldStorage;
-            vector<vector<DataStorage>> pathsStorage;
-            std::string configPath;
-            std::string pathsPath;
-            std::string EfieldLogHeader;
-            std::string BfieldLogHeader;
-            std::string eLogHeader;
-
-            double simulation_time = 0;
-            double dummy_time = 0;
-            double start_time = 0;
-            double end_time = 45;   
-            double time_interval = 0.0001;
-            uint64_t STEPS_TAKEN = 0;
-            double GUN_ACTIVE_TIME = 1;         
-            double GUN_PERIOD = 9.3;
-            uint64_t NUM_OF_ELECTRONS = 1;
-            uint64_t NUM_OF_BUNCHS = 1;
-            double Ein = 0.04;
-            double EinStd = 0;
-            vector3d gunPosition;
-            vector3d gunDirection = vector3d(1,0,0);
-
-            shared_ptr<mutex> ui_mutex;
-            UIHandler ui_handler;
-            shared_ptr<mutex> state_mutex;
-            uint8_t state = 0x0;
-
-            MultiThreadEngine MTEngine;
-            unsigned int MAX_THREAD_COUNT = 1;
-            bool MULTI_THREAD = false;
-        public:
-            Simulator();
-            ~Simulator(){}
-
-            void enableMultiThreading(unsigned int thread_count);
-            void setdT(double dT);
-            void setEin(double E_in);
-            void setEinStd(double Ein_Std);
-            void setNumberofElectrons(uint64_t num_of_electrons);
-            void setNumberofBunchs(uint64_t num_of_bunchs);
-            void setStartTime(double starttime);
-            void setEndTime(double end_time);
-            void setGunActiveTime(double gun_ns);
-            void setGunPeriod(double pi);
-            void setGunPosition(vector3d pos);
-            void setGunDirection(vector3d dir);
-            void setRFPath(std::string path);
-            void setBPath(std::string path);
-            void setPathsPath(std::string path);
-            void setConfigPath(std::string path);
-
-            virtual void run();
-            void openLogs();
-            void closeLogs();
-            virtual void getConfig(Configuration& config) = 0;
-            virtual void logEfield(double time, bool) = 0;
-            virtual void logBfield() = 0;
-            void logPaths();
-            shared_ptr<mutex> getUIMutex();
-        };
-    \end{minted}
-    \caption{Simulator class definition}
-    \label{fig:sim_class}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-        class RhodotronSimulator : public Simulator{
-        private:
-            double R1;
-            double R2;
-            CoaxialRFField E_field;
-            MagneticField B_field;
-
-            void _runMT();
-            void _runST();
-        public:
-            RhodotronSimulator(double phase_lag);
-            RhodotronSimulator(Configuration& config);
-
-            void StartUIHandler();
-            void StopUIHandler();
-            void DeclareService(std::string pipe_name);
-
-            void setFreq(double frequency);
-            void setPhaseLag(double phase_lag);
-            void setEmax(double E_max);
-            void setR1(double r1);
-            void setR2(double r2);
-            void addMagnet(double B, double r, vector3d position);
-            void addMagnet(Magnet m);
-
-            void updateSimulation();
-            void getConfig(Configuration& config);
-            void logEfield(double time, bool end);
-            void logBfield();
-
-            void run();
-            void notifyUI(double time);
-
-            void setState(uint8_t state_);
-        };
-    \end{minted}
-    \caption{RhodotronSimulator class definition}
-    \label{fig:rhodosim_class}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-            class RFField{
-            protected:
-                double E;                       // MV/m
-                double E_max = 0;               // MV/m
-                double frequency = 107.5;       // MHz
-                double phase_lag = 0;           // degree
-            public:
-                RFField();
-                RFField(double phase_lag);
-                virtual ~RFField() {}
-
-                virtual vector3d getField(vector3d position);              
-                virtual double getField(double R);
-                virtual int log(DataStorage& rf, double time, bool end = false);
-                vector3d actOn(Electron& e);    
-                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);
-
-                double getE() {return E;}
-                void setEmax(double E_max) {this->E_max = E_max; update(0);}
-                void setFreq(double freq){ frequency = freq;}
-                void setPhaseLag(double phaselag){ phase_lag = phaselag; update(0);}
-                virtual void update(double time);
-            };
-        \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
-            class CoaxialRFField : public RFField{
-            private:
-                double r1 = 0.188;                         // m
-                double r2 = 0.753;                         // m
-                double E_max_pos = r1;                     // m
-                std::vector<CoaxialRFField*> _childs;
-                double E_radial(double R) const;
-            public:
-                CoaxialRFField();
-                CoaxialRFField(double phase_lag);
-                ~CoaxialRFField() override;
-                void setR1(double r1);
-                void setR2(double r2);
-                void setEmaxPos(double Emaxpos);
-
-                vector3d getField(vector3d position) const override;
-                double getField(double R) const override;
-                vector3d actOn(Electron& e);
-                vector3d actOnAndGetRungeKuttaCoef(Electron& e, double dt);    
-                void update(double time) override;
-
-                int log(DataStorage& rf, double time, bool end = false) override;
-
-                std::shared_ptr<CoaxialRFField> Copy();
-                void split(uint32_t amount_of_child);
-                CoaxialRFField* child(uint32_t index);
-            };
-        \end{minted}
-    \end{subfigure}
-    \caption{CoaxialRFField class definition}
-    \label{fig:rf_class}
-\end{figure}
-
-\chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : -5
-
-        Simulation settings : 
-        ph = -5 deg, gt = 1 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.81044 m
-        Magnet guide = 0.25852 m
-        Rho = 0.088477 m
-        Drift time of the first electron in the bunch : 7.688 ns
-        Drift time of the last electron in the bunch : 7.487 ns
-        Max energy = 0.47581 MeV
-        RMS = 0.0058165 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37766 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.597 ns
-        Drift time of the last electron in the bunch : 5.617 ns
-        Max energy = 0.89172 MeV
-        RMS = 0.0099018 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.314 ns
-        Drift time of the last electron in the bunch : 5.325 ns
-        Max energy = 1.298 MeV
-        RMS = 0.013879 MeV
-
-        Electron with the most energy : 623) 1.6999 MeV,	RMS of bunch : 0.017981 MeV
-
-        Total steps calculated : 12468052652
-        Simulation finished in : 632050015 us     ( 632.1 s )
-
-    \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_1ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        Optimal phase with the least RMS : 0
-
-        Simulation settings : 
-        ph = 0 deg, gt = 0.8 ns, enum = 1000
-        dT = 0.001 ns, dT_out = 0.01 ns
-
-        For the 1th magnet:
-        Optimum out path = 0.80787 m
-        Magnet guide = 0.2574 m
-        Rho = 0.088379 m
-        Drift time of the first electron in the bunch : 7.629 ns
-        Drift time of the last electron in the bunch : 7.48 ns
-        Max energy = 0.47579 MeV
-        RMS = 0.0038689 MeV
-
-        For the 2th magnet:
-        Optimum out path = 1.0833 m
-        Magnet guide = 0.37765 m
-        Rho = 0.098898 m
-        Drift time of the first electron in the bunch : 5.589 ns
-        Drift time of the last electron in the bunch : 5.605 ns
-        Max energy = 0.89169 MeV
-        RMS = 0.0068848 MeV
-
-        For the 3th magnet:
-        Optimum out path = 1.1705 m
-        Magnet guide = 0.41573 m
-        Rho = 0.10223 m
-        Drift time of the first electron in the bunch : 5.311 ns
-        Drift time of the last electron in the bunch : 5.318 ns
-        Max energy = 1.298 MeV
-        RMS = 0.0096887 MeV
-
-        Electron with the most energy : 629) 1.6999 MeV,	RMS of bunch : 0.012318 MeV
-
-        Total steps calculated : 12455378454
-        Simulation finished in : 631136046 us     ( 631.1 s )        
-    \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
-\label{fig:lout_opt_08ns_Erms}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png}
-        \caption*{$dt=10^{-2}$ns, $\Delta E=1.047$MeV}
-    \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png}
-        \caption*{$dt=10^{-4}$ns, $\Delta E=0.006$MeV}
-    \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
-    \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
-        #            Rhodotron Simulation Configuration File
-        # ================================================================
-        #    M.Furkan Er                                     22/09/2022   
-        # ================================================================
-        #
-        # emax = Maximum electric field strength (MV/m)
-        # ein = Energy of electrons coming out of the gun (MeV)
-        # einstd = Standard deviation of energy of electrons coming out of the gun (MeV)
-        # targeten = Max energy on the output gif (MeV)
-        # freq = Frequency of the RF field (MHz)
-        # phaselag = phase lag of the first electrons (degree)
-        # starttime = time to start firing the gun (ns)
-        # endtime = ns to run the simulation (ns)
-        # dt = time interval to do the calculations (ns)
-        # guntime = how long a gun pulse is (ns)
-        # gunperiod = time between two gun pulses (ns)
-        # enum = number of electrons to simulate in a bunch
-        # bunchnum = number of times the gun fires
-        # r1 = radius of the inner cylinder (m)
-        # r2 = radius of the outer cylinder (m)
-        # epath = path to store the electric field data
-        # bpath = path to store the magnetic field data
-        # cpath = path to store the settings
-        # ppath = path to store electron data
-        # multh = enable or disable multitheading
-        # thcount = set the maximum thread to be used
-        # magrotation = degrees of rotation to enter each magnet 
-        # addmagnet = takes 3 input. (B , R, < Radial distance of center >)
-        # output = output file name
-
-        # E FIELD CONFIGURATION 
-        emax=1.170
-        freq=107.3
-        phaselag=10.0
-        r1=0.1840
-        r2=0.7380
-
-        # B FIELD CONFIGURATION 
-        magrotation=5.0
-
-        # GUN CONFIGURATION 
-        einmean=0.040
-        einstd=0.0000
-        targeten=2.0
-        guntime=1.0
-        gunperiod=9.3
-        enum=50
-        bunchnum=1
-
-        # SIM CONFIGURATION 
-        starttime=0
-        endtime=10
-        dt=0.0000010000
-        epath=xy/rf.dat
-        bpath=xy/magnet.dat
-        cpath=xy/settings.dat
-        ppath=xy/paths/
-        multh=1
-        thcount=10     
-    \end{minted}
-\caption{An example \textit{config.in} file.}
-\label{fig:config_file}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
-        -- Simulation Configuration --
-        Emax : 0.96     MV/m
-        Freq : 107.5    MHz
-        Phase Lag : -5  degree
-        EndTime : 100   ns
-        dT : 0.0001     ns
-        guntime : 0.8   ns
-        gunperiod : 9.3 ns
-        enum : 100
-        bunchnum : 2
-        R1 : 0.188241   m
-        R2 : 0.752967   m
-        Magnet count :  5
-        Ein : 0.04      MeV
-        TargetE : 2.5   MeV
-        --------------------------------
-
-                     ...Simulation is running...
-        V_____________________________________________________V
-        [####################################                 ]
-    \end{minted}
-\caption{Example of console output while simulation is running.}
-\label{fig:console_output_running}
-\end{figure}
-
-\chapter{Data and Graphs}\label{appendix:data_graph}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png}
-    \end{subfigure}
-
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png}
-    \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 2.783228     & 0.034660  & 0.011537 \\ \hline
-        1e-03 & 0.117124     & 0.115775  & 0.001071 \\ \hline
-        9e-04 & 0.104552     & 0.128983  & 0.001820 \\  \hline
-        8e-04 & 0.092252     & 0.143251  & 0.002585 \\ \hline
-        7e-04 & 0.080144     & 0.158808  & 0.003228 \\ \hline
-        6e-04 & 0.068258     & 0.182359  & 0.002426 \\\hline
-        5e-04 & 0.056554     & 0.215104  & 0.002807 \\\hline
-        4e-04 & 0.044931     & 0.262952  & 0.005119 \\\hline
-        3e-04 & 0.033467     & 0.341552  & 0.002610 \\\hline
-        2e-04 & 0.022158     & 0.501784  & 0.005709 \\\hline
-        1e-04 & 0.011006     & 0.973145  & 0.005849 \\\hline
-        9e-05 & 0.009899     & 1.084032  & 0.010985 \\\hline
-        8e-05 & 0.008792     & 1.216145  & 0.012486 \\\hline
-        7e-05 & 0.007688     & 1.387908  & 0.019031 \\\hline
-        6e-05 & 0.006586     & 1.604475  & 0.011775 \\\hline
-        5e-05 & 0.005485     & 1.926505  & 0.014535 \\\hline
-        4e-05 & 0.004384     & 2.395898  & 0.009702 \\\hline
-        3e-05 & 0.003286     & 3.178265  & 0.014099 \\\hline
-        2e-05 & 0.002189     & 4.740706  & 0.022709 \\\hline
-        1e-05 & 0.001094     & 9.441138  & 0.027266 \\\hline
-        1e-06 & 0.000109     & 93.888320 & 0.290820 \\ \hline
-    \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:lf_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        1e-02 & 1.047130     & 0.048943   & 0.011642 \\\hline
-        1e-03 & 0.066912     & 0.239299   & 0.003483 \\\hline
-        9e-04 & 0.059899     & 0.268007   & 0.004530 \\\hline
-        8e-04 & 0.053028     & 0.296154   & 0.004146 \\\hline
-        7e-04 & 0.046183     & 0.333123   & 0.004259 \\\hline
-        6e-04 & 0.039452     & 0.384046   & 0.002458 \\\hline
-        5e-04 & 0.032734     & 0.456387   & 0.003888 \\\hline
-        4e-04 & 0.026072     & 0.563011   & 0.004803 \\\hline
-        3e-04 & 0.019474     & 0.742440   & 0.006169 \\\hline
-        2e-04 & 0.012926     & 1.103559   & 0.007649 \\\hline
-        1e-04 & 0.006437     & 2.178779   & 0.009733 \\\hline
-        9e-05 & 0.005791     & 2.411302   & 0.012266 \\\hline
-        8e-05 & 0.005145     & 2.704117   & 0.012683 \\\hline
-        7e-05 & 0.004500     & 3.078304   & 0.013281 \\\hline
-        6e-05 & 0.003856     & 3.589154   & 0.014472 \\\hline
-        5e-05 & 0.003212     & 4.297561   & 0.009546 \\\hline
-        4e-05 & 0.002568     & 5.369322   & 0.012127 \\\hline
-        3e-05 & 0.001925     & 7.136687   & 0.007845 \\\hline
-        2e-05 & 0.001283     & 10.679166  & 0.012126 \\\hline
-        1e-05 & 0.000641     & 21.325229  & 0.011661 \\\hline
-        1e-06 & 0.000064     & 212.824121 & 0.040967 \\\hline
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
-    \label{tab:rk2_mag_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.114422     & 0.028398 & 0.009294 \\
-    1.00E-02 & 0.019233     & 0.036245 & 0.002182 \\
-    1.00E-03 & 0.002141     & 0.147979 & 0.00125  \\
-    9.00E-04 & 0.001749     & 0.172161 & 0.00794  \\
-    8.00E-04 & 0.001516     & 0.184629 & 0.004359 \\
-    7.00E-04 & 0.00152      & 0.20445  & 0.001919 \\
-    6.00E-04 & 0.001049     & 0.234947 & 0.004416 \\
-    5.00E-04 & 0.000974     & 0.278938 & 0.010969 \\
-    4.00E-04 & 0.0009       & 0.336847 & 0.003028 \\
-    3.00E-04 & 0.000587     & 0.441771 & 0.005859 \\
-    2.00E-04 & 0.000433     & 0.652066 & 0.006637 \\
-    1.00E-04 & 0.0002       & 1.280059 & 0.016027 \\
-    9.00E-05 & 0.000145     & 1.41908  & 0.013122 \\
-    8.00E-05 & 0.000153     & 1.592492 & 0.011332 \\
-    7.00E-05 & 0.000162     & 1.806561 & 0.009931 \\
-    6.00E-05 & 0.000123     & 2.103571 & 0.011143 \\
-    5.00E-05 & 0.000084     & 2.515006 & 0.01393  \\
-    4.00E-05 & 0.000092     & 3.140471 & 0.014138 \\
-    3.00E-05 & 0.000053     & 4.158715 & 0.009474 \\
-    2.00E-05 & 0.000045     & 6.231734 & 0.015236 \\
-    1.00E-05 & 0.000022     & 12.39871 & 0.039575 \\
-    1.00E-06 & 0.000003     & 123.318  & 0.299559
-    \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:lf_statE_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.055355     & 0.031054 & 0.003281 \\
-        1.00E-02 & 0.009868     & 0.063656 & 0.000893 \\
-        1.00E-03 & 0.001141     & 0.435864 & 0.005332 \\
-        9.00E-04 & 0.001325     & 0.478216 & 0.00595  \\
-        8.00E-04 & 0.001112     & 0.533789 & 0.003897 \\
-        7.00E-04 & 0.000705     & 0.60586  & 0.005441 \\
-        6.00E-04 & 0.000687     & 0.703851 & 0.009447 \\
-        5.00E-04 & 0.000474     & 0.840173 & 0.00913  \\
-        4.00E-04 & 0.00046      & 1.039166 & 0.005874 \\
-        3.00E-04 & 0.000456     & 1.378822 & 0.007995 \\
-        2.00E-04 & 0.000207     & 2.045464 & 0.008499 \\
-        1.00E-04 & 0.000127     & 4.052472 & 0.014711 \\
-        9.00E-05 & 0.000091     & 4.500401 & 0.015404 \\
-        8.00E-05 & 0.000124     & 5.048922 & 0.014392 \\
-        7.00E-05 & 0.000062     & 5.773208 & 0.031443 \\
-        6.00E-05 & 0.000057     & 6.726501 & 0.020609 \\
-        5.00E-05 & 0.00006      & 8.045931 & 0.014246 \\
-        4.00E-05 & 0.000039     & 10.04809 & 0.012756 \\
-        3.00E-05 & 0.000045     & 13.39669 & 0.028057 \\
-        2.00E-05 & 0.000023     & 20.03889 & 0.006436 \\
-        1.00E-05 & 0.000016     & 40.0818  & 0.120627 \\
-        1.00E-06 & 0.000003     & 400.2421 & 0.554172
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:rk2_statE_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-    5.00E-02 & 0.986005     & 0.030314 & 0.009209 \\
-    1.00E-02 & 0.154314     & 0.036833 & 0.004068 \\
-    1.00E-03 & 0.01476      & 0.131783 & 0.002352 \\
-    9.00E-04 & 0.013618     & 0.150984 & 0.005618 \\
-    8.00E-04 & 0.011863     & 0.161336 & 0.003117 \\
-    7.00E-04 & 0.010109     & 0.179693 & 0.002658 \\
-    6.00E-04 & 0.009277     & 0.205356 & 0.002912 \\
-    5.00E-04 & 0.007527     & 0.242352 & 0.003093 \\
-    4.00E-04 & 0.006084     & 0.294269 & 0.001551 \\
-    3.00E-04 & 0.00449      & 0.383982 & 0.001711 \\
-    2.00E-04 & 0.002897     & 0.563762 & 0.004214 \\
-    1.00E-04 & 0.001458     & 1.101252 & 0.008064 \\
-    9.00E-05 & 0.001376     & 1.229321 & 0.0089   \\
-    8.00E-05 & 0.001232     & 1.381441 & 0.01057  \\
-    7.00E-05 & 0.001027     & 1.574994 & 0.011933 \\
-    6.00E-05 & 0.000853     & 1.833183 & 0.006065 \\
-    5.00E-05 & 0.00074      & 2.184948 & 0.013416 \\
-    4.00E-05 & 0.000596     & 2.72503  & 0.016356 \\
-    3.00E-05 & 0.000467     & 3.617576 & 0.017581 \\
-    2.00E-05 & 0.000308     & 5.394629 & 0.027885 \\
-    1.00E-05 & 0.00015      & 10.75182 & 0.03301  \\
-    1.00E-06 & 0.000017     & 106.9198 & 0.373175
-    \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:lf_statE90_table}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    dt(ns)       & $\Delta E_{avg}$(MeV) & $\mu T_{sim}$(s)    & $\sigma T_{sim}$(s) \\\hline
-        5.00E-02 & 0.587777     & 0.034741 & 0.012735 \\
-        1.00E-02 & 0.09943      & 0.059945 & 0.001318 \\
-        1.00E-03 & 0.009987     & 0.38199  & 0.005941 \\
-        9.00E-04 & 0.007946     & 0.417119 & 0.005683 \\
-        8.00E-04 & 0.007999     & 0.466052 & 0.006398 \\
-        7.00E-04 & 0.006732     & 0.525791 & 0.003782 \\
-        6.00E-04 & 0.005541     & 0.612876 & 0.007114 \\
-        5.00E-04 & 0.005022     & 0.732091 & 0.012129 \\
-        4.00E-04 & 0.004031     & 0.906845 & 0.012156 \\
-        3.00E-04 & 0.002779     & 1.199367 & 0.014536 \\
-        2.00E-04 & 0.001897     & 1.782653 & 0.016993 \\
-        1.00E-04 & 0.000895     & 3.52464  & 0.029778 \\
-        9.00E-05 & 0.000858     & 3.916115 & 0.041066 \\
-        8.00E-05 & 0.000731     & 4.409459 & 0.040828 \\
-        7.00E-05 & 0.00066      & 5.012686 & 0.042727 \\
-        6.00E-05 & 0.000561     & 5.851793 & 0.038488 \\
-        5.00E-05 & 0.000471     & 7.002315 & 0.046152 \\
-        4.00E-05 & 0.000363     & 8.747954 & 0.063936 \\
-        3.00E-05 & 0.000264     & 11.64305 & 0.091404 \\
-        2.00E-05 & 0.000184     & 17.44533 & 0.123198 \\
-        1.00E-05 & 0.000093     & 34.93332 & 0.391012 \\
-        1.00E-06 & 0.000011     & 348.494  & 3.237203
-    \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
-    \label{tab:rk2_statE90_table}
-\end{table}
-% START OF BIBLIOGRAPHY
+%%%%%%
 
 \begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
-
-    \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
-
-    \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
-
     \bibitem{cpu_instruction_speed}
     Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775. 
-
-    \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018
-
 \end{thebibliography}
 
-% END OF BIBLIOGRAPHY
-
 \end{document}

### 2023-08-17 subsections/tools/tools.tex
changes from Erkcan & Gokhan hocas

@@
 
-\section{Poisson Superfish}
+\section{Available Tools}
+
+\subsection{Poisson Superfish}
 Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
-for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments.
+for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments \cite{poi-sup}.
 It is commonly used in the field of accelerator physics to simulate and optimize the behavior of charged particle beams as they pass through various electromagnetic structures, such as cavities and magnets.
 
-\section{CST Studio Suite}
+\subsection{CST Studio Suite}
 CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.

### 2023-08-25 msthesis.tex
25/08/2023 update

@@
 \documentclass[a4paper,oneside,12pt]{report}
-\usepackage{styles/fbe_tez}
 \usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
 \usepackage{amsmath, amsthm} % Some extra symbols
+%\usepackage{subcaption}
+\usepackage{styles/fbe_tez}
 \usepackage[bottom]{footmisc}
@@
     \sym{E}{Energy}
+    \sym{W}{Energy}
     \sym{\textbf{$\vec{E}$}}{Electric field}
@@
    \sym{RF}{Radio Frequency}
+   \sym{POC}{Proof of Concept}
+   \sym{CPU}{Central Processing Unit}
    \sym{s}{Second}
@@
    \sym{V}{Volt}
+   \sym{W}{Watt}
 
@@
 MeV-level electron beams, both as is and as X-Ray sources, are especially useful for industrial and medical applications. 
-For example, high-energy beams (5–10 MeV) are used in medical accelerators and provide services such as medical device sterilization and food irradiation;
-with medium energy devices (400 keV–5 MeV) wires, cables and tires are improved, factory flue gases or wastewater can be treated.
+For instance,  high-energy beams (ranging from 5 to 10 MeV) find application in medical accelerators and in services such as sterilizing medical devices and irradiating food. 
+Meanwhile, medium-energy devices (ranging from 400 keV to 5 MeV) contribute to the improvement of wires, cables, and tires, and also play a role in treating factory flue gases and wastewater.
 Although most of the industrial electron accelerators operating at MeV-level are linear accelerators at the moment, due to their compact nature, circular accelerators have been gaining prominence.
@@
 Rose-pattle accelerator is a type of circular accelerator suitable for producing electron beams at MeV-level energy. 
-It that was developed in 1989 and was named \textit{Rhodotron} \cite{rhodo_pottier}. This name was trademarked by \textit{IBA Group} in the following years.
+It was developed in 1989 and was named \textit{Rhodotron} \cite{rhodo_pottier}. This name was trademarked by \textit{IBA Group} in the following years.
 
@@
 \end{eqnarray}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
+Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have:
 \begin{equation}
@@
 \end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}
+Therefore from \fromeqs{Frel}{Frel_parallel},
 \begin{eqnarray}
@@
 \subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
+Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality:
 \begin{equation}
@@
 
-For $ \mu = 0 $, we have the time component of the equation;
+For $ \mu = 0 $, we have the time component of the equation:
 \begin{eqnarray}
@@
 \end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components;
+This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components:
 \begin{equation*}
@@
 \end{equation*}
-Which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
+which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
 
@@
 The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality;
+It can create force in any direction with respect to velocity. Therefore, we have the following equality:
 \begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
@@
 \end{equation}
-Acceleration due to electric field can be simplified as;
+Acceleration due to electric field can be simplified as:
 \begin{eqnarray*}
@@
 \end{figure}
+
+\subsection{Acceleration Cavities} \label{sec:theory_cavities}
+Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
+These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
+
+RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
+They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
+The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
+The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
+The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
+
+To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
+The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
+These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
+
+In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
+By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
+This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
+This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
+Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
+    \caption{An RF cavity used in KAHVELab}
+\end{figure}
+
+\subsection{Bending Magnets}
+Bending magnets, also known as dipole magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
+They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
+
+According to the Lorentz Force Law (\fromsec{lorentz-force}), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
+vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
+
 \subsection{Key Concepts}
@@
 \end{equation}
-Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
+where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
 
@@
 at which the accelerator can transform the supplied RF power into acceleration.
-
-\subsection{Acceleration Cavities} \label{sec:theory_cavities}
-Radiofrequency (RF) cavities, also known as accelerating cavities or resonant cavities, are key components in particle accelerators. 
-These cavities generate strong electromagnetic fields at specific frequencies to accelerate charged particles through clever engineering.
-
-RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
-The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
-The RF cavity is designed to be resonant, meaning that it naturally amplifies the electric fields at its resonant frequency. 
-The resonant frequency is determined by the cavity's dimensions and the speed of light in the cavity material.
-
-To achieve efficient energy transfer to the particles, the RF cavity is driven by an external RF power source operating at the resonant frequency. 
-The power source supplies radiofrequency energy to the cavity, which causes the electric fields inside the cavity to oscillate at the desired frequency. 
-These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity.
-
-In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
-By carefully shaping the cavity and adjusting the electromagnetic fields, the particles can experience focusing effects as they pass through the cavity. 
-This helps to maintain a tight and controlled beam. To ensure efficient acceleration, it is essential to maintain phase stability. 
-This means that the particles should experience the strongest electric fields at the correct time during their passage through the cavity. 
-Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
-    \caption{An RF cavity used in KAHVELab}
-\end{figure}
-
-\subsection{Bending Magnets}
-Bending magnets, also known as dipole magnets, are fundamental components used in particle accelerators to control the trajectory of charged particles. 
-They utilize the Ampere's Law to exert a magnetic field that interacts with the charged particles in the accelerator.
-
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
-vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
+It is defined as
+\begin{equation} \label{eq:shunt}
+    Z_s = \frac{V_{acc}^2}{P_{diss}}
+\end{equation}
+where $V_{acc}$ is the accelerating potential in which the particle is subjected to, 
+$P_{diss}$ is the power dissipated on the cavity walls. 
+An example \textit{shunt impedance} calculation can be found in \fromsec{cavity_of_a_rhodotron}.
 
@@
 
-Electrons undergo four different stages during a single pass. 
+Electrons undergo four different stages inside the accelerator. 
 They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity.
@@
 Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
-
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
+Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest. (\fromfig{rhodo_cavity_field_dist})
+
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/cst/cavity_E_field_dist.png}
+        \caption*{$\vecthreeBF{E}$ field.}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{./figures/cst/cavity_B_field_dist.png}
+        \caption*{$\vecthreeBF{B}$ field.}
+    \end{subfigure}
+    \caption{$\vecthreeBF{E}$ and $\vecthreeBF{B}$ eigenmode field distributions inside a coaxial cavity.}
+    \label{fig:rhodo_cavity_field_dist}
+\end{figure}
+For a cavity defined by the volume between two coaxial cylinders of equal lengths ($h$) with radii of $R_1$ and $R_2$, where $R_1 < R_2$, located at the origin (\fromfig{int_curve}),
+first eigenmode solution of the $E$ and $B$ fields are \cite{rhodo_pottier}
+\begin{eqnarray}
+    E &=& \frac{E_0}{r} \cos(\frac{\pi z}{h}) \sin(\omega t + \phi) \\
+    B &=& \frac{B_0}{r} \sin(\frac{\pi z}{h}) \cos(\omega t + \phi)
+\end{eqnarray}
+where $\omega=2\pi f$, $f$ is the resonance frequency.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.6\textwidth]{./figures/illustrations/rhodo_integral_curve.pdf}
+    \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}}
+    \label{fig:int_curve}
+\end{figure}
+Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by the following equation:
+\begin{eqnarray} 
+    V_{acc} &=& 2 \int_{R_1}^{R_2} |E|^2 dr \\
+            &=& 2 E_0 \int_{R_1}^{R_2} \frac{dr}{r} \\
+            &=& 2 E_0 \ln(\frac{R_2}{R_1}) \label{eq:v_acc}
+\end{eqnarray}
+Dissipated power $P_{diss}$, on the other hand, can be calculated as follows \cite{rf}:
+\begin{eqnarray} 
+    P_{diss} &=& \frac{1}{2} \int \int \rho_s | H_{||} |^2 dA \nonumber \\
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta \label{eq:p_diss_C_curve}
+\end{eqnarray}
+where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
+Integral curve \textbf{C} is defined as the circumference of cylindrically symmetrical cross sectional area of the cavity (\fromfig{int_curve}).
+This curve can be seperated to its line components and total power dissipation of this curve, $P_C$ will be equal to sum of the power dissipated in these lines.
+Since $\vecthreeBF{B}$ is always parallel to the surface we can use $\vecthreeBF{B}$ directly:
+\begin{eqnarray}
+    P_{diss} &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (
+                   2\int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_1}
+                 + 2\int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_2} 
+                 + 2\int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}})d\theta \nonumber\\
+             %&=& \frac{\rho_s B_0^2 \cos^2(\omega t + \phi)}{2\mu_0^2} \int_0^{2\pi} 
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (2I_A + 2I_B + 2I_C)d\theta 
+                 = \frac{2\rho_s \pi}{\mu_0^2}(I_A + I_B + I_C)
+\end{eqnarray}
+\begin{eqnarray}
+    I_A = \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_1} &=& B_0^2 \frac{h}{4R_1} \\
+    I_B = \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_2} &=& B_0^2 \frac{h}{4R_2} \\
+    I_C = \int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}} &=& B_0^2 \ln(\frac{R_2}{R_1})
+\end{eqnarray}
+inserting $H_0=B_0/\mu_0$, finally we have the dissipated power:
+\begin{equation} \label{eq:p_diss}
+    P_{diss} = \rho_s \pi H_o ( \frac{h}{2R_1} + \frac{h}{2R_2} + 2\ln(\frac{R_2}{R_1}) )
+\end{equation}
+Therefore, from \fromeq{shunt}, using \fromeqs{v_acc}{p_diss} also $E_0/H_0 = Z_0 \approx 120 \pi$:
+\begin{eqnarray}
+    Z_s &=& \frac{4E_0^2}{H_0^2 \pi \rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{2R_1} + \frac{h}{2R_2} + 2 \ln(\frac{R_2}{R_1}))} \\
+        &=& \frac{8 \pi 60^2}{\rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{4}(\frac{1}{R_1} + \frac{1}{R_2}) + \ln(\frac{R_2}{R_1}))}
+\end{eqnarray}
+where, time dependencies have been removed from $\vecthreeBF{E}$ and $\vecthreeBF{B}$ 
+and the maximum values for $V_{acc}$ and $P_{diss}$ have been used. 
+However, particles do not interact with constant $\vecthreeBF{E}$ field during acceleration. 
+Therefore, a more useful parameter called \textit{effective shunt impedance} can be defined:
+\begin{equation}
+    Z_{se} = Z_s T^2
+\end{equation}
+where $T$ is the \textit{transit time factor}, a correctional coefficent that contain the changing field effects during acceleration.
+For a relativistic electron crossing the axis at time 0, $T$ can be found by \cite{rhodo_pottier}:
+\begin{eqnarray}
+    T &=& \frac{S_i(\frac{2 \pi R_2}{\lambda}) - S_i(\frac{2 \pi R_1}{\lambda})}{\ln(\frac{R_2}{R_1})} \\
+    S_i(\theta) &=& \int_0^{\theta} \frac{\sin(x)}{x} dx
+\end{eqnarray}
+for a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$:
+\begin{equation}
+    T(\phi) = T \cos(\phi)
+\end{equation} 
+Putting all these calculations together, energy gain of a relativistic electron, passing the origin at $\phi / \omega$ as calculated by \textit{J. Pottier} is \cite{rhodo_pottier}
+\begin{eqnarray}
+    \Delta E &=& q V_{acc}^{ef} \\
+    \Delta E &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)
+\end{eqnarray}
+where $ V_{acc}^{ef} = V_{acc} T(\phi)$ is the effective accelerating potential.
+If $\Delta E$ is taken in \textit{MeV}, $Z_{se}$ in $M\Omega$ and $P_{diss}$ in \textit{MW}, this equality becomes
+\begin{equation} \label{eq:W_gain_each_pass_pottier}
+    \Delta E = Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi) \quad MeV
+\end{equation}
+With the expectation that the electrons will accelerate to speeds $\approx c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
 This constraint helps with  phase stability and synchronization of the beam.
@@
 Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
-
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} \cos \phi  
-\end{equation}
-where $P$ is the dissipated power, $\phi$ is the phase lag, typically taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
+$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$. Typically, phase lag $\phi$ is taken as $15^\circ$ \cite{rhodo_pottier}.
+
+Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $\Delta E \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
 \begin{figure}[H]
@@
 \end{figure}
-Total energy gain after $n$ passes, $W$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
+Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m}.
 \begin{equation}
     \label{eq:W_total_gain_pottier}
-    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
+    \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
 \end{equation}
@@
 CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
-It's widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
+It is widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
 The software provides a comprehensive set of tools for simulating and analyzing the behavior of electromagnetic fields and their interactions with different materials, structures and charged particles.
@@
 like the Large Hadron Collider (LHC) \cite{root}. It has become an essential tool in particle physics research, 
-and it's used by physicists around the world to analyze and interpret data.
+and it is used by physicists around the world to analyze and interpret data.
 
@@
 The first and the most important design parameter for a cavity is the operating RF frequency.
-After an operating RF frequency is set and the desired $R1/R2$ relation \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
+After an operating RF frequency is set and the desired $R1/R2$ relation in \fromfig{pottier_table1} is selected, design parameters of acceleration plane of the cavity is fully determined.
 
@@
 \end{eqnarray*}
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
+When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
 \begin{eqnarray} \label{eq:f_lf_rk_mag_1}
@@
     \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
+    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ ns}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns}
     \label{fig:lf_rk2_perp_stat_E_comparison}
 \end{figure}
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
+Taking the $dt=10^{-5}$ ns for the reference point as before, the relative performance can be calculated.
 \begin{eqnarray*}
@@
 It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame after a simulation run has been completed can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
+Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_1.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_5.png}
     \caption{Render frame of \textit{GUI}.}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Edist.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Edist_2.png}
     \caption{Analyze frame of \textit{GUI} E distribution.}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_1.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_3.png}
     \caption{Analyze frame of \textit{GUI} E(t).}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_muE.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_muE_3.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sE.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sE_3.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
@@
 After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
-Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunuties.
+Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunities.
 
@@
 \chapter{Supporting Figures} \label{appendix:supp}
-
 \begin{figure}
     \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
+    \includegraphics[angle=270,origin=c, width=.9\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
     \caption{Technical drawing of upper part of the cavity. \cite{sinan}}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulate_frame.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulation_frame.png}
     \caption{Simulate frame of \textit{GUI}.}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_2.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_6.png}
     \caption{Render frame of \textit{GUI}.}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sR.png}
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sR_3.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
@@
 
+    \bibitem{rf}
+    E. Jensen,
+    \emph{RF Cavity Design},
+    CERN Yellow Report CERN-2014-009, pp.405-429
+
 \end{thebibliography}

### 2023-08-25 subsections/simulation/gui/gui.tex
25/08/2023 update

@@
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_1.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
     \caption{Render frame of \textit{GUI}.}
@@
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
     \caption{Analyze frame of \textit{GUI} E distribution.}
@@
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_1.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
     \caption{Analyze frame of \textit{GUI} E(t).}
@@
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
@@
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE.png}
+    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
     \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}

### 2023-08-25 subsections/theory/common/common_start_theory.tex
25/08/2023 update

@@
 Rose-pattle accelerator is a type of circular accelerator suitable for producing electron beams at MeV-level energy. 
-It that was developed in 1989 and was named \textit{Rhodotron} \cite{rhodo_pottier}. This name was trademarked by \textit{IBA Group} in the following years.
+It was developed in 1989 and was named \textit{Rhodotron} \cite{rhodo_pottier}. This name was trademarked by \textit{IBA Group} in the following years.

### 2023-08-25 subsections/theory/rhodotron/rhodotron.tex
25/08/2023 update

@@
 \newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
+
+\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
 
@@
 \end{figure}
-\subsection{Key Concepts}
-
-\subsubsection{Resonance Frequency}
-Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
-It is determined by the physical dimensions and the speed of light in the cavity's medium. 
-In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
-\begin{equation}
-    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
-    \label{eq:f_r_rec}
-\end{equation}
-Where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
-
-\subsubsection{Bunch}
-Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
-
-\subsubsection{Phase Stability}
-Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
-It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
-which is crucial for achieving efficient particle acceleration. 
-Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
-ensuring that they receive the correct energy boosts and interact predictably with detectors. 
-Deviations in phase stability can lead to particle loss and decreased beam quality.
-
-\subsubsection{Phase Lag}
-Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
-It describes the difference in phase angles within their respective cycles, between two signals.
-
-\subsubsection{Shunt Impedance}
-The shunt impedance of an RF accelerator is a measure of the efficiency 
-at which the accelerator can transform the supplied RF power into acceleration.
 
@@
 Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-% TODO : ADD RF CAVITY PICTURE HERE
 \begin{figure}[H]
@@
 
-According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
+According to the Lorentz Force Law (\fromsec{lorentz-force}), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
 vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
+
+\subsection{Key Concepts}
+
+\subsubsection{Resonance Frequency}
+Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
+It is determined by the physical dimensions and the speed of light in the cavity's medium. 
+In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
+\begin{equation}
+    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
+    \label{eq:f_r_rec}
+\end{equation}
+where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
+
+\subsubsection{Bunch}
+Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
+
+\subsubsection{Phase Stability}
+Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
+It ensures that the phases of various electromagnetic fields or particles remain synchronized, 
+which is crucial for achieving efficient particle acceleration. 
+Maintaining phase stability is essential to prevent particles from becoming out of phase as they travel through accelerator structures, 
+ensuring that they receive the correct energy boosts and interact predictably with detectors. 
+Deviations in phase stability can lead to particle loss and decreased beam quality.
+
+\subsubsection{Phase Lag}
+Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
+It describes the difference in phase angles within their respective cycles, between two signals.
+
+\subsubsection{Shunt Impedance}
+The shunt impedance of an RF accelerator is a measure of the efficiency 
+at which the accelerator can transform the supplied RF power into acceleration.
+It is defined as
+\begin{equation} \label{eq:shunt}
+    Z_s = \frac{V_{acc}^2}{P_{diss}}
+\end{equation}
+where $V_{acc}$ is the accelerating potential in which the particle is subjected to, 
+$P_{diss}$ is the power dissipated on the cavity walls. 
+An example \textit{shunt impedance} calculation can be found in \fromsec{cavity_of_a_rhodotron}.
 
@@
 Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
-% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????
+Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest. (\fromfig{rhodo_cavity_field_dist})
 
-With the expectation that the electrons will accelerate to speeds $>=0.9 c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
+\begin{figure}[H]
+    \captionsetup[subfigure]{justification=centering}
+    \captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/cst/cavity_E_field_dist.png}
+        \caption*{$\vecthreeBF{E}$ field.}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{../../../figures/cst/cavity_B_field_dist.png}
+        \caption*{$\vecthreeBF{B}$ field.}
+    \end{subfigure}
+    \caption{$\vecthreeBF{E}$ and $\vecthreeBF{B}$ eigenmode field distributions inside a coaxial cavity.}
+    \label{fig:rhodo_cavity_field_dist}
+\end{figure}
+For a cavity defined by the volume between two coaxial cylinders of equal lengths ($h$) with radii of $R_1$ and $R_2$, where $R_1 < R_2$, located at the origin (\fromfig{int_curve}),
+first eigenmode solution of the $E$ and $B$ fields are \cite{rhodo_pottier}
+\begin{eqnarray}
+    E &=& \frac{E_0}{r} \cos(\frac{\pi z}{h}) \sin(\omega t + \phi) \\
+    B &=& \frac{B_0}{r} \sin(\frac{\pi z}{h}) \cos(\omega t + \phi)
+\end{eqnarray}
+where $\omega=2\pi f$, $f$ is the resonance frequency.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.6\textwidth]{../../../figures/illustrations/rhodo_integral_curve.pdf}
+    \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}}
+    \label{fig:int_curve}
+\end{figure}
+Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by the following equation:
+\begin{eqnarray} 
+    V_{acc} &=& 2 \int_{R_1}^{R_2} |E|^2 dr \\
+            &=& 2 E_0 \int_{R_1}^{R_2} \frac{dr}{r} \\
+            &=& 2 E_0 \ln(\frac{R_2}{R_1}) \label{eq:v_acc}
+\end{eqnarray}
+Dissipated power $P_{diss}$, on the other hand, can be calculated as follows \cite{rf}:
+\begin{eqnarray} 
+    P_{diss} &=& \frac{1}{2} \int \int \rho_s | H_{||} |^2 dA \nonumber \\
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta \label{eq:p_diss_C_curve}
+\end{eqnarray}
+where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
+Integral curve \textbf{C} is defined as the circumference of cylindrically symmetrical cross sectional area of the cavity (\fromfig{int_curve}).
+This curve can be seperated to its line components and total power dissipation of this curve, $P_C$ will be equal to sum of the power dissipated in these lines.
+Since $\vecthreeBF{B}$ is always parallel to the surface we can use $\vecthreeBF{B}$ directly:
+\begin{eqnarray}
+    P_{diss} &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (
+                   2\int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_1}
+                 + 2\int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_2} 
+                 + 2\int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}})d\theta \nonumber\\
+             %&=& \frac{\rho_s B_0^2 \cos^2(\omega t + \phi)}{2\mu_0^2} \int_0^{2\pi} 
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (2I_A + 2I_B + 2I_C)d\theta 
+                 = \frac{2\rho_s \pi}{\mu_0^2}(I_A + I_B + I_C)
+\end{eqnarray}
+\begin{eqnarray}
+    I_A = \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_1} &=& B_0^2 \frac{h}{4R_1} \\
+    I_B = \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_2} &=& B_0^2 \frac{h}{4R_2} \\
+    I_C = \int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}} &=& B_0^2 \ln(\frac{R_2}{R_1})
+\end{eqnarray}
+inserting $H_0=B_0/\mu_0$, finally we have the dissipated power:
+\begin{equation} \label{eq:p_diss}
+    P_{diss} = \rho_s \pi H_o ( \frac{h}{2R_1} + \frac{h}{2R_2} + 2\ln(\frac{R_2}{R_1}) )
+\end{equation}
+Therefore, from \fromeq{shunt}, using \fromeqs{v_acc}{p_diss} also $E_0/H_0 = Z_0 \approx 120 \pi$:
+\begin{eqnarray}
+    Z_s &=& \frac{4E_0^2}{H_0^2 \pi \rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{2R_1} + \frac{h}{2R_2} + 2 \ln(\frac{R_2}{R_1}))} \\
+        &=& \frac{8 \pi 60^2}{\rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{4}(\frac{1}{R_1} + \frac{1}{R_2}) + \ln(\frac{R_2}{R_1}))}
+\end{eqnarray}
+where, time dependencies have been removed from $\vecthreeBF{E}$ and $\vecthreeBF{B}$ 
+and the maximum values for $V_{acc}$ and $P_{diss}$ have been used. 
+However, particles do not interact with constant $\vecthreeBF{E}$ field during acceleration. 
+Therefore, a more useful parameter called \textit{effective shunt impedance} can be defined:
+\begin{equation}
+    Z_{se} = Z_s T^2
+\end{equation}
+where $T$ is the \textit{transit time factor}, a correctional coefficent that contain the changing field effects during acceleration.
+For a relativistic electron crossing the axis at time 0, $T$ can be found by \cite{rhodo_pottier}:
+\begin{eqnarray}
+    T &=& \frac{S_i(\frac{2 \pi R_2}{\lambda}) - S_i(\frac{2 \pi R_1}{\lambda})}{\ln(\frac{R_2}{R_1})} \\
+    S_i(\theta) &=& \int_0^{\theta} \frac{\sin(x)}{x} dx
+\end{eqnarray}
+for a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$:
+\begin{equation}
+    T(\phi) = T \cos(\phi)
+\end{equation} 
+Putting all these calculations together, energy gain of a relativistic electron, passing the origin at $\phi / \omega$ as calculated by \textit{J. Pottier} is \cite{rhodo_pottier}
+\begin{eqnarray}
+    \Delta E &=& q V_{acc}^{ef} \\
+    \Delta E &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)
+\end{eqnarray}
+where $ V_{acc}^{ef} = V_{acc} T(\phi)$ is the effective accelerating potential.
+If $\Delta E$ is taken in \textit{MeV}, $Z_{se}$ in $M\Omega$ and $P_{diss}$ in \textit{MW}, this equality becomes
+\begin{equation} \label{eq:W_gain_each_pass_pottier}
+    \Delta E = Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi) \quad MeV
+\end{equation}
+With the expectation that the electrons will accelerate to speeds $\approx c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
 This constraint helps with  phase stability and synchronization of the beam.
@@
 Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
-$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.
+$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$. Typically, phase lag $\phi$ is taken as $15^\circ$ \cite{rhodo_pottier}.
 
-Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
-\begin{equation}
-    \label{eq:W_gain_each_pass_pottier}
-    W_1 = Z_{sp}^{1/2} P^{1/2} \cos \phi  
-\end{equation}
-where $P$ is the dissipated power, $\phi$ is the phase lag, typically taken as $15^\circ$ \cite{rhodo_pottier}.
-
-Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
+Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $\Delta E \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
 \begin{figure}[H]

### 2023-08-29 msthesis.tex
savunma oncesi son push

@@
     \sym{E}{Energy}
-    \sym{W}{Energy}
+    \sym{$e^-$}{Electron}
+    \sym{$e^- - \vec{E}$}{Electron Electric Field Interaction}
+    \sym{$e^- - \vec{B}$}{Electron Magnetic Field Interaction}
+    \sym{$e^- - EM$}{Electron Electro-Magnetic Field Interaction}
     \sym{\textbf{$\vec{E}$}}{Electric field}
@@
    \sym{RF}{Radio Frequency}
+   \sym{RMS}{Root Mean Square}
    \sym{POC}{Proof of Concept}
@@
       \centering
-      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z.png}
+      \includegraphics[width=0.97\linewidth]{./figures/superfish/superfish107_z_highlighted.png}
       \caption{107.5 MHz unmodified}
@@
       \centering
-      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z}
+      \includegraphics[width=0.99\linewidth]{./figures/superfish/superfish180_z_highlighted.png}
       \caption{180 MHz unmodified}
@@
       \centering
-      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z.png}
+      \includegraphics[width=0.95\linewidth]{./figures/superfish/superfish107mod_z_highlighted.png}
       \caption{107.5 MHz truncated}
@@
       \centering
-      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z.png}
+      \includegraphics[width=\linewidth]{./figures/superfish/superfish180mod_z_highlighted.png}
       \caption{180 MHz truncated}
@@
     \item $4.5$in EIA RF flange for RF input
-    \item ISO100-KF vacuum connector flanges for vacuum pumps
+    \item ISO-100KF vacuum connector flanges for vacuum pumps
     \item ISO-63 KF flange for probe insertion
-    \item KF40 flanges for beam line vacuum gauges
+    \item KF-40 flanges for beam line vacuum gauges
 \end{itemize}
@@
       \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
+      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_final_cropped_5.jpeg}
+      \caption{Beam enter \& exit flanges.}
     \end{subfigure}%
@@
       \centering
-      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
-    \end{subfigure}
-    \caption{Assembled cavity as the current stage.}
+      \includegraphics[width=.96\linewidth]{./figures/manif/assembled/rhodo_final_4_cropped.jpeg}
+      \caption{RF input \& probe flanges.}
+    \end{subfigure}
+    \caption{Flanges on the assembled cavity.}
+    \label{fig:manif_assembled_flanges}
+\end{figure}
+
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.9\linewidth]{./figures/manif/assembled/rhodo_final_cropped.jpeg}
+    \caption{Current stage of the cavity.}
     \label{fig:manif_assembled}
@@
 Regarding the cavity manufacturing process, it is in the concluding stages.
-The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
-After the heat treatment operation, 
-the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
-
-As far as the magnets concerned, it was decided to be kept on hold in the early stages of the project, 
-due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
+The sheet bars and the flanges of the upper and the lower parts have been welded, the cavity is getting ready for heat treatment.
+After the heat treatment operation, the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
+
+As far as the magnets were concerned, it was decided to be kept on hold in the early stages of the project, 
+due to the disagreement on the energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
 and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
@@
 \textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
-several improvements and new feature implementations are underway in the mean time. 
+Several improvements and new feature implementations are underway in the meantime. 
 They include the following;
@@
 before the cavity production is completed and the performance is compared with the predictions of the tool;
-however, the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
+However, the capabilities it presents, coupled with the analogous results obtained from other extensively utilized simulation tools, 
 lead to the inference that it holds promise.

### 2023-08-29 subsections/design/cavity/cavity.tex
savunma oncesi son push

@@
       \centering
-      \includegraphics[width=0.97\linewidth]{../../../figures/superfish/superfish107_z.png}
+      \includegraphics[width=0.97\linewidth]{../../../figures/superfish/superfish107_z_highlighted.png}
       \caption{107.5 MHz unmodified}
@@
       \centering
-      \includegraphics[width=0.99\linewidth]{../../../figures/superfish/superfish180_z}
+      \includegraphics[width=0.99\linewidth]{../../../figures/superfish/superfish180_z_highlighted.png}
       \caption{180 MHz unmodified}
@@
       \centering
-      \includegraphics[width=0.95\linewidth]{../../../figures/superfish/superfish107mod_z.png}
+      \includegraphics[width=0.95\linewidth]{../../../figures/superfish/superfish107mod_z_highlighted.png}
       \caption{107.5 MHz truncated}
@@
       \centering
-      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180mod_z.png}
+      \includegraphics[width=\linewidth]{../../../figures/superfish/superfish180mod_z_highlighted.png}
       \caption{180 MHz truncated}

### 2023-08-29 subsections/design/magnet/magnet.tex
savunma oncesi son push

@@
 \end{figure}
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for syncronizing them with the RF field in the cavity. 
+In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for synchronizing them with the RF field in the cavity. 
 This syncronization, also called phase stability, is the fundamental constraint of magnet design. 

### 2023-08-29 subsections/future/future_work.tex
savunma oncesi son push

@@
 Regarding the cavity manufacturing process, it is in the concluding stages.
-The sheet bars and the flanges of the upper and the lower parts have been produced and are being welded and getting ready for heat treatment.
-After the heat treatment operation, 
-the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
+The sheet bars and the flanges of the upper and the lower parts have been welded, the cavity is getting ready for heat treatment.
+After the heat treatment operation, the supporting toroidal sheets will be removed and the inside surface will be polished before cyanide copper plating.
 
-As far as the magnets concerned, it was decided to be kept on hold in the early stages of the project, 
-due to the disagreement on energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
+As far as the magnets were concerned, it was decided to be kept on hold in the early stages of the project, 
+due to the disagreement on the energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
 and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 

### 2023-08-29 subsections/production/manifacturing/mani.tex
başlık eklendi
savunma oncesi son push

@@
     \item $4.5$in EIA RF flange for RF input
-    \item ISO100-KF vacuum connector flanges for vacuum pumps
+    \item ISO-100KF vacuum connector flanges for vacuum pumps
     \item ISO-63 KF flange for probe insertion
-    \item KF40 flanges for beam line vacuum gauges
+    \item KF-40 flanges for beam line vacuum gauges
 \end{itemize}
-
 After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
@@
       \centering
-      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_assembled_2_cropped.jpeg}
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped_5.jpeg}
+      \caption{Beam enter \& exit flanges.}
     \end{subfigure}%
@@
       \centering
-      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_assembled_1_cropped.jpeg}
+      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_final_4_cropped.jpeg}
+      \caption{RF input \& probe flanges.}
     \end{subfigure}
-    \caption{Assembled cavity as the current stage.}
+    \caption{Flanges on the assembled cavity.}
+    \label{fig:manif_assembled_flanges}
+\end{figure}
+
+\begin{figure}
+    \captionsetup{justification=centering}
+    \centering
+    \includegraphics[width=.9\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped.jpeg}
+    \caption{Current stage of the cavity.}
     \label{fig:manif_assembled}

### 2023-09-18 msthesis.tex
changes after def

@@
 \newcommand{\parDerivS}[2]{\frac{\partial^2 #1}{\partial #2^2}}
+\newcommand{\deriv}[2]{\frac{d #1}{d #2}}
 \newcommand{\derivS}[2]{\frac{d^2 #1}{d#2^2}}
@@
 
-\newcommand{\fromeq}[1]{\textit{equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{equations \ref{eq:#1} and \ref{eq:#2}}}
-\newcommand{\fromeqsth}[3]{\textit{equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
-
-\newcommand{\fromfig}[1]{\textit{figure \ref{fig:#1}}}
-\newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
-\newcommand{\fromfigf}[4]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
-\newcommand{\fromfigsix}[6]{\textit{figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
-
-\newcommand{\fromch}[1]{\textit{chapter \ref{ch:#1}}}
-
-\newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
-\newcommand{\fromsecs}[2]{\textit{sections \ref{sec:#1} and \ref{sec:#2}}}
+\newcommand{\fromeq}[1]{\textit{Equation \ref{eq:#1}}}
+\newcommand{\fromeqs}[2]{\textit{Equations \ref{eq:#1} and \ref{eq:#2}}}
+\newcommand{\fromeqsth}[3]{\textit{Equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
+\newcommand{\fromeqsf}[4]{\textit{Equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
+
+\newcommand{\fromfig}[1]{\textit{Figure \ref{fig:#1}}}
+\newcommand{\fromfigs}[2]{\textit{Figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromfigf}[4]{\textit{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
+\newcommand{\fromfigsix}[6]{\textit{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
+
+\newcommand{\fromch}[1]{\textit{Chapter \ref{ch:#1}}}
+
+\newcommand{\fromsec}[1]{\textit{Section \ref{sec:#1}}}
+\newcommand{\fromsecs}[2]{\textit{Sections \ref{sec:#1} and \ref{sec:#2}}}
 
@@
 \subsection{Relation between momentum and acceleration}
-In classical mechanics, Newton's second law defines force, $\vecthreeBF{F}$, and states 
+In classical mechanics, Newton's second law defines force, $\vecthreeBF{F}$, and relation
 \begin{equation} \label{eq:newton_second_law}
-    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
+    \vecthreeBF{F} = \frac{d \vecthreeBF{p}}{d t} = m \frac{d \vecthreeBF{v}}{d t} = m \vecthreeBF{a} ,
 \end{equation}
 where $\vecthreeBF{p}$ is the momentum, $m\vecthreeBF{v}$ of the particle. 
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor:
+In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where 
 \begin{equation}
-    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = = \frac{1}{\sqrt{1-\beta^2}}
+    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
             = \frac{1}{\sqrt{1- (\dotProd{v}{v})/ c^2}} =  \frac{1}{\sqrt{1- \dotProd{\beta}{\beta}}}
 \end{equation}
-Considering these two statements, we can find the relation between momentum and acceleration as follows:
+is the Lorentz Factor.
+
+Considering these two statements, we can find the relation between momentum and acceleration as 
 \begin{eqnarray}
-    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
-    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
-    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
+    \deriv{\vecthree{p}}{t} &=& m_0 \deriv{(\gamma \vecthree{v})}{t} = m_0 \{  \deriv{\gamma}{t}\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}  \} \\
+    \deriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\deriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
+    \deriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}  \} .
 \end{eqnarray}
-thus,
+Therefore force can be written as
 \begin{equation} \label{eq:Frel}
-    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
+    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \} .
 \end{equation}
-It is clear that acceleration is not necessarily parallel to the force anymore.
-
-To start separating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$.
+It is clear that acceleration is not necessarily parallel to the force. 
+To start separating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$ as
 \begin{equation} \label{eq:a_F_parallels}
@@
     \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
+        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta \: ,
     \end{aligned}
 \end{equation}
+where 
 \begin{eqnarray}
     \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
-                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
+                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} .
 \end{eqnarray}
-Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have:
-\begin{equation}
-    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
-\end{equation}
-inserting this into \fromeq{a_F_parallels},
+$\gamma^2 \beta^2 + 1 = \gamma^2 $ and \fromeq{a_F_parallels} can be used to achieve
 \begin{eqnarray}
+    \dotProd{\textbf{F}}{\beta} &=& m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} ) \nonumber \\
     \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
                         &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
-                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
+                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} . \label{eq:Frel_parallel}
 \end{eqnarray}
@@
                     &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
+                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp} .
 \end{eqnarray}
-We finally have two separate equations which are in similar form with \fromeq{newton_second_law}.
+We finally have two separate equations which are in similar form with \fromeq{newton_second_law},
 \begin{equation} \label{eq:Frel_para_and_perp}
@@
     \begin{aligned}
-        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
+        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} .
     \end{aligned}
@@
 \subsection{Lorentz Force} \label{sec:lorentz-force}
-Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
+Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by 
 \begin{equation} \label{eq:lf}
-    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
+    \frac{d \vecthree{p}}{d t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B}) , 
 \end{equation}
@@
 \subsection{Relativistic Lorentz Force}
-Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality:
+Similar to non-relativistic version, relativistic Lorentz Force is given by the 4-vector equality
 \begin{equation}
-    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
+    \frac{d p^{\mu}}{d \tau} = q F^{\mu \nu} u_{\nu} ,
 \end{equation}
-where $ \partial \tau = \partial t / \gamma $ and greek letters are Lorentz indices,
-\begin{equation}
+where $ d \tau = d t / \gamma $ and greek letters are Lorentz indices
+\begin{equation*}
     \begin{aligned}
@@
         \end{bmatrix} 
-    \end{aligned}
-\end{equation}
+    \end{aligned} ,
+\end{equation*}
 where $W$ is the energy of the particle and $\gamma$ is the Lorentz factor mentioned in the previous section.
 
-For $ \mu = 0 $, we have the time component of the equation:
+For $ \mu = 0 $, we have the time component of the equation
 \begin{eqnarray}
-    \frac{\gamma}{c}\frac{\partial W}{\partial t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot \partial \vecthree{r}}{\partial t} \\
-    \frac{\partial W}{\partial t} &=& q \frac{\vecthree{E}\cdot \partial \vecthree{r}} {\partial t}
+    \frac{\gamma}{c}\frac{d W}{d t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot d \vecthree{r}}{d t} \\
+    \frac{d W}{d t} &=& q \frac{\vecthree{E}\cdot d \vecthree{r}} {d t} .
 \end{eqnarray}
-This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components:
+This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components
 \begin{equation*}
-    \frac{\partial \vecthree{p}}{\partial \tau} = \gamma \frac{\partial \vecthree{p}}{\partial t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B})
+    \frac{d \vecthree{p}}{d \tau} = \gamma \frac{d \vecthree{p}}{d t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B}) ,
 \end{equation*}
@@
 Due to the nature of the cross product, Lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
-Therefore the acceleration of the magnetic field is straightforward
+Therefore the acceleration of the magnetic field is straightforward,
+\vspace{-10pt}
 \begin{equation*}
-    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
+    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B} .
 \end{equation*}
+\vspace{-10pt}
 The same thing cannot be said about electric field however. 
-It can create force in any direction with respect to velocity. Therefore, we have the following equality:
+It can create force in any direction with respect to velocity. Therefore, we have the equality
 \begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
@@
     \begin{aligned}
-        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
+        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \} .
     \end{aligned}    
 \end{equation}
-Acceleration due to electric field can be simplified as:
+
+Acceleration due to electric field can be simplified as
+\vspace{-10pt}
 \begin{eqnarray*}
@@
                                 &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
+                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} .
 \end{eqnarray*}
+\vspace{-10pt}
 Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
@@
     \begin{aligned}
-        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
+        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} ) ,
     \end{aligned}
@@
 These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity. 
+\newline
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
+    \caption{An RF cavity used in KAHVELab}
+\end{figure}
 
@@
 Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
-    \caption{An RF cavity used in KAHVELab}
-\end{figure}
 
@@
 It is determined by the physical dimensions and the speed of light in the cavity's medium. 
-In a rectangular cavity for example, the resonance frequency can be calculated from \fromeq{f_r_rec}.
+In a rectangular cavity for example, the resonance frequency can be calculated by
 \begin{equation}
@@
 \end{description}
+
+\begin{itemize}
+    \item \textit{First Acceleration:} Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+(\fromfig{rhod_cycle_1})
+    \item \textit{Inner Shielding:} Inner shielding While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
+(\fromfig{rhod_cycle_2})
+    \item \textit{Second Acceleration:} Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+(\fromfig{rhod_cycle_3})
+    \item \textit{Recirculating Magnets:} After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+(\fromfig{rhod_cycle_4})
+\end{itemize}
 
@@
 \begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
+    \deriv{y}{x} = f(x, y)
 \end{equation}
@@
     \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
+        E_{Pottier} &=& 0.593 MeV \nonumber\\
+        E_{CST} &=& 0.521 MeV  \label{eq:poc_E_results}\\
+        E_{POC} &=& 0.532 MeV \nonumber
     \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+    \caption*{$P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
+\end{figure}
+As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced similar results, $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
+
+However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
+This inconsistency between $E_{Pottier}$ and $E_{CST}$, $\Delta E_{(Pottier-CST)}/E_{CST} \approx 14\%$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
 Since using a single software would have made the process error prone.
@@
     \centering
+    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
     \begin{tabular}{|l|l|l|l|}
@@
     \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
     \label{tab:lf_statE90_table}

### 2023-09-18 subsections/simulation/poc/poc.tex
changes after def

@@
     \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
+        E_{Pottier} &=& 0.593 MeV \nonumber\\
+        E_{CST} &=& 0.521 MeV  \label{eq:poc_E_results}\\
+        E_{POC} &=& 0.532 MeV \nonumber
     \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
+    \caption*{$P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
 \end{figure}
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced similar results, $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
+
+However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
+This inconsistency between $E_{Pottier}$ and $E_{CST}$, $\Delta E_{(Pottier-CST)}/E_{CST} \approx 14\%$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
 Since using a single software would have made the process error prone.

### 2023-09-18 subsections/theory/rhodotron/rhodotron.tex
changes after def

@@
 These oscillating fields then transfer energy to the passing particles, increasing their kinetic energy by pushing and pulling on the charged particles as they pass through the cavity. 
+\newline
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.75\textwidth]{../../../figures/pill_box.jpeg}
+    \caption{An RF cavity used in KAHVELab}
+\end{figure}
 
@@
 Precise timing and synchronization of the RF power source with the particle beam are crucial to achieve phase stability and maximize energy transfer.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.75\textwidth]{../../../figures/pill_box.jpeg}
-    \caption{An RF cavity used in KAHVELab}
-\end{figure}
 
@@
 They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity. 
+This stages are explained further below.
 
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+%\begin{description}
+%    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
 (\fromfig{rhod_cycle_1})
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed. (\fromfig{rhod_cycle_2})
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+%    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed. (\fromfig{rhod_cycle_2})
+%    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
 (\fromfig{rhod_cycle_3})
-    \item[Recirculating Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+%    \item[Recirculating Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
 (\fromfig{rhod_cycle_4})
-\end{description}
+%\end{description}
+
+\begin{itemize}
+    \item \textit{First Acceleration:} Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+(\fromfig{rhod_cycle_1})
+    \item \textit{Inner Shielding:} Inner shielding While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
+(\fromfig{rhod_cycle_2})
+    \item \textit{Second Acceleration:} Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+(\fromfig{rhod_cycle_3})
+    \item \textit{Recirculating Magnets:} After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+(\fromfig{rhod_cycle_4})
+\end{itemize}
 

### 2023-09-18 msthesis.tex
push for sina1

@@
 \usepackage{notoccite}
-\usepackage{subcaption}
+%\usepackage{subcaption}
+\usepackage{subfigure}
+%\usepackage{caption}
 \usepackage{tabu}
@@
 \newcommand{\fromfigs}[2]{\textit{Figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromfigth}[3]{\textit{figures \ref{fig:#1}, \ref{fig:#2} and \ref{fig:#3}}}
 \newcommand{\fromfigf}[4]{\textit{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
@@
 
+\newpage
 \section{Accelerating Charged Particles}
@@
 In classical mechanics, Newton's second law defines force, $\vecthreeBF{F}$, and relation
+\vspace{-10pt}
 \begin{equation} \label{eq:newton_second_law}
     \vecthreeBF{F} = \frac{d \vecthreeBF{p}}{d t} = m \frac{d \vecthreeBF{v}}{d t} = m \vecthreeBF{a}   ,
+    \vspace{-10pt}
 \end{equation}
 where $\vecthreeBF{p}$ is the momentum, $m\vecthreeBF{v}$ of the particle.
-In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where 
+
+In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $, where 
+\vspace{-10pt}
 \begin{equation}
@@
             = \frac{1}{\sqrt{1- (\dotProd{v}{v})/ c^2}} =  \frac{1}{\sqrt{1- \dotProd{\beta}{\beta}}}
-\end{equation}
-is the Lorentz Factor.
+            \vspace{-10pt}
+\end{equation} is the Lorentz Factor.
 
 Considering these two statements, we can find the relation between momentum and acceleration as 
+\vspace{-10pt}
 \begin{eqnarray}
-    \deriv{\vecthree{p}}{t} &=& m_0 \deriv{(\gamma \vecthree{v})}{t} = m_0 \{  \deriv{\gamma}{t}\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}  \} \\
-    \deriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\deriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
+    \deriv{\vecthree{p}}{t} &=& m_0 \deriv{(\gamma \vecthree{v})}{t} = m_0 \{  \deriv{\gamma}{t}\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}   ,  \} \\
+    \deriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\deriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a}   , \\
     \deriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}  \} .
+    \vspace{-10pt}
 \end{eqnarray}
 Therefore force can be written as
+\vspace{-10pt}
 \begin{equation} \label{eq:Frel}
     \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \} .
+    \vspace{-10pt}
 \end{equation}
+
 It is clear that acceleration is not necessarily parallel to the force. 
 To start separating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and $\vecthreeBF{F}_{||}$ as
+\vspace{-10pt}
 \begin{equation} \label{eq:a_F_parallels}
     \begin{aligned}
-        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
+        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta  ,
     \end{aligned}
@@
     \begin{aligned}
-        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta \: ,
+        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta  ,
     \end{aligned}
+    \vspace{-10pt}
 \end{equation}
 where 
+\vspace{-10pt}
 \begin{eqnarray}
@@
                                 &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} .
+                                \vspace{-10pt}
 \end{eqnarray}
-$\gamma^2 \beta^2 + 1 = \gamma^2 $ and \fromeq{a_F_parallels} can be used to achieve
+Then, $\gamma^2 \beta^2 + 1 = \gamma^2 $ and \fromeq{a_F_parallels} can be used to achieve
+\vspace{-10pt}
 \begin{eqnarray}
-    \dotProd{\textbf{F}}{\beta} &=& m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} ) \nonumber \\
+    \dotProd{\textbf{F}}{\beta} &=& m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )   , \nonumber \\
     \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
@@
                         &=& m_0 \gamma^3 \vecthreeBF{a}_{||} . \label{eq:Frel_parallel}
+                        \vspace{-20pt}
 \end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel},
+Therefore from \fromeqs{Frel}{Frel_parallel}, force can be rearranged as
+\vspace{-10pt}
 \begin{eqnarray}
@@
                     &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp} .
+                    \vspace{-10pt}
 \end{eqnarray}
+
 We finally have two separate equations which are in similar form with \fromeq{newton_second_law},
+\vspace{-10pt}
 \begin{equation} \label{eq:Frel_para_and_perp}
     \begin{aligned}
-        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
+        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}  ,
     \end{aligned}
@@
 Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by 
+\vspace{-10pt}
 \begin{equation} \label{eq:lf}
     \frac{d \vecthree{p}}{d t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B}) , 
+    \vspace{-10pt}
 \end{equation}
@@
 Similar to non-relativistic version, relativistic Lorentz Force is given by the 4-vector equality
+\vspace{-10pt}
 \begin{equation}
     \frac{d p^{\mu}}{d \tau} = q F^{\mu \nu} u_{\nu} ,
+    \vspace{-10pt}
 \end{equation}
-where $ d \tau = d t / \gamma $ and greek letters are Lorentz indices
+where $ d \tau = d t / \gamma $, greek letters are Lorentz indices and \textit{p, F, u} are
+\vspace{-10pt}
 \begin{equation*}
@@
         \end{bmatrix}    
-    \end{aligned}
+    \end{aligned} ,
     \qquad\qquad
@@
         \end{bmatrix} 
-    \end{aligned}
+    \end{aligned} ,
     \qquad\qquad
@@
     \end{aligned} ,
+    \vspace{-10pt}
 \end{equation*}
@@
 
-For $ \mu = 0 $, we have the time component of the equation
+For $ \mu = 0 $, we have the time component of the equation as
+\vspace{-10pt}
 \begin{eqnarray}
-    \frac{\gamma}{c}\frac{d W}{d t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot d \vecthree{r}}{d t} \\
+    \frac{\gamma}{c}\frac{d W}{d t} &=& \frac{q \gamma \vecthree{E}\cdot \vecthree{v}}{c} = \frac{q \gamma}{c}  \frac{\vecthree{E}  \cdot d \vecthree{r}}{d t}   ,\\
     \frac{d W}{d t} &=& q \frac{\vecthree{E}\cdot d \vecthree{r}} {d t} .
+    \vspace{-10pt}
 \end{eqnarray}
 This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components
+\vspace{-10pt}
 \begin{equation*}
     \frac{d \vecthree{p}}{d \tau} = \gamma \frac{d \vecthree{p}}{d t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B}) ,
+    \vspace{-10pt}
 \end{equation*}
@@
     \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B} .
+    \vspace{-10pt}
 \end{equation*}
-\vspace{-10pt}
 The same thing cannot be said about electric field however. 
 It can create force in any direction with respect to velocity. Therefore, we have the equality
+\vspace{-10pt}
 \begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
@@
         \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
-    \end{aligned}
+    \end{aligned}  ,
     \qquad \qquad
@@
     \end{aligned}    
+    \vspace{-10pt}
 \end{equation}
@@
                                 &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} .
+                                \vspace{-10pt}
 \end{eqnarray*}
+Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
 \vspace{-10pt}
-Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
 \begin{equation} \label{eq:acc_of_E_and_B}
@@
         \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
-    \end{aligned}
+    \end{aligned}  ,
     \qquad \qquad
@@
     \end{aligned}
+    \vspace{-10pt}
 \end{equation}
@@
     \includegraphics[width=.9\textwidth]{./figures/kahvelab_linac.png}
-    \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}}
+    \caption{A linear proton accelerator in KAHVELab. \cite{kahvelab_linac}}
 \end{figure}
@@
     \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
-    \caption{An RF cavity used in KAHVELab}
+    \caption{An RF cavity used in KAHVELab.}
 \end{figure}
@@
 In a rectangular cavity for example, the resonance frequency can be calculated by
-\begin{equation}
-    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}
+\vspace{-10pt}\begin{equation}
+    f_{klm} = \frac{c}{2\pi \sqrt{\mu_r \epsilon_r}} \sqrt{(\frac{k}{w})^2 + (\frac{l}{u})^2 + (\frac{m}{v})^2}  ,
     \label{eq:f_r_rec}
-\end{equation}
+\vspace{-10pt}\end{equation}
 where $w$, $u$, $v$ are the dimensions of the cavity, $\mu_r$ and $\epsilon_r$ are relative permability and permittivity of the cavity respectably.
@@
 It is defined as
-\begin{equation} \label{eq:shunt}
-    Z_s = \frac{V_{acc}^2}{P_{diss}}
-\end{equation}
+\vspace{-10pt}\begin{equation} \label{eq:shunt}
+    Z_s = \frac{V_{acc}^2}{P_{diss}}  ,
+\vspace{-10pt}\end{equation}
 where $V_{acc}$ is the accelerating potential in which the particle is subjected to, 
@@
 They are accelerated between the cylinderical plates and are shielded from the changing RF field while inside the inner cylinder and outside the cavity. 
-
-\begin{description}
-    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
+This stages are explained further below.
+
+%\begin{description}
+%    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
 (\fromfig{rhod_cycle_1})
-    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed. (\fromfig{rhod_cycle_2})
-    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
+%    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed. (\fromfig{rhod_cycle_2})
+%    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
 (\fromfig{rhod_cycle_3})
-    \item[Recirculating Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
+%    \item[Recirculating Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
 (\fromfig{rhod_cycle_4})
-\end{description}
+%\end{description}
 
@@
 
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:rhodo_cavity_field_dist}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering $\vecthreeBF{E}$ field]{{\includegraphics[width=0.45\textwidth]{./figures/cst/cavity_E_field_dist.png} }}%
+    \qquad\subfigure[\centering $\vecthreeBF{B}$ field]{{\includegraphics[width=0.45\textwidth]{./figures/cst/cavity_B_field_dist.png} }}%
+    \vspace{20pt}
+    \caption{$\vecthreeBF{E}$ and $\vecthreeBF{B}$ eigenmode field distributions inside a coaxial cavity.}
+    \label{fig:rhodo_cavity_field_dist}
 \end{figure}
@@
 first eigenmode solution of the $E$ and $B$ fields are \cite{rhodo_pottier}
-\begin{eqnarray}
-    E &=& \frac{E_0}{r} \cos(\frac{\pi z}{h}) \sin(\omega t + \phi) \\
-    B &=& \frac{B_0}{r} \sin(\frac{\pi z}{h}) \cos(\omega t + \phi)
-\end{eqnarray}
+\vspace{-10pt}\begin{eqnarray}
+    E &=& \frac{E_0}{r} \cos(\frac{\pi z}{h}) \sin(\omega t + \phi)  , \\
+    B &=& \frac{B_0}{r} \sin(\frac{\pi z}{h}) \cos(\omega t + \phi)  ,
+\vspace{-10pt}\end{eqnarray}
 where $\omega=2\pi f$, $f$ is the resonance frequency.
@@
     \includegraphics[width=.6\textwidth]{./figures/illustrations/rhodo_integral_curve.pdf}
-    \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}}
+    \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}.}
     \label{fig:int_curve}
 \end{figure}
-Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by the following equation:
-\begin{eqnarray} 
+Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by
+\vspace{-10pt}\begin{eqnarray} 
     V_{acc} &=& 2 \int_{R_1}^{R_2} |E|^2 dr \\
             &=& 2 E_0 \int_{R_1}^{R_2} \frac{dr}{r} \\
-            &=& 2 E_0 \ln(\frac{R_2}{R_1}) \label{eq:v_acc}
-\end{eqnarray}
-Dissipated power $P_{diss}$, on the other hand, can be calculated as follows \cite{rf}:
-\begin{eqnarray} 
+            &=& 2 E_0 \ln(\frac{R_2}{R_1}). \label{eq:v_acc}
+\vspace{-10pt}\end{eqnarray}
+Dissipated power $P_{diss}$, on the other hand, can be calculated as \cite{rf}
+\vspace{-10pt}\begin{eqnarray} 
     P_{diss} &=& \frac{1}{2} \int \int \rho_s | H_{||} |^2 dA \nonumber \\
-             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta \label{eq:p_diss_C_curve}
-\end{eqnarray}
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta . \label{eq:p_diss_C_curve}
+\vspace{-10pt}\end{eqnarray}
 where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
@@
 This curve can be seperated to its line components and total power dissipation of this curve, $P_C$ will be equal to sum of the power dissipated in these lines.
-Since $\vecthreeBF{B}$ is always parallel to the surface we can use $\vecthreeBF{B}$ directly:
-\begin{eqnarray}
+Since $\vecthreeBF{B}$ is always parallel to the surface we can use $\vecthreeBF{B}$ directly as
+\vspace{-10pt}\begin{eqnarray}
     P_{diss} &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (
@@
                  + 2\int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}})d\theta \nonumber\\
-             %&=& \frac{\rho_s B_0^2 \cos^2(\omega t + \phi)}{2\mu_0^2} \int_0^{2\pi} 
              &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (2I_A + 2I_B + 2I_C)d\theta 
-                 = \frac{2\rho_s \pi}{\mu_0^2}(I_A + I_B + I_C)
-\end{eqnarray}
-\begin{eqnarray}
-    I_A = \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_1} &=& B_0^2 \frac{h}{4R_1} \\
-    I_B = \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_2} &=& B_0^2 \frac{h}{4R_2} \\
-    I_C = \int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}} &=& B_0^2 \ln(\frac{R_2}{R_1})
-\end{eqnarray}
-inserting $H_0=B_0/\mu_0$, finally we have the dissipated power:
-\begin{equation} \label{eq:p_diss}
-    P_{diss} = \rho_s \pi H_o ( \frac{h}{2R_1} + \frac{h}{2R_2} + 2\ln(\frac{R_2}{R_1}) )
-\end{equation}
-Therefore, from \fromeq{shunt}, using \fromeqs{v_acc}{p_diss} also $E_0/H_0 = Z_0 \approx 120 \pi$:
-\begin{eqnarray}
+                 = \frac{2\rho_s \pi}{\mu_0^2}(I_A + I_B + I_C)   ,\\
+    I_A &=& \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_1} = B_0^2 \frac{h}{4R_1}   ,\\
+    I_B &=& \int_{0}^{\frac{h}{2}} |B|^2 r dz \Big|_{r=R_2} = B_0^2 \frac{h}{4R_2}   ,\\
+    I_C &=& \int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}} = B_0^2 \ln(\frac{R_2}{R_1}) .
+\vspace{-10pt}\end{eqnarray}
+Inserting $H_0=B_0/\mu_0$, finally we have the dissipated power
+\vspace{-10pt}\begin{equation} \label{eq:p_diss}
+    P_{diss} = \rho_s \pi H_o ( \frac{h}{2R_1} + \frac{h}{2R_2} + 2\ln(\frac{R_2}{R_1}) ).
+\vspace{-10pt}\end{equation}
+Therefore, from \fromeq{shunt}, using \fromeqs{v_acc}{p_diss} also $E_0/H_0 = Z_0 \approx 120 \pi$ we have
+\vspace{-10pt}\begin{eqnarray}
     Z_s &=& \frac{4E_0^2}{H_0^2 \pi \rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{2R_1} + \frac{h}{2R_2} + 2 \ln(\frac{R_2}{R_1}))} \\
-        &=& \frac{8 \pi 60^2}{\rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{4}(\frac{1}{R_1} + \frac{1}{R_2}) + \ln(\frac{R_2}{R_1}))}
-\end{eqnarray}
+        &=& \frac{8 \pi 60^2}{\rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{4}(\frac{1}{R_1} + \frac{1}{R_2}) + \ln(\frac{R_2}{R_1}))}   ,
+\vspace{-10pt}\end{eqnarray}
 where, time dependencies have been removed from $\vecthreeBF{E}$ and $\vecthreeBF{B}$ 
@@
 However, particles do not interact with constant $\vecthreeBF{E}$ field during acceleration. 
-Therefore, a more useful parameter called \textit{effective shunt impedance} can be defined:
-\begin{equation}
-    Z_{se} = Z_s T^2
-\end{equation}
+Therefore, a more useful parameter called \textit{effective shunt impedance} can be defined as
+\vspace{-10pt}\begin{equation}
+    Z_{se} = Z_s T^2  ,
+\vspace{-10pt}\end{equation}
 where $T$ is the \textit{transit time factor}, a correctional coefficent that contain the changing field effects during acceleration.
-For a relativistic electron crossing the axis at time 0, $T$ can be found by \cite{rhodo_pottier}:
-\begin{eqnarray}
-    T &=& \frac{S_i(\frac{2 \pi R_2}{\lambda}) - S_i(\frac{2 \pi R_1}{\lambda})}{\ln(\frac{R_2}{R_1})} \\
-    S_i(\theta) &=& \int_0^{\theta} \frac{\sin(x)}{x} dx
-\end{eqnarray}
-for a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$:
-\begin{equation}
-    T(\phi) = T \cos(\phi)
-\end{equation} 
+For a relativistic electron crossing the axis at time 0, $T$ can be found by \cite{rhodo_pottier}
+\vspace{-10pt}\begin{eqnarray}
+    T &=& \frac{S_i(\frac{2 \pi R_2}{\lambda}) - S_i(\frac{2 \pi R_1}{\lambda})}{\ln(\frac{R_2}{R_1})}   ,\\
+    S_i(\theta) &=& \int_0^{\theta} \frac{\sin(x)}{x} dx .
+\vspace{-10pt}\end{eqnarray}
+For a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$ as
+\vspace{-10pt}\begin{equation}
+    T(\phi) = T \cos(\phi) .
+\vspace{-10pt}\end{equation} 
 Putting all these calculations together, energy gain of a relativistic electron, passing the origin at $\phi / \omega$ as calculated by \textit{J. Pottier} is \cite{rhodo_pottier}
-\begin{eqnarray}
+\vspace{-10pt}\begin{eqnarray}
     \Delta E &=& q V_{acc}^{ef} \\
-    \Delta E &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)
-\end{eqnarray}
+             &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)  ,
+\vspace{-10pt}\end{eqnarray}
 where $ V_{acc}^{ef} = V_{acc} T(\phi)$ is the effective accelerating potential.
 If $\Delta E$ is taken in \textit{MeV}, $Z_{se}$ in $M\Omega$ and $P_{diss}$ in \textit{MW}, this equality becomes
-\begin{equation} \label{eq:W_gain_each_pass_pottier}
-    \Delta E = Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi) \quad MeV
-\end{equation}
+\vspace{-10pt}\begin{equation} \label{eq:W_gain_each_pass_pottier}
+    \Delta E = Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi) \quad MeV .
+\vspace{-10pt}\end{equation}
 With the expectation that the electrons will accelerate to speeds $\approx c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
@@
 
-In the table below, optimized characteristics of a rhodotron cavity can be observed. 
+In the \fromfig{pottier_table1}, optimized characteristics of a rhodotron cavity can be observed. 
 \begin{figure}[H]
@@
     \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
+    \caption{Optimized characteristics of a rhodotron cavity. \cite{rhodo_pottier}}
     \label{fig:pottier_table1}
@@
     \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
+    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$. \cite{rhodo_pottier}}
     \label{fig:pottier_table2}
 \end{figure}
-Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m}.
-\begin{equation}
+Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m} as
+\vspace{-10pt}\begin{equation}
     \label{eq:W_total_gain_pottier}
-    \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
+    \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV .
+\vspace{-10pt}\end{equation}
 
@@
     \includegraphics[width=\textwidth]{./figures/illustrations/rhod1.pdf}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
+    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_1}
@@
     \includegraphics[width=\textwidth]{./figures/illustrations/rhod2.pdf}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
+    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_2}
@@
     \includegraphics[width=\textwidth]{./figures/illustrations/rhod3.pdf}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
+    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_3}
@@
     \includegraphics[width=\textwidth]{./figures/illustrations/rhod4.pdf}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
+    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_4}
@@
 \subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
+The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE can be written as
+\vspace{-10pt}\begin{equation}
+    \ddot{x} = \derivS{x}{t} = f(x) .\label{eq:second-order-ODE}
+\vspace{-10pt}\end{equation}
+
 The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
@@
 The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
+\vspace{-10pt}\begin{eqnarray}
+    a(t_0) &=& f(x_0)   , \nonumber \\
+    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2}   ,\label{eq:leapfrog_sync_x}\\
+    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2} . \label{eq:leapfrog_sync_v}
+\vspace{-10pt}\end{eqnarray}
+For more stability, this version can be rearranged to what is called 'kick-drift-kick' form as
+\vspace{-10pt}\begin{eqnarray} \label{eq:leapfrog}
+    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2}   , \nonumber \\
+    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t   , \\
+    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2} . \nonumber
+\vspace{-10pt}\end{eqnarray}
 This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
@@
 
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta \cite{runge} \cite{kutta}, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-\begin{equation} \label{eq:first-order-ODE}
-    \deriv{y}{x} = f(x, y)
-\end{equation}
+The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta \cite{runge} \cite{kutta}, 
+family of numerical methods
+used to solve ordinary differential equations (ODEs) that are in the form as
+\vspace{-10pt}\begin{equation} \label{eq:first-order-ODE}
+    \deriv{y}{x} = f(x, y) .
+\vspace{-10pt}\end{equation}
 The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-\begin{equation} \label{eq:general-rk}
+of function evaluations at different points within each step as
+\vspace{-10pt}\begin{equation} \label{eq:general-rk}
     \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
+        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i  ,
     \end{aligned}
@@
     \begin{aligned}
-        x_{n+1} = x_n + \delta x 
+        x_{n+1} = x_n + \delta x   ,
     \end{aligned}
-\end{equation}
+\vspace{-10pt}\end{equation}
 where 
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
+\vspace{-10pt}\begin{eqnarray} \label{eq:general-rk-coef}
+    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j) .
+\vspace{-10pt}\end{eqnarray}
+These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a particular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
+The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$ which can be observed in \fromfig{Butcher}.
 \begin{figure}[h!]
@@
     \]
-    \caption{Butcher Tableau}
+    \caption{Butcher Tableau.}
     \label{fig:Butcher}
 \end{figure}
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
+The simplest Runge-Kutta method is the \textit{Euler's method} with the following \textit{Butcher tableau},
 \[ 
@@
         & 1
-    \end{array}
+    \end{array} .
 \]
+
 The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
 The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
+Two of the most used \textit{Butcher tableaus} for \textit{RK4} given in \fromfig{Butcher-RK4}.
+The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
+Its main advantage is that its error coefficients are smaller than the other.
+But it costs more floating point operations per step.
+Resulting in slower calculations.
+
 \begin{figure}[h!]
     \centering
-    \begin{subfigure}{.5\textwidth}
+    \begin{minipage}{.5\textwidth}
         \[ 
@@
         \]  
-    \end{subfigure}%
-    \begin{subfigure}{.5\textwidth}
+    \end{minipage}%
+    \begin{minipage}{.5\textwidth}
         \[ 
@@
         \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
+    \end{minipage}
+    \vspace{20pt}
+    \caption{Butcher Tableau for RK4.}
     \label{fig:Butcher-RK4}
 \end{figure}
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
 
@@
 Using $f_{RF}=107.5$ MHz \& $f_{RF}=180$ MHz for comparison:
-\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
+\vspace{-10pt}\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
     \begin{aligned}
-        f_{107.5} = 107.5 \textrm{ MHz} \\
-        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m \\
-        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m \\
-        R_1 = \frac{R_2}{4} = 0.188 m \\
-        h = \frac{\lambda}{2} = 1.394 m 
+        f_{107.5} = 107.5 \textrm{ MHz}  , \\
+        \lambda_{107.5}  = \frac{c}{f_{107.5}} = 2.789 m   ,\\
+        R_2 = 0.27 \times \lambda_{107.5} = 0.753 m   ,\\
+        R_1 = \frac{R_2}{4} = 0.188 m   ,\\
+        h = \frac{\lambda}{2} = 1.394 m .
     \end{aligned}
@@
     \begin{aligned}
-        f_{180} = 180 \textrm{ MHz} \\
-        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m \\
-        R_2 = 0.27 \times\lambda_{180} = 0.450 m \\
-        R_1 = \frac{R_2}{4} = 0.113 m \\
-        h = \frac{\lambda}{2} = 0.833 m 
+        f_{180} = 180 \textrm{ MHz}   ,\\
+        \lambda_{180}  = \frac{c}{f_{180}} = 1.666 m  , \\
+        R_2 = 0.27 \times\lambda_{180} = 0.450 m  , \\
+        R_1 = \frac{R_2}{4} = 0.113 m  , \\
+        h = \frac{\lambda}{2} = 0.833 m . 
     \end{aligned}
-\end{eqnarray}
-In the following figures, \textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
+\vspace{-10pt}\end{eqnarray}
+In the \fromfigth{107_simple_cavity_design}{180_simple_cavity_design}{cst_simple_cavity_designs}, 
+\textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz]{{\includegraphics[width=.45\textwidth]{./figures/superfish/superfish107.png} }}%
+    \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.45\textwidth]{./figures/superfish/superfish180.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
+    \label{fig:107_simple_cavity_design}
+\end{figure}
+
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz]{{\includegraphics[width=.48\textwidth]{./figures/cst/cst107.png} }}%
+    \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.44\textwidth]{./figures/cst/cst180.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
+    \label{fig:180_simple_cavity_design}
+\end{figure}
+
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst107_e.png} }}%
+    \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.47\textwidth]{./figures/cst/cst180_e.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
+    \label{fig:cst_simple_cavity_designs}
+\end{figure}
+As mentioned by \textit{Pottier}, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
+In the \fromfig{107_180_modified_cavities_superfish}, \textit{Poission Superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.45\textwidth]{./figures/superfish/superfish107mod.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.45\textwidth]{./figures/superfish/superfish180mod.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poisson SUPERFISH field results of truncated cavities.} 
+    \label{fig:107_180_modified_cavities_superfish}
+\end{figure}
+
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst107mod.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.47\textwidth]{./figures/cst/cst180mod.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST eigenmode results of truncated cavities.} 
+    \label{fig:107_180_modified_cavities_cst_eigenmode}
+\end{figure}
+
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.46\textwidth]{./figures/cst/cst107mod_e.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.44\textwidth]{./figures/cst/cst180mod_e.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST electric field results of truncated cavities.} 
+    \label{fig:107_180_modified_cavities_cst_field}
+\end{figure}
+
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.485\textwidth]{./figures/superfish/superfish107_z_highlighted.png} }}%
+    \qquad\subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{./figures/superfish/superfish180_z_highlighted.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poisson Superfish calculations with \textit{unmodified} cavities.} 
+    \label{fig:107_cavity_shunt_diff}
+\end{figure}
+
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.475\textwidth]{./figures/superfish/superfish107mod_z_highlighted.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{./figures/superfish/superfish180mod_z_highlighted.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poisson Superfish calculations with \textit{truncated} cavities.} 
+    \label{fig:180_cavity_shunt_diff}
+\end{figure}
+One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff} as
+\vspace{-10pt}\begin{equation*}
     \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
+        \Delta Z_{107.5}=2.5\%   ,
     \end{aligned}
@@
     \begin{aligned}
-        \Delta Z_{180}=2.7\%
+        \Delta Z_{180}=2.7\% .
     \end{aligned}
-\end{equation*}
+\vspace{-10pt}\end{equation*}
 
@@
 Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \end{subfigure}
-    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}}
+    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}}
+    \label{fig:magnet_design_illustrations}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/design/Ltot.png} }}%
+    \qquad\subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/design/tt300_mag.png} }}%
+    \vspace{20pt}
+    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}} 
     \label{fig:magnet_design_illustrations}
@@
 As discussed earlier, by assuming the electron is traveling at $c$, phase stability can be achieved by designing the whole trajectory to be $n \lambda$, where $\lambda$ is the wavelength of the RF field.
-In other words, total trajectory of synchronous particle needs to satisfy the following equality:
-\begin{equation}
-    L_{pass} = n \lambda
-\end{equation} 
-Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice:
-\begin{equation}
-    L_{pass} = \lambda
-\end{equation}
+In other words, total trajectory of synchronous particle needs to satisfy
+\vspace{-10pt}\begin{equation}
+    L_{pass} = n \lambda .
+\vspace{-10pt}\end{equation} 
+Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice, which leads to
+\vspace{-10pt}\begin{equation}
+    L_{pass} = \lambda .
+\vspace{-10pt}\end{equation}
 
@@
     \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
+    \caption{Trejectory of a particle in single pass.}
     \label{fig:magnet_design}
@@
 From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
-$L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall:
-\begin{eqnarray}
-    L_{in} &=& 2R_2 \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  \nonumber \\
-    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho \label{eq:magnet_lambda_constraint}
-\end{eqnarray}
+$L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall the constraints are
+\vspace{-10pt}\begin{eqnarray}
+    L_{in} &=& 2R_2   , \nonumber\\
+    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho  , \nonumber \\
+    L_{pass} &=& L_{in} + L_{out}  ,  \nonumber \\
+    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho . \label{eq:magnet_lambda_constraint}
+\vspace{-10pt}\end{eqnarray}
 After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
 Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-\begin{eqnarray}
-    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L} \nonumber \\
-    \rho &=&  \tan (\gamma) (R_2 + d + L) \nonumber\\
-    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho) \nonumber\\
-    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda \nonumber\\
-    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}} \label{eq:magnet_rho_constraint} \\
-    L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 \label{eq:magnet_L_constraint}
-\end{eqnarray}
+\vspace{-10pt}\begin{eqnarray}
+    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  , \nonumber \\
+    \rho &=&  \tan (\gamma) (R_2 + d + L)  , \nonumber\\
+    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho)  , \nonumber\\
+    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda   ,\nonumber\\
+    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}}   ,\label{eq:magnet_rho_constraint} \\
+    L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 . \label{eq:magnet_L_constraint}
+\vspace{-10pt}\end{eqnarray}
+
 \textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
@@
 after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
-\begin{eqnarray*}
-    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV \\
-    W_{total} &=& 394 keV \\
-    \beta_{40keV} &\approx& 0.374 \\
-    \beta_{394keV} &\approx& 0.825
-\end{eqnarray*}
+it can be observed that
+\vspace{-10pt}\begin{eqnarray*}
+    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV   ,\\
+    W_{total} &=& 394 keV   ,\\
+    \beta_{40keV} &\approx& 0.374   ,\\
+    \beta_{394keV} &\approx& 0.825 .
+\vspace{-10pt}\end{eqnarray*}
 It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
@@
 Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\begin{eqnarray*}
-    L_{pass} &=& K \\
-    L_{in} + L_{out} &=& K
-\end{eqnarray*}
+\vspace{-10pt}\begin{eqnarray*}
+    L_{pass} &=& K ,\\
+    L_{in} + L_{out} &=& K .
+\vspace{-10pt}\end{eqnarray*}
 Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\begin{equation} \label{eq:mag_sweep_constraint}
-    L_{out} = K
-\end{equation}
+\vspace{-10pt}\begin{equation} \label{eq:mag_sweep_constraint}
+    L_{out} = K .
+\vspace{-10pt}\end{equation}
 To start, an optimization criteria for the following pass such as
@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
+    \caption{Initial design of the proposed rhodotron, $\gamma=9^\circ$.}
     \label{fig:initial_design}
 \end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:initial_design_cross_section}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Axial cross section]{{\includegraphics[width=.46\textwidth]{./figures/cst/cst_first_design3.png} }}%
+    \qquad\subfigure[\centering Cross section at acceleration plane]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_first_design2.png} }}%
+    \vspace{20pt}
+    \caption{\centering Initial design of the proposed rhodotron.} 
+    \label{fig:initial_design_cross_section}
 \end{figure}
 The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:initial_magnet_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_first_magnet_design1.png} }}%
+    \qquad\subfigure[\centering ]{{\includegraphics[width=.46\textwidth]{./figures/cst/cst_first_magnet_design2.png} }}%
+    \vspace{20pt}
+    \caption{\centering Initial magnet design.} 
+    \label{fig:initial_magnet_design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
+    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design}, $\gamma=15^\circ$.}
     \label{fig:initial_three_magnet_design}
@@
 Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \caption{$|r|$ vs $Energy$ simulation of initial design.}
+    \label{fig:initial_designs_PIC_phase_space_monitor}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_first_design4.png} }}%
+    \vspace{20pt}\newline
+    \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_second_design3.png} }}%
+    \vspace{20pt}
+    \caption{\centering $|r|$ vs $Energy$ simulation of initial design.} 
     \label{fig:initial_designs_PIC_phase_space_monitor}
@@
 Improved designs can be seen in the figures below.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:improved_cavity_design}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_sinan_cavity_design1.png} }}%
+    \qquad\subfigure[\centering ]{{\includegraphics[width=.47\textwidth]{./figures/cst/cst_sinan_cavity_design2.png} }}%
+    \vspace{20pt}
+    \caption{\centering Improved cavity design.} 
+    \label{fig:improved_cavity_design}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
@@
     \label{fig:improved_magnet_design_cross_section}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure{{\includegraphics[width=.475\textwidth]{./figures/cst/cst_second_magnet_design2.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.443\textwidth]{./figures/cst/cst_second_magnet_design3.png} }}%
+    \vspace{20pt}
+    \caption{\centering Cross section and coils of improved magnet design.} 
+    \label{fig:improved_magnet_design_cross_section}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
@@
 \begin{itemize}
-    \item Get electron energy $E_{in}$
-    \item Get the RF field definitions
-    \item Get the magnet design parameters if there is any
-    \item Do following until the simulation time has ellapsed
+    \item Get electron energy $E_{in}$,
+    \item Get the RF field definitions,
+    \item Get the magnet design parameters if there is any,
+    \item Do following until the simulation time has ellapsed,
     \begin{enumerate}
-        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
-        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
-        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
-        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
-        \item Calculate new $E_t$
+        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$),
+        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force},
+        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x},
+        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v},
+        \item Calculate new $E_t$.
     \end{enumerate}
@@
     \end{minted}
-    \caption{Core logic loop of the POC}
+    \caption{Core logic loop of the POC.}
     \label{fig:POC_core_logic}
 \end{figure}
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
+After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} 
+with $\phi_{lag}=15^\circ$, $P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz for one pass, 
+the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} were found to be
 % 40 kW total power
@@
 % f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.593 MeV \nonumber\\
-        E_{CST} &=& 0.521 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.532 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced similar results, $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
-
-However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$, $\Delta E_{(Pottier-CST)}/E_{CST} \approx 14\%$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+\vspace{-10pt}\begin{eqnarray}
+    E_{Pottier} &=& 0.593 MeV  , \nonumber\\
+    E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
+    E_{POC} &=& 0.532 MeV . \nonumber
+\vspace{-10pt}\end{eqnarray}
+
+As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced similar results; $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
+while \fromeq{W_gain_each_pass_pottier} was noticably different; $\Delta E_{(Pottier-CST)}/E_{CST} \approx 14\%$.
+This inconsistency between \fromeq{W_gain_each_pass_pottier} and  \textit{CST} simulation was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
 Since using a single software would have made the process error prone.
@@
 $\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as follows:
+To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as
 \begin{itemize}
-    \item $\mu E$: Average energy
-    \item $E_{rms}$: Root mean square of energy
-    \item $R_{rms}$: Root mean square of \e positions
+    \item $\mu E$: Average energy,
+    \item $E_{rms}$: Root mean square of energy,
+    \item $R_{rms}$: Root mean square of \e positions.
 \end{itemize}
@@
     \centering
-    \captionsetup{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
@@
     \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
+    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
     \label{fig:phlag_opt}
@@
 Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{subfigure}{\textwidth}
@@
     \end{subfigure}
-    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}}
+    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
+    \label{fig:3D_e_EM_interaction_first}
+\end{figure} \fi
+\begin{figure}[H]
+    %%\captionsetup[subfigure]{justification=centering}
+    %%\captionsetup{justification=centering}
+    \begin{minipage}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+            vector3d CoaxialRFField::actOn(Electron& e){
+                vector3d Efield = getField(e.pos);                          // Calculate E vector
+                vector3d F_m = Efield*1E6*eQMratio;                         // Calculate F/m vector
+                vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma();   // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \end{minipage}
+
+    \begin{minipage}{\textwidth}
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+            vector3d MagneticField::actOn(Electron& e){
+                if (isInside(e.pos) == -1)
+                    return vector3d(0,0,0);
+                vector3d Bfield = getField(e.pos);                          // Calculate B vector
+                vector3d F_m = (e.vel % Bfield)*eQMratio;                   // Calculate F/m vector
+                vector3d acc = (F_m)/e.gamma();                             // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \end{minipage}
+    \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
     \label{fig:3D_e_EM_interaction_first}
@@
 Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
+    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation} $P=40$kW, $f=107.5$MHz.}
+    \label{fig:example_gnuplot_renders}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Unsyncronized \e gun period, $T_g = 5ns$]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/5ns_gnuplot.png}}}%
+    \vspace{15pt}
+    \centering
+    \subfigure[\centering Syncronized \e gun period, $T_g = 9.3ns$]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/9_3ns_gnuplot.png}}}%
+    \vspace{15pt}
+    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}, $P=40$kW, $f=107.5$MHz.} 
     \label{fig:example_gnuplot_renders}
@@
 Initial results at $dt=0.01$ns proved the suspicion of \eB interaction being broken. However, the energy gain would decrease tremendously as $dt$ decreased.
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
+    \label{fig:mag_lf_render}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.8\textwidth]{./figures/rhodoSim/mag_lf_001dt.png} }}%
+    \vspace{15pt}
+    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.8\textwidth]{./figures/rhodoSim/mag_lf_00001dt.png} }}%
+    \vspace{15pt}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T.}
     \label{fig:mag_lf_render}
@@
 Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{fig:mag_lf_rk2_comparison}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{./figures/analiz/mag_lf_rk2_dt-E.png} }}%
+    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
+    \vspace{20pt}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
+    \label{fig:mag_lf_rk2_comparison}
 \end{figure}
 The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
+To investigate the data further, one can define a performance measurement, $F$ as
+\vspace{-10pt}\begin{eqnarray*}
+    F &\propto& 1/T  , \\
+    F &\propto& 1/\Delta E . 
+\vspace{-10pt}\end{eqnarray*}
 When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
+relative performance can be calculated as
+\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
+    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\nonumber\\
+    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\nonumber\\
+    T_{LF}^1 &=& 9.44 \pm 0.03 s, \nonumber\\
+    T_{RK}^1 &=& 21.33 \pm 0.02 s, \nonumber\\
+    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \nonumber\\ %0.003
+    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \nonumber\\ %0.001
+    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
+\vspace{-10pt}\end{eqnarray}
+Also, another relative performance can be obsered from the data as
+\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
+    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \nonumber\\
+    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \nonumber\\ %0.0032
+    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \nonumber\\ %0.0022
+    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
+\vspace{-10pt}\end{eqnarray}
+Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. 
+After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
+\vspace{-10pt}\begin{equation}
+    F_{LF}/F_{RK} = 1.36 \pm 0.05.
+\vspace{-10pt}\end{equation}
 Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
@@
 Both configurations had an \egun located at $(-0.753, 0, 0)$m, directed at $(1, 0, 0)$ firing electrons with the kinetic energy of $1$MeV. 
-\begin{figure}[H]
+\iffalse \begin{figure}[H]
     \centering
@@
     \caption{Illustration of test setups.}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{./figures/illustrations/statE_1.png} }}%
+    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{./figures/illustrations/statE_2.png} }}%
+    \vspace{20pt}
+    \caption{Illustration of test setups.}
 \end{figure}
@@
 Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
-\begin{eqnarray}
+\vspace{-10pt}\begin{eqnarray}
     \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
@@
              &=& 2.65616 \times 1.506 \\
-    \Delta V^1 &=& 4 MV \\
-    \Delta E^1 &=& 4 MeV \\
-    E_{exitTH}^1 &=& 5 MeV
-\end{eqnarray}
-In the second test on the other hand, the beam would be injected into a different static uniform electric field, \\
+             &=& 4 MV, \\
+    \Delta E^1 &=& 4 MeV, \\
+    E_{exitTH}^1 &=& 5 MeV.
+\vspace{-10pt}\end{eqnarray}
+
+In the second test on the other hand, the beam would be injected into a different static uniform electric field,
 $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-\begin{eqnarray}
+\vspace{-10pt}\begin{eqnarray}
     \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
@@
                  &=& 5.31232 \times 0.753 \\
-    \Delta V^2   &=& 4 MV \\
-    \Delta E^2   &=& 4 MeV \\
-    E_{exitTH}^2 &=& 5 MeV
-\end{eqnarray}
+                 &=& 4 MV, \\
+    \Delta E^2   &=& 4 MeV, \\
+    E_{exitTH}^2 &=& 5 MeV.
+\vspace{-10pt}\end{eqnarray}
+
 Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
@@
 Results from these tests can be observed in \fromfig{lf_rk2_perp_stat_E_comparison} and \fromfig{lf_rk2_par_stat_E_comparison} of \fromapp{data_graph}.
-\begin{figure}[H]
+\iffalse \begin{figure}[H]
     \centering
@@
     \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+    \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Setup-1, $\textbf{V}_{\parallel}$=4MV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/statE_par.png} }}%
+    \vspace{15pt}
+    \subfigure[\centering Setup-2, $\textbf{V}_{\perp}$=4MV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/statE_perp.png} }}%
+    \vspace{15pt}
+    \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns.}
+\end{figure}
+
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns}
     \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-Taking the $dt=10^{-5}$ ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.9\textwidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png} }}%
+    \vspace{15pt}
+    \subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.9\textwidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png} }}%
+    \vspace{15pt}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns.}
+    \label{fig:lf_rk2_perp_stat_E_comparison}
+\end{figure}
+Taking the $dt=10^{-5}$ ns for the reference point as before, using the data
+\vspace{-10pt}\begin{eqnarray*}
     \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
+        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV, \\
+        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV, \\
+        T_{LF}^1 &=& 12.40 \pm 0.04 s, \\
+        T_{RK}^1 &=& 40.08 \pm 0.12 s, 
     \end{aligned}
@@
     \begin{aligned}
-        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV \\
-        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV \\
-        T_{LF}^2 &=& 10.75 \pm 0.04 s \\
-        T_{RK}^2 &=& 34.93 \pm 0.39 s 
+        \Delta E_{LF}^2 &=& 15 \times 10^{-5} MeV, \\
+        \Delta E_{RK}^2 &=& 9.3 \times 10^{-5} MeV, \\
+        T_{LF}^2 &=& 10.75 \pm 0.04 s, \\
+        T_{RK}^2 &=& 34.93 \pm 0.39 s, 
     \end{aligned}
-\end{eqnarray*}
-
-\begin{eqnarray} \label{eq:f_lf_rk_1}
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s \nonumber\\ %0.003
-    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02
-\end{eqnarray}
-
-\begin{eqnarray} \label{eq:f_lf_rk_2}
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s \nonumber\\ %0.011
-    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03
-\end{eqnarray}
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than \textit{RK4} in parallel and perpendicular electric fields respectably.
-This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph}),
-\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s \nonumber\\ %0.0022
-    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02
-\end{eqnarray}
-\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62 \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00 \nonumber\\ %0.0071 -> 0,0126
-    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1
-\end{eqnarray}
+\vspace{-10pt}\end{eqnarray*}
+the relative performances can be calculated as
+\vspace{-10pt}\begin{eqnarray} 
+    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s, \nonumber\\ %0.003
+    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s, \nonumber\\ %0.003
+    F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02, \label{eq:f_lf_rk_1}
+\vspace{-10pt}\end{eqnarray}
+and
+\vspace{-10pt}\begin{eqnarray}  
+    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s, \nonumber\\ %0.004
+    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s, \nonumber\\ %0.011
+    F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03. \label{eq:f_lf_rk_2}
+\vspace{-10pt}\end{eqnarray}
+
+\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than 
+\textit{RK4} in parallel and perpendicular electric fields respectably.
+This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph})
+and calculating other relative performances as
+\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_3}
+    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV, \nonumber\\
+    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s, \nonumber\\ %0.0032
+    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s, \nonumber\\ %0.0022
+    F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02,
+\vspace{-10pt}\end{eqnarray}
+and
+\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_4}
+    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV, \nonumber\\
+    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62, \nonumber\\ %0.0055
+    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00, \nonumber\\ %0.0071 -> 0,0126
+    F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1.
+\vspace{-10pt}\end{eqnarray}
 The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as in \fromeq{lf_rk_eE_relative_performance}.
-\begin{equation}\label{eq:lf_rk_eE_relative_performance}
-    F_{LF}/F_{RK} = 2.11 \pm 0.03
-\end{equation}
+the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as
+\vspace{-10pt}\begin{equation}\label{eq:lf_rk_eE_relative_performance}
+    F_{LF}/F_{RK} = 2.11 \pm 0.03.
+\vspace{-10pt}\end{equation}
 Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
@@
 There were four competing architecture for these worker threads,
-\begin{enumerate}
-    \item Have a thread pool that calculates \eEM in a queue 
-    \item Assign a thread to each bunch
-    \item Assign random electrons to each thread and calculate \eEM with global time
-    \item Assign random electrons to each thread and calculate \eEM with local thread time
-\end{enumerate}
-\textbf{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
-\textbf{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textbf{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textbf{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
+\begin{itemize}
+    \item \textit{Architecture 1:} Have a thread pool that calculates \eEM in a queue 
+    \item \textit{Architecture 2:} Assign a thread to each bunch
+    \item \textit{Architecture 3:} A ssign random electrons to each thread and calculate \eEM with global time
+    \item \textit{Architecture 4:} Assign random electrons to each thread and calculate \eEM with local thread time
+\end{itemize}
+
+\textit{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
+
+\textit{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
+
+\textit{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
+
+\textit{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
 This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
@@
 Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textbf{Architecture 2} \& \textbf{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textbf{Architecture 4} was chosed to be implemented.
+An implementation that can use both \textit{Architecture 2} \& \textit{Architecture 4} when necessary would be a better approach considering these methods;
+nevertheless, \textit{Architecture 4} was chosed to be implemented.
 
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
+An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.95\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
     \caption{An Illustration of the first GUI design.}
@@
 \end{figure}
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
-An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
@@
 The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
-    \caption{The configuration frame of implementated first GUI design.}
-    \label{fig:gui_config}
-\end{figure}
 The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
@@
 
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
-
-\subsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
+In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. 
+Available frames of this version of the \textit{GUI} are discussed further in the following sections.
 \subsection{Simulation Frame}
@@
 
+\newpage
+\subsection{Configuration Frame}
+This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
+    \caption{The configuration frame of implementated first GUI design.}
+    \label{fig:gui_config}
+\end{figure}
+
+\newpage
 \subsection{Render Frame}
@@
 Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_5.png}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_render_frame_5.png}
     \caption{Render frame of \textit{GUI}.}
@@
 Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
+In the current version, energy distribution histogram and \textit{E(t)} graph of each electron are implementated into this frame.
 This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Edist_2.png}
+In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist_2.png}
     \caption{Analyze frame of \textit{GUI} E distribution.}
@@
 
-\begin{figure}
+\begin{figure}[h!]
     \centering
@@
 
+\newpage
+
 \subsection{Sweep Frame}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_muE_3.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_sweep_muE_3.png}
+    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ $\mu E$ result.}
     \label{fig:gui_sweep_muE}
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sE_3.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
+\newpage
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_sweep_sE_3.png}
+    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ sweep $\sigma E$ result.}
     \label{fig:gui_sweep_sE}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
-    \caption{Rhodotron in KAHVELab}
+    \caption{Rhodotron in KAHVELab.}
 \end{figure}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
-    \caption{Rhodotron cavity and \e gun}
+    \caption{Rhodotron cavity and \e gun.}
 \end{figure}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
-    \caption{Vertical cross section of the beam injection line}
+    \caption{Vertical cross section of the beam injection line.}
 \end{figure}
@@
     \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
-    \caption{Cross section of the acceleration plane}
+    \caption{Cross section of the acceleration plane.}
 \end{figure}
@@
 \begin{itemize}
-    \item $4.5$in EIA RF flange for RF input
-    \item ISO-100KF vacuum connector flanges for vacuum pumps
-    \item ISO-63 KF flange for probe insertion
-    \item KF-40 flanges for beam line vacuum gauges
+    \item $4.5$in EIA RF flange for RF input,
+    \item ISO-100KF vacuum connector flanges for vacuum pumps,
+    \item ISO-63 KF flange for probe insertion,
+    \item KF-40 flanges for beam line vacuum gauges.
 \end{itemize}
@@
 which would be removed after the heat treatment.
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_polishing}
-\end{figure}
-
+\end{figure} \fi
 \begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+    \centering
+    \subfigure[\centering Bottom part of the cavity while polishing]{{\includegraphics[width=.48\textwidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.48\textwidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{Polishing of the inner surface of cavity.}
+    \label{fig:manif_polishing}
+\end{figure}
+
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_toroidal_sheets}
-\end{figure}
-
+\end{figure} \fi
 \begin{figure}
-    \captionsetup{justification=centering}
+    \centering
+    \subfigure[\centering Bottom part of the cavity with the exposed beam line in inner cylinder]{{\includegraphics[width=.48\textwidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.48\textwidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
+    \label{fig:manif_toroidal_sheets}
+\end{figure}
+
+\begin{figure}
+    %%\captionsetup{justification=centering}
     \centering
@@
 \begin{figure}
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \centering
@@
 
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_welding}
-\end{figure}
-
+\end{figure} \fi
 \begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+    \centering
+    \subfigure[\centering Welding sheet bars]{{\includegraphics[width=.48\textwidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.48\textwidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{\centering TIG welding.} 
+    \label{fig:manif_welding}
+\end{figure}
+
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_assembled_flanges}
-\end{figure}
-
+\end{figure} \fi
 \begin{figure}
-    \captionsetup{justification=centering}
+    \centering
+    \subfigure[\centering Beam enter \& exit flanges]{{\includegraphics[width=.48\textwidth]{./figures/manif/assembled/rhodo_final_cropped_5.jpeg} }}%
+    \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.48\textwidth]{./figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{\centering Flanges on the assembled cavity.} 
+    \label{fig:manif_assembled_flanges}
+\end{figure}
+
+\begin{figure}
+    %%\captionsetup{justification=centering}
     \centering
@@
 They include the following;
-\begin{figure}[H]
+\iffalse \begin{figure}[H]
     \begin{subfigure}[t]{0.5\textwidth}
@@
     \end{subfigure}
-\end{figure}
+\end{figure} \fi
+\begin{figure}[H]
+    \begin{minipage}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Electric and magnetic field import
+            \item Field generator module to directly produce field files from specified cavity
+            \item Synchrotron radiation calculations to determine radiation and energy loss
+            \item \ee interactions
+            \item Redesign of the GUI
+            \item 3D render in GUI
+        \end{itemize}
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Refactoring of the \eEM interaction and logging to improve performance
+            \item Refactoring of the GUI Render Frame to improve render speed
+            \item Refactoring the magnet class to introduce field leaks
+            \item Extention of analysis tools in Analyze Frame
+            \item $L_{out}$ sweep in Sweep Frame
+        \end{itemize}
+    \end{minipage}
+\end{figure}
+
 After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
@@
     \centering
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
+    %\captionsetup{justification=centering}
+    \begin{minipage}{\textwidth}
         \centering
@@
         \end{minted}
-    \end{subfigure} 
+    \end{minipage} 
     \\
-    \begin{subfigure}{\textwidth}
+    \begin{minipage}{\textwidth}
         \centering
@@
         \end{minted}
-    \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
+    \end{minipage}
+    \caption{$L_{out}$ Optimization For Single \e.}
     \label{fig:lout_opt_single_e}
@@
         \centering
-        \captionsetup{justification=centering}
+        %\captionsetup{justification=centering}
         \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
@@
         \end{minted}
-    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design}
+    \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
     \label{fig:phlag_opt_n_pass}
@@
 \begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
+    \begin{minipage}{\textwidth}
         \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
@@
         \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
+    \end{minipage}
+
+    \begin{minipage}{\textwidth}
         \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
@@
         \end{minted}
-    \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
+    \end{minipage}
+    \caption{* and \% operators of \textit{vector3d} class.}
     \label{fig:vector3d_dot_cross_product}
@@
     \end{minted}
-\caption{Logic of is \e inside the shape of magnet}
+\caption{Logic of is \e inside the shape of magnet.}
 \label{fig:is_inside_halfsphere}
@@
     \end{minted}
-\caption{RK4-1 implemenation of \eEM}
+\caption{RK4-1 implemenation of \eEM.}
 \label{fig:rk1_EM}
@@
     \centering
-    \captionsetup{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
@@
     \end{minted}
-\caption{RK4-2 implemenation of \eEM}
+\caption{RK4-2 implemenation of \eEM.}
 \label{fig:rk2_EM}
@@
     \end{minted}
-    \caption{Electron class definition}
+    \caption{Electron class definition.}
     \label{fig:e_class}
@@
     \end{minted}
-    \caption{Bunch class definition}
+    \caption{Bunch class definition.}
     \label{fig:bunch_class}
@@
     \end{minted}
-    \caption{Gun class definition}
+    \caption{Gun class definition.}
     \label{fig:gun_class}
@@
     \end{minted}
-    \caption{Simulator class definition}
+    \caption{Simulator class definition.}
     \label{fig:sim_class}
@@
     \end{minted}
-    \caption{RhodotronSimulator class definition}
+    \caption{RhodotronSimulator class definition.}
     \label{fig:rhodosim_class}
@@
 \begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
-    \begin{subfigure}{\textwidth}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
+    \begin{minipage}{\textwidth}
         \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
@@
         \end{minted}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
+    \end{minipage}
+
+    \begin{minipage}{\textwidth}
         \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
@@
         \end{minted}
-    \end{subfigure}
-    \caption{CoaxialRFField class definition}
+    \end{minipage}
+    \caption{CoaxialRFField class definition.}
     \label{fig:rf_class}
@@
     \centering
-    \captionsetup{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
@@
     \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV}
+\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at $P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV.}
 \label{fig:lout_opt_1ns_Erms}
@@
     \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at \\$P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at $P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV.}
 \label{fig:lout_opt_08ns_Erms}
@@
     \end{subfigure}
-    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2.}
     \label{fig:mag_rk_render}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \captionsetup{justification=centering}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=1.047$MeV]{{\includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png} }}%
+    \vspace{20pt}\newline
+    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.006$MeV]{{\includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png} }}%
+    \vspace{20pt}
+    \caption{\centering Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2.} 
+    \label{fig:mag_rk_render}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    %\captionsetup{justification=centering}
     \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \caption{Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
     \label{fig:lf_rk1_rk2_comparison}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png} }}%
+    \vspace{20pt}\newline
+    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png} }}%
+    \vspace{20pt}
+    \caption{\centering Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.} 
+    \label{fig:lf_rk1_rk2_comparison}
+\end{figure}
+
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns.}
     \label{fig:lf_rk2_par_stat_E_comparison}
+\end{figure}\fi 
+\begin{figure}
+    \centering
+    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png} }}%
+    \vspace{20pt}\newline
+    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}}}%
+    \vspace{20pt}
+    \caption{\centering Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns.} 
+    \label{fig:lf_rk2_par_stat_E_comparison}
 \end{figure}
@@
     \centering
+    \caption{\textit{Leap-frog} data on $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
     \begin{tabular}{|l|l|l|l|}
@@
     \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{tab:lf_mag_table}
@@
     \centering
+    \caption{\textit{RK4-2} data on $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
     \begin{tabular}{|l|l|l|l|}
@@
     \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{tab:rk2_mag_table}
@@
     \centering
+    \caption{\textit{LF} data on $E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns.}
     \begin{tabular}{|l|l|l|l|}
@@
     \end{tabular}
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
     \label{tab:lf_statE_table}
@@
     \centering
+    \caption{\textit{RK4-2} data on $E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns.}
     \begin{tabular}{|l|l|l|l|}
@@
     \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
     \label{tab:rk2_statE_table}
@@
     \centering
-    \caption{\textit{LF} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns}
+    \caption{\textit{LF} data on $E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns.}
     \begin{tabular}{|l|l|l|l|}
@@
     \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns}
     \label{tab:rk2_statE90_table}
@@
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep running.}
+    \caption{Sweep frame of \textit{GUI}  $\phi_{lag}$ sweep running.}
     \label{fig:gui_sweep_running}
@@
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sR_3.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma R$ result.}
+    \caption{Sweep frame of \textit{GUI}  $\phi_{lag}$ sweep $\sigma R$ result.}
     \label{fig:gui_sweep_sR}

### 2023-09-18 subsections/design/cavity/cavity.tex
push for sina1

@@
 \usepackage{tabu}
-\usepackage{subcaption}
+%\usepackage{subcaption}
+\usepackage{subfigure}
 \usepackage[a4paper, total={6in, 8in}]{geometry}
@@
 \newcommand{\fromfigs}[2]{\textit{figures \ref{fig:#1} and \ref{fig:#2}}}
+\newcommand{\fromfigth}[3]{\textit{figures \ref{fig:#1}, \ref{fig:#2} and \ref{fig:#3}}}
 \newcommand{\fromsec}[1]{\textit{section \ref{sec:#1}}}
+
+\newcommand{\comment}[1]{}
 
@@
 \end{figure}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz]{{\includegraphics[width=.45\textwidth]{../../../figures/superfish/superfish107.png} }}%
+    \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.45\textwidth]{../../../figures/superfish/superfish180.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
+    \label{fig:107_simple_cavity_design}
+\end{figure}
 
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz]{{\includegraphics[width=.48\textwidth]{../../../figures/cst/cst107.png} }}%
+    \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.44\textwidth]{../../../figures/cst/cst180.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
+    \label{fig:180_simple_cavity_design}
+\end{figure}
 
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-As mentioned by POTTIER, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-Below, \textit{Poission superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst107_e.png} }}%
+    \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst180_e.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
+    \label{fig:cst_simple_cavity_designs}
+\end{figure}
+As mentioned by \textit{Pottier}, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
+In the \fromfig{107_180_modified_cavities_superfish}, \textit{Poission Superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.45\textwidth]{../../../figures/superfish/superfish107mod.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.45\textwidth]{../../../figures/superfish/superfish180mod.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poisson SUPERFISH field results of truncated cavities.} 
+    \label{fig:107_180_modified_cavities_superfish}
+\end{figure}
 
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst107mod.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst180mod.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST eigenmode results of truncated cavities.} 
+    \label{fig:107_180_modified_cavities_cst_eigenmode}
+\end{figure}
 
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst107mod_e.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.44\textwidth]{../../../figures/cst/cst180mod_e.png} }}%
+    \vspace{20pt}
+    \caption{\centering CST electric field results of truncated cavities.} 
+    \label{fig:107_180_modified_cavities_cst_field}
+\end{figure}
 
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.485\textwidth]{../../../figures/superfish/superfish107_z_highlighted.png} }}%
+    \qquad\subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{../../../figures/superfish/superfish180_z_highlighted.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poisson Superfish calculations with \textit{unmodified} cavities.} 
+    \label{fig:107_cavity_shunt_diff}
+\end{figure}
 
+\iffalse
 \begin{figure}[H]
@@
 \end{figure}
-One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff};
-\begin{equation*}
+\fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.475\textwidth]{../../../figures/superfish/superfish107mod_z_highlighted.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{../../../figures/superfish/superfish180mod_z_highlighted.png} }}%
+    \vspace{20pt}
+    \caption{\centering Poisson Superfish calculations with \textit{truncated} cavities.} 
+    \label{fig:180_cavity_shunt_diff}
+\end{figure}
+One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff} as
+\vspace{-10pt}\begin{equation*}
     \begin{aligned}
-        \Delta Z_{107.5}=2.5\%
+        \Delta Z_{107.5}=2.5\%   ,
     \end{aligned}

### 2023-09-18 subsections/design/first_design/first_design.tex
push for sina1

@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
-    \caption{Initial design of the proposed rhodotron \\ $\gamma=9^\circ$}
+    \caption{Initial design of the proposed rhodotron, $\gamma=9^\circ$.}
     \label{fig:initial_design}
 \end{figure}
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:initial_design_cross_section}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Axial cross section]{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst_first_design3.png} }}%
+    \qquad\subfigure[\centering Cross section at acceleration plane]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_first_design2.png} }}%
+    \vspace{20pt}
+    \caption{\centering Initial design of the proposed rhodotron.} 
+    \label{fig:initial_design_cross_section}
 \end{figure}
 The magnets used in this design is the simplest in terms of design parameters. It consists of an iron casing encapsulating the shape of desired magnetic field, which are created by two coils inside.
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:initial_magnet_design}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_first_magnet_design1.png} }}%
+    \qquad\subfigure[\centering ]{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst_first_magnet_design2.png} }}%
+    \vspace{20pt}
+    \caption{\centering Initial magnet design.} 
+    \label{fig:initial_magnet_design}
 \end{figure}
@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_design2.png}
-    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design} \\ $\gamma=15^\circ$}
+    \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design}, $\gamma=15^\circ$.}
     \label{fig:initial_three_magnet_design}
@@
     \label{fig:initial_designs_PIC_phase_space_monitor}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{../../../figures/cst/cst_first_design4.png} }}%
+    \vspace{20pt}\newline
+    \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{../../../figures/cst/cst_second_design3.png} }}%
+    \vspace{20pt}
+    \caption{\centering $|r|$ vs $Energy$ simulation of initial design.} 
+    \label{fig:initial_designs_PIC_phase_space_monitor}
 \end{figure}
@@
     \label{fig:improved_cavity_design}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_sinan_cavity_design1.png} }}%
+    \qquad\subfigure[\centering ]{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst_sinan_cavity_design2.png} }}%
+    \vspace{20pt}
+    \caption{\centering Improved cavity design.} 
+    \label{fig:improved_cavity_design}
 \end{figure}
@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.7\linewidth]{../../../figures/cst/cst_second_magnet_design1.png}
@@
     \label{fig:improved_magnet_design_cross_section}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure{{\includegraphics[width=.475\textwidth]{../../../figures/cst/cst_second_magnet_design2.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.443\textwidth]{../../../figures/cst/cst_second_magnet_design3.png} }}%
+    \vspace{20pt}
+    \caption{\centering Cross section and coils of improved magnet design.} 
+    \label{fig:improved_magnet_design_cross_section}
 \end{figure}
@@
     \centering
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_magnet_design4.png}

### 2023-09-18 subsections/design/magnet/magnet.tex
push for sina1

@@
     \end{subfigure}
-    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}}
+    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}}
+    \label{fig:magnet_design_illustrations}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/Ltot.png} }}%
+    \qquad\subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/tt300_mag.png} }}%
+    \vspace{20pt}
+    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}} 
     \label{fig:magnet_design_illustrations}
@@
     \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
-    \caption{Trejectory of a particle in single pass}
+    \caption{Trejectory of a particle in single pass.}
     \label{fig:magnet_design}

### 2023-09-18 subsections/production/manifacturing/mani.tex
push for sina1

@@
 
+\newcommand{\comment}[1]{}
+
 %----../../..++++.
@@
     \label{fig:manif_polishing}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Bottom part of the cavity while polishing]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{Polishing of the inner surface of cavity.}
+    \label{fig:manif_polishing}
 \end{figure}
 
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_toroidal_sheets}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Bottom part of the cavity with the exposed beam line in inner cylinder]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
+    \label{fig:manif_toroidal_sheets}
 \end{figure}
@@
     \label{fig:manif_welding}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Welding sheet bars]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/welding/rhodo_assembled_welding_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{\centering TIG welding.} 
+    \label{fig:manif_welding}
 \end{figure}
 
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_assembled_flanges}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Beam enter \& exit flanges]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/assembled/rhodo_final_cropped_5.jpeg} }}%
+    \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.48\textwidth]{../../../figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{\centering Flanges on the assembled cavity.} 
+    \label{fig:manif_assembled_flanges}
 \end{figure}

### 2023-09-18 subsections/simulation/gui/gui.tex
push for sina1

@@
 
+Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
+An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
 \begin{figure}[H]
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \includegraphics[width=0.95\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
     \caption{An Illustration of the first GUI design.}
@@
 The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
+The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
+For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
+By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+
+In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. 
+Available frames of this version of the \textit{GUI} are discussed further in the following sections.
+\subsection{Simulation Frame}
+This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
+It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
+
+\newpage
+\subsection{Configuration Frame}
+This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
 \begin{figure}[h]
@@
 \end{figure}
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
 
-In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. This version of the \textit{GUI} has the following frames;
-
-\subsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
-Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\subsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
-Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
-
+\newpage
 \subsection{Render Frame}
@@
 Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
+    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
     \caption{Render frame of \textit{GUI}.}
@@
 Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, \textbf{E} distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
+In the current version, energy distribution histogram and \textit{E(t)} graph of each electron are implementated into this frame.
 This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting \textbf{E} distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
-\begin{figure}
+In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
+    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
     \caption{Analyze frame of \textit{GUI} E distribution.}
@@
 \end{figure}
+
+\newpage
 
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ $\mu E$ result.}
+    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
+    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ $\mu E$ result.}
     \label{fig:gui_sweep_muE}
 \end{figure}
-\begin{figure}
+\newpage
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
-    \caption{Sweep frame of \textit{GUI} \\ $\phi_{lag}$ sweep $\sigma E$ result.}
+    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
+    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ sweep $\sigma E$ result.}
     \label{fig:gui_sweep_sE}

### 2023-09-18 subsections/simulation/intermediate_versions/intermediate.tex
push for sina1

--- 2023-08-17 subsections/simulation/intermediate_versions/intermediate.tex
@@
     \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}\\$P=12$kW, $f=107.5$MHz}
+    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation} $P=40$kW, $f=107.5$MHz.}
+    \label{fig:example_gnuplot_renders}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Unsyncronized \e gun period, $T_g = 5ns$]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/5ns_gnuplot.png}}}%
+    \vspace{15pt}
+    \centering
+    \subfigure[\centering Syncronized \e gun period, $T_g = 9.3ns$]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}}}%
+    \vspace{15pt}
+    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}, $P=40$kW, $f=107.5$MHz.} 
     \label{fig:example_gnuplot_renders}
@@
     \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T}
+    \label{fig:mag_lf_render}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.8\textwidth]{../../../figures/rhodoSim/mag_lf_001dt.png} }}%
+    \vspace{15pt}
+    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.8\textwidth]{../../../figures/rhodoSim/mag_lf_00001dt.png} }}%
+    \vspace{15pt}
+    \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T.}
     \label{fig:mag_lf_render}
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction\\ $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{fig:mag_lf_rk2_comparison}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png} }}%
+    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
+    \vspace{20pt}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
+    \label{fig:mag_lf_rk2_comparison}
 \end{figure}
 The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
-To investigate the data further, one can define a performance measurement, $F$.
-\begin{eqnarray*}
-    F &\propto& 1/T \\
-    F &\propto& 1/\Delta E 
-\end{eqnarray*}
-When $dt=10^-5$ns was taken as reference point due to providing a good balance of accuracy and computational intensity,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV \nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV \nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s \nonumber\\ %0.001
-    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01
-\end{eqnarray}
-Also, observing from the data,
-\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s \nonumber\\ %0.0022
-    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1
-\end{eqnarray}
-Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\begin{equation}
-    F_{LF}/F_{RK} = 1.36 \pm 0.05
-\end{equation}
+To investigate the data further, one can define a performance measurement, $F$ as
+\vspace{-10pt}\begin{eqnarray*}
+    F &\propto& 1/T  , \\
+    F &\propto& 1/\Delta E . 
+\vspace{-10pt}\end{eqnarray*}
+When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
+relative performance can be calculated as
+\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
+    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\nonumber\\
+    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\nonumber\\
+    T_{LF}^1 &=& 9.44 \pm 0.03 s, \nonumber\\
+    T_{RK}^1 &=& 21.33 \pm 0.02 s, \nonumber\\
+    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \nonumber\\ %0.003
+    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \nonumber\\ %0.001
+    F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
+\vspace{-10pt}\end{eqnarray}
+Also, another relative performance can be obsered from the data as
+\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
+    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \nonumber\\
+    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \nonumber\\ %0.0032
+    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \nonumber\\ %0.0022
+    F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
+\vspace{-10pt}\end{eqnarray}
+Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. 
+After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
+\vspace{-10pt}\begin{equation}
+    F_{LF}/F_{RK} = 1.36 \pm 0.05.
+\vspace{-10pt}\end{equation}
 Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
@@
     \caption{Illustration of test setups.}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{../../../figures/illustrations/statE_1.png} }}%
+    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{../../../figures/illustrations/statE_2.png} }}%
+    \vspace{20pt}
+    \caption{Illustration of test setups.}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Render of the test setups. \\ $E_{in}=1$ MeV, $t_{end}=6$ns}
-\end{figure}
-
-\begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+    \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Setup-1, $\textbf{V}_{\parallel}$=4MV]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/statE_par.png} }}%
+    \vspace{15pt}
+    \subfigure[\centering Setup-2, $\textbf{V}_{\perp}$=4MV]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/statE_perp.png} }}%
+    \vspace{15pt}
+    \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns.}
+\end{figure}
+
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \end{subfigure}
-    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction\\ $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ns}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns}
     \label{fig:lf_rk2_perp_stat_E_comparison}
-\end{figure}
-Taking the $dt=10^{-5}$ns for the reference point as before, the relative performance can be calculated.
-\begin{eqnarray*}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.9\textwidth]{../../../figures/analiz/90staticE_lf_rk2_dt-E_3.png} }}%
+    \vspace{15pt}
+    \subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.9\textwidth]{../../../figures/analiz/90staticE_lf_rk2_dt-Tsim.png} }}%
+    \vspace{15pt}
+    \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns.}
+    \label{fig:lf_rk2_perp_stat_E_comparison}
+\end{figure}
+Taking the $dt=10^{-5}$ ns for the reference point as before, using the data
+\vspace{-10pt}\begin{eqnarray*}
     \begin{aligned}
-        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV \\
-        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV \\
-        T_{LF}^1 &=& 12.40 \pm 0.04 s \\
-        T_{RK}^1 &=& 40.08 \pm 0.12 s \\
+        \Delta E_{LF}^1 &=& 22 \times 10^{-6} MeV, \\
+        \Delta E_{RK}^1 &=& 16 \times 10^{-6} MeV, \\
+        T_{LF}^1 &=& 12.40 \pm 0.04 s, \\
+        T_{RK}^1 &=& 40.08 \pm 0.12 s, 
     \end{aligned}
@@
     \centering
-    \captionsetup{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{subfigure}{\textwidth}
@@
     \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e}
+    \caption{$L_{out}$ Optimization For Single \e.}
     \label{fig:lout_opt_single_e}
@@
 \begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{subfigure}{\textwidth}
@@
     \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class}
+    \caption{* and \% operators of \textit{vector3d} class.}
     \label{fig:vector3d_dot_cross_product}
@@
     \end{minted}
-\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
+\caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$.}
 \label{fig:rk1_B}
@@
 \begin{figure}[H]
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \centering
-    \captionsetup{justification=centering}
+    %\captionsetup{justification=centering}
     \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}

### 2023-09-18 subsections/simulation/poc/poc.tex
push for sina1

--- 2023-08-17 subsections/simulation/poc/poc.tex
@@
 % f = 107.5
-\begin{figure}[H]
-    \begin{eqnarray}
-        E_{Pottier} &=& 0.565 MeV \nonumber\\
-        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
-        E_{POC} &=& 0.873 MeV \nonumber
-    \end{eqnarray}
-    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
-\end{figure}
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
-This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+\vspace{-10pt}\begin{eqnarray}
+    E_{Pottier} &=& 0.593 MeV  , \nonumber\\
+    E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
+    E_{POC} &=& 0.532 MeV . \nonumber
+\vspace{-10pt}\end{eqnarray}
+
+As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced similar results; $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
+while \fromeq{W_gain_each_pass_pottier} was noticably different; $\Delta E_{(Pottier-CST)}/E_{CST} \approx 14\%$.
+This inconsistency between \fromeq{W_gain_each_pass_pottier} and  \textit{CST} simulation was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
 Since using a single software would have made the process error prone.

### 2023-09-18 subsections/theory/rhodotron/rhodotron.tex
push for sina1

@@
     \includegraphics[width=.9\textwidth]{../../../figures/kahvelab_linac.png}
-    \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}}
+    \caption{A linear proton accelerator in KAHVELab. \cite{kahvelab_linac}}
 \end{figure}
@@
     \includegraphics[width=.75\textwidth]{../../../figures/pill_box.jpeg}
-    \caption{An RF cavity used in KAHVELab}
+    \caption{An RF cavity used in KAHVELab.}
 \end{figure}
@@
     \label{fig:rhodo_cavity_field_dist}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering $\vecthreeBF{E}$ field]{{\includegraphics[width=0.45\textwidth]{../../../figures/cst/cavity_E_field_dist.png} }}%
+    \qquad\subfigure[\centering $\vecthreeBF{B}$ field]{{\includegraphics[width=0.45\textwidth]{../../../figures/cst/cavity_B_field_dist.png} }}%
+    \vspace{20pt}
+    \caption{$\vecthreeBF{E}$ and $\vecthreeBF{B}$ eigenmode field distributions inside a coaxial cavity.}
+    \label{fig:rhodo_cavity_field_dist}
 \end{figure}
@@
     \includegraphics[width=.6\textwidth]{../../../figures/illustrations/rhodo_integral_curve.pdf}
-    \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}}
+    \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}.}
     \label{fig:int_curve}
 \end{figure}
-Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by the following equation:
-\begin{eqnarray} 
+Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by
+\vspace{-10pt}\begin{eqnarray} 
     V_{acc} &=& 2 \int_{R_1}^{R_2} |E|^2 dr \\
             &=& 2 E_0 \int_{R_1}^{R_2} \frac{dr}{r} \\
-            &=& 2 E_0 \ln(\frac{R_2}{R_1}) \label{eq:v_acc}
-\end{eqnarray}
-Dissipated power $P_{diss}$, on the other hand, can be calculated as follows \cite{rf}:
-\begin{eqnarray} 
+            &=& 2 E_0 \ln(\frac{R_2}{R_1}). \label{eq:v_acc}
+\vspace{-10pt}\end{eqnarray}
+Dissipated power $P_{diss}$, on the other hand, can be calculated as \cite{rf}
+\vspace{-10pt}\begin{eqnarray} 
     P_{diss} &=& \frac{1}{2} \int \int \rho_s | H_{||} |^2 dA \nonumber \\
-             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta \label{eq:p_diss_C_curve}
-\end{eqnarray}
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta . \label{eq:p_diss_C_curve}
+\vspace{-10pt}\end{eqnarray}
 where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
@@
     \includegraphics[width=.9\textwidth]{../../../figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
+    \caption{Optimized characteristics of a rhodotron cavity. \cite{rhodo_pottier}}
     \label{fig:pottier_table1}
@@
     \includegraphics[width=.9\textwidth]{../../../figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
+    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$. \cite{rhodo_pottier}}
     \label{fig:pottier_table2}
 \end{figure}
-Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m}.
-\begin{equation}
+Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m} as
+\vspace{-10pt}\begin{equation}
     \label{eq:W_total_gain_pottier}
-    \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
-\end{equation}
+    \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV .
+\vspace{-10pt}\end{equation}
 
@@
     \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod1.pdf}
-    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
+    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_1}
@@
     \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod2.pdf}
-    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
+    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_2}
@@
     \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod3.pdf}
-    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
+    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_3}
@@
     \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod4.pdf}
-    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
+    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron.}
     \label{fig:rhod_cycle_4}

### 2023-09-18 subsections/tools/numericalmethods/leap-frog-runge-kutta.tex
changes after def
push for sina1

--- 2023-07-02 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
@@
 
-\section{Numerical Integration Methods}
+\section{Algorithms}
 
 \subsection{Leapfrog} \label{sec:leapfrog}
-The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
+The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE can be written as
+\vspace{-10pt}\begin{equation}
+    \ddot{x} = \derivS{x}{t} = f(x) .\label{eq:second-order-ODE}
+\vspace{-10pt}\end{equation}
 
-\begin{equation}
-    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
-\end{equation}
-\newline
 The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space.
@@
 The idea is straight forward; in the time interval $\Delta t$, 
-\begin{eqnarray}
-    a(t_0) &=& f(x_0) \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
-    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
-\end{eqnarray}
-
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
-\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
-    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
-\end{eqnarray}
-
+\vspace{-10pt}\begin{eqnarray}
+    a(t_0) &=& f(x_0)   , \nonumber \\
+    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2}   ,\label{eq:leapfrog_sync_x}\\
+    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2} . \label{eq:leapfrog_sync_v}
+\vspace{-10pt}\end{eqnarray}
+For more stability, this version can be rearranged to what is called 'kick-drift-kick' form as
+\vspace{-10pt}\begin{eqnarray} \label{eq:leapfrog}
+    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2}   , \nonumber \\
+    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t   , \\
+    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2} . \nonumber
+\vspace{-10pt}\end{eqnarray}
 This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
 
-\subsection{Runge Kutta}
+\subsection{Runge Kutta} \label{sec:rungekutta}
 
-The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
-used to solve ordinary differential equations (ODEs) that are in the following form
-
-\begin{equation} \label{eq:first-order-ODE}
-    \parDeriv{y}{x} = f(x, y)
-\end{equation}
-
+The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta \cite{runge} \cite{kutta}, 
+family of numerical methods
+used to solve ordinary differential equations (ODEs) that are in the form as
+\vspace{-10pt}\begin{equation} \label{eq:first-order-ODE}
+    \deriv{y}{x} = f(x, y) .
+\vspace{-10pt}\end{equation}
 The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
-of function evaluations at different points within each step.
-
-\begin{equation} \label{eq:general-rk}
+of function evaluations at different points within each step as
+\vspace{-10pt}\begin{equation} \label{eq:general-rk}
     \begin{aligned}
-        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
+        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i  ,
     \end{aligned}
@@
     \begin{aligned}
-        x_{n+1} = x_n + \delta x 
+        x_{n+1} = x_n + \delta x   ,
     \end{aligned}
-\end{equation}
-
+\vspace{-10pt}\end{equation}
 where 
-
-\begin{eqnarray} \label{eq:general-rk-coef}
-    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
-\end{eqnarray}
-
-These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
-
+\vspace{-10pt}\begin{eqnarray} \label{eq:general-rk-coef}
+    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j) .
+\vspace{-10pt}\end{eqnarray}
+These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a particular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
+The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$ which can be observed in \fromfig{Butcher}.
 \begin{figure}[h!]
@@
     \]
-    \caption{Butcher Tableau}
+    \caption{Butcher Tableau.}
     \label{fig:Butcher}
 \end{figure}
-
-The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
-
+The simplest Runge-Kutta method is the \textit{Euler's method} with the following \textit{Butcher tableau},
 \[ 
@@
         & 1
-    \end{array}
+    \end{array} .
 \]
@@
 The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
+Two of the most used \textit{Butcher tableaus} for \textit{RK4} given in \fromfig{Butcher-RK4}.
+The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
+Its main advantage is that its error coefficients are smaller than the other.
+But it costs more floating point operations per step.
+Resulting in slower calculations.
 
@@
     \centering
-    \begin{subfigure}{.5\textwidth}
+    \begin{minipage}{.5\textwidth}
         \[ 
@@
         \]  
-    \end{subfigure}
-    \caption{Butcher Tableau for RK4}
+    \end{minipage}
+    \vspace{20pt}
+    \caption{Butcher Tableau for RK4.}
     \label{fig:Butcher-RK4}
 \end{figure}
-
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
-Its main advantage is that its error coefficients are smaller than the other.
-But it costs more floating point operations per step.
-Resulting in slower calculations.
 

### 2023-09-19 msthesis.tex
enstitü versiyonu

@@
 %\examinerv{}
-\dateofapproval{DD.MM.YYYY}
+\dateofapproval{29.08.2023}
 
@@
 % ACK PAGE
-\begin{acknowledgements}
-Acknowledgements come here...
-\end{acknowledgements}
+%\begin{acknowledgements}
+%Acknowledgements come here...
+%\end{acknowledgements}
 
@@
 \begin{eqnarray}
-    \deriv{\vecthree{p}}{t} &=& m_0 \deriv{(\gamma \vecthree{v})}{t} = m_0 \{  \deriv{\gamma}{t}\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}   ,  \} \\
+    \deriv{\vecthree{p}}{t} &=& m_0 \deriv{(\gamma \vecthree{v})}{t} = m_0 \{  \deriv{\gamma}{t}\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}   \} ,\\
     \deriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\deriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a}   , \\
@@
 \begin{eqnarray}
-    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
+    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \nonumber\\
                                 &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} .
@@
 \begin{eqnarray}
-    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
-                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
-                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
+    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \nonumber\\
+                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \nonumber\\
+                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \nonumber\\
+                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \nonumber\\
                     &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp} .
@@
 \vspace{-10pt}
-\begin{eqnarray*}
-    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
-                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
+\begin{eqnarray}
+    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \nonumber \\
+                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \nonumber\\
+                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \nonumber\\
+                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \nonumber\\
                                 &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} .
                                 \vspace{-10pt}
-\end{eqnarray*}
+\end{eqnarray}
 Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
@@
     \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
+    \vspace{20pt}
     \caption{An RF cavity used in KAHVELab.}
@@
 \begin{itemize}
-    \item \textit{First Acceleration:} Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
-(\fromfig{rhod_cycle_1})
-    \item \textit{Inner Shielding:} Inner shielding While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
-(\fromfig{rhod_cycle_2})
-    \item \textit{Second Acceleration:} Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
-(\fromfig{rhod_cycle_3})
-    \item \textit{Recirculating Magnets:} After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
-(\fromfig{rhod_cycle_4})
+    \item \textit{First Acceleration:} Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity (\fromfig{rhod_cycle_1}).
+    \item \textit{Inner Shielding:} Inner shielding While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed (\fromfig{rhod_cycle_2}).
+    \item \textit{Second Acceleration:} Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity (\fromfig{rhod_cycle_3}).
+    \item \textit{Recirculating Magnets:} After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again (\fromfig{rhod_cycle_4}).
 \end{itemize}
@@
 Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
-Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest. (\fromfig{rhodo_cavity_field_dist})
+Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest (\fromfig{rhodo_cavity_field_dist}).
 
@@
 \vspace{-10pt}\begin{eqnarray}
-    E &=& \frac{E_0}{r} \cos(\frac{\pi z}{h}) \sin(\omega t + \phi)  , \\
-    B &=& \frac{B_0}{r} \sin(\frac{\pi z}{h}) \cos(\omega t + \phi)  ,
+    E &=& \frac{E_0}{r} \cos\left( \frac{\pi z}{h} \right) \sin \left( \omega t + \phi \right)  , \\
+    B &=& \frac{B_0}{r} \sin\left( \frac{\pi z}{h}\right) \cos\left( \omega t + \phi\right)  ,
 \vspace{-10pt}\end{eqnarray}
@@
     \includegraphics[width=.6\textwidth]{./figures/illustrations/rhodo_integral_curve.pdf}
+    \vspace{20pt}
     \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}.}
@@
 \end{figure}
+
 Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by
 \vspace{-10pt}\begin{eqnarray} 
-    V_{acc} &=& 2 \int_{R_1}^{R_2} |E|^2 dr \\
-            &=& 2 E_0 \int_{R_1}^{R_2} \frac{dr}{r} \\
+    V_{acc} &=& 2 \int_{R_1}^{R_2} |E|^2 dr \nonumber\\
+            &=& 2 E_0 \int_{R_1}^{R_2} \frac{dr}{r} \nonumber\\
             &=& 2 E_0 \ln(\frac{R_2}{R_1}). \label{eq:v_acc}
@@
 \vspace{-10pt}\end{eqnarray}
+\clearpage
 where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
@@
 \vspace{-10pt}\begin{eqnarray}
-    Z_s &=& \frac{4E_0^2}{H_0^2 \pi \rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{2R_1} + \frac{h}{2R_2} + 2 \ln(\frac{R_2}{R_1}))} \\
+    Z_s &=& \frac{4E_0^2}{H_0^2 \pi \rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{2R_1} + \frac{h}{2R_2} + 2 \ln(\frac{R_2}{R_1}))} \nonumber\\
         &=& \frac{8 \pi 60^2}{\rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{4}(\frac{1}{R_1} + \frac{1}{R_2}) + \ln(\frac{R_2}{R_1}))}   ,
@@
 \vspace{-10pt}\begin{eqnarray}
-    \Delta E &=& q V_{acc}^{ef} \\
+    \Delta E &=& q V_{acc}^{ef} \nonumber\\
              &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)  ,
-\vspace{-10pt}\end{eqnarray}
+\vspace{-20pt}\end{eqnarray}
 where $ V_{acc}^{ef} = V_{acc} T(\phi)$ is the effective accelerating potential.
@@
 \vspace{-10pt}\end{equation}
+
 With the expectation that the electrons will accelerate to speeds $\approx c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
 This constraint helps with  phase stability and synchronization of the beam.
-
 In the \fromfig{pottier_table1}, optimized characteristics of a rhodotron cavity can be observed. 
@@
 Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
+\vspace{20pt}
 \begin{figure}[h!]
     \centering
-    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
-\end{figure}
+    \includegraphics[width=.95\textwidth]{./figures/cpu_instruction_speed.png}
+    \vspace{20pt}
+    \caption{Amount of clock cycle for mathematical operations in various processors \cite{cpu_instruction_speed}.}
+\end{figure}
+
 Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
 Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
@@
 \vspace{-10pt}\begin{eqnarray}
-    a(t_0) &=& f(x_0)   , \nonumber \\
+    a(t_0) &=& f(x_0)   , \\
     x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2}   ,\label{eq:leapfrog_sync_x}\\
@@
 \vspace{-10pt}\begin{eqnarray} \label{eq:leapfrog}
-    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2}   , \nonumber \\
+    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2}   ,  \\
     x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t   , \\
-    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2} . \nonumber
+    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2} . 
 \vspace{-10pt}\end{eqnarray}
@@
 \fi
+\vspace{20pt}
 \begin{figure}[H]
@@
     \label{fig:107_simple_cavity_design}
+    \vspace{20pt}
 \end{figure}
@@
     \label{fig:180_simple_cavity_design}
+    \vspace{20pt}
 \end{figure}
@@
     \vspace{20pt}
-    \caption{\centering Poisson SUPERFISH field results of truncated cavities.} 
+    \caption{\centering Poisson Superfish field results of truncated cavities.} 
     \label{fig:107_180_modified_cavities_superfish}
+    \vspace{20pt}
 \end{figure}
@@
     \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.485\textwidth]{./figures/superfish/superfish107_z_highlighted.png} }}%
-    \qquad\subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{./figures/superfish/superfish180_z_highlighted.png} }}%
+    \vspace{20pt}
+    \subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{./figures/superfish/superfish180_z_highlighted.png} }}%
     \vspace{20pt}
@@
     \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.475\textwidth]{./figures/superfish/superfish107mod_z_highlighted.png} }}%
-    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{./figures/superfish/superfish180mod_z_highlighted.png} }}%
+    \vspace{20pt}
+    \subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{./figures/superfish/superfish180mod_z_highlighted.png} }}%
     \vspace{20pt}
@@
 One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff} as
-\vspace{-10pt}\begin{equation*}
+\vspace{-10pt}\begin{equation}
     \begin{aligned}
@@
     \end{aligned}
-\vspace{-10pt}\end{equation*}
+\vspace{-10pt}\end{equation}
 
@@
     \end{subfigure}
-    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}}
+    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.}
     \label{fig:magnet_design_illustrations}
 \end{figure} \fi
+\vspace{20pt}
 \begin{figure}[H]
@@
     \vspace{20pt}
-    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}} 
+    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.} 
     \label{fig:magnet_design_illustrations}
@@
     \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
+    \vspace{20pt}
     \caption{Trejectory of a particle in single pass.}
@@
 \end{figure}
+\clearpage
 From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
@@
 \vspace{-10pt}\begin{eqnarray}
-    L_{in} &=& 2R_2   , \nonumber\\
-    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho  , \nonumber \\
-    L_{pass} &=& L_{in} + L_{out}  ,  \nonumber \\
+    L_{in} &=& 2R_2   , \\
+    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho  , \\
+    L_{pass} &=& L_{in} + L_{out}  ,   \\
     \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho . \label{eq:magnet_lambda_constraint}
-\vspace{-10pt}\end{eqnarray}
+\vspace{-20pt}\end{eqnarray}
+
 After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
@@
 \vspace{-10pt}\begin{eqnarray}
-    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  , \nonumber \\
-    \rho &=&  \tan (\gamma) (R_2 + d + L)  , \nonumber\\
-    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho)  , \nonumber\\
-    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda   ,\nonumber\\
+    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  ,\\
+    \rho &=&  \tan (\gamma) (R_2 + d + L)  , \\
+    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho)  , \\
+    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda   ,\\
     \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}}   ,\label{eq:magnet_rho_constraint} \\
     L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 . \label{eq:magnet_L_constraint}
-\vspace{-10pt}\end{eqnarray}
+\vspace{-20pt}\end{eqnarray}
 
@@
 it can be observed that
-\vspace{-10pt}\begin{eqnarray*}
+\vspace{-10pt}\begin{eqnarray}
     W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV   ,\\
@@
     \beta_{394keV} &\approx& 0.825 .
-\vspace{-10pt}\end{eqnarray*}
+\vspace{-20pt}\end{eqnarray}
 It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
@@
 Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\vspace{-10pt}\begin{eqnarray*}
+\vspace{-10pt}\begin{eqnarray}
     L_{pass} &=& K ,\\
     L_{in} + L_{out} &=& K .
-\vspace{-10pt}\end{eqnarray*}
+\vspace{-20pt}\end{eqnarray}
 Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
@@
 \vspace{-10pt}\end{equation}
+\clearpage
 To start, an optimization criteria for the following pass such as
+\vspace{-10pt}
 \begin{itemize}
@@
     \item All of the above with decided weights
-\end{itemize}
+\vspace{-10pt}\end{itemize}
 needs be selected.
@@
     \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
+    \vspace{20pt}
     \caption{Initial design of the proposed rhodotron, $\gamma=9^\circ$.}
@@
 \end{figure} \fi
+\vspace{20pt}
 \begin{figure}[H]
@@
     \centering
-    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_first_magnet_design1.png} }}%
-    \qquad\subfigure[\centering ]{{\includegraphics[width=.46\textwidth]{./figures/cst/cst_first_magnet_design2.png} }}%
+    \subfigure{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_first_magnet_design1.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.46\textwidth]{./figures/cst/cst_first_magnet_design2.png} }}%
     \vspace{20pt}
@@
 \end{figure}
-
+\vspace{20pt}
 \begin{figure}[H]
@@
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
+    \vspace{20pt}
     \caption{Magnetic field in acceleration plate of initial magnet design.}
@@
 \end{figure}
+\clearpage
 \fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
+After adding two more magnets and using $\gamma=15^\circ$, the second prototype design was created (\fromfig{initial_three_magnet_design}).
+
 \begin{figure}[H]
@@
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
+    \vspace{20pt}
     \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design}, $\gamma=15^\circ$.}
@@
     \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_first_design4.png} }}%
-    \vspace{20pt}\newline
+    \vspace{20pt}
     \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_second_design3.png} }}%
@@
 \end{figure} \fi
-\begin{figure}[H]
-    \centering
-    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_sinan_cavity_design1.png} }}%
-    \qquad\subfigure[\centering ]{{\includegraphics[width=.47\textwidth]{./figures/cst/cst_sinan_cavity_design2.png} }}%
+\vspace{20pt}
+\begin{figure}[H]
+    \centering
+    \subfigure{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_sinan_cavity_design1.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.47\textwidth]{./figures/cst/cst_sinan_cavity_design2.png} }}%
     \vspace{20pt}
@@
     \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
+    \vspace{20pt}
     \caption{Improved magnet design.}
@@
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
+    \vspace{20pt}
     \caption{Magnetic field in acceleration plate of improved magnet design.}
@@
 \section{Proof of Concept}
-The POC worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
-Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
+The proof of concept (POC) worked with interacting an electron with the EM field provided, at discrete time steps $dt$. 
+The core sequence of this software is provided below and the implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
+Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$:
 \begin{itemize}
@@
 \end{itemize}
-The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
+\clearpage
 \begin{figure}[H]
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Core logic loop of the POC.}
@@
 \end{figure}
+
 After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} 
@@
 \vspace{-10pt}\begin{eqnarray}
-    E_{Pottier} &=& 0.593 MeV  , \nonumber\\
+    E_{Pottier} &=& 0.593 MeV  , \\
     E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
-    E_{POC} &=& 0.532 MeV . \nonumber
-\vspace{-10pt}\end{eqnarray}
+    E_{POC} &=& 0.532 MeV . 
+\vspace{-20pt}\end{eqnarray}
 
@@
 This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
-
+\clearpage
 Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
@@
 To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as
-\begin{itemize}
+\vspace{-10pt}\begin{itemize}
     \item $\mu E$: Average energy,
@@
 \end{itemize}
+
 Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
@@
 For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
+\vspace{20pt}
 \begin{figure}[H]
@@
     \end{minted}
+    \vspace{20pt}
     \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
@@
 \end{figure}
+\clearpage
 Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
@@
 
-Interaction logic for \eE and \eB in 3D can be found in \fromfig{3D_e_EM_interaction_first}.
+Implementations for \eE and \eB interactions in 3D can be found in \fromfigs{3D_e_E_interaction_first}{3D_e_B_interaction_first}, 
+where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
 \iffalse \begin{figure}[H]
@@
 \end{figure} \fi
+\iffalse \vspace{20pt}
 \begin{figure}[H]
@@
     \end{minipage}
+    \vspace{20pt}
     \caption{\eEM  interaction logic from \fromeq{acc_of_E_and_B}.}
     \label{fig:3D_e_EM_interaction_first}
-\end{figure}
-Where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+\end{figure}\fi
+\begin{figure}[H]
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        vector3d CoaxialRFField::actOn(Electron& e){
+            vector3d Efield = getField(e.pos);                        // Calculate E vector
+            vector3d F_m = Efield*1E6*eQMratio;                       // Calculate F/m vector
+            vector3d acc = (F_m - e.vel*(e.vel*F_m)/(c*c))/e.gamma(); // Calculate a vector
+            return acc;
+        }
+    \end{minted}
+    \vspace{20pt}
+    \caption{\eE interaction logic from \fromeq{acc_of_E_and_B}.}
+    \label{fig:3D_e_E_interaction_first}
+\end{figure}
+\vspace{20pt}
+\begin{figure}[H]
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+            vector3d MagneticField::actOn(Electron& e){
+                if (isInside(e.pos) == -1)
+                    return vector3d(0,0,0);
+                vector3d Bfield = getField(e.pos);                        // Calculate B vector
+                vector3d F_m = (e.vel % Bfield)*eQMratio;                 // Calculate F/m vector
+                vector3d acc = (F_m)/e.gamma();                           // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \vspace{20pt}
+    \caption{\eB interaction logic from \fromeq{acc_of_E_and_B}.}
+    \label{fig:3D_e_B_interaction_first}
+\end{figure}
 
@@
 \textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
-
-More rigerous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
-Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
-Results from these tests can be observed in \fromfig{mag_lf_rk2_comparison}.
+\clearpage
 \iffalse \begin{figure}
@@
 \end{figure} \fi
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 \end{figure}
-The data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
+More rigorous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
+Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
+
+Example renders from these tests can be observed in \fromfig{mag_lf_rk2_comparison} and
+the data from these tests can be found in \fromtabs{lf_mag_table}{rk2_mag_table} of \fromapp{data_graph}.
 To investigate the data further, one can define a performance measurement, $F$ as
-\vspace{-10pt}\begin{eqnarray*}
+\vspace{-10pt}\begin{eqnarray}
     F &\propto& 1/T  , \\
     F &\propto& 1/\Delta E . 
-\vspace{-10pt}\end{eqnarray*}
+\vspace{-10pt}\end{eqnarray}
 When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
@@
 \vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
-    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\nonumber\\
-    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\nonumber\\
-    T_{LF}^1 &=& 9.44 \pm 0.03 s, \nonumber\\
-    T_{RK}^1 &=& 21.33 \pm 0.02 s, \nonumber\\
-    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \nonumber\\ %0.003
-    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \nonumber\\ %0.001
+    \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\\
+    \Delta E_{RK}^1 &=& 64 \times 10^{-5} MeV,\\
+    T_{LF}^1 &=& 9.44 \pm 0.03 s, \\
+    T_{RK}^1 &=& 21.33 \pm 0.02 s, \\
+    \Delta E_{LF} \times T_{LF} &=& 104 \times 10^{-4} \pm 10^{-4} MeV s, \\ %0.003
+    \Delta E_{RK} \times T_{RK} &=& 137 \times 10^{-4} \pm 2\times 10^{-4}  MeV s, \\ %0.001
     F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
@@
 \vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
-    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \nonumber\\
-    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \nonumber\\ %0.0032
-    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \nonumber\\ %0.0022
+    \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \\
+    T_{LF}(dt=3 \times 10^{-5})  &=& 3.18 \pm 0.02 s, \\ %0.0032
+    T_{RK}(dt=5 \times 10^{-5})  &=& 4.30 \pm 0.01 s, \\ %0.0022
     F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
@@
 \end{figure}
+\clearpage
 In the first test, the beam would be injected into a static uniform electric field \\
 $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
-
-Considering the $\vecthreeBF{E}$ is parallel to the beam path, potential difference $V$ in the trejectory until \vecNum{-0.753}{0}{0}m is
+Considering the $\vecthreeBF{E}$ is parallel to the beam path, beam energy at exit can be calculated as
 \vspace{-10pt}\begin{eqnarray}
-    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \\
-             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \\
-             &=& 2.65616 \times 1.506 \\
+    \Delta V^1 &=& - \int \dotProdBF{E}{ds} \nonumber\\
+             &=& - \int_{-0.753}^{0.753} -2.65616 \times dx \nonumber\\
+             &=& 2.65616 \times 1.506 \nonumber\\
              &=& 4 MV, \\
@@
 $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m where $-0.753<x<0.753$ and $-0.753<y<0.753$, $\vecthreeBF{E}=0$ elsewhere.
+Beam energy at exit can be calculated as
 \vspace{-10pt}\begin{eqnarray}
-    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \\
-                 &=& - \int_{0}^{0.753} -5.31232 \times dy \\
-                 &=& 5.31232 \times 0.753 \\
+    \Delta V^2   &=& - \int \dotProdBF{E}{ds} \nonumber \\
+                 &=& - \int_{0}^{0.753} -5.31232 \times dy \nonumber \\
+                 &=& 5.31232 \times 0.753 \nonumber \\
                  &=& 4 MV, \\
@@
     \end{aligned}
-\vspace{-10pt}\end{eqnarray*}
+\vspace{-20pt}\end{eqnarray*}
 the relative performances can be calculated as
 \vspace{-10pt}\begin{eqnarray} 
-    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s, \nonumber\\ %0.003
-    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s, \nonumber\\ %0.003
+    \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s, \\ %0.003
+    \Delta E_{RK}^1 \times T_{RK}^1 &=& 640 \times 10^{-6} \pm 2\times 10^{-6}  MeV s, \\ %0.003
     F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02, \label{eq:f_lf_rk_1}
-\vspace{-10pt}\end{eqnarray}
+\vspace{-20pt}\end{eqnarray}
 and
 \vspace{-10pt}\begin{eqnarray}  
-    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s, \nonumber\\ %0.004
-    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s, \nonumber\\ %0.011
+    \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s, \\ %0.004
+    \Delta E_{RK}^2 \times T_{RK}^2 &=& 320 \times 10^{-5} 4 \pm 10^{-5} MeV s, \\ %0.011
     F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03. \label{eq:f_lf_rk_2}
@@
 \vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_3}
-    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV, \nonumber\\
-    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s, \nonumber\\ %0.0032
-    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s, \nonumber\\ %0.0022
+    \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV, \\
+    T_{LF}^1(dt=2 \times 10^{-5})  &=& 6.23 \pm 0.02 s, \\ %0.0032
+    T_{RK}^1(dt=3 \times 10^{-5})  &=& 13.40 \pm 0.03 s, \\ %0.0022
     F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02,
@@
 \vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_4}
-    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV, \nonumber\\
-    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62, \nonumber\\ %0.0055
-    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00, \nonumber\\ %0.0071 -> 0,0126
+    \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV, \\
+    T_{LF}^2(dt=3 \times 10^{-5})  &=& 3.62, \\ %0.0055
+    T_{RK}^2(dt=5 \times 10^{-5})  &=& 7.00, \\ %0.0071 -> 0,0126
     F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1.
@@
 After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
+
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
+    \vspace{20pt}
+    \caption{An Illustration of the multithreading architecture.}
+    \label{fig:multh_illustration}
+\end{figure}
+
 Focus of this section is the worker threads, also known as \eEM interaction threads.
@@
 \begin{itemize}
-    \item \textit{Architecture 1:} Have a thread pool that calculates \eEM in a queue 
-    \item \textit{Architecture 2:} Assign a thread to each bunch
-    \item \textit{Architecture 3:} A ssign random electrons to each thread and calculate \eEM with global time
-    \item \textit{Architecture 4:} Assign random electrons to each thread and calculate \eEM with local thread time
+    \item \textit{Architecture 1:} Have a thread pool that calculates \eEM in a queue. 
+    \item \textit{Architecture 2:} Assign a thread to each bunch.
+    \item \textit{Architecture 3:} A ssign random electrons to each thread and calculate \eEM with global time.
+    \item \textit{Architecture 4:} Assign random electrons to each thread and calculate \eEM with local thread time.
 \end{itemize}
@@
 \textit{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
-
+\clearpage
 \textit{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
@@
 
-The implemenation can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
+The implemenation of multithreading can be found in \fromfigf{_runMT}{fireAllWithFireTimesMT}{setupPool}{threadLoop} in \fromapp{intermediate_codes}.
 
@@
     \centering
-    \includegraphics[width=0.95\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \vspace{20pt}
     \caption{An Illustration of the first GUI design.}
@@
 
-\newpage
 \subsection{Configuration Frame}
@@
 Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
+
+\clearpage
 \begin{figure}[h]
@@
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
+    \vspace{20pt}
     \caption{The configuration frame of implementated first GUI design.}
@@
 
-\newpage
+\clearpage
 \subsection{Render Frame}
@@
     \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_3.png}
+    \includegraphics[width=0.9\linewidth]{./figures/rhodoSim/GUI_analyze_Et_3.png}
     \caption{Analyze frame of \textit{GUI} E(t).}
@@
 \end{figure}
-
-\newpage
 
@@
 \end{figure}
-\newpage
+\clearpage
 \begin{figure}[h]
@@
 \section{Final Design} \label{sec:final_design}
-In the following figures, rendered visuals of the final design can be observed \cite{sinan}.
+In the \fromfigf{fin_rend_lab}{fin_rend_cav_egun}{fin_rend_cs_bil}{fin_rend_cs_ap}, 
+rendered visuals of the final design can be observed \cite{sinan}.
+\vspace{20pt}
 \begin{figure}[H]
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
+    \vspace{10pt}
     \caption{Rhodotron in KAHVELab.}
+    \label{fig:fin_rend_lab}
 \end{figure}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
+    \vspace{20pt}
     \caption{Rhodotron cavity and \e gun.}
+    \label{fig:fin_rend_cav_egun}
 \end{figure}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
+    \vspace{20pt}
     \caption{Vertical cross section of the beam injection line.}
+    \label{fig:fin_rend_cs_bil}
 \end{figure}
@@
     \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
+    \vspace{20pt}
     \caption{Cross section of the acceleration plane.}
+    \label{fig:fin_rend_cs_ap}
 \end{figure}
@@
 Technical drawings of the design mentioned in \fromsec{final_design} can be found in \fromfigs{techd_rhod}{techd_mid}, \fromfig{techd_up} of \fromapp{supp}.
+
 \begin{figure}
     \centering
-    \includegraphics[angle=270,origin=c, width=.98\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
-    \caption{Technical drawing of the rhodotron cavity. \cite{sinan}}
+    \includegraphics[angle=270,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
+    \vspace{20pt}
+    \caption{Technical drawing of the rhodotron cavity \cite{sinan}.}
     \label{fig:techd_rhod}
@@
     \centering
-    \includegraphics[angle=270,origin=c, width=\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \caption{Technical drawing of middle part of the cavity which contains the beam line. \cite{sinan}}
+    \includegraphics[angle=270,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \vspace{20pt}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line \cite{sinan}.}
     \label{fig:techd_mid}
@@
 \end{figure} \fi
+
 \begin{figure}
     \centering
-    \subfigure[\centering Bottom part of the cavity while polishing]{{\includegraphics[width=.48\textwidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg} }}%
-    \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.48\textwidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
+    \subfigure[\centering Bottom part of the cavity while polishing]{{\includegraphics[width=.46\textwidth]{./figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.46\textwidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
     \vspace{20pt}
@@
     \centering
-    \subfigure[\centering Bottom part of the cavity with the exposed beam line in inner cylinder]{{\includegraphics[width=.48\textwidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg} }}%
-    \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.48\textwidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
+    \subfigure[\centering Bottom part of the cavity with the exposed beam line in inner cylinder]{{\includegraphics[width=.46\textwidth]{./figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.46\textwidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
     \vspace{20pt}
@@
     \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
+    \vspace{20pt}
     \caption{Welded sheet bars.}
@@
     \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
+    \vspace{20pt}
     \caption{Middle part of the cavity containing the beam line.}
@@
     \centering
-    \subfigure[\centering Welding sheet bars]{{\includegraphics[width=.48\textwidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg} }}%
-    \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.48\textwidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
+    \subfigure[\centering Welding sheet bars]{{\includegraphics[width=.46\textwidth]{./figures/manif/welding/rhodo_assembled_welding_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.46\textwidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
     \vspace{20pt}
@@
     \centering
-    \subfigure[\centering Beam enter \& exit flanges]{{\includegraphics[width=.48\textwidth]{./figures/manif/assembled/rhodo_final_cropped_5.jpeg} }}%
-    \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.48\textwidth]{./figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
+    \subfigure[\centering Beam enter \& exit flanges]{{\includegraphics[width=.46\textwidth]{./figures/manif/assembled/rhodo_final_cropped_5.jpeg} }}%
+    \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.46\textwidth]{./figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
     \vspace{20pt}
@@
     \includegraphics[width=.9\linewidth]{./figures/manif/assembled/rhodo_final_cropped.jpeg}
+    \vspace{20pt}
     \caption{Current stage of the cavity.}
@@
 \textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
-Several improvements and new feature implementations are underway in the meantime. 
-They include the following;
+Several improvements and new feature implementations are underway in the meantime:
 \iffalse \begin{figure}[H]
@@
     \end{minipage}
-\end{figure}
+\vspace{-10pt}\end{figure}
 
@@
     \\
+    \vspace{10pt}
     \begin{minipage}{\textwidth}
@@
     \end{minipage}
+    \vspace{20pt}
     \caption{$L_{out}$ Optimization For Single \e.}
@@
         \end{minted}
+    \vspace{20pt}
     \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
@@
     \end{minipage}
-
+    \vspace{10pt}
     \begin{minipage}{\textwidth}
@@
     \end{minipage}
+    \vspace{20pt}
     \caption{* and \% operators of \textit{vector3d} class.}
     \label{fig:vector3d_dot_cross_product}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
-        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
-            vector3d relative = e_position - hs_position;       
-            // r/5 can be changed, use this for now                                
-            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
-                return true;                                                                 
-            }
-            return false;
-        }
-    \end{minted}
-\caption{Logic of is \e inside the shape of magnet.}
-\label{fig:is_inside_halfsphere}
 \end{figure}
@@
     \end{minted}
+    \vspace{20pt}
 \caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
@@
 \end{figure}
+\clearpage
+\begin{figure}[H]
+    \centering
+    %\captionsetup{justification=centering}
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
+            vector3d relative = e_position - hs_position;       
+            // r/5 can be changed, use this for now                                
+            if ( relative.magnitude() <= r && relative * hs_position.direction() >= -r/5){      
+                return true;                                                                 
+            }
+            return false;
+        }
+    \end{minted}
+    \vspace{20pt}
+\caption{Logic of is \e inside the shape of magnet.}
+\label{fig:is_inside_halfsphere}
+\end{figure}
+\vspace{20pt}
 \begin{figure}[H]
@@
     \end{minted}
+    \vspace{20pt}
 \caption{RK4-1 implemenation of \eEM.}
@@
     \end{minted}
+    \vspace{20pt}
 \caption{RK4-2 implemenation of \eEM.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Multithreading main-thread logic.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Multithreading electron assign logic.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Multithreading worker-threads setup logic.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Multithreading worker-thread logic.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{UI-Console handler thread logic.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Electron class definition.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Bunch class definition.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{Gun class definition.}
@@
             vector<vector<DataStorage>> pathsStorage;
-            std::string configPath;
-            std::string pathsPath;
-            std::string EfieldLogHeader;
-            std::string BfieldLogHeader;
-            std::string eLogHeader;
+            std::string configPath, pathsPath;
+            std::string EfieldLogHeader, BfieldLogHeader, eLogHeader;
 
             double simulation_time = 0;
-            double dummy_time = 0;
             double start_time = 0;
@@
             unsigned int MAX_THREAD_COUNT = 1;
-            bool MULTI_THREAD = false;
         public:
@@
             void setNumberofBunchs(uint64_t num_of_bunchs);
-            void setStartTime(double starttime);
-            void setEndTime(double end_time);
+            void setSimTime(double starttime, double endtime);
             void setGunActiveTime(double gun_ns);
@@
     \end{minted}
+    \vspace{10pt}
     \caption{Simulator class definition.}
@@
     \end{minted}
+    \vspace{20pt}
     \caption{RhodotronSimulator class definition.}
@@
     \end{minipage}
+    \vspace{20pt}
     \caption{CoaxialRFField class definition.}
@@
     \end{minted}
-\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at $P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV.}
+    \vspace{20pt}
+\caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at $P=30$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV.}
 \label{fig:lout_opt_1ns_Erms}
@@
     \end{minted}
-\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at $P=12$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV.}
+    \vspace{20pt}
+\caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at $P=30$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV.}
 \label{fig:lout_opt_08ns_Erms}
@@
     \centering
-    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=1.047$MeV]{{\includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_001dt.png} }}%
+    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=1.047$MeV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/mag_rk_001dt.png} }}%
     \vspace{20pt}\newline
-    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.006$MeV]{{\includegraphics[width=\linewidth]{./figures/rhodoSim/mag_rk_00001dt.png} }}%
+    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.006$MeV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/mag_rk_00001dt.png} }}%
     \vspace{20pt}
@@
     \end{minted}
+    \vspace{20pt}
 \caption{An example \textit{config.in} file.}
@@
     \end{minted}
+    \vspace{20pt}
 \caption{Example of console output while simulation is running.}
@@
 \end{figure} \fi
-\begin{figure}
-    \centering
-    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png} }}%
-    \vspace{20pt}\newline
-    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png} }}%
+\begin{figure}[H]
+    \centering
+    \subfigure{{\includegraphics[width=0.8\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png} }}%
+    \vspace{20pt}
+    \subfigure{{\includegraphics[width=0.8\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png} }}%
     \vspace{20pt}
@@
 \end{figure}\fi 
-\begin{figure}
-    \centering
-    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png} }}%
-    \vspace{20pt}\newline
-    \subfigure{{\includegraphics[width=\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}}}%
+\begin{figure}[H]
+    \centering
+    \subfigure{{\includegraphics[width=0.9\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png} }}%
+    \vspace{20pt}
+    \subfigure{{\includegraphics[width=0.9\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}}}%
     \vspace{20pt}
@@
     \caption{\textit{Leap-frog} data on $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
+    \vspace{10pt}
     \begin{tabular}{|l|l|l|l|}
@@
     \caption{\textit{RK4-2} data on $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
+    \vspace{10pt}
     \begin{tabular}{|l|l|l|l|}
@@
     \caption{\textit{LF} data on $E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns.}
+    \vspace{10pt}
     \begin{tabular}{|l|l|l|l|}
@@
     \caption{\textit{RK4-2} data on $E_{in}=1$MeV, $\vecthreeBF{E}=(-2.65616, 0, 0)$ MV/m, $t_{end}=6$ns.}
+    \vspace{10pt}
     \begin{tabular}{|l|l|l|l|}
@@
     \caption{\textit{LF} data on $E_{in}=1$MeV, $\vecthreeBF{E}=(0, -5.31232, 0)$ MV/m, $t_{end}=6$ns.}
+    \vspace{10pt}
     \begin{tabular}{|l|l|l|l|}
@@
 \chapter{Supporting Figures} \label{appendix:supp}
-\begin{figure}
-    \centering
-    \includegraphics[angle=270,origin=c, width=.9\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
-    \caption{Technical drawing of upper part of the cavity. \cite{sinan}}
+\begin{figure}[H]
+    \centering
+    \includegraphics[angle=270,origin=c, width=.8\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
+    \vspace{20pt}
+    \caption{Technical drawing of upper part of the cavity \cite{sinan}.}
     \label{fig:techd_up}

### 2023-09-19 subsections/design/cavity/cavity.tex
enstitü versiyonu

@@
     \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.485\textwidth]{../../../figures/superfish/superfish107_z_highlighted.png} }}%
-    \qquad\subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{../../../figures/superfish/superfish180_z_highlighted.png} }}%
+    \vspace{20pt}
+    \subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{../../../figures/superfish/superfish180_z_highlighted.png} }}%
     \vspace{20pt}
@@
     \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.475\textwidth]{../../../figures/superfish/superfish107mod_z_highlighted.png} }}%
-    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{../../../figures/superfish/superfish180mod_z_highlighted.png} }}%
+    \vspace{20pt}
+    \subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{../../../figures/superfish/superfish180mod_z_highlighted.png} }}%
     \vspace{20pt}

### 2023-09-19 subsections/design/first_design/first_design.tex
enstitü versiyonu

@@
     \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
+    \vspace{20pt}
     \caption{Initial design of the proposed rhodotron, $\gamma=9^\circ$.}
@@
     \centering
-    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_first_magnet_design1.png} }}%
-    \qquad\subfigure[\centering ]{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst_first_magnet_design2.png} }}%
+    \subfigure{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_first_magnet_design1.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst_first_magnet_design2.png} }}%
     \vspace{20pt}
@@
 \end{figure}
+\vspace{20pt}
+\begin{figure}[H]
+    \centering
+    %%\captionsetup{justification=centering}
+    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
+    \vspace{20pt}
+    \caption{Magnetic field in acceleration plate of initial magnet design.}
+    \label{fig:initial_magnet_design_B}
+\end{figure}
+\clearpage
+\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
+After adding two more magnets and using $\gamma=15^\circ$, the second prototype design was created (\fromfig{initial_three_magnet_design}).
 
@@
     %%\captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-
-After adding two more magnets and using $\gamma=15^\circ$, the following second prototype design was created
-\begin{figure}[H]
-    \centering
-    %%\captionsetup{justification=centering}
     \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_design2.png}
+    \vspace{20pt}
     \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design}, $\gamma=15^\circ$.}
@@
     \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{../../../figures/cst/cst_first_design4.png} }}%
-    \vspace{20pt}\newline
+    \vspace{20pt}
     \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{../../../figures/cst/cst_second_design3.png} }}%
@@
 \end{figure} \fi
+\vspace{20pt}
 \begin{figure}[H]
     \centering
-    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_sinan_cavity_design1.png} }}%
-    \qquad\subfigure[\centering ]{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst_sinan_cavity_design2.png} }}%
+    \subfigure{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_sinan_cavity_design1.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst_sinan_cavity_design2.png} }}%
     \vspace{20pt}
@@
     \includegraphics[width=.7\linewidth]{../../../figures/cst/cst_second_magnet_design1.png}
+    \vspace{20pt}
     \caption{Improved magnet design.}
@@
     \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_magnet_design4.png}
+    \vspace{20pt}
     \caption{Magnetic field in acceleration plate of improved magnet design.}

### 2023-09-19 subsections/design/magnet/magnet.tex
enstitü versiyonu

@@
     \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
+    \vspace{20pt}
     \caption{Trejectory of a particle in single pass.}

### 2023-09-19 subsections/future/future_work.tex
push for sina1
enstitü versiyonu

@@
 \usepackage{notoccite}
-\usepackage{subcaption}
+%\usepackage{subcaption}
+\usepackage{caption}
+\usepackage{subfigure}
 \usepackage{tabu}
@@
 \textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
-Several improvements and new feature implementations are underway in the meantime. 
-They include the following;
-\begin{figure}[H]
+Several improvements and new feature implementations are underway in the meantime:
+\iffalse \begin{figure}[H]
     \begin{subfigure}[t]{0.5\textwidth}
@@
     \end{subfigure}
-\end{figure}
+\end{figure} \fi
+\begin{figure}[H]
+    \begin{minipage}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Electric and magnetic field import
+            \item Field generator module to directly produce field files from specified cavity
+            \item Synchrotron radiation calculations to determine radiation and energy loss
+            \item \ee interactions
+            \item Redesign of the GUI
+            \item 3D render in GUI
+        \end{itemize}
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
+        \begin{itemize}
+            \item Refactoring of the \eEM interaction and logging to improve performance
+            \item Refactoring of the GUI Render Frame to improve render speed
+            \item Refactoring the magnet class to introduce field leaks
+            \item Extention of analysis tools in Analyze Frame
+            \item $L_{out}$ sweep in Sweep Frame
+        \end{itemize}
+    \end{minipage}
+\vspace{-10pt}\end{figure}
+
 After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 

### 2023-09-19 subsections/production/manifacturing/mani.tex
enstitü versiyonu

--- 2023-08-29 subsections/production/manifacturing/mani.tex
@@
     \label{fig:manif_polishing}
+\end{figure} \fi
+
+\begin{figure}
+    \centering
+    \subfigure[\centering Bottom part of the cavity while polishing]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{Polishing of the inner surface of cavity.}
+    \label{fig:manif_polishing}
 \end{figure}
 
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_toroidal_sheets}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Bottom part of the cavity with the exposed beam line in inner cylinder]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
+    \label{fig:manif_toroidal_sheets}
 \end{figure}
@@
 \begin{figure}
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \centering
     \includegraphics[width=.8\linewidth]{../../../figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
+    \vspace{20pt}
     \caption{Welded sheet bars.}
@@
 \begin{figure}
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \centering
     \includegraphics[width=.7\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
+    \vspace{20pt}
     \caption{Middle part of the cavity containing the beam line.}
@@
     \label{fig:manif_welding}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Welding sheet bars]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/welding/rhodo_assembled_welding_cropped.jpeg} }}%
+    \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{\centering TIG welding.} 
+    \label{fig:manif_welding}
 \end{figure}
 
-\begin{figure}
-    \captionsetup[subfigure]{justification=centering}
-    \captionsetup{justification=centering}
+\iffalse \begin{figure}
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
     \centering
@@
     \label{fig:manif_assembled_flanges}
+\end{figure} \fi
+\begin{figure}
+    \centering
+    \subfigure[\centering Beam enter \& exit flanges]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/assembled/rhodo_final_cropped_5.jpeg} }}%
+    \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
+    \vspace{20pt}
+    \caption{\centering Flanges on the assembled cavity.} 
+    \label{fig:manif_assembled_flanges}
 \end{figure}
@@
 \begin{figure}
-    \captionsetup{justification=centering}
+    %%\captionsetup{justification=centering}
     \centering
     \includegraphics[width=.9\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped.jpeg}
+    \vspace{20pt}
     \caption{Current stage of the cavity.}

### 2023-09-19 subsections/production/technical_drawings/techd.tex
enstitü versiyonu

--- 2023-07-18 subsections/production/manifacturing/mani.tex
@@
 %%%%%%
-% Start of mani.tex
-\section{Manifacturing}
+% Start of techd.tex
+\section{Technical Drawing}
+Technical drawings of the design mentioned in \fromsec{final_design} can be found in \fromfigs{techd_rhod}{techd_mid}, \fromfig{techd_up} of \fromapp{supp}.
 
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
+    \vspace{20pt}
+    \caption{Technical drawing of the rhodotron cavity \cite{sinan}.}
+    \label{fig:techd_rhod}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[angle=270,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \vspace{20pt}
+    \caption{Technical drawing of middle part of the cavity which contains the beam line \cite{sinan}.}
+    \label{fig:techd_mid}
+\end{figure}
 %%%%%%

### 2023-09-19 subsections/simulation/gui/gui.tex
enstitü versiyonu

@@
     \centering
-    \includegraphics[width=0.95\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \vspace{20pt}
     \caption{An Illustration of the first GUI design.}
@@
     \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
+    \vspace{20pt}
     \caption{The configuration frame of implementated first GUI design.}
@@
     \centering
-    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
+    \includegraphics[width=0.9\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
     \caption{Analyze frame of \textit{GUI} E(t).}

### 2023-09-19 subsections/simulation/intermediate_versions/intermediate.tex
enstitü versiyonu

@@
 After the sizable refactoring done for 3D capabilities, this implementation was obselete.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/multh_arc.png}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
+
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/multh_arc.png}
+    \vspace{20pt}
+    \caption{An Illustration of the multithreading architecture.}
+    \label{fig:multh_illustration}
+\end{figure}
+
 Focus of this section is the worker threads, also known as \eEM interaction threads.

### 2023-09-19 subsections/theory/programming/programming.tex
enstitü versiyonu

@@
 Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
+\vspace{20pt}
 \begin{figure}[h!]
     \centering
-    \includegraphics[width=.9\textwidth]{../../../figures/cpu_instruction_speed.png}
-    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
+    \includegraphics[width=.95\textwidth]{../../../figures/cpu_instruction_speed.png}
+    \vspace{20pt}
+    \caption{Amount of clock cycle for mathematical operations in various processors \cite{cpu_instruction_speed}.}
 \end{figure}
+
 Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-
 Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.

### 2023-09-19 subsections/theory/rhodotron/rhodotron.tex
enstitü versiyonu

@@
     \includegraphics[width=.75\textwidth]{../../../figures/pill_box.jpeg}
+    \vspace{20pt}
     \caption{An RF cavity used in KAHVELab.}
@@
     \includegraphics[width=.6\textwidth]{../../../figures/illustrations/rhodo_integral_curve.pdf}
+    \vspace{20pt}
     \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}.}

### 2023-10-16 msthesis.tex
push of institute online check version

@@
     % Abbreviations in alphabetical order
-   \sym{2D}{One Dimensional}
+   \sym{1D}{One Dimensional}
    \sym{2D}{Two Dimensional}
@@
    \sym{KAHVELab}{Kandilli Detector Accelerator and \\Instrumentation Laboratory}
+   \sym{LF}{Leap-Frog}
    \sym{Linac}{Linear Particle Accelerator}
@@
    \sym{RF}{Radio Frequency}
+   \sym{RK}{Runge-Kutta}
+   \sym{RK4}{Forth Order Runge-Kutta}
    \sym{RMS}{Root Mean Square}
@@
 
-\pagenumbering{arabic}
-
 \newcommand{\vecthreeBF}[1]{\vec{\textbf{#1}}}
@@
 \chapter{INTRODUCTION AND THEORY}
+\pagenumbering{arabic}
 
@@
 \end{equation}
-
+\clearpage
 It is clear that acceleration is not necessarily parallel to the force. 
@@
     \includegraphics[width=.9\textwidth]{./figures/kahvelab_linac.png}
-    \caption{A linear proton accelerator in KAHVELab. \cite{kahvelab_linac}}
+    \vspace{20pt}
+    \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}.}
 \end{figure}
@@
 RF cavities are typically hollow metallic structures made of or coated with high-conductivity materials such as copper. 
-They are designed to resonate at a specific frequency, which is determined by the size and shape of the cavity. 
 The cavity is often cylindrical or spherical in shape, and its inner surface is polished to minimize energy losses through resistive heating.
@@
     \centering
-    \includegraphics[width=.6\textwidth]{./figures/illustrations/rhodo_integral_curve.pdf}
+    \includegraphics[width=.55\textwidth]{./figures/illustrations/rhodo_integral_curve.pdf}
     \vspace{20pt}
@@
 \vspace{-10pt}\end{eqnarray}
-\clearpage
 where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
@@
 where $T$ is the \textit{transit time factor}, a correctional coefficent that contain the changing field effects during acceleration.
+\clearpage
 For a relativistic electron crossing the axis at time 0, $T$ can be found by \cite{rhodo_pottier}
@@
 \vspace{-10pt}\end{eqnarray}
+
 For a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$ as
@@
     \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity. \cite{rhodo_pottier}}
+    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}.}
     \label{fig:pottier_table1}
@@
     \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$. \cite{rhodo_pottier}}
+    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}.}
     \label{fig:pottier_table2}
@@
 
+\clearpage
 \section{Basic Concepts in Programming}
@@
 Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-\vspace{20pt}
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.95\textwidth]{./figures/cpu_instruction_speed.png}
-    \vspace{20pt}
-    \caption{Amount of clock cycle for mathematical operations in various processors \cite{cpu_instruction_speed}.}
-\end{figure}
 
@@
 Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.95\textwidth]{./figures/cpu_instruction_speed.png}
+    \vspace{20pt}
+    \caption{Amount of clock cycle for mathematical operations in various processors \cite{cpu_instruction_speed}.}
+\end{figure}
 
@@
 
+\clearpage
 \section{Algorithms}
@@
 \end{figure}
+
 The simplest Runge-Kutta method is the \textit{Euler's method} with the following \textit{Butcher tableau},
@@
 Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
-
+\clearpage
 In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and it will be the focus of all further calculations.
 Using $f_{RF}=107.5$ MHz \& $f_{RF}=180$ MHz for comparison:
-\vspace{-10pt}\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
+\vspace{-20pt}\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
     \begin{aligned}
@@
 
+\clearpage
 \section{Magnet Design} \label{sec:magnet_design}
@@
     \centering
-    \includegraphics[width=.8\linewidth]{./figures/design/magnet_design.png}
+    \includegraphics[width=.7\linewidth]{./figures/design/magnet_design.png}
     \vspace{20pt}
@@
 Implementations for \eE and \eB interactions in 3D can be found in \fromfigs{3D_e_E_interaction_first}{3D_e_B_interaction_first}, 
-where * and \% are, dot-product and cross-product respectably. (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes})
+where * and \% are, dot-product and cross-product respectably (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes}).
 \iffalse \begin{figure}[H]
@@
 \vspace{-10pt}\end{eqnarray}
+\clearpage
 Uncertainty of \fromeq{f_lf_rk_mag_2} was taken high due to the approximation. 
@@
 \end{figure} \fi
-\vspace{20pt}
-\begin{figure}[H]
-    \centering
-    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{./figures/illustrations/statE_1.png} }}%
-    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{./figures/illustrations/statE_2.png} }}%
-    \vspace{20pt}
+\vspace{10pt}
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.381\textwidth]{./figures/illustrations/statE_1.png} }}%
+    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.389\textwidth]{./figures/illustrations/statE_2.png} }}%
+    \vspace{15pt}
     \caption{Illustration of test setups.}
@@
 % Start of intermediate.tex
+\clearpage
 \section{Graphical User Interface}
@@
 An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
+\vspace{10pt}
 \begin{figure}[H]
@@
     \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \vspace{20pt}
     \caption{An Illustration of the first GUI design.}
@@
 \end{figure}
+\clearpage
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
@@
 Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
-
+\clearpage
 \subsection{Configuration Frame}
@@
 Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
-
-\clearpage
+\vspace{10pt}
 \begin{figure}[h]
@@
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
-    \vspace{20pt}
     \caption{The configuration frame of implementated first GUI design.}
@@
 Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
+\vspace{10pt}
 \begin{figure}[h]
@@
 In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
+\vspace{10pt}
 \begin{figure}[h!]
@@
     \label{fig:gui_analyze_Et}
+    \vspace{20pt}
 \end{figure}
@@
 In the \fromfigf{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_running}{gui_sweep_sR} of \fromapp{supp}, this frame can be inspected in detail.
-
+\vspace{10pt}
 \begin{figure}[h]
@@
     \label{fig:gui_sweep_sE}
+    \vspace{10pt}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
     \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=1.047$MeV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/mag_rk_001dt.png} }}%
-    \vspace{20pt}\newline
+    \vspace{20pt}
     \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.006$MeV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/mag_rk_00001dt.png} }}%
@@
     Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volumes 40–41, Part 2,
-    1989,
-    Pages 943-945,
+    Vol. 40–41,
+    No 2,
+    pp 943-945,
+    1989.
+
+    \bibitem{kahvelab_linac}
+    Adıgüzel, A., S. Açıksöz, A. Çağlar, H. Çetinkaya, Ş. Esen, D. Halis, A. Hamparsunoğlu, T.B. İlhan, A. Kılıçgedik, O. Koçer, S. Oğur, S. Öz, A. Özbey, V.E. Özcan and N.G. Ünel
+    \emph{Ion source and LEBT of KAHVELab proton beamline},
+    Journal of Instrumentation,
+    Vol. 18,
+    2023
 
     \bibitem{rhodo_prototype}
-    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
+    Bassaler, J.M., J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
     \emph{Rhodotron: an accelerator for industrial irradiation},
     Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, Issues 1–4,
-    1992,
-    Pages 92-95,A:
+    Volume 68, No. 1–4,
+    Pages 92-95,
+    1992.
 
     \bibitem{rhodos}
-    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.
+    Jongen, Y.,
+    \emph{Manufacturing of Electron Accelerators},
+    Ion Beam Applications (IBA) Chemin du Cyclotron 3,
+    B-1348 Louvain-la-Neuve, Belgium.
+    2001.
+
+    \bibitem{rf}
+    Jensen E., in Proceedings of the CAS–CERN Accelerator School: Advanced Accelerator Physics CERN–2014–009,
+    edited by W. Herr, Trondheim, Norway,
+    pp. 405–430,
+    2013.
 
     \bibitem{cpu_instruction_speed}
-    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.
+    Fukushima, T., 
+    \emph{Reduction of Round-off Errors in Symplectic Integrators},
+    The Astronomical Journal,
+    Vol. 121,
+    pp. 1768-1775,
+    2001.
+
+    \bibitem{poi-sup}
+    User's Guide for the POISSON / SUPERFISH group of codes, 
+    Los Alamos National Laboratory, New Mexico, USA, 1987. Accessed on Aug 10, 2023.
+
+    \bibitem{root}
+    The European Organization for Nuclear Research, 
+    "ROOT - An Object Oriented Data Analysis Framework Release v6.20/04, 01/04/2020", 2020,
+    https://zenodo.org/record/3895855, accessed on Aug 10, 2023.
+
+    \bibitem{gnuplot}
+    Williams, T, "Gnuplot 5.4: An Interactive
+    Plotting Program", 2020, http://gnuplot.info, accessed on Aug 10, 2023.
 
     \bibitem{runge}
-    Runge, Carl David Tolmé (1895), \emph{Über die numerische Auflösung von Differentialgleichungen}, Mathematische Annalen, Springer, 46 (2): 167–178.
+    Runge, C. D. T.,
+    \emph{Über die numerische Auflösung von Differentialgleichungen}, 
+    Mathematische Annalen, 
+    Springer, 
+    Vol. 46,
+    No. 2,
+    pp. 167–178,
+    1895.
 
     \bibitem{kutta}
-    Kutta, Wilhelm (1901), \emph{Beitrag zur näherungsweisen Integration totaler Differentialgleichungen}, Zeitschrift für Mathematik und Physik, 46: 435–453.
+    Kutta, W, 
+    \emph{Beitrag zur näherungsweisen Integration totaler Differentialgleichungen}, 
+    Zeitschrift für Mathematik und Physik, 
+    Vol. 46,
+    pp. 435–453,
+    1901.
 
     \bibitem{cite:rhodo_design}
-    W.~Kleeven, M.~Abs, J.~Brison, E.~Forton, J.~Hubert and J.~Van de Walle,
+    Kleeven, W., M. Abs, J. Brison, E. Forton, J. Hubert and J. Van de Walle,
     \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
     9th International Particle Accelerator Conference,
-    2018
+    2018.
 
     \bibitem{sinan}
-    Privite communication, Sinan ÖZ
-
-    \bibitem{gnuplot}
-    Williams, T. and Kelley, C. (2020). Gnuplot 5.4: An Interactive
-    Plotting Program. URL http://gnuplot.info.
-
-    \bibitem{root}
-    Rene Brun and Fons Rademakers, ROOT - An Object Oriented Data Analysis Framework,
-    Proceedings AIHENP'96 Workshop, Lausanne, Sep. 1996,
-    Nucl. Inst. \& Meth. in Phys. Res. A 389 (1997) 81-86.
-    See also "ROOT" [software], Release v6.20/04, 01/04/2020,
-    (https://zenodo.org/record/3895855).
-
-    \bibitem{poi-sup}
-    J. H. Billen and L. M. Young, “Poisson Superfish,” LA-UR-96-1834.
-
-    \bibitem{kahvelab_linac}
-    A. Adıgüzel, S. Açıksöz, A. Çağlar, H. Çetinkaya, Ş. Esen, D. Halis, A. Hamparsunoğlu, T.B. İlhan, A. Kılıçgedik, O. Koçer, S. Oğur, S. Öz, A. Özbey, V.E. Özcan and N.G. Ünel
-    \emph{Ion source and LEBT of KAHVELab proton beamline},
-    Journal of Instrumentation,
-    Volume 18, January 2023
-
-    \bibitem{rf}
-    E. Jensen,
-    \emph{RF Cavity Design},
-    CERN Yellow Report CERN-2014-009, pp.405-429
+    Privite communication with Sinan Öz.
 

### 2023-10-16 subsections/simulation/gui/gui.tex
push of institute online check version

@@
     \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \vspace{20pt}
     \caption{An Illustration of the first GUI design.}
@@
     \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
-    \vspace{20pt}
     \caption{The configuration frame of implementated first GUI design.}

### 2023-10-16 subsections/simulation/intermediate_versions/intermediate.tex
push of institute online check version

@@
 \end{figure} \fi
-\vspace{20pt}
-\begin{figure}[H]
-    \centering
-    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.423\textwidth]{../../../figures/illustrations/statE_1.png} }}%
-    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.432\textwidth]{../../../figures/illustrations/statE_2.png} }}%
-    \vspace{20pt}
+\vspace{10pt}
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering Setup-1 parallel $\vecthreeBF{E}$ field]{{\includegraphics[width=0.381\textwidth]{../../../figures/illustrations/statE_1.png} }}%
+    \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.389\textwidth]{../../../figures/illustrations/statE_2.png} }}%
+    \vspace{15pt}
     \caption{Illustration of test setups.}

### 2023-10-16 subsections/theory/rhodotron/rhodotron.tex
push of institute online check version

@@
     \includegraphics[width=.9\textwidth]{../../../figures/kahvelab_linac.png}
-    \caption{A linear proton accelerator in KAHVELab. \cite{kahvelab_linac}}
+    \vspace{20pt}
+    \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}.}
 \end{figure}
@@
     \centering
-    \includegraphics[width=.6\textwidth]{../../../figures/illustrations/rhodo_integral_curve.pdf}
+    \includegraphics[width=.55\textwidth]{../../../figures/illustrations/rhodo_integral_curve.pdf}
     \vspace{20pt}
@@
     \includegraphics[width=.9\textwidth]{../../../figures/pottier_table1.png}
-    \caption{Optimized characteristics of a rhodotron cavity. \cite{rhodo_pottier}}
+    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}.}
     \label{fig:pottier_table1}
@@
     \includegraphics[width=.9\textwidth]{../../../figures/pottier_table2.png}
-    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$. \cite{rhodo_pottier}}
+    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}.}
     \label{fig:pottier_table2}

### 2023-12-03 msthesis.tex
compiled from remote
cleanup after remote
compile of euler method caption fix
compile of assist abb fix
calistay puısh

@@
 %\cosuperii{Title and Name of Cosupervisor II}
-\examineri{Asst. Prof. Bora Akgün}
+\examineri{Assist. Prof. Bora Akgün}
 \examinerii{Assoc. Prof. Bora Işıldak}
@@
 
-\newcommand{\fromeq}[1]{\textit{Equation \ref{eq:#1}}}
-\newcommand{\fromeqs}[2]{\textit{Equations \ref{eq:#1} and \ref{eq:#2}}}
-\newcommand{\fromeqsth}[3]{\textit{Equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}}
-\newcommand{\fromeqsf}[4]{\textit{Equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}}
-
-\newcommand{\fromfig}[1]{\textit{Figure \ref{fig:#1}}}
-\newcommand{\fromfigs}[2]{\textit{Figures \ref{fig:#1} and \ref{fig:#2}}}
-\newcommand{\fromfigth}[3]{\textit{figures \ref{fig:#1}, \ref{fig:#2} and \ref{fig:#3}}}
-\newcommand{\fromfigf}[4]{\textit{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}}
-\newcommand{\fromfigsix}[6]{\textit{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}}
-
-\newcommand{\fromch}[1]{\textit{Chapter \ref{ch:#1}}}
-
-\newcommand{\fromsec}[1]{\textit{Section \ref{sec:#1}}}
-\newcommand{\fromsecs}[2]{\textit{Sections \ref{sec:#1} and \ref{sec:#2}}}
-
-\newcommand{\fromapp}[1]{\textit{Appendix \ref{appendix:#1}}}
-
-\newcommand{\fromtab}[1]{\textit{Table \ref{tab:#1}}}
-\newcommand{\fromtabs}[2]{\textit{Tables \ref{tab:#1} and \ref{tab:#2}}}
-\newcommand{\fromtabf}[4]{\textit{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}}
+\newcommand{\fromeq}[1]{Equation \ref{eq:#1}}
+\newcommand{\fromeqs}[2]{Equations \ref{eq:#1} and \ref{eq:#2}}
+\newcommand{\fromeqsth}[3]{Equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}
+\newcommand{\fromeqsf}[4]{Equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}
+
+\newcommand{\fromfig}[1]{Figure \ref{fig:#1}}
+\newcommand{\fromfigs}[2]{Figures \ref{fig:#1} and \ref{fig:#2}}
+\newcommand{\fromfigth}[3]{Figures \ref{fig:#1}, \ref{fig:#2} and \ref{fig:#3}}
+\newcommand{\fromfigf}[4]{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3} and \ref{fig:#4}}
+\newcommand{\fromfigsix}[6]{Figures \ref{fig:#1}, \ref{fig:#2}, \ref{fig:#3}, \ref{fig:#4}, \ref{fig:#5} and \ref{fig:#6}}
+
+\newcommand{\fromch}[1]{Chapter \ref{ch:#1}}
+
+\newcommand{\fromsec}[1]{Section \ref{sec:#1}}
+\newcommand{\fromsecs}[2]{Sections \ref{sec:#1} and \ref{sec:#2}}
+
+\newcommand{\fromapp}[1]{Appendix \ref{appendix:#1}}
+
+\newcommand{\fromtab}[1]{Table \ref{tab:#1}}
+\newcommand{\fromtabs}[2]{Tables \ref{tab:#1} and \ref{tab:#2}}
+\newcommand{\fromtabf}[4]{Tables \ref{tab:#1}, \ref{tab:#2}, \ref{tab:#3} and \ref{tab:#4}}
 
@@
 Considering these two statements, we can find the relation between momentum and acceleration as 
-\vspace{-10pt}
+\vspace{-15pt}
 \begin{eqnarray}
@@
 \end{eqnarray}
+\vspace{-30pt}
+\newline
 Therefore force can be written as
-\vspace{-10pt}
+\vspace{-15pt}
 \begin{equation} \label{eq:Frel}
@@
 
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in 1989 \cite{rhodo_pottier}. 
+Rhodotron Accelerator is a type of particle accelerator that was proposed by Jacques POTTIER in 1989 \cite{rhodo_pottier}. 
 First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. It is named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
@@
 
-\subsubsection{Acceleration cycle of Rhodotron}
+\subsubsection{Acceleration Cycle of Rhodotron}
 
@@
 
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
+Note that division is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
 Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
@@
 
-Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}.
+Concurrency in single core can be achieved by implementing clever scheduling of list of operations called threads.
 This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time.
@@
 
-Threads utilize \textit{mutexes}, short for "mutual exclusion," 
+Threads utilize mutexes, short for ``mutual exclusion,''
 to synchronize and manage access to shared resources 
@@
 
-In OOP, \textit{inheritance} enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
-\textit{Polymorphism} allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
+In OOP, inheritance enables the creation of new classes based on existing ones, facilitating code reuse and hierarchy. 
+Polymorphism allows objects of different classes to be treated uniformly through a common interface, enhancing flexibility and extensibility. 
 By providing abstraction, OOP simplifies complex systems by focusing on essential features and interactions, making software development more manageable, scalable, and maintainable.
@@
 \subsection{Poisson Superfish}
-Poisson Superfish is a software package developed by the \textit{Los Alamos National Laboratory} 
+Poisson Superfish is a software package developed by the Los Alamos National Laboratory 
 for the design and analysis of electromagnetic fields, particularly those related to particle accelerators and high-energy physics experiments \cite{poi-sup}.
@@
 \subsection{CST Studio Suite}
-CST Studio Suite is a powerful software package developed by \textit{Simulia} for electromagnetic simulation and analysis.
+CST Studio Suite is a powerful software package developed by Simulia for electromagnetic simulation and analysis.
 It is widely used in various industries, including electronics, telecommunications, automotive, aerospace, and more, to design and optimize electromagnetic devices and systems.
@@
 The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space. 
-The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion.
+The method gets its name from the way it calculates the values of the solution at each time step, which resembles a leapfrogging motion. 
 It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
@@
 These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a particular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
-The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$ which can be observed in \fromfig{Butcher}.
+The coefficients of any Runge-Kutta method can be visualized by a tableau called Butcher Tableau which can be observed in \fromfig{Butcher}.
 \begin{figure}[h!]
@@
 
-The simplest Runge-Kutta method is the \textit{Euler's method} with the following \textit{Butcher tableau},
+The simplest Runge-Kutta method is the Euler's method the Butcher tableau of which can be observed in \fromfig{Butcher_euler}.
+
+\begin{figure}[h!]
 \[ 
@@
         & 1
-    \end{array} .
+    \end{array}
 \] 
+\caption{Butcher tableau of Euler's method.}
+\label{fig:Butcher_euler}
+\end{figure}
 
@@
 The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
-Two of the most used \textit{Butcher tableaus} for \textit{RK4} given in \fromfig{Butcher-RK4}.
-The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}.
+Two of the most used Butcher tableaus for RK4 given in \fromfig{Butcher-RK4}.
+The second tableau in \fromfig{Butcher-RK4} is called the ``3/8 rule''.
 Its main advantage is that its error coefficients are smaller than the other.
@@
 For simple coaxial cavity, the height should be $\lambda/2$, where $\lambda$ is the wavelength of the external RF supply \cite{rhodo_pottier}.
-Simulation tools such as \textit{CST Studio}, \textit{Poisson SUPERFISH} can be used to confirm this condition.
+Simulation tools such as CST Studio and Poisson Superfish can be used to confirm this condition.
 \clearpage
@@
 In the \fromfigth{107_simple_cavity_design}{180_simple_cavity_design}{cst_simple_cavity_designs}, 
-\textit{Poisson Superfish} and \textit{CST} simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
+Poisson Superfish and CST simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
 \iffalse
@@
 \end{figure}
-As mentioned by \textit{Pottier}, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
-In the \fromfig{107_180_modified_cavities_superfish}, \textit{Poission Superfish} results of such a modification with matching height increase to keep resonant frequency can be found.
+As mentioned by Pottier, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
+In the \fromfig{107_180_modified_cavities_superfish}, Poission Superfish results of such a modification with matching height increase to keep resonant frequency can be found.
 \iffalse
@@
     \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{unmodified} cavities}
+    \caption{Poisson Superfish calculations with unmodified cavities}
     \label{fig:107_cavity_shunt_diff}
@@
     \vspace{20pt}
-    \caption{\centering Poisson Superfish calculations with \textit{unmodified} cavities.} 
+    \caption{\centering Poisson Superfish calculations with unmodified cavities.} 
     \label{fig:107_cavity_shunt_diff}
@@
     \end{subfigure}
-    \caption{Poisson Superfish calculations with \textit{truncated} cavities}
+    \caption{Poisson Superfish calculations with truncated cavities}
     \label{fig:180_cavity_shunt_diff}
@@
     \vspace{20pt}
-    \caption{\centering Poisson Superfish calculations with \textit{truncated} cavities.} 
+    \caption{\centering Poisson Superfish calculations with truncated cavities.} 
     \label{fig:180_cavity_shunt_diff}
@@
 
-\textit{Equations \ref{eq:magnet_rho_constraint} and \ref{eq:magnet_L_constraint}} define 2 constraints.
-As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
+\fromeqs{magnet_rho_constraint}{magnet_L_constraint} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
 Therefore only the magnet design parameters $\rho$, $\gamma$ and $L$ are left. Together with the constraints, one free variable defines the whole magnet design. 
@@
 needs be selected.
-Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
+Using a simulation software such as CST Studio Particle Module, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (sweeping) and analyzing the results.
 This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.
@@
 However, one caviat of this technique is that, available simulation softwares are not well suited for this kind of process.
-As mentioned above, \textit{CST Studio Particle Module} has a \textit{parameter sweep} functionality.
-But the calculation times are too slow to be useful in this particular problem.
-\textit{A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.}
+As mentioned above, CST Studio Particle Module has a parameter sweep functionality.
+But the calculation times are too slow to be useful in this particular problem. A custom built software offering magnet optimizing sweep functionality will be discussed in the following chapter.
 
@@
 \end{figure}
-These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using \textit{CST Studio Particle Module PIC Solver}.
+These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using CST Studio Particle Module PIC Solver.
 Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
@@
 
-After various similar observations in \textit{CST} similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
+After various similar observations in CST similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
 as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-\emph{The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.}
+The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.
 
@@
 
-After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} 
+After simulating the synchronous electron mentioned in \fromsec{cavity_of_a_rhodotron} 
 with $\phi_{lag}=15^\circ$, $P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz for one pass, 
-the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} were found to be
+the results from POC, CST and \fromeq{W_gain_each_pass_pottier} were found to be
 % 40 kW total power
@@
 
-As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced similar results; $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
+As can be observed in \fromeq{poc_E_results}, POC software and CST produced similar results; $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
 while \fromeq{W_gain_each_pass_pottier} was noticably different; $\Delta E_{(Pottier-CST)}/E_{CST} \approx 14\%$.
-This inconsistency between \fromeq{W_gain_each_pass_pottier} and  \textit{CST} simulation was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
+This inconsistency between \fromeq{W_gain_each_pass_pottier} and  CST simulation was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on CST.
 Since using a single software would have made the process error prone.
 
-After the results obtained from \textit{POC} were found to be promising, a decision was made to develop a more robust simulation software.
-This software was named \textit{Rhodotron Simulation} for the current stage and started development in October, 2021.
+After the results obtained from POC were found to be promising, a decision was made to develop a more robust simulation software.
+This software was named Rhodotron Simulation for the current stage and started development in October, 2021.
 The development and improvement efforts are still ongoing.
 
-During the development of \textit{Rhodotron Simulation} software, several intermediate builds have been implemented and tested.
+During the development of Rhodotron Simulation software, several intermediate builds have been implemented and tested.
 The following sections in this chapter investigates their implementations further.
@@
 \subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
-Initial step of improving \textit{POC} towards \textit{Rhodotron Simulation} was to implement \textit{$L_{out}$ optimizations} to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
+Initial step of improving POC towards Rhodotron Simulation was to implement $L_{out}$ optimizations to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
 First approach was to hang the \e outside of the cavity for $t_{out} = L_{out}/v$, then inject it back to the cavity with reversed $\vecthreeBF{v}$.
@@
 
-\subsection{$\phi_{lag}$ Optimization For Bunches} \label{sec:philag_sweep}
+\subsection{$\phi_{lag}$ Optimization for Bunches} \label{sec:philag_sweep}
 After successfully accelerating single \e, particle bunches were implemented to approximate a real \e gun. 
 They were modeled as $N$ electrons fired from an \e gun at even time intervals.
-This approach was taken because the amount of time gun fires, defined as \textit{Gun Active Time, $t_g$}, is a crucial part of pulsed \e gun design.
+This approach was taken because the amount of time gun fires, defined as Gun Active Time, $t_g$, is a crucial part of pulsed \e gun design.
 \clearpage
@@
 $\phi_{lag}$ for a bunch was defined as the RF phase when the first \e of the bunch has entered the cavity and it defines the starting time of the current pass.
-To use the \textit{parameter sweep} method, as used in \textit{$L_{out}$ optimization}, relevant bunch characteristics are defined as
+To use the parameter sweep method, as used in $L_{out}$ optimization, relevant bunch characteristics are defined as
 \vspace{-10pt}\begin{itemize}
@@
 Optimal $\phi_{lag}$ would produce maximum $\mu E$ while minimizing $E_{rms}$ \& $R_{rms}$. For the first pass, 
-$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (\textit{see \fromfig{phlag_opt}}).
-For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as \textit{ROOT framework}. 
+$E_{rms}$ and $R_{rms}$ would be vaguely dependent of each other; therefore, initial implementation of $\phi_{lag}$ sweep was based on minimizing $E_{rms}$ during simulation (see \fromfig{phlag_opt}).
+For $\mu E$ considerations, data from the software would be analyzed either manually or by using external tools such as ROOT framework. 
 \vspace{20pt}
@@
 \clearpage
-Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented (\textit{see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}}).
+Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented ({see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}).
 This version can be useful for optimizing $\phi_{lag}$ in case of production issues in magnets.
@@
 \subsection{Simulation in 3D}
-After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the \textit{Rhodotron Simulation}.
+After successfully implementing \eE interaction in 1D and confirming the usefulness of this tool, the decision was made to proceed with implementing a 3D version of the Rhodotron Simulation.
 Although complete refactoring of the software was necessary, this upgrade was crucial for implementation of \eB interaction.
-The refactoring effort included proper implementation of \textit{OOP}, details of which can be seen in \fromfigsix{e_class}{bunch_class}{gun_class}{sim_class}{rhodosim_class}{rf_class} of \fromapp{intermediate_codes}.
+The refactoring effort included proper implementation of OOP, details of which can be seen in \fromfigsix{e_class}{bunch_class}{gun_class}{sim_class}{rhodosim_class}{rf_class} of \fromapp{intermediate_codes}.
 
@@
 Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, \textit{gnuplot} was integrated into \textit{Rhodotron Simulation} to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as \textit{gif} animations. 
+For this purpose, gnuplot was integrated into Rhodotron Simulation to produce 2D visualization of acceleration plane. 
+Rendered results could be stored as gif animations. 
 Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
@@
     \end{subfigure}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation} $P=40$kW, $f=107.5$MHz.}
+    \caption{Example gnuplot renders of Rhodotron Simulation $P=40$kW, $f=107.5$MHz.}
     \label{fig:example_gnuplot_renders}
@@
     \vspace{15pt}
-    \caption{Example \textit{gnuplot} renders of \textit{Rhodotron Simulation}, $P=40$kW, $f=107.5$MHz.} 
+    \caption{Example gnuplot renders of Rhodotron Simulation, $P=40$kW, $f=107.5$MHz.} 
     \label{fig:example_gnuplot_renders}
@@
 Decreasing $dt$ would be the best way to increase accuracy of the results; however, this is not sustainable due to computing power limitations. 
-Until this point, \textit{Rhodotron Simulation} have been using \fromsec{leapfrog} for \eEM interactions. 
+Until this point, Rhodotron Simulation have been using \fromsec{leapfrog} for \eEM interactions. 
 To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
 \subsubsection{RK4-1}
-First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using \textit{RK4}.
-After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the \textit{Leap-frog} method. 
+First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using RK4.
+After $\vecthreeBF{a}_{EM} = \vecthreeBF{a}_{E} + \vecthreeBF{a}_{B}$ was calculated, \e would move and accelerate using the Leap-frog method. 
 The idea was to produce more refined interaction results, leading to improved accuracy especially in \eB.
-RF field was kept static during the RK4 computation, due to ongoing \textit{multithreading} implementation efforts. 
+RF field was kept static during the RK4 computation, due to ongoing multithreading implementation efforts. 
 The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
 \subsubsection{RK4-2}
-Following the implementation of \textit{RK4-1}, revisions were made to the integration method for \textit{RK4} to replace \textit{Leap-frog}.
-Instead of calculating $\vecthreeBF{a}_{EM}$ using \textit{RK4}, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
+Following the implementation of RK4-1, revisions were made to the integration method for RK4 to replace Leap-frog.
+Instead of calculating $\vecthreeBF{a}_{EM}$ using RK4, $\vecthreeBF{r}$ and $\vecthreeBF{v}$ would be determined directly.
 
 These three methods were then tested in the same setup as \fromfig{mag_lf_render}. The results can be found in \fromfig{lf_rk1_rk2_comparison} of \fromapp{data_graph}.
-\textit{RK4-1} was decided to be abandoned as it produced the same accuracy in twice the simulation time of \textit{RK4-2}.
+RK4-1 was decided to be abandoned as it produced the same accuracy in twice the simulation time of RK4-2.
 \clearpage
@@
 \end{figure}
-More rigorous testing was done with \textit{Leap-frog} and \textit{RK4-2} however. 
+More rigorous testing was done with Leap-frog and RK4-2 however. 
 Still using the setup in \fromfig{mag_lf_render}, each $dt$ configuration was simulated 10 times, calculating average and standard deviations afterwards.
@@
 \vspace{-10pt}\end{equation}
-Therefore, \textit{Leap-frog} was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to \textit{RK4}. However,
-\textit{RK4} was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into \textit{Rhodotron Simulation} for the user to decide.
-\textit{RK4-2} renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
+Therefore, Leap-frog was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to RK4. However,
+RK4 was promising in situations where decreasing the stepsize, $dt$, is not viable. Therefore both were integrated into Rhodotron Simulation for the user to decide.
+RK4-2 renders from these test can be found in \fromfig{mag_rk_render} of \fromapp{example_simulation_runs}.
 
 \subsection{Acceleration in Electric Field}
-After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of \textit{Leap-frog} and \textit{RK4}.
+After the accuracy concerns regarding the \eB interaction were raised, it was decided to test \eE and compare the performance of Leap-frog and RK4.
 
@@
 
-\textit{Leap-frog} provides $2.4$ times and $2.0$ times less overacceleration per simulation time than 
-\textit{RK4} in parallel and perpendicular electric fields respectably.
+Leap-frog provides $2.4$ times and $2.0$ times less overacceleration per simulation time than 
+RK4 in parallel and perpendicular electric fields respectably.
 This results can be tested further with obsering from the data (see \fromtabf{lf_statE_table}{rk2_statE_table}{lf_statE90_table}{rk2_statE90_table} of \fromapp{data_graph})
@@
 The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
-the performance of \textit{Leap-frog} relative to \textit{RK4} in \eE interaction can be calculated as
+the performance of Leap-frog relative to RK4 in \eE interaction can be calculated as
 \vspace{-10pt}\begin{equation}\label{eq:lf_rk_eE_relative_performance}
@@
 \vspace{-10pt}\end{equation}
-Therefore, it can be concluded that \textit{Leap-frog} outperforms \textit{RK4} with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
+Therefore, it can be concluded that Leap-frog outperforms RK4 with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
 
@@
 There have been a number of different approaches for implementation. 
-First implemenation was done when the \textit{Rhodotron Simulation} was only capable of 1D simulations.
+First implemenation was done when the Rhodotron Simulation was only capable of 1D simulations.
 After the sizable refactoring done for 3D capabilities, this implementation was obselete.
@@
 (see \fromfig{console_output_running} in \fromapp{example_simulation_runs} for example console notification, \fromfig{ui_thread} in \fromapp{intermediate_codes} for implemenation)
-or communucating with the \textit{GUI} that will be disscussed in the next section.
+or communucating with the GUI that will be disscussed in the next section.
 
@@
 \begin{itemize}
-    \item \textit{Architecture 1:} Have a thread pool that calculates \eEM in a queue. 
-    \item \textit{Architecture 2:} Assign a thread to each bunch.
-    \item \textit{Architecture 3:} A ssign random electrons to each thread and calculate \eEM with global time.
-    \item \textit{Architecture 4:} Assign random electrons to each thread and calculate \eEM with local thread time.
+    \item Architecture 1: Have a thread pool that calculates \eEM in a queue. 
+    \item Architecture 2: Assign a thread to each bunch.
+    \item Architecture 3: A ssign random electrons to each thread and calculate \eEM with global time.
+    \item Architecture 4: Assign random electrons to each thread and calculate \eEM with local thread time.
 \end{itemize}
 
-\textit{Architecture 1} would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in \textit{RK4}.
+Architecture 1 would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in RK4.
 \clearpage
-\textit{Architecture 2} was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
-
-\textit{Architecture 3} was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
-
-\textit{Architecture 4} was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
+Architecture 2 was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
+
+Architecture 3 was inefficient and wasteful since all the worker threads would wait the main thread to get the next time after they finish calculation, while the main thread would be waiting for the slowest worker thread.
+
+Architecture 4 was thought to be the best performer. It would give freedom to calculate the whole simulation to each thread while giving up the global time.
 This would also mean thread-safety is ensured since there is no shared data between the worker threads. 
@@
 This would lead to larger memory allocations and more time spent setting up simulations. 
-Therefore, \textit{Architecture 4} is not ideal for fast calculations and when the memory is an important constraint.
-An implementation that can use both \textit{Architecture 2} \& \textit{Architecture 4} when necessary would be a better approach considering these methods;
-nevertheless, \textit{Architecture 4} was chosed to be implemented.
+Therefore, Architecture 4 is not ideal for fast calculations and when the memory is an important constraint.
+An implementation that can use both Architecture 2 \& Architecture 4 when necessary would be a better approach considering these methods;
+nevertheless, Architecture 4 was chosed to be implemented.
 
@@
 
-Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
+Until this point, Rhodotron Simulation could be used with a configration file, defining the problem that would be simulated.
 An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
@@
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
-
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+For this reason, a GUI was decided to be built, using ROOT framework. 
+This would also enable Rhodotron simulation to make use of analysis tools offered by ROOT.
+
+The initial design of the Rhodotron Simulation GUI can be observed in \fromfig{gui_illustration}.
+The GUI would be a standalone application, running the Rhodotron Simulation as a service when needed. 
+For this reason, the now called simulation engine was updated to be able to run as a background service of GUI.
+By this approach, one could also ignore the GUI altogether and use the simulation engine as before, as these are two seperate products.
 
 In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. 
-Available frames of this version of the \textit{GUI} are discussed further in the following sections.
+Available frames of this version of the GUI are discussed further in the following sections.
 \subsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+This frame spawns and manages the simulation engine, configures and starts the simulation. 
+It has a progress bar that shows the current progress of the simulation, communucating with UI handler thread in simulation engine.
 Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
@@
 \subsection{Configuration Frame}
-This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
+This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, RF description, \egun, simulation configuration regions.
 Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
@@
 \subsection{Render Frame}
-Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
+Since the rendering capabilities of ROOT is superior than gnuplot, the user can render a playback of the simulation in real time, 
 see a specific time frame, export as snapshot or animated gif file.
@@
     \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_render_frame_5.png}
-    \caption{Render frame of \textit{GUI}.}
+    \caption{Render frame of GUI.}
     \label{fig:gui_render_1}
@@
 Analyze frame provides tools for analyzing and visualizing the simulation data. 
-In the current version, energy distribution histogram and \textit{E(t)} graph of each electron are implementated into this frame.
+In the current version, energy distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
 This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
-In \fromfig{gui_analyze_Edist}, \textit{Analyze Frame} plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, \textit{Analyze Frame} plotting \textbf{E(t)} graphs can be observed.
+In \fromfig{gui_analyze_Edist}, Analyze Frame plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, Analyze Frame plotting \textbf{E(t)} graphs can be observed.
 \vspace{10pt}
@@
     \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist_2.png}
-    \caption{Analyze frame of \textit{GUI} E distribution.}
+    \caption{Analyze frame of GUI E distribution.}
     \label{fig:gui_analyze_Edist}
@@
     \includegraphics[width=0.9\linewidth]{./figures/rhodoSim/GUI_analyze_Et_3.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
+    \caption{Analyze frame of GUI E(t).}
     \label{fig:gui_analyze_Et}
@@
 \subsection{Sweep Frame}
-Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into \textit{GUI} in a seperate frame named \textit{Sweep Frame}.
+Parameter sweep method that was discussed in \fromsecs{lout_sweep}{philag_sweep} was integrated into GUI in a seperate frame named Sweep Frame.
 $\phi_{lag}$ sweep was the first parameter to be implemented.
@@
     \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_sweep_muE_3.png}
-    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ $\mu E$ result.}
+    \caption{Sweep frame of GUI $\phi_{lag}$ $\mu E$ result.}
     \label{fig:gui_sweep_muE}
@@
     \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_sweep_sE_3.png}
-    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ sweep $\sigma E$ result.}
+    \caption{Sweep frame of GUI $\phi_{lag}$ sweep $\sigma E$ result.}
     \label{fig:gui_sweep_sE}
@@
 
-As mentioned before, \textit{GUI} is the latest and ongoing development effort in this project.
+As mentioned before, GUI is the latest and ongoing development effort in this project.
 New analysis and sweep features will be implemented and current capabilities will be improved in the near future.
@@
 
-As discussed before, production efforts of a \textit{Rhodotron-type} accelerator are still ongoing in KAHVELab.
+As discussed before, production efforts of a Rhodotron-type accelerator are still ongoing in KAHVELab.
 This accelerator will be used at $f=107.5$MHz $P=50-100$kW to achieve beams with the energy range of $1-5$MeV.
@@
 The cavity itself was manifactured as 5 main parts, using 5mm thick stainless steel sheet. 
-
 Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
@@
 % START OF FUTURE_WORK
-
 \chapter{CONCLUSION}
@@
 As far as the magnets were concerned, it was decided to be kept on hold in the early stages of the project, 
-due to the disagreement on the energy gain amount between the calculations of \textit{J. POTTIER} \cite{rhodo_pottier} 
-and the simulation results from \textit{CST Studio Suite} \& \textit{Rhodotron Simulation}. 
+due to the disagreement on the energy gain amount between the calculations of J. POTTIER \cite{rhodo_pottier} 
+and the simulation results from CST Studio Suite \& Rhodotron Simulation. 
 The software is planned to be used in magnet design and beam optimizations in KAHVELab after the initial tests are completed.
 
-\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
+Rhodotron Simulation, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
 Several improvements and new feature implementations are underway in the meantime:
@@
 \end{figure} \fi
-\begin{figure}[H]
-    \begin{minipage}[t]{0.5\textwidth}
 \begin{itemize}
@@
     \item 3D render in GUI
-        \end{itemize}
-    \end{minipage}
-    \begin{minipage}[t]{0.5\textwidth}
-        \begin{itemize}
     \item Refactoring of the \eEM interaction and logging to improve performance
@@
 \end{itemize}
-    \end{minipage}
-\vspace{-10pt}\end{figure}
 
 After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
-Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunities.
+Complementary bending magnet design will be the first challange of Rhodotron Simulation, which will provide tremendous testing and improvement opportunities.
 
 \section{Discussion}
-In conclusion, a new computational \eEM interaction simulation and analysis tool that focuses on designing and improving \textit{Rhodotron-type} accelerators has been successfully developed; 
-a \textit{Rhodotron-type} accelerator with an operating frequency of $107.5$ MHz and a target energy of $1-5$ MeV has been designed and is currently being manufactured.
+In conclusion, a new computational \eEM interaction simulation and analysis tool that focuses on designing and improving Rhodotron-type accelerators has been successfully developed; 
+a Rhodotron-type accelerator with an operating frequency of $107.5$ MHz and a target energy of $1-5$ MeV has been designed and is currently being manufactured.
 
@@
 \newpage
+
+% START OF BIBLIOGRAPHY
+
+\begin{thebibliography}{9}
+
+    \bibitem{rhodo_pottier}
+    Jacques Pottier,
+    \emph{A new type of rf electron accelerator: The rhodotron},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Vol. 40–41,
+    No 2,
+    pp 943-945,
+    1989.
+
+    \bibitem{kahvelab_linac}
+    Adıgüzel, A., S. Açıksöz, A. Çağlar, H. Çetinkaya, Ş. Esen, D. Halis, A. Hamparsunoğlu, T.B. İlhan, A. Kılıçgedik, O. Koçer, S. Oğur, S. Öz, A. Özbey, V.E. Özcan and N.G. Ünel
+    \emph{Ion source and LEBT of KAHVELab proton beamline},
+    Journal of Instrumentation,
+    Vol. 18,
+    2023
+
+    \bibitem{rhodo_prototype}
+    Bassaler, J.M., J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
+    \emph{Rhodotron: an accelerator for industrial irradiation},
+    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
+    Volume 68, No. 1–4,
+    Pages 92-95,
+    1992.
+
+    \bibitem{rhodos}
+    Jongen, Y.,
+    \emph{Manufacturing of Electron Accelerators},
+    Ion Beam Applications (IBA) Chemin du Cyclotron 3,
+    B-1348 Louvain-la-Neuve, Belgium.
+    2001.
+
+    \bibitem{rf}
+    Jensen E., in Proceedings of the CAS–CERN Accelerator School: Advanced Accelerator Physics CERN–2014–009,
+    edited by W. Herr, Trondheim, Norway,
+    pp. 405–430,
+    2013.
+
+    \bibitem{cpu_instruction_speed}
+    Fukushima, T., 
+    \emph{Reduction of Round-off Errors in Symplectic Integrators},
+    The Astronomical Journal,
+    Vol. 121,
+    pp. 1768-1775,
+    2001.
+
+    \bibitem{poi-sup}
+    User's Guide for the POISSON / SUPERFISH group of codes, 
+    Los Alamos National Laboratory, New Mexico, USA, 1987. Accessed on Aug 10, 2023.
+
+    \bibitem{root}
+    The European Organization for Nuclear Research, 
+    "ROOT - An Object Oriented Data Analysis Framework Release v6.20/04, 01/04/2020", 2020,
+    https://zenodo.org/record/3895855, accessed on Aug 10, 2023.
+
+    \bibitem{gnuplot}
+    Williams, T, "Gnuplot 5.4: An Interactive
+    Plotting Program", 2020, http://gnuplot.info, accessed on Aug 10, 2023.
+
+    \bibitem{runge}
+    Runge, C. D. T.,
+    \emph{Über die numerische Auflösung von Differentialgleichungen}, 
+    Mathematische Annalen, 
+    Springer, 
+    Vol. 46,
+    No. 2,
+    pp. 167–178,
+    1895.
+
+    \bibitem{kutta}
+    Kutta, W, 
+    \emph{Beitrag zur näherungsweisen Integration totaler Differentialgleichungen}, 
+    Zeitschrift für Mathematik und Physik, 
+    Vol. 46,
+    pp. 435–453,
+    1901.
+
+    \bibitem{cite:rhodo_design}
+    Kleeven, W., M. Abs, J. Brison, E. Forton, J. Hubert and J. Van de Walle,
+    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
+    9th International Particle Accelerator Conference,
+    2018.
+
+    \bibitem{sinan}
+    Privite communication with Sinan Öz.
+
+\end{thebibliography}
+
+% END OF BIBLIOGRAPHY
 
@@
 \end{figure}
-% START OF BIBLIOGRAPHY
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Vol. 40–41,
-    No 2,
-    pp 943-945,
-    1989.
-
-    \bibitem{kahvelab_linac}
-    Adıgüzel, A., S. Açıksöz, A. Çağlar, H. Çetinkaya, Ş. Esen, D. Halis, A. Hamparsunoğlu, T.B. İlhan, A. Kılıçgedik, O. Koçer, S. Oğur, S. Öz, A. Özbey, V.E. Özcan and N.G. Ünel
-    \emph{Ion source and LEBT of KAHVELab proton beamline},
-    Journal of Instrumentation,
-    Vol. 18,
-    2023
-
-    \bibitem{rhodo_prototype}
-    Bassaler, J.M., J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, No. 1–4,
-    Pages 92-95,
-    1992.
-
-    \bibitem{rhodos}
-    Jongen, Y.,
-    \emph{Manufacturing of Electron Accelerators},
-    Ion Beam Applications (IBA) Chemin du Cyclotron 3,
-    B-1348 Louvain-la-Neuve, Belgium.
-    2001.
-
-    \bibitem{rf}
-    Jensen E., in Proceedings of the CAS–CERN Accelerator School: Advanced Accelerator Physics CERN–2014–009,
-    edited by W. Herr, Trondheim, Norway,
-    pp. 405–430,
-    2013.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, T., 
-    \emph{Reduction of Round-off Errors in Symplectic Integrators},
-    The Astronomical Journal,
-    Vol. 121,
-    pp. 1768-1775,
-    2001.
-
-    \bibitem{poi-sup}
-    User's Guide for the POISSON / SUPERFISH group of codes, 
-    Los Alamos National Laboratory, New Mexico, USA, 1987. Accessed on Aug 10, 2023.
-
-    \bibitem{root}
-    The European Organization for Nuclear Research, 
-    "ROOT - An Object Oriented Data Analysis Framework Release v6.20/04, 01/04/2020", 2020,
-    https://zenodo.org/record/3895855, accessed on Aug 10, 2023.
-
-    \bibitem{gnuplot}
-    Williams, T, "Gnuplot 5.4: An Interactive
-    Plotting Program", 2020, http://gnuplot.info, accessed on Aug 10, 2023.
-
-    \bibitem{runge}
-    Runge, C. D. T.,
-    \emph{Über die numerische Auflösung von Differentialgleichungen}, 
-    Mathematische Annalen, 
-    Springer, 
-    Vol. 46,
-    No. 2,
-    pp. 167–178,
-    1895.
-
-    \bibitem{kutta}
-    Kutta, W, 
-    \emph{Beitrag zur näherungsweisen Integration totaler Differentialgleichungen}, 
-    Zeitschrift für Mathematik und Physik, 
-    Vol. 46,
-    pp. 435–453,
-    1901.
-
-    \bibitem{cite:rhodo_design}
-    Kleeven, W., M. Abs, J. Brison, E. Forton, J. Hubert and J. Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018.
-
-    \bibitem{sinan}
-    Privite communication with Sinan Öz.
-
-\end{thebibliography}
-
-% END OF BIBLIOGRAPHY
 

### 2023-12-03 subsections/design/magnet/magnet.tex
push of institute online check version
calistay puısh

@@
 %%%%%%
-
+\clearpage
 \section{Magnet Design} \label{sec:magnet_design}
@@
     \centering
-    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
+    \includegraphics[width=.7\linewidth]{../../../figures/design/magnet_design.png}
     \vspace{20pt}

### 2023-12-03 subsections/simulation/gui/gui.tex
calistay puısh

@@
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
-For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
-This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.
+For this reason, a GUI was decided to be built, using ROOT framework. 
+This would also enable Rhodotron simulation to make use of analysis tools offered by ROOT.
 
-The initial design of the \textit{Rhodotron Simulation GUI} can be observed in \fromfig{gui_illustration}.
-The \textit{GUI} would be a standalone application, running the \textit{Rhodotron Simulation} as a service when needed. 
-For this reason, the now called \textit{simulation engine} was updated to be able to run as a background service of \textit{GUI}.
-By this approach, one could also ignore the \textit{GUI} altogether and use the \textit{simulation engine} as before, as these are two seperate products.
+The initial design of the Rhodotron Simulation GUI can be observed in \fromfig{gui_illustration}.
+The GUI would be a standalone application, running the Rhodotron Simulation as a service when needed. 
+For this reason, the now called simulation engine was updated to be able to run as a background service of GUI.
+By this approach, one could also ignore the GUI altogether and use the simulation engine as before, as these are two seperate products.
 
 In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. 
-Available frames of this version of the \textit{GUI} are discussed further in the following sections.
+Available frames of this version of the GUI are discussed further in the following sections.
 \subsection{Simulation Frame}
-This frame spawns and manages the \textit{simulation engine}, configures and starts the simulation. 
-It has a progress bar that shows the current progress of the simulation, communucating with \textit{UI handler thread} in \textit{simulation engine}.
+This frame spawns and manages the simulation engine, configures and starts the simulation. 
+It has a progress bar that shows the current progress of the simulation, communucating with UI handler thread in simulation engine.
 Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
@@
     \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
-    \caption{Render frame of \textit{GUI}.}
+    \caption{Render frame of GUI.}
     \label{fig:gui_render_1}
@@
     \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
-    \caption{Analyze frame of \textit{GUI} E distribution.}
+    \caption{Analyze frame of GUI E distribution.}
     \label{fig:gui_analyze_Edist}
@@
     \includegraphics[width=0.9\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
-    \caption{Analyze frame of \textit{GUI} E(t).}
+    \caption{Analyze frame of GUI E(t).}
     \label{fig:gui_analyze_Et}
@@
     \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
-    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ $\mu E$ result.}
+    \caption{Sweep frame of GUI $\phi_{lag}$ $\mu E$ result.}
     \label{fig:gui_sweep_muE}
@@
     \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
-    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ sweep $\sigma E$ result.}
+    \caption{Sweep frame of GUI $\phi_{lag}$ sweep $\sigma E$ result.}
     \label{fig:gui_sweep_sE}

### 2023-12-03 subsections/simulation/intermediate_versions/intermediate.tex
calistay puısh

@@
     \end{subfigure}
-    \caption{$L_{out}$ Optimization For Single \e.}
+    \caption{$L_{out}$ Optimization for Single \e.}
     \label{fig:lout_opt_single_e}
@@
     \end{subfigure}
-    \caption{* and \% operators of \textit{vector3d} class.}
+    \caption{* and \% operators of vector3d class.}
     \label{fig:vector3d_dot_cross_product}
@@
     \end{minted}
-\caption{An example \textit{config.in} file.}
+\caption{An example config.in file.}
 \label{fig:config_file}
@@
     \end{tabular}
-    \caption{\textit{Leap-frog} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \caption{Leap-frog data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{tab:lf_mag_table}
@@
     \end{tabular}
-    \caption{\textit{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
+    \caption{RK4-2} data on \\$E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns}
     \label{tab:rk2_mag_table}

### 2023-12-03 subsections/theory/programming/programming.tex
push of institute online check version
calistay puısh

@@
 %%%%%%
-
+\clearpage
 \section{Basic Concepts in Programming}
@@
 Table below shows the amount of clock cycles required for some mathematical calculations in various processors.
-\vspace{20pt}
-\begin{figure}[h!]
+
+Note that division is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
+Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
+
+\begin{figure}[H]
     \centering
@@
 
-Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.
-Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
-
 \subsection{Concurrency}

### 2023-12-03 subsections/tools/numericalmethods/leap-frog-runge-kutta.tex
enstitü versiyonu
push of institute online check version
fix of euler method buthcer tableau caption
calistay puısh

@@
 %%%%%%
-
+\clearpage
 \section{Algorithms}
@@
 \end{figure}
-The simplest Runge-Kutta method is the \textit{Euler's method} with the following \textit{Butcher tableau},
+
+The simplest Runge-Kutta method is the Euler's method the Butcher tableau of which can be observed in \fromfig{Butcher_euler}.
+
+\begin{figure}[h!]
 \[ 

### 2024-01-07 msthesis.tex
Spiral corrected

@@
 \usepackage{xcolor}
+\usepackage{showframe}
 
@@
     % Then Greek symbols in alphabetical order
+    \sym{$\beta$}{Beta Factor}
     \sym{$\gamma$}{Lorentz Factor}
-    \sym{$\beta$}{Beta Factor}
     \sym{$\phi_{lag}$}{Phase Lag}
@@
    \sym{KAHVELab}{Kandilli Detector Accelerator and \\Instrumentation Laboratory}
+   \vspace{10pt}
    \sym{LF}{Leap-Frog}
@@
 
-\subsection{Relation between momentum and acceleration}
+\subsection{Relation Between Momentum and Acceleration}
 In classical mechanics, Newton's second law defines force, $\vecthreeBF{F}$, and relation
@@
     \deriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \deriv{\vecthree{v}}{t}  \} .
-    \vspace{-10pt}
+    \vspace{-15pt}
 \end{eqnarray}
-\vspace{-30pt}
+\vspace{-35pt}
 \newline
 Therefore force can be written as
-\vspace{-15pt}
+\vspace{-20pt}
 \begin{equation} \label{eq:Frel}
     \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \} .
-    \vspace{-10pt}
+    \vspace{-15pt}
 \end{equation}
-\clearpage
+
 It is clear that acceleration is not necessarily parallel to the force. 
@@
 where 
-\vspace{-10pt}
+\vspace{-17pt}
 \begin{eqnarray}
@@
                                 &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} .
-                                \vspace{-10pt}
 \end{eqnarray}
+
+\vspace{-40pt}
+\noindent
 Then, $\gamma^2 \beta^2 + 1 = \gamma^2 $ and \fromeq{a_F_parallels} can be used to achieve
-\vspace{-10pt}
+\vspace{-20pt}
 \begin{eqnarray}
@@
                         &=& m_0 \gamma^3 \vecthreeBF{a}_{||} . \label{eq:Frel_parallel}
+\end{eqnarray}
+
+\vspace{-41pt}
+\noindent
+Therefore from \fromeqs{Frel}{Frel_parallel}, force can be rearranged as
 \vspace{-20pt}
-\end{eqnarray}
-Therefore from \fromeqs{Frel}{Frel_parallel}, force can be rearranged as
-\vspace{-10pt}
 \begin{eqnarray}
@@
                     &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp} .
-                    \vspace{-10pt}
 \end{eqnarray}
 
+\vspace{-20pt}
 We finally have two separate equations which are in similar form with \fromeq{newton_second_law},
-\vspace{-10pt}
+\vspace{-20pt}
 \begin{equation} \label{eq:Frel_para_and_perp}
@@
     \end{aligned}
+    \vspace{-18pt}
 \end{equation}
@@
 Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by 
-\vspace{-10pt}
+\vspace{-12pt}
 \begin{equation} \label{eq:lf}
     \frac{d \vecthree{p}}{d t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B}) , 
-    \vspace{-10pt}
+    \vspace{-12pt}
 \end{equation}
@@
 Similar to non-relativistic version, relativistic Lorentz Force is given by the 4-vector equality
-\vspace{-10pt}
+\vspace{-11pt}
 \begin{equation}
     \frac{d p^{\mu}}{d \tau} = q F^{\mu \nu} u_{\nu} ,
-    \vspace{-10pt}
+    \vspace{-11pt}
 \end{equation}
@@
 \vspace{-10pt}
-\begin{equation*}
+\begin{equation}
     \begin{aligned}
@@
     \end{aligned} ,
-    \qquad\qquad
+    \quad
     \begin{aligned}
@@
     \vspace{-10pt}
-\end{equation*}
+\end{equation}
 where $W$ is the energy of the particle and $\gamma$ is the Lorentz factor mentioned in the previous section.
@@
 For $ \mu = 0 $, we have the time component of the equation as
-\vspace{-10pt}
+\vspace{-12pt}
 \begin{eqnarray}
@@
     \frac{d W}{d t} &=& q \frac{\vecthree{E}\cdot d \vecthree{r}} {d t} .
-    \vspace{-10pt}
 \end{eqnarray}
+
+\vspace{-33pt}
+\noindent
 This is the definition of work done by an electric field. For $ \mu = 1,2,3 $, we have the spacial components
-\vspace{-10pt}
-\begin{equation*}
+\vspace{-11pt}
+\begin{equation}
     \frac{d \vecthree{p}}{d \tau} = \gamma \frac{d \vecthree{p}}{d t} = q \gamma (\vecthree{E} + \vecthree{v} \times \vecthree{B}) ,
-    \vspace{-10pt}
-\end{equation*}
+    \vspace{-11pt}
+\end{equation}
 which simplifies to non-relativistic Lorentz Force in \fromeq{lf}.
 
-\subsection{Acceleration caused by Lorentz force}
+\subsection{Acceleration Caused by Lorentz Force}
 Due to the nature of the cross product, Lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
@@
 \vspace{-10pt}
-\begin{equation*}
+\begin{equation}
     \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B} .
-    \vspace{-10pt}
-\end{equation*}
+    \vspace{-20pt}
+\end{equation}
 The same thing cannot be said about electric field however. 
 It can create force in any direction with respect to velocity. Therefore, we have the equality
-\vspace{-10pt}
+\vspace{-15pt}
 \begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
@@
 Acceleration due to electric field can be simplified as
-\vspace{-10pt}
+\vspace{-20pt}
 \begin{eqnarray}
@@
                                 &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} .
-                                \vspace{-10pt}
 \end{eqnarray}
+
+\vspace{-27pt}
+\noindent
 Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
@@
     \end{aligned}
-    \vspace{-10pt}
+    \vspace{-12pt}
 \end{equation}
@@
 Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/kahvelab_linac.png}
-    \vspace{20pt}
+
+\vspace{22pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.7\textwidth]{./figures/kahvelab_linac.png}
+    %\vspace{22pt}
+    \vspace{-1pt}
     \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}.}
@@
     \centering
-    \includegraphics[width=.75\textwidth]{./figures/pill_box.jpeg}
-    \vspace{20pt}
+    \includegraphics[width=.5\textwidth]{./figures/pill_box.jpeg}
+    %\vspace{22pt}
+    \vspace{-1pt}
     \caption{An RF cavity used in KAHVELab.}
@@
 
+\vspace{-15pt}
 In addition to accelerating the particles, RF cavities are often designed to provide focusing forces. 
@@
 
-\subsubsection{Resonance Frequency}
+\subsubsection{\hspace{4pt}Resonance Frequency}\hspace{4pt}
 Resonance frequency is the frequency in which the electromagnetic fields form standing waves in a cavity.
@@
 
-\subsubsection{Bunch}
+\subsubsection{\hspace{4pt}Bunch}\hspace{4pt}
 Bunch refers to a tightly grouped collection of charged particles, such as electrons or protons, that are accelerated and maintained close together within a particle accelerator.
 
-\subsubsection{Phase Stability}
+\subsubsection{\hspace{4pt}Phase Stability}\hspace{4pt}
 Phase stability refers to the preservation of the timing relationship between particles and fields within an accelerator. 
@@
 
-\subsubsection{Phase Lag}
+\subsubsection{\hspace{4pt}Phase Lag}\hspace{4pt}
 Phase lag refers to the time delay between the oscillations of two interacting waveforms or particles. 
@@
 
-\subsubsection{Shunt Impedance}
+\subsubsection{\hspace{4pt}Shunt Impedance}\hspace{4pt}
 The shunt impedance of an RF accelerator is a measure of the efficiency 
@@
 Rhodotron Accelerator is a type of particle accelerator that was proposed by Jacques POTTIER in 1989 \cite{rhodo_pottier}. 
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. It is named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
+First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. It is named after the greek word for rose, rhodos, due to the shape of the design \cite{rhodos}.
 
@@
 
-\subsubsection{Acceleration Cycle of Rhodotron}
-
+\subsubsection{\hspace{4pt}Acceleration Cycle of Rhodotron}\hspace{4pt}
 Electrons undergo four different stages inside the accelerator. 
@@
 
-\subsubsection{Cavity of a Rhodotron} \label{sec:cavity_of_a_rhodotron}
-
+\subsubsection{\hspace{4pt}Cavity of a Rhodotron}\hspace{4pt} \label{sec:cavity_of_a_rhodotron}
 Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
@@
 \end{figure} \fi
+\vspace{22pt}
 \begin{figure}[H]
@@
     \qquad\subfigure[\centering $\vecthreeBF{B}$ field]{{\includegraphics[width=0.45\textwidth]{./figures/cst/cavity_B_field_dist.png} }}%
-    \vspace{20pt}
+    %\vspace{22pt}
+    \vspace{4pt}
     \caption{$\vecthreeBF{E}$ and $\vecthreeBF{B}$ eigenmode field distributions inside a coaxial cavity.}
@@
 \end{figure}
+\vspace{-15pt}
 For a cavity defined by the volume between two coaxial cylinders of equal lengths ($h$) with radii of $R_1$ and $R_2$, where $R_1 < R_2$, located at the origin (\fromfig{int_curve}),
 first eigenmode solution of the $E$ and $B$ fields are \cite{rhodo_pottier}
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-12pt}
+\begin{eqnarray}
     E &=& \frac{E_0}{r} \cos\left( \frac{\pi z}{h} \right) \sin \left( \omega t + \phi \right)  , \\
     B &=& \frac{B_0}{r} \sin\left( \frac{\pi z}{h}\right) \cos\left( \omega t + \phi\right)  ,
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-33pt}
+\noindent
 where $\omega=2\pi f$, $f$ is the resonance frequency.
@@
     \includegraphics[width=.55\textwidth]{./figures/illustrations/rhodo_integral_curve.pdf}
-    \vspace{20pt}
+    %\vspace{5pt}
+    \vspace{-20pt}
     \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}.}
@@
 
+\vspace{-15pt}
 Because acceleration potential is located on the $z=0$ plane and $\vecthreeBF{E} \parallel \hat{r}$, $V_{acc}$ can be found by
@@
             &=& 2 E_0 \ln(\frac{R_2}{R_1}). \label{eq:v_acc}
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-30pt}
+\noindent
 Dissipated power $P_{diss}$, on the other hand, can be calculated as \cite{rf}
@@
     P_{diss} &=& \frac{1}{2} \int \int \rho_s | H_{||} |^2 dA \nonumber \\
-             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta . \label{eq:p_diss_C_curve}
-\vspace{-10pt}\end{eqnarray}
+             &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} \int_C | B_{||} |^2 r ds d\theta , \label{eq:p_diss_C_curve}
+\end{eqnarray}
+
+\vspace{-30pt}
+\noindent
 where $\rho_s$ is the areal skin resistivity ( $\rho_s \approx 2.51 \times 10^{-7} f^{1/2}$ for copper \cite{rhodo_pottier} ), $B=\mu H$, $\mu$ is permeability, $\mu_0$ is the vacuum permability. 
@@
 Since $\vecthreeBF{B}$ is always parallel to the surface we can use $\vecthreeBF{B}$ directly as
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-10pt}
+\begin{eqnarray}
     P_{diss} &=& \frac{\rho_s}{2\mu_0^2} \int_0^{2\pi} (
@@
     I_C &=& \int_{R_1}^{R_2} |B|^2 r dr \Big|_{z=\frac{h}{2}} = B_0^2 \ln(\frac{R_2}{R_1}) .
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-30pt}
+\noindent
 Inserting $H_0=B_0/\mu_0$, finally we have the dissipated power
@@
 Therefore, from \fromeq{shunt}, using \fromeqs{v_acc}{p_diss} also $E_0/H_0 = Z_0 \approx 120 \pi$ we have
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-10pt}
+\begin{eqnarray}
     Z_s &=& \frac{4E_0^2}{H_0^2 \pi \rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{2R_1} + \frac{h}{2R_2} + 2 \ln(\frac{R_2}{R_1}))} \nonumber\\
         &=& \frac{8 \pi 60^2}{\rho_s} \frac{ \ln^2(\frac{R_2}{R_1})}{(\frac{h}{4}(\frac{1}{R_1} + \frac{1}{R_2}) + \ln(\frac{R_2}{R_1}))}   ,
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-30pt}
+\noindent
 where, time dependencies have been removed from $\vecthreeBF{E}$ and $\vecthreeBF{B}$ 
@@
 Therefore, a more useful parameter called \textit{effective shunt impedance} can be defined as
-\vspace{-10pt}\begin{equation}
+\vspace{-20pt}
+\begin{equation}
     Z_{se} = Z_s T^2  ,
-\vspace{-10pt}\end{equation}
+\end{equation}
+
+\vspace{-40pt}
+\noindent
 where $T$ is the \textit{transit time factor}, a correctional coefficent that contain the changing field effects during acceleration.
-\clearpage
+
 For a relativistic electron crossing the axis at time 0, $T$ can be found by \cite{rhodo_pottier}
@@
     S_i(\theta) &=& \int_0^{\theta} \frac{\sin(x)}{x} dx .
-\vspace{-10pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\vspace{-10pt}
 For a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$ as
-\vspace{-10pt}\begin{equation}
+\vspace{-20pt}\begin{equation}
     T(\phi) = T \cos(\phi) .
-\vspace{-10pt}\end{equation} 
+\vspace{-20pt}\end{equation} 
 Putting all these calculations together, energy gain of a relativistic electron, passing the origin at $\phi / \omega$ as calculated by \textit{J. Pottier} is \cite{rhodo_pottier}
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-18pt}\begin{eqnarray}
     \Delta E &=& q V_{acc}^{ef} \nonumber\\
              &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)  ,
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-40pt}
+\noindent
 where $ V_{acc}^{ef} = V_{acc} T(\phi)$ is the effective accelerating potential.
 If $\Delta E$ is taken in \textit{MeV}, $Z_{se}$ in $M\Omega$ and $P_{diss}$ in \textit{MW}, this equality becomes
-\vspace{-10pt}\begin{equation} \label{eq:W_gain_each_pass_pottier}
+\vspace{-18pt}
+\begin{equation} \label{eq:W_gain_each_pass_pottier}
     \Delta E = Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi) \quad MeV .
-\vspace{-10pt}\end{equation}
-
+\end{equation}
+
+\vspace{-18pt}
 With the expectation that the electrons will accelerate to speeds $\approx c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
@@
 In the \fromfig{pottier_table1}, optimized characteristics of a rhodotron cavity can be observed. 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table1.png}
+\vspace{15pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.8\textwidth]{./figures/pottier_table1_cropped.png}
+    \vspace{-8pt}
     \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}.}
@@
 \end{figure}
+
+\vspace{-15pt}
 Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
@@
 Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $\Delta E \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.9\textwidth]{./figures/pottier_table2.png}
+\vspace{15pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.8\textwidth]{./figures/pottier_table2_cropped.png}
+    \vspace{-13pt}
     \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}.}
@@
 \end{figure}
+
+\vspace{-15pt}
 Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m} as
-\vspace{-10pt}\begin{equation}
+\vspace{-20pt}
+\begin{equation}
     \label{eq:W_total_gain_pottier}
     \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV .
-\vspace{-10pt}\end{equation}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod1.pdf}
+\end{equation}
+
+\vspace{-15pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{./figures/illustrations/rhod1.pdf}
     \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron.}
@@
 \end{figure}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod2.pdf}
+\begin{figure}[!th]
+    \centering
+    \includegraphics[width=0.6\textwidth]{./figures/illustrations/rhod2.pdf}
     \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron.}
@@
     \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod3.pdf}
+    \includegraphics[width=0.6\textwidth]{./figures/illustrations/rhod3.pdf}
     \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron.}
@@
 \end{figure}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{./figures/illustrations/rhod4.pdf}
+
+\vspace{-50pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{./figures/illustrations/rhod4.pdf}
     \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron.}
@@
 
-\clearpage
 \section{Basic Concepts in Programming}
@@
 Although not discussed in the following chapters, mathematical operations were reduced to addition, subtraction and multiplication when found to be possible while developing computationally intensive software in \fromch{simulation}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=.95\textwidth]{./figures/cpu_instruction_speed.png}
-    \vspace{20pt}
-    \caption{Amount of clock cycle for mathematical operations in various processors \cite{cpu_instruction_speed}.}
-\end{figure}
-
 \subsection{Concurrency}
@@
 
+\vspace{18pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.95\textwidth]{./figures/cpu_instruction_speed.png}
+    %\vspace{15pt}
+    \vspace{-3pt}
+    \caption{Amount of clock cycle for mathematical operations in various processors \cite{cpu_instruction_speed}.}
+\end{figure}
+
+\vspace{-5pt}
 Concurrency in single core can be achieved by implementing clever scheduling of list of operations called threads.
@@
 
-\clearpage
 \section{Algorithms}
@@
 The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE can be written as
-\vspace{-10pt}\begin{equation}
+\vspace{-15pt}
+\begin{equation}
     \ddot{x} = \derivS{x}{t} = f(x) .\label{eq:second-order-ODE}
@@
 It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
+
 The idea is straight forward; in the time interval $\Delta t$, 
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}
+\begin{eqnarray}
     a(t_0) &=& f(x_0)   , \\
@@
     v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2} . \label{eq:leapfrog_sync_v}
-\vspace{-10pt}\end{eqnarray}
-For more stability, this version can be rearranged to what is called 'kick-drift-kick' form as
-\vspace{-10pt}\begin{eqnarray} \label{eq:leapfrog}
+\end{eqnarray}
+
+\vspace{-40pt}
+\noindent
+For more stability, this version can be rearranged to what is called `kick-drift-kick' form as
+\vspace{-20pt}
+\begin{eqnarray} \label{eq:leapfrog}
     v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2}   ,  \\
@@
     v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2} . 
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-40pt}
+\noindent
 This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.
@@
 used to solve ordinary differential equations (ODEs) that are in the form as
-\vspace{-10pt}\begin{equation} \label{eq:first-order-ODE}
+\vspace{-15pt}\begin{equation} \label{eq:first-order-ODE}
     \deriv{y}{x} = f(x, y) .
 \vspace{-10pt}\end{equation}
+
+\vspace{-20pt}
+\noindent
 The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
 of function evaluations at different points within each step as
-\vspace{-10pt}\begin{equation} \label{eq:general-rk}
+\vspace{-15pt}\begin{equation} \label{eq:general-rk}
     \begin{aligned}
@@
     \end{aligned}
-\vspace{-10pt}\end{equation}
+\end{equation}
+
+\vspace{-35pt}
+\noindent
 where 
-\vspace{-10pt}\begin{eqnarray} \label{eq:general-rk-coef}
+\vspace{-15pt}\begin{eqnarray} \label{eq:general-rk-coef}
     k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j) .
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-35pt}
+\noindent
 These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a particular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
@@
     \]
+    \vspace{-24pt}
     \caption{Butcher Tableau.}
@@
 
+\vspace{-13pt}
 The simplest Runge-Kutta method is the Euler's method the Butcher tableau of which can be observed in \fromfig{Butcher_euler}.
 
-\begin{figure}[h!]
+\begin{figure}[H]
 \[ 
@@
 \] 
+\vspace{-24pt}
 \caption{Butcher tableau of Euler's method.}
@@
 
+\vspace{-15pt}
 The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
@@
     \end{minipage}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Butcher Tableau for RK4.}
@@
 Simulation tools such as CST Studio and Poisson Superfish can be used to confirm this condition.
-\clearpage
+
+In the \fromfigth{107_simple_cavity_design}{180_simple_cavity_design}{cst_simple_cavity_designs}, 
+Poisson Superfish and CST simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
+
 In the following examples, $p=1$ from \fromfig{pottier_table1} was used, and it will be the focus of all further calculations.
 Using $f_{RF}=107.5$ MHz \& $f_{RF}=180$ MHz for comparison:
-\vspace{-20pt}\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
+\vspace{-30pt}
+\begin{eqnarray} \label{eq:107_180_MHZ_cavity_design_parameters}
     \begin{aligned}
@@
     \end{aligned}
-\vspace{-10pt}\end{eqnarray}
-In the \fromfigth{107_simple_cavity_design}{180_simple_cavity_design}{cst_simple_cavity_designs}, 
-Poisson Superfish and CST simulations of two cavities defined by \fromeq{107_180_MHZ_cavity_design_parameters} can be observed.
+\end{eqnarray}
+
+\vspace{-10pt}
 \iffalse
@@
     \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.45\textwidth]{./figures/superfish/superfish180.png} }}%
-    \vspace{20pt}
+    %\vspace{20pt}
+    \vspace{5pt}
     \caption{\centering Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
@@
 \fi
-\vspace{20pt}
 \begin{figure}[H]
@@
     \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.44\textwidth]{./figures/cst/cst180.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
     \label{fig:180_simple_cavity_design}
-    \vspace{20pt}
+    \vspace{5pt}
 \end{figure}
@@
     \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.47\textwidth]{./figures/cst/cst180_e.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
     \label{fig:cst_simple_cavity_designs}
-\end{figure}
+    \vspace{-10pt}
+\end{figure}
+
 As mentioned by Pottier, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
 In the \fromfig{107_180_modified_cavities_superfish}, Poission Superfish results of such a modification with matching height increase to keep resonant frequency can be found.
+
+\vspace{20pt}
 \iffalse
@@
     \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.45\textwidth]{./figures/superfish/superfish180mod.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering Poisson Superfish field results of truncated cavities.} 
     \label{fig:107_180_modified_cavities_superfish}
-    \vspace{20pt}
+    \vspace{10pt}
 \end{figure}
@@
     \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.47\textwidth]{./figures/cst/cst180mod.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering CST eigenmode results of truncated cavities.} 
@@
 
+\vspace{8pt}
 \iffalse
@@
     \centering
-    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.46\textwidth]{./figures/cst/cst107mod_e.png} }}%
-    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.44\textwidth]{./figures/cst/cst180mod_e.png} }}%
-    \vspace{20pt}
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.44\textwidth]{./figures/cst/cst107mod_e.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.42\textwidth]{./figures/cst/cst180mod_e.png} }}%
+    \vspace{5pt}
     \caption{\centering CST electric field results of truncated cavities.} 
@@
 
+\vspace{10pt}
 \iffalse
@@
     \centering
-    \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.485\textwidth]{./figures/superfish/superfish107_z_highlighted.png} }}%
-    \vspace{20pt}
-    \subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{./figures/superfish/superfish180_z_highlighted.png} }}%
-    \vspace{20pt}
+    \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.465\textwidth]{./figures/superfish/superfish107_z_highlighted.png} }}%
+    \vspace{5pt}
+    \subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.475\linewidth]{./figures/superfish/superfish180_z_highlighted.png} }}%
     \caption{\centering Poisson Superfish calculations with unmodified cavities.} 
@@
     \centering
-    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.475\textwidth]{./figures/superfish/superfish107mod_z_highlighted.png} }}%
-    \vspace{20pt}
-    \subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{./figures/superfish/superfish180mod_z_highlighted.png} }}%
-    \vspace{20pt}
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.455\textwidth]{./figures/superfish/superfish107mod_z_highlighted.png} }}%
+    \vspace{5pt}
+    \subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.480\textwidth]{./figures/superfish/superfish180mod_z_highlighted.png} }}%
+    \vspace{5pt}
     \caption{\centering Poisson Superfish calculations with truncated cavities.} 
@@
 \end{figure}
+
+\vspace{-10pt}
 One can observe the shunt impedance gain between truncated and unmodified cavities in \fromfigs{107_cavity_shunt_diff}{180_cavity_shunt_diff} as
-\vspace{-10pt}\begin{equation}
+\vspace{-22pt}\begin{equation}
     \begin{aligned}
@@
     \end{aligned}
-\vspace{-10pt}\end{equation}
-
-\clearpage
+\end{equation}
+
 \section{Magnet Design} \label{sec:magnet_design}
@@
 Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
+
+In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for synchronizing them with the RF field in the cavity. 
+This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
+Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass. 
 \iffalse \begin{figure}[H]
@@
     \centering
-    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/design/Ltot.png} }}%
-    \qquad\subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{./figures/design/tt300_mag.png} }}%
-    \vspace{20pt}
+    \subfigure{{\includegraphics[width=.45\textwidth]{./figures/design/Ltot.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.45\textwidth]{./figures/design/tt300_mag.png} }}%
+    \vspace{0pt}
     \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.} 
     \label{fig:magnet_design_illustrations}
-\end{figure}
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for synchronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass.
+    \vspace{-15pt}
+\end{figure}
 
@@
 In other words, total trajectory of synchronous particle needs to satisfy
-\vspace{-10pt}\begin{equation}
+\vspace{-22pt}\begin{equation}
     L_{pass} = n \lambda .
-\vspace{-10pt}\end{equation} 
+\vspace{-22pt}\end{equation} 
 Since $n>1$ would require unnecessarily long and expensive beam guide and magnets, $n=1$ is the most efficient choice, which leads to
-\vspace{-10pt}\begin{equation}
+\vspace{-22pt}\begin{equation}
     L_{pass} = \lambda .
@@
     \includegraphics[width=.7\linewidth]{./figures/design/magnet_design.png}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Trejectory of a particle in single pass.}
     \label{fig:magnet_design}
-\end{figure}
-\clearpage
+    \vspace{-15pt}
+\end{figure}
+
 From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
 $L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall the constraints are
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-22pt}\begin{eqnarray}
     L_{in} &=& 2R_2   , \\
@@
     \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho . \label{eq:magnet_lambda_constraint}
-\vspace{-20pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\vspace{-20pt}
 After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
 Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}\begin{eqnarray}
     \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  ,\\
@@
     L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 . \label{eq:magnet_L_constraint}
-\vspace{-20pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\vspace{-10pt}
 \fromeqs{magnet_rho_constraint}{magnet_L_constraint} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).
@@
 it can be observed that
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}\begin{eqnarray}
     W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV   ,\\
@@
     \beta_{394keV} &\approx& 0.825 .
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-40pt}
+\noindent
 It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
@@
 Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}\begin{eqnarray}
     L_{pass} &=& K ,\\
     L_{in} + L_{out} &=& K .
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-40pt}
+\noindent
 Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
-\vspace{-10pt}\begin{equation} \label{eq:mag_sweep_constraint}
+\vspace{-20pt}\begin{equation} \label{eq:mag_sweep_constraint}
     L_{out} = K .
-\vspace{-10pt}\end{equation}
-\clearpage
-To start, an optimization criteria for the following pass such as
-\vspace{-10pt}
+\vspace{-15pt}\end{equation}
+
+To start, an optimization criteria for the following pass needs to be selected. 
+Some example criteria can be found in the list below.
 \begin{itemize}
@@
     \item All of the above with decided weights
-\vspace{-10pt}\end{itemize}
-needs be selected.
+\end{itemize}
+
 Using a simulation software such as CST Studio Particle Module, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (sweeping) and analyzing the results.
@@
 After considering the earlier simulations mentioned in \fromsecs{cavity_design}{magnet_design}, an initial design was created.
+
+\vspace{20pt}
 \begin{figure}[H]
@@
     %%\captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{./figures/cst/cst_first_design1.png}
-    \vspace{20pt}
+    \includegraphics[width=.7\linewidth]{./figures/cst/cst_first_design1.png}
+    \vspace{0pt}
     \caption{Initial design of the proposed rhodotron, $\gamma=9^\circ$.}
     \label{fig:initial_design}
-\end{figure}
+    \vspace{-10pt}
+\end{figure}
+
 \iffalse \begin{figure}[H]
@@
     \end{subfigure}
-    \caption{Initial design of the proposed rhodotron.}
+    \caption{Cross sections of initial design.}
     \label{fig:initial_design_cross_section}
@@
     \qquad\subfigure[\centering Cross section at acceleration plane]{{\includegraphics[width=.45\textwidth]{./figures/cst/cst_first_design2.png} }}%
-    \vspace{20pt}
-    \caption{\centering Initial design of the proposed rhodotron.} 
+    \vspace{0pt}
+    \caption{\centering Cross sections of the initial design.} 
     \label{fig:initial_design_cross_section}
+    \vspace{-12pt}
 \end{figure}
@@
 \end{figure} \fi
+
+\vspace{18pt}
 \begin{figure}[H]
@@
     \qquad\subfigure{{\includegraphics[width=.46\textwidth]{./figures/cst/cst_first_magnet_design2.png} }}%
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{\centering Initial magnet design.} 
@@
 \end{figure}
-\vspace{20pt}
+
 \begin{figure}[H]
@@
     %%\captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_first_magnet_design3.png}
-    \vspace{20pt}
+    \includegraphics[width=.7\linewidth]{./figures/cst/cst_first_magnet_design3.png}
+    \vspace{0pt}
     \caption{Magnetic field in acceleration plate of initial magnet design.}
     \label{fig:initial_magnet_design_B}
-\end{figure}
-\clearpage
+    \vspace{-10pt}
+\end{figure}
+
 \fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
@@
 
+\vspace{20pt}
 \begin{figure}[H]
@@
     %%\captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_design2.png}
-    \vspace{20pt}
+    \includegraphics[width=.6\linewidth]{./figures/cst/cst_second_design2.png}
+    \vspace{0pt}
     \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design}, $\gamma=15^\circ$.}
     \label{fig:initial_three_magnet_design}
-\end{figure}
+    \vspace{-10pt}
+\end{figure}
+
 These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using CST Studio Particle Module PIC Solver.
 Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
-\iffalse \begin{figure}[H]
-    %\captionsetup[subfigure]{justification=centering}
-    %\captionsetup{justification=centering}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
-      \caption{One pass simulation of \fromfig{initial_design}}
-    \end{subfigure}
-    \centering
-    \begin{subfigure}[b]{.8\textwidth}
-      \centering
-      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
-      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
-    \end{subfigure}
-    \caption{$|r|$ vs $Energy$ simulation of initial design.}
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure} \fi
-\begin{figure}[H]
-    \centering
-    \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_first_design4.png} }}%
-    \vspace{20pt}
-    \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_second_design3.png} }}%
-    \vspace{20pt}
-    \caption{\centering $|r|$ vs $Energy$ simulation of initial design.} 
-    \label{fig:initial_designs_PIC_phase_space_monitor}
-\end{figure}
+
 The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
@@
 
+\iffalse \begin{figure}[H]
+    %\captionsetup[subfigure]{justification=centering}
+    %\captionsetup{justification=centering}
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/cst/cst_first_design4.png}
+      \caption{One pass simulation of \fromfig{initial_design}}
+    \end{subfigure}
+    \centering
+    \begin{subfigure}[b]{.8\textwidth}
+      \centering
+      \includegraphics[width=\linewidth]{./figures/cst/cst_second_design3.png}
+      \caption{Two pass simulation of \fromfig{initial_three_magnet_design}}
+    \end{subfigure}
+    \caption{$|r|$ vs $Energy$ simulation of initial design.}
+    \label{fig:initial_designs_PIC_phase_space_monitor}
+\end{figure} \fi
+\begin{figure}[H]
+    \centering
+    \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_first_design4.png} }}%
+    \vspace{1pt}
+    \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{./figures/cst/cst_second_design3.png} }}%
+    \vspace{5pt}
+    \caption{\centering $|r|$ vs $Energy$ simulation of initial design.} 
+    \label{fig:initial_designs_PIC_phase_space_monitor}
+\end{figure}
+
 Several improvements were made to KAHVELab Rhodotron initial designs \cite{sinan}.
@@
 Improved designs can be seen in the figures below.
+
 \iffalse \begin{figure}[H]
@@
     \qquad\subfigure{{\includegraphics[width=.47\textwidth]{./figures/cst/cst_sinan_cavity_design2.png} }}%
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{\centering Improved cavity design.} 
@@
 
+\vspace{10pt}
 \begin{figure}[H]
@@
     \includegraphics[width=.7\linewidth]{./figures/cst/cst_second_magnet_design1.png}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Improved magnet design.}
     \label{fig:improved_magnet_design}
+    \vspace{5pt}
 \end{figure}
@@
     \qquad\subfigure{{\includegraphics[width=.443\textwidth]{./figures/cst/cst_second_magnet_design3.png} }}%
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{\centering Cross section and coils of improved magnet design.} 
     \label{fig:improved_magnet_design_cross_section}
+    \vspace{5pt}
 \end{figure}
@@
     \includegraphics[width=.8\linewidth]{./figures/cst/cst_second_magnet_design4.png}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Magnetic field in acceleration plate of improved magnet design.}
@@
 \end{figure}
+
+\vspace{-10pt}
 From \fromfigs{initial_magnet_design_B}{improved_magnet_design_B}, it can be observed that improved magnet design reduces magnetic field leak in enter and exit openings considerably. 
@@
 \end{itemize}
-\clearpage
-\begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-        for (double t=0; t<SimuTime; t+=dT){
-            double RelBeta  = v/c;
-            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-
-            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
-            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
-
-            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
-            v = v + acc*dT*ns;
-
-            RelBeta  = v/c;
-            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
-            Et=RelGamma*E0; 
-        }
-    \end{minted}
-    \vspace{20pt}
-    \caption{Core logic loop of the POC.}
-    \label{fig:POC_core_logic}
-\end{figure}
 
@@
 % f = 107.5
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}\begin{eqnarray}
     E_{Pottier} &=& 0.593 MeV  , \\
@@
     E_{POC} &=& 0.532 MeV . 
-\vspace{-20pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\begin{figure}[H]
+    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        for (double t=0; t<SimuTime; t+=dT){
+            double RelBeta  = v/c;
+            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+
+            double ef=Eradial(r_pos*1000,t,0); // convert position to mm
+            double acc=ef*1E6*eQMratio/(RelGamma*RelGamma*RelGamma);
+
+            r_pos = r_pos + v * dT*ns + 1/2*acc*(dT*ns)*(dT*ns);
+            v = v + acc*dT*ns;
+
+            RelBeta  = v/c;
+            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
+            Et=RelGamma*E0; 
+        }
+    \end{minted}
+    \vspace{-3pt}
+    \caption{Core logic loop of the POC.}
+    \label{fig:POC_core_logic}
+\end{figure}
+
+%\vspace{-15pt}
+
+\vspace{-15pt}
 As can be observed in \fromeq{poc_E_results}, POC software and CST produced similar results; $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.
@@
 
-\subsection{$L_{out}$ Optimization For Single \e} \label{sec:lout_sweep}
+\subsection{$L_{out}$ Optimization for Single \e} \label{sec:lout_sweep}
 Initial step of improving POC towards Rhodotron Simulation was to implement $L_{out}$ optimizations to help optimazing magnet designs, as discussed in \fromsec{parameter_sweep}.
@@
 This approach was taken because the amount of time gun fires, defined as Gun Active Time, $t_g$, is a crucial part of pulsed \e gun design.
-\clearpage
+
 Addition of bunches would immediately proven useful when finding optimal phase lag for bunch entry.
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{-3pt}
     \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
@@
 \end{figure}
-\clearpage
+
+\vspace{-15pt}
 Since $\phi_{lag}$ is relatively easy to change after production, another version of \fromfig{phlag_opt} that was modified for given magnet design parameters was also implemented ({see \fromfig{phlag_opt_n_pass} in \fromapp{intermediate_codes}).
@@
 
-Implementations for \eE and \eB interactions in 3D can be found in \fromfigs{3D_e_E_interaction_first}{3D_e_B_interaction_first}, 
+Implementations for \eE and \eB interactions in 3D can be found in \fromfigs{3D_e_E_interaction_first}{3D_e_B_interaction_first} of \fromapp{intermediate_codes}, 
 where * and \% are, dot-product and cross-product respectably (\fromfig{vector3d_dot_cross_product} of \fromapp{intermediate_codes}).
+
+Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
+For this purpose, gnuplot was integrated into Rhodotron Simulation to produce 2D visualization of acceleration plane. 
+Rendered results could be stored as gif animations. 
+Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
+
+\vspace{20pt}
 \iffalse \begin{figure}[H]
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{-3pt}
     \caption{\eE interaction logic from \fromeq{acc_of_E_and_B}.}
@@
 \end{figure}
-\vspace{20pt}
-\begin{figure}[H]
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
-            vector3d MagneticField::actOn(Electron& e){
-                if (isInside(e.pos) == -1)
-                    return vector3d(0,0,0);
-                vector3d Bfield = getField(e.pos);                        // Calculate B vector
-                vector3d F_m = (e.vel % Bfield)*eQMratio;                 // Calculate F/m vector
-                vector3d acc = (F_m)/e.gamma();                           // Calculate a vector
-                return acc;
-            }
-        \end{minted}
-    \vspace{20pt}
-    \caption{\eB interaction logic from \fromeq{acc_of_E_and_B}.}
-    \label{fig:3D_e_B_interaction_first}
-\end{figure}
-
-Simulating in 3D had one other benefit; it was now possible to visualize the results by rendering the interaction data. 
-For this purpose, gnuplot was integrated into Rhodotron Simulation to produce 2D visualization of acceleration plane. 
-Rendered results could be stored as gif animations. 
-Two of such renders can be seen in \fromfig{example_gnuplot_renders}.
+
 \iffalse \begin{figure}[H]
@@
     \subfigure[\centering Unsyncronized \e gun period, $T_g = 5ns$]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/5ns_gnuplot.png}}}%
-    \vspace{15pt}
+    \vspace{1pt}
     \centering
     \subfigure[\centering Syncronized \e gun period, $T_g = 9.3ns$]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/9_3ns_gnuplot.png}}}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Example gnuplot renders of Rhodotron Simulation, $P=40$kW, $f=107.5$MHz.} 
@@
     \centering
-    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.8\textwidth]{./figures/rhodoSim/mag_lf_001dt.png} }}%
-    \vspace{15pt}
-    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.8\textwidth]{./figures/rhodoSim/mag_lf_00001dt.png} }}%
-    \vspace{15pt}
+    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.9\textwidth]{./figures/rhodoSim/mag_lf_001dt.png} }}%
+    \vspace{1pt}
+    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.9\textwidth]{./figures/rhodoSim/mag_lf_00001dt.png} }}%
+    \vspace{5pt}
     \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T.}
@@
 To test newer approaches, two additional version of  \eEM interaction that are using \fromsec{rungekutta} were added.
-\subsubsection{RK4-1}
+\subsubsection{\hspace{4pt}RK4-1}\hspace{4pt}
 First approach for integrating \fromsec{rungekutta} into \eEM interaction was to calculate $\vecthreeBF{a}_{E}$ and $\vecthreeBF{a}_{B}$ from \fromeq{acc_of_E_and_B} using RK4.
@@
 The implementation can be found in \fromfigs{rk1_B}{rk1_EM}.
-\subsubsection{RK4-2}
+\subsubsection{\hspace{4pt}RK4-2}\hspace{4pt}
 Following the implementation of RK4-1, revisions were made to the integration method for RK4 to replace Leap-frog.
@@
 RK4-1 was decided to be abandoned as it produced the same accuracy in twice the simulation time of RK4-2.
-\clearpage
+
 \iffalse \begin{figure}
@@
     \centering
-    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{./figures/analiz/mag_lf_rk2_dt-E.png} }}%
-    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
-    \vspace{20pt}
+    \vspace{-5pt}
+    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.9\textwidth]{./figures/analiz/mag_lf_rk2_dt-E.png} }}%
+    \vspace{1pt}
+    \subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.9\textwidth]{./figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
+    \vspace{5pt}
     \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
@@
 To investigate the data further, one can define a performance measurement, $F$ as
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}\begin{eqnarray}
     F &\propto& 1/T  , \\
     F &\propto& 1/\Delta E . 
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-15pt}
 When $dt=10^{-5}$ ns was taken as reference point due to providing a good balance of accuracy and computational intensity, 
 relative performance can be calculated as
-\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
+\vspace{-20pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_1}
     \Delta E_{LF} &=& 110 \times 10^{-5} MeV,\\
@@
     F_{LF}/F_{RK} &=& \frac{\Delta E_{RK} \times T_{RK} }{\Delta E_{LF} \times T_{LF}^1} = 1.32 \pm 0.01 .
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-15pt}
 Also, another relative performance can be obsered from the data as
-\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
+\vspace{-20pt}\begin{eqnarray} \label{eq:f_lf_rk_mag_2}
     \Delta E_{LF} (dt=3 \times 10^{-5}) \approx \Delta E_{RK} (dt=5 \times 10^{-5}) &\approx& 32.5 \times 10^{-4} MeV, \\
@@
     F_{LF}/F_{RK} = \frac{T_{RK}(dt=5 \times 10^{-5})}{T_{LF}(dt=3 \times 10^{-5})} &=& 1.4 \pm 0.1.
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
 \clearpage
@@
 After combining \fromeqs{f_lf_rk_mag_1}{f_lf_rk_mag_2}, $F$ can be calculated as
-\vspace{-10pt}\begin{equation}
+\vspace{-20pt}\begin{equation}
     F_{LF}/F_{RK} = 1.36 \pm 0.05.
-\vspace{-10pt}\end{equation}
+\vspace{-20pt}\end{equation}
 Therefore, Leap-frog was found to be the better choice as it provided with $1.36 \pm 0.05$ times accuracy in \eB interactions at a given time with respect to RK4. However,
@@
 \end{figure} \fi
-\vspace{10pt}
+\vspace{20pt}
 \begin{figure}[H]
@@
     \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.389\textwidth]{./figures/illustrations/statE_2.png} }}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Illustration of test setups.}
@@
     E_{exitTH}^1 &=& 5 MeV.
-\vspace{-10pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\vspace{-15pt}
 In the second test on the other hand, the beam would be injected into a different static uniform electric field,
@@
     E_{exitTH}^2 &=& 5 MeV.
-\vspace{-10pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\vspace{-15pt}
 Therefore, in the both tests, the beam was expected to exit $\vecthreeBF{E}$ with $E_{exitTH} = 5$ MeV. 
@@
     \subfigure[\centering Setup-1, $\textbf{V}_{\parallel}$=4MV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/statE_par.png} }}%
-    \vspace{15pt}
+    \vspace{1pt}
     \subfigure[\centering Setup-2, $\textbf{V}_{\perp}$=4MV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/statE_perp.png} }}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns.}
@@
     \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.9\textwidth]{./figures/analiz/90staticE_lf_rk2_dt-E_3.png} }}%
-    \vspace{15pt}
+    \vspace{1pt}
     \subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.9\textwidth]{./figures/analiz/90staticE_lf_rk2_dt-Tsim.png} }}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns.}
@@
 Taking the $dt=10^{-5}$ ns for the reference point as before, using the data
-\vspace{-10pt}\begin{eqnarray*}
+\vspace{-15pt}\begin{eqnarray}
     \begin{aligned}
@@
     \end{aligned}
-\vspace{-20pt}\end{eqnarray*}
+\end{eqnarray}
+
+\vspace{-31pt}
+\noindent
 the relative performances can be calculated as
-\vspace{-10pt}\begin{eqnarray} 
+\vspace{-17pt}\begin{eqnarray} 
     \Delta E_{LF}^1 \times T_{LF}^1 &=& 270 \times 10^{-6} \pm 10^{-6} MeV s, \\ %0.003
@@
     F_{LF}^1/F_{RK}^1 &=& \frac{\Delta E_{RK}^1 \times T_{RK}^1 }{\Delta E_{LF}^1 \times T_{LF}^1} = 2.4 \pm 0.02, \label{eq:f_lf_rk_1}
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-31pt}
+\noindent
 and
-\vspace{-10pt}\begin{eqnarray}  
+\vspace{-17pt}\begin{eqnarray}  
     \Delta E_{LF}^2 \times T_{LF}^2 &=& 160 \times 10^{-5} \pm 10^{-5} MeV s, \\ %0.004
@@
     F_{LF}^2/F_{RK}^2 &=& \frac{\Delta E_{RK}^2 \times T_{RK}^2 }{\Delta E_{LF}^2 \times T_{LF}^2} = 2.0  \pm 0.03. \label{eq:f_lf_rk_2}
-\vspace{-10pt}\end{eqnarray}
-
+\end{eqnarray}
+
+\vspace{-10pt}
 Leap-frog provides $2.4$ times and $2.0$ times less overacceleration per simulation time than 
@@
 and calculating other relative performances as
-\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_3}
+\vspace{-17pt}\begin{eqnarray} \label{eq:f_lf_rk_3}
     \Delta E_{LF}^1 (dt=2 \times 10^{-5}) = \Delta E_{RK}^1 (dt=3 \times 10^{-5}) &=& 45 \times 10^{-6} MeV, \\
@@
     F_{LF}^1/F_{RK}^1 = \frac{T_{RK}^1(dt=3 \times 10^{-5})}{T_{LF}^1(dt=2 \times 10^{-5})} &=& 2.15 \pm 0.02,
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-31pt}
+\noindent
 and
-\vspace{-10pt}\begin{eqnarray} \label{eq:f_lf_rk_4}
+\vspace{-20pt}
+\begin{eqnarray} \label{eq:f_lf_rk_4}
     \Delta E_{LF}^2 (dt=3 \times 10^{-5}) \approx \Delta E_{RK}^2 (dt=5 \times 10^{-5}) &\approx& 470 \times 10^{-6} MeV, \\
@@
     F_{LF}^2/F_{RK}^2 = \frac{T_{RK}^2(dt=5 \times 10^{-5})}{T_{LF}^2(dt=3 \times 10^{-5})} &=& 1.9 \pm 0.1.
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-10pt}
 The last uncertainty was taken high due to the approximation of $467 \approx 471$. After combining \fromeqsf{f_lf_rk_1}{f_lf_rk_2}{f_lf_rk_3}{f_lf_rk_4},
 the performance of Leap-frog relative to RK4 in \eE interaction can be calculated as
-\vspace{-10pt}\begin{equation}\label{eq:lf_rk_eE_relative_performance}
+\vspace{-20pt}\begin{equation}\label{eq:lf_rk_eE_relative_performance}
     F_{LF}/F_{RK} = 2.11 \pm 0.03.
-\vspace{-10pt}\end{equation}
+\vspace{-20pt}\end{equation}
 Therefore, it can be concluded that Leap-frog outperforms RK4 with the relative performance of $2.11 \pm 0.03$ in \eE interactions with static uniform $\vecthreeBF{E}$ field.
@@
 
+\vspace{20pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
+    \vspace{-20pt}
+    \caption{An Illustration of the multithreading architecture.}
+    \label{fig:multh_illustration}
+\end{figure}
+
+\clearpage
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
@@
 or communucating with the GUI that will be disscussed in the next section.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/multh_arc.png}
-    \vspace{20pt}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
 
@@
 Architecture 1 would require constant waiting in worker threads to get mutexes of $\vecthreeBF{E}$ field, especially in RK4.
-\clearpage
+
 Architecture 2 was performing well in configurations with a large number of bunches, but was not increasing performance in lower bunch count configurations as expected.
@@
 % Start of intermediate.tex
-\clearpage
 \section{Graphical User Interface}
@@
 An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}.
-\vspace{10pt}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-\clearpage
+
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
@@
 Available frames of this version of the GUI are discussed further in the following sections.
+\vspace{-10pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{./figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \vspace{-20pt}
+    \caption{An Illustration of the first GUI design.}
+    \label{fig:gui_illustration}
+\end{figure}
+
 \subsection{Simulation Frame}
@@
 It has a progress bar that shows the current progress of the simulation, communucating with UI handler thread in simulation engine.
-Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
+Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_simulation_frame.png}
+    \vspace{-20pt}
+    \caption{Simulate frame of \textit{GUI}.}
+    \label{fig:gui_simulate_1}
+\end{figure}
+
 \clearpage
@@
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_config_frame.png}
+    \vspace{-30pt}
     \caption{The configuration frame of implementated first GUI design.}
@@
     \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_render_frame_5.png}
+    \vspace{-20pt}
     \caption{Render frame of GUI.}
@@
     \includegraphics[width=0.8\linewidth]{./figures/rhodoSim/GUI_analyze_Edist_2.png}
+    \vspace{-20pt}
     \caption{Analyze frame of GUI E distribution.}
@@
     \includegraphics[width=0.9\linewidth]{./figures/rhodoSim/GUI_analyze_Et_3.png}
+    \vspace{-20pt}
     \caption{Analyze frame of GUI E(t).}
@@
     \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_sweep_muE_3.png}
+    \vspace{-20pt}
     \caption{Sweep frame of GUI $\phi_{lag}$ $\mu E$ result.}
@@
     \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_sweep_sE_3.png}
+    \vspace{-20pt}
     \caption{Sweep frame of GUI $\phi_{lag}$ sweep $\sigma E$ result.}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_in_lab.JPG}
-    \vspace{10pt}
+    \vspace{-20pt}
     \caption{Rhodotron in KAHVELab.}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_1.png}
-    \vspace{20pt}
+    \vspace{-20pt}
     \caption{Rhodotron cavity and \e gun.}
@@
     \includegraphics[width=\linewidth]{./figures/design/final_design_2.png}
-    \vspace{20pt}
+    \vspace{-20pt}
     \caption{Vertical cross section of the beam injection line.}
@@
     \includegraphics[angle=90, origin=c, width=\linewidth]{./figures/design/final_design_3.png}
-    \vspace{20pt}
+    \vspace{-40pt}
     \caption{Cross section of the acceleration plane.}
@@
 
-\begin{figure}
+\vspace{-20pt}
+\begin{figure}[H]
     \centering
     \includegraphics[angle=270,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{Technical drawing of the rhodotron cavity \cite{sinan}.}
@@
 \end{figure}
-
-\begin{figure}
+\clearpage
+\begin{figure}[!th]
     \centering
     \includegraphics[angle=270,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \vspace{20pt}
+    \vspace{10pt}
     \caption{Technical drawing of middle part of the cavity which contains the beam line \cite{sinan}.}
@@
     \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.46\textwidth]{./figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{Polishing of the inner surface of cavity.}
     \label{fig:manif_polishing}
+    \vspace{5pt}
 \end{figure}
@@
 \end{figure} \fi
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
     \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.46\textwidth]{./figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
@@
 
-\begin{figure}
+\begin{figure}[H]
     %%\captionsetup{justification=centering}
@@
     \includegraphics[width=.8\linewidth]{./figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Welded sheet bars.}
-\end{figure}
-
-\begin{figure}
+    \vspace{5pt}
+\end{figure}
+
+\begin{figure}[H]
     %%\captionsetup{justification=centering}
@@
     \includegraphics[width=.7\linewidth]{./figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Middle part of the cavity containing the beam line.}
@@
     \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.46\textwidth]{./figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering TIG welding.} 
     \label{fig:manif_welding}
+    \vspace{5pt}
 \end{figure}
@@
     \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.46\textwidth]{./figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering Flanges on the assembled cavity.} 
@@
     \includegraphics[width=.9\linewidth]{./figures/manif/assembled/rhodo_final_cropped.jpeg}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Current stage of the cavity.}
@@
 \begin{itemize}
-    \item Electric and magnetic field import
-    \item Field generator module to directly produce field files from specified cavity
-    \item Synchrotron radiation calculations to determine radiation and energy loss
-    \item \ee interactions
-    \item Redesign of the GUI
-    \item 3D render in GUI
-    \item Refactoring of the \eEM interaction and logging to improve performance
-    \item Refactoring of the GUI Render Frame to improve render speed
-    \item Refactoring the magnet class to introduce field leaks
-    \item Extention of analysis tools in Analyze Frame
-    \item $L_{out}$ sweep in Sweep Frame
+    \item Electric and magnetic field import,
+    \item Field generator module to directly produce field files from specified cavity,
+    \item Synchrotron radiation calculations to determine radiation and energy loss,
+    \item \ee interactions,
+    \item Redesign of the GUI,
+    \item 3D render in GUI,
+    \item Refactoring of the \eEM interaction and logging to improve performance,
+    \item Refactoring of the GUI Render Frame to improve render speed,
+    \item Refactoring the magnet class to introduce field leaks,
+    \item Extention of analysis tools in Analyze Frame,
+    \item $L_{out}$ sweep in Sweep Frame.
 \end{itemize}
@@
 
-% START OF BIBLIOGRAPHY
-
-\begin{thebibliography}{9}
-
-    \bibitem{rhodo_pottier}
-    Jacques Pottier,
-    \emph{A new type of rf electron accelerator: The rhodotron},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Vol. 40–41,
-    No 2,
-    pp 943-945,
-    1989.
-
-    \bibitem{kahvelab_linac}
-    Adıgüzel, A., S. Açıksöz, A. Çağlar, H. Çetinkaya, Ş. Esen, D. Halis, A. Hamparsunoğlu, T.B. İlhan, A. Kılıçgedik, O. Koçer, S. Oğur, S. Öz, A. Özbey, V.E. Özcan and N.G. Ünel
-    \emph{Ion source and LEBT of KAHVELab proton beamline},
-    Journal of Instrumentation,
-    Vol. 18,
-    2023
-
-    \bibitem{rhodo_prototype}
-    Bassaler, J.M., J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
-    \emph{Rhodotron: an accelerator for industrial irradiation},
-    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
-    Volume 68, No. 1–4,
-    Pages 92-95,
-    1992.
-
-    \bibitem{rhodos}
-    Jongen, Y.,
-    \emph{Manufacturing of Electron Accelerators},
-    Ion Beam Applications (IBA) Chemin du Cyclotron 3,
-    B-1348 Louvain-la-Neuve, Belgium.
-    2001.
-
-    \bibitem{rf}
-    Jensen E., in Proceedings of the CAS–CERN Accelerator School: Advanced Accelerator Physics CERN–2014–009,
-    edited by W. Herr, Trondheim, Norway,
-    pp. 405–430,
-    2013.
-
-    \bibitem{cpu_instruction_speed}
-    Fukushima, T., 
-    \emph{Reduction of Round-off Errors in Symplectic Integrators},
-    The Astronomical Journal,
-    Vol. 121,
-    pp. 1768-1775,
-    2001.
-
-    \bibitem{poi-sup}
-    User's Guide for the POISSON / SUPERFISH group of codes, 
-    Los Alamos National Laboratory, New Mexico, USA, 1987. Accessed on Aug 10, 2023.
-
-    \bibitem{root}
-    The European Organization for Nuclear Research, 
-    "ROOT - An Object Oriented Data Analysis Framework Release v6.20/04, 01/04/2020", 2020,
-    https://zenodo.org/record/3895855, accessed on Aug 10, 2023.
-
-    \bibitem{gnuplot}
-    Williams, T, "Gnuplot 5.4: An Interactive
-    Plotting Program", 2020, http://gnuplot.info, accessed on Aug 10, 2023.
-
-    \bibitem{runge}
-    Runge, C. D. T.,
-    \emph{Über die numerische Auflösung von Differentialgleichungen}, 
-    Mathematische Annalen, 
-    Springer, 
-    Vol. 46,
-    No. 2,
-    pp. 167–178,
-    1895.
-
-    \bibitem{kutta}
-    Kutta, W, 
-    \emph{Beitrag zur näherungsweisen Integration totaler Differentialgleichungen}, 
-    Zeitschrift für Mathematik und Physik, 
-    Vol. 46,
-    pp. 435–453,
-    1901.
-
-    \bibitem{cite:rhodo_design}
-    Kleeven, W., M. Abs, J. Brison, E. Forton, J. Hubert and J. Van de Walle,
-    \emph{Design and Simulation Tools for the High-Intensity Industrial Rhodotron Electron Accelerator},
-    9th International Particle Accelerator Conference,
-    2018.
-
-    \bibitem{sinan}
-    Privite communication with Sinan Öz.
-
-\end{thebibliography}
-
-% END OF BIBLIOGRAPHY
+\bibliographystyle{styles/fbe_tez_v11.bst} %Still may have problems\n
+\bibliography{msthesis} %Still may have problems
 
@@
 \chapter{Intermediate Codes} \label{appendix:intermediate_codes}
+\vspace{30pt}
 \begin{figure}[H]
@@
     \end{minipage}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{$L_{out}$ Optimization For Single \e.}
@@
         \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{$\phi_{lag}$ Optimization For Initial Bunch Design.}
@@
 \end{figure}
-\vspace{20pt}
+
+\vspace{5pt}
 \begin{figure}[H]
@@
     \end{minipage}
-    \vspace{20pt}
+
+    \vspace{5pt}
     \caption{* and \% operators of \textit{vector3d} class.}
     \label{fig:vector3d_dot_cross_product}
+\end{figure}
+
+\begin{figure}[H]
+        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+            vector3d MagneticField::actOn(Electron& e){
+                if (isInside(e.pos) == -1)
+                    return vector3d(0,0,0);
+                vector3d Bfield = getField(e.pos);                        // Calculate B vector
+                vector3d F_m = (e.vel % Bfield)*eQMratio;                 // Calculate F/m vector
+                vector3d acc = (F_m)/e.gamma();                           // Calculate a vector
+                return acc;
+            }
+        \end{minted}
+    \vspace{-3pt}
+    \caption{\eB interaction logic from \fromeq{acc_of_E_and_B}.}
+    \label{fig:3D_e_B_interaction_first}
 \end{figure}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{RK4-1 implemenation of \e-$\vecthreeBF{B}$}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{Logic of is \e inside the shape of magnet.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{RK4-1 implemenation of \eEM.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{RK4-2 implemenation of \eEM.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Multithreading main-thread logic.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Multithreading electron assign logic.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Multithreading worker-threads setup logic.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Multithreading worker-thread logic.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{UI-Console handler thread logic.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Electron class definition.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Bunch class definition.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Gun class definition.}
@@
     \end{minted}
-    \vspace{10pt}
+
+    \vspace{5pt}
     \caption{Simulator class definition.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{RhodotronSimulator class definition.}
@@
     \end{minipage}
-    \vspace{20pt}
+
+    \vspace{5pt}
     \caption{CoaxialRFField class definition.}
@@
 \chapter{Example Simulation Runs} \label{appendix:example_simulation_runs}
-
+\vspace{30pt}
 \begin{figure}[H]
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{$\phi_{lag}$, $\rho$ \& $L$ optimization at $P=30$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=1$ns, $E_{in}=40$KeV.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{$\phi_{lag}$ \& $\rho$ \& $L$ optimization at $P=30$KW, $R_1=0.188$m, $R_2=0.753$m, $t_g=0.8$ns, $E_{in}=40$KeV.}
@@
     \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=1.047$MeV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/mag_rk_001dt.png} }}%
-    \vspace{20pt}
+    \vspace{10pt}
     \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.006$MeV]{{\includegraphics[width=0.85\textwidth]{./figures/rhodoSim/mag_rk_00001dt.png} }}%
-    \vspace{20pt}
+
+    \vspace{5pt}
     \caption{\centering Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T using RK4-2.} 
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{An example \textit{config.in} file.}
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{0pt}
 \caption{Example of console output while simulation is running.}
@@
 \chapter{Data and Graphs}\label{appendix:data_graph}
-
+\vspace{30pt}
 \iffalse \begin{figure}[H]
@@
     \subfigure{{\includegraphics[width=0.8\linewidth]{./figures/analiz/lf_rk1_rk2_dt-E_3.png} }}%
-    \vspace{20pt}
+    \vspace{10pt}
     \subfigure{{\includegraphics[width=0.8\linewidth]{./figures/analiz/lf_rk1_rk2_dt-Tsim_3.png} }}%
-    \vspace{20pt}
+
+    \vspace{0pt}
     \caption{\centering Comparing Leap-frog, RK4-1, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.} 
@@
     \subfigure{{\includegraphics[width=0.9\linewidth]{./figures/analiz/staticE_lf_rk2_dt-E.png} }}%
-    \vspace{20pt}
+    \vspace{10pt}
     \subfigure{{\includegraphics[width=0.9\linewidth]{./figures/analiz/staticE_lf_rk2_dt-Tsim.png}}}%
-    \vspace{20pt}
+
+    \vspace{0pt}
     \caption{\centering Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\parallel}$=4MV, $t_{end}=6$ns.} 
@@
 \chapter{Supporting Figures} \label{appendix:supp}
+\vspace{30pt}
 \begin{figure}[H]
@@
     \includegraphics[angle=270,origin=c, width=.8\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
-    \vspace{20pt}
+    \vspace{10pt}
     \caption{Technical drawing of upper part of the cavity \cite{sinan}.}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_simulation_frame.png}
-    \caption{Simulate frame of \textit{GUI}.}
-    \label{fig:gui_simulate_1}
-\end{figure}
-
-\begin{figure}
+\vspace{-30pt}
+\begin{figure}[H]
     \centering
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_render_frame_6.png}
+
+    \vspace{-20pt}
     \caption{Render frame of \textit{GUI}.}
@@
 
-\begin{figure}
+\vspace{-30pt}
+\begin{figure}[H]
     \centering
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_analyze_Et_2.png}
+
+    \vspace{-20pt}
     \caption{Analyze frame of \textit{GUI} E(t).}
@@
 
-\begin{figure}
+\vspace{-30pt}
+\begin{figure}[H]
     \centering
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_running.png}
+
+    \vspace{-20pt}
     \caption{Sweep frame of \textit{GUI}  $\phi_{lag}$ sweep running.}
@@
 
-\begin{figure}
+\vspace{-30pt}
+\begin{figure}[H]
     \centering
     \includegraphics[width=\linewidth]{./figures/rhodoSim/GUI_sweep_sR_3.png}
+
+    \vspace{-20pt}
     \caption{Sweep frame of \textit{GUI}  $\phi_{lag}$ sweep $\sigma R$ result.}

### 2024-01-07 subsections/design/cavity/cavity.tex
Spiral corrected

@@
     \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.45\textwidth]{../../../figures/superfish/superfish180.png} }}%
-    \vspace{20pt}
+    %\vspace{20pt}
+    \vspace{5pt}
     \caption{\centering Poission Superfish results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
@@
     \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.44\textwidth]{../../../figures/cst/cst180.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering CST Eigenmode results for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
     \label{fig:180_simple_cavity_design}
-    \vspace{20pt}
+    \vspace{5pt}
 \end{figure}
@@
     \qquad\subfigure[\centering 180 MHz]{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst180_e.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering CST Electric field solutions for \fromeq{107_180_MHZ_cavity_design_parameters}.} 
     \label{fig:cst_simple_cavity_designs}
+    \vspace{-10pt}
 \end{figure}
+
 As mentioned by Pottier, truncated cone terminations in inner cylinder can improve the shunt empedance $Z$ of the cavity \cite{rhodo_pottier}. 
 In the \fromfig{107_180_modified_cavities_superfish}, Poission Superfish results of such a modification with matching height increase to keep resonant frequency can be found.
+
+\vspace{20pt}
 \iffalse
@@
     \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.45\textwidth]{../../../figures/superfish/superfish180mod.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering Poisson Superfish field results of truncated cavities.} 
     \label{fig:107_180_modified_cavities_superfish}
-    \vspace{20pt}
+    \vspace{10pt}
 \end{figure}
@@
     \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst180mod.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering CST eigenmode results of truncated cavities.} 
@@
     \centering
-    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst107mod_e.png} }}%
-    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.44\textwidth]{../../../figures/cst/cst180mod_e.png} }}%
-    \vspace{20pt}
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.44\textwidth]{../../../figures/cst/cst107mod_e.png} }}%
+    \qquad\subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.42\textwidth]{../../../figures/cst/cst180mod_e.png} }}%
+    \vspace{5pt}
     \caption{\centering CST electric field results of truncated cavities.} 
@@
     \centering
-    \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.485\textwidth]{../../../figures/superfish/superfish107_z_highlighted.png} }}%
-    \vspace{20pt}
-    \subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.495\linewidth]{../../../figures/superfish/superfish180_z_highlighted.png} }}%
-    \vspace{20pt}
+    \subfigure[\centering 107.5 MHz unmodified]{{\includegraphics[width=.465\textwidth]{../../../figures/superfish/superfish107_z_highlighted.png} }}%
+    \vspace{5pt}
+    \subfigure[\centering 180 MHz unmodified]{{\includegraphics[width=0.475\linewidth]{../../../figures/superfish/superfish180_z_highlighted.png} }}%
     \caption{\centering Poisson Superfish calculations with unmodified cavities.} 
@@
     \centering
-    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.475\textwidth]{../../../figures/superfish/superfish107mod_z_highlighted.png} }}%
-    \vspace{20pt}
-    \subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.5\textwidth]{../../../figures/superfish/superfish180mod_z_highlighted.png} }}%
-    \vspace{20pt}
+    \subfigure[\centering 107.5 MHz truncated]{{\includegraphics[width=.455\textwidth]{../../../figures/superfish/superfish107mod_z_highlighted.png} }}%
+    \vspace{5pt}
+    \subfigure[\centering 180 MHz truncated]{{\includegraphics[width=.480\textwidth]{../../../figures/superfish/superfish180mod_z_highlighted.png} }}%
+    \vspace{5pt}
     \caption{\centering Poisson Superfish calculations with truncated cavities.} 
@@
     \end{aligned}
-\vspace{-10pt}\end{equation}
+\end{equation}
 

### 2024-01-07 subsections/design/first_design/first_design.tex
Spiral corrected

@@
     %%\captionsetup{justification=centering}
-    \includegraphics[width=.5\linewidth]{../../../figures/cst/cst_first_design1.png}
-    \vspace{20pt}
+    \includegraphics[width=.7\linewidth]{../../../figures/cst/cst_first_design1.png}
+    \vspace{0pt}
     \caption{Initial design of the proposed rhodotron, $\gamma=9^\circ$.}
     \label{fig:initial_design}
+    \vspace{-10pt}
 \end{figure}
+
 \iffalse \begin{figure}[H]
@@
     \qquad\subfigure[\centering Cross section at acceleration plane]{{\includegraphics[width=.45\textwidth]{../../../figures/cst/cst_first_design2.png} }}%
-    \vspace{20pt}
-    \caption{\centering Initial design of the proposed rhodotron.} 
+    \vspace{0pt}
+    \caption{\centering Cross sections of the initial design.} 
     \label{fig:initial_design_cross_section}
+    \vspace{-12pt}
 \end{figure}
@@
     \qquad\subfigure{{\includegraphics[width=.46\textwidth]{../../../figures/cst/cst_first_magnet_design2.png} }}%
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{\centering Initial magnet design.} 
@@
 \end{figure}
+
+\begin{figure}[H]
+    \centering
+    %%\captionsetup{justification=centering}
+    \includegraphics[width=.7\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
+    \vspace{0pt}
+    \caption{Magnetic field in acceleration plate of initial magnet design.}
+    \label{fig:initial_magnet_design_B}
+    \vspace{-10pt}
+\end{figure}
+
+\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
+After adding two more magnets and using $\gamma=15^\circ$, the second prototype design was created (\fromfig{initial_three_magnet_design}).
+
 \vspace{20pt}
@@
     %%\captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_first_magnet_design3.png}
-    \vspace{20pt}
-    \caption{Magnetic field in acceleration plate of initial magnet design.}
-    \label{fig:initial_magnet_design_B}
-\end{figure}
-\clearpage
-\fromfig{initial_magnet_design_B} shows that this design provides relatively uniform magnetic field inside, although magnetic field gradient in the openings can be improved.
-After adding two more magnets and using $\gamma=15^\circ$, the second prototype design was created (\fromfig{initial_three_magnet_design}).
-
-\begin{figure}[H]
-    \centering
-    %%\captionsetup{justification=centering}
-    \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_design2.png}
-    \vspace{20pt}
+    \includegraphics[width=.6\linewidth]{../../../figures/cst/cst_second_design2.png}
+    \vspace{0pt}
     \caption{Initial cavity with three magnets as shown in \fromfig{initial_magnet_design}, $\gamma=15^\circ$.}
     \label{fig:initial_three_magnet_design}
+    \vspace{-10pt}
 \end{figure}
+
 These designs, together with $40$ keV $e^-$ gun injecting with phase lag of $15^\circ$ for $1$ ns, was simulated at RF power of $12$ kW using CST Studio Particle Module PIC Solver.
 Results of these simulations can be found in \fromfig{initial_designs_PIC_phase_space_monitor}.
+
+The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
+When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
+Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
+This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
+
+After various similar observations in CST similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
+as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
+The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.
+
 \iffalse \begin{figure}[H]
@@
     \subfigure[\centering One pass simulation of \fromfig{initial_design}]{{\includegraphics[width=.8\textwidth]{../../../figures/cst/cst_first_design4.png} }}%
-    \vspace{20pt}
+    \vspace{1pt}
     \subfigure[\centering Two pass simulation of \fromfig{initial_three_magnet_design}]{{\includegraphics[width=.8\textwidth]{../../../figures/cst/cst_second_design3.png} }}%
-    \vspace{20pt}
+    \vspace{5pt}
     \caption{\centering $|r|$ vs $Energy$ simulation of initial design.} 
@@
 \end{figure}
-The behavior of the beam in the \fromfig{initial_designs_PIC_phase_space_monitor} after the first pass indicates that phase stability is not maintained. 
-When the simulation results are examined further, it was observed that the beam started the second pass at $t \approx 12$ ns after the injection. 
-Considering the starting phase lag $\phi_{lag}=15^\circ$, this would mean phase lag of the second pass was $\phi_{lag2}=120^\circ$.
-This result can be observed in \fromfig{initial_designs_PIC_phase_space_monitor}, as the beam decelerates after a short acceleration in the beginning of the second pass.
-
-After various similar observations in CST similations, underlying cause of this problem was thought to be the $L_{pass} = n \lambda$ approach on magnet design failing in low energies, 
-as anticipated and discussed earlier in the \fromsec{parameter_sweep}.
-The necessity for an alternative tool, capable of aiding researchers in improving beam behavior, was deemed evident.
 
@@
     \qquad\subfigure{{\includegraphics[width=.47\textwidth]{../../../figures/cst/cst_sinan_cavity_design2.png} }}%
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{\centering Improved cavity design.} 
@@
     \includegraphics[width=.7\linewidth]{../../../figures/cst/cst_second_magnet_design1.png}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Improved magnet design.}
     \label{fig:improved_magnet_design}
+    \vspace{5pt}
 \end{figure}
@@
     \qquad\subfigure{{\includegraphics[width=.443\textwidth]{../../../figures/cst/cst_second_magnet_design3.png} }}%
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{\centering Cross section and coils of improved magnet design.} 
     \label{fig:improved_magnet_design_cross_section}
+    \vspace{5pt}
 \end{figure}
@@
     \includegraphics[width=.8\linewidth]{../../../figures/cst/cst_second_magnet_design4.png}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Magnetic field in acceleration plate of improved magnet design.}

### 2024-01-07 subsections/design/magnet/magnet.tex
Spiral corrected

@@
 %%%%%%
-\clearpage
 \section{Magnet Design} \label{sec:magnet_design}
@@
     \centering
-    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/Ltot.png} }}%
-    \qquad\subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/tt300_mag.png} }}%
-    \vspace{20pt}
+    \subfigure{{\includegraphics[width=.45\textwidth]{../../../figures/design/Ltot.png} }}%
+    \qquad\subfigure{{\includegraphics[width=.45\textwidth]{../../../figures/design/tt300_mag.png} }}%
+    \vspace{0pt}
     \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.} 
     \label{fig:magnet_design_illustrations}
+    \vspace{-15pt}
 \end{figure}
-In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for synchronizing them with the RF field in the cavity. 
-This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
-Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass.
 
@@
     \includegraphics[width=.7\linewidth]{../../../figures/design/magnet_design.png}
-    \vspace{20pt}
+    \vspace{0pt}
     \caption{Trejectory of a particle in single pass.}
     \label{fig:magnet_design}
+    \vspace{-15pt}
 \end{figure}
-\clearpage
+
 From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
 $L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall the constraints are
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-22pt}\begin{eqnarray}
     L_{in} &=& 2R_2   , \\
@@
     \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho . \label{eq:magnet_lambda_constraint}
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
 
+\vspace{-20pt}
 After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
 Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-20pt}\begin{eqnarray}
     \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  ,\\
@@
     L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 . \label{eq:magnet_L_constraint}
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
 
+\vspace{-10pt}
 \fromeqs{magnet_rho_constraint}{magnet_L_constraint} define 2 constraints. As already discussed, it has been assumed that cavity design is set (\textit{i.e} $R_2$, $\lambda$, $d$ are already defined).

### 2024-01-07 subsections/simulation/gui/gui.tex
Spiral corrected

@@
 An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}.
-\vspace{10pt}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
-    \caption{An Illustration of the first GUI design.}
-    \label{fig:gui_illustration}
-\end{figure}
-\clearpage
+
 This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
@@
 Available frames of this version of the GUI are discussed further in the following sections.
+\vspace{-10pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
+    \vspace{-20pt}
+    \caption{An Illustration of the first GUI design.}
+    \label{fig:gui_illustration}
+\end{figure}
+
 \subsection{Simulation Frame}
@@
     \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
+    \vspace{-30pt}
     \caption{The configuration frame of implementated first GUI design.}
@@
     \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
+    \vspace{-20pt}
     \caption{Render frame of GUI.}
@@
     \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
+    \vspace{-20pt}
     \caption{Analyze frame of GUI E distribution.}
@@
     \includegraphics[width=0.9\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
+    \vspace{-20pt}
     \caption{Analyze frame of GUI E(t).}
@@
     \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
+    \vspace{-20pt}
     \caption{Sweep frame of GUI $\phi_{lag}$ $\mu E$ result.}
@@
     \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
+    \vspace{-20pt}
     \caption{Sweep frame of GUI $\phi_{lag}$ sweep $\sigma E$ result.}

### 2024-01-07 subsections/simulation/intermediate_versions/intermediate.tex
Spiral corrected

@@
     \subfigure[\centering Unsyncronized \e gun period, $T_g = 5ns$]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/5ns_gnuplot.png}}}%
-    \vspace{15pt}
+    \vspace{1pt}
     \centering
     \subfigure[\centering Syncronized \e gun period, $T_g = 9.3ns$]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/9_3ns_gnuplot.png}}}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Example gnuplot renders of Rhodotron Simulation, $P=40$kW, $f=107.5$MHz.} 
@@
     \centering
-    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.8\textwidth]{../../../figures/rhodoSim/mag_lf_001dt.png} }}%
-    \vspace{15pt}
-    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.8\textwidth]{../../../figures/rhodoSim/mag_lf_00001dt.png} }}%
-    \vspace{15pt}
+    \subfigure[\centering $dt=10^{-2}$ns, $\Delta E=2.783$MeV]{{\includegraphics[width=0.9\textwidth]{../../../figures/rhodoSim/mag_lf_001dt.png} }}%
+    \vspace{1pt}
+    \subfigure[\centering $dt=10^{-4}$ns, $\Delta E=0.011$MeV]{{\includegraphics[width=0.9\textwidth]{../../../figures/rhodoSim/mag_lf_00001dt.png} }}%
+    \vspace{5pt}
     \caption{Energy gain of $1$MeV bunch in \textbf{B}=$0.1$T.}
@@
     \centering
-    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png} }}%
-    \qquad\subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.8\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
-    \vspace{20pt}
+    \vspace{-5pt}
+    \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.9\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-E.png} }}%
+    \vspace{1pt}
+    \subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.9\textwidth]{../../../figures/analiz/mag_lf_rk2_dt-Tsim.png} }}%
+    \vspace{5pt}
     \caption{Comparing Leap-frog, RK4-2 performance on \eB interaction $E_{in}=1$MeV, \textbf{B}=$0.1$T, $t_{end}=5$ns.}
@@
     \qquad\subfigure[\centering Setup-2, perpendicular $\vecthreeBF{E}$ field]{{\includegraphics[width=0.389\textwidth]{../../../figures/illustrations/statE_2.png} }}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Illustration of test setups.}
@@
     \subfigure[\centering Setup-1, $\textbf{V}_{\parallel}$=4MV]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/statE_par.png} }}%
-    \vspace{15pt}
+    \vspace{1pt}
     \subfigure[\centering Setup-2, $\textbf{V}_{\perp}$=4MV]{{\includegraphics[width=0.85\textwidth]{../../../figures/rhodoSim/statE_perp.png} }}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Render of the test setups.  $E_{in}=1$ MeV, $t_{end}=6$ ns.}
@@
     \subfigure[\centering $dt$ vs $\Delta E$]{{\includegraphics[width=0.9\textwidth]{../../../figures/analiz/90staticE_lf_rk2_dt-E_3.png} }}%
-    \vspace{15pt}
+    \vspace{1pt}
     \subfigure[\centering $dt$ vs $T_{sim}$]{{\includegraphics[width=0.9\textwidth]{../../../figures/analiz/90staticE_lf_rk2_dt-Tsim.png} }}%
-    \vspace{15pt}
+    \vspace{5pt}
     \caption{Comparing Leap-frog, RK4-2 performance on \eE interaction $E_{in}=1$MeV, $\textbf{V}_{\perp}$=4MV, $t_{end}=6$ ns.}
@@
 
+\vspace{20pt}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\linewidth]{../../../figures/illustrations/multh_arc.png}
+    \vspace{-20pt}
+    \caption{An Illustration of the multithreading architecture.}
+    \label{fig:multh_illustration}
+\end{figure}
+
+\clearpage
 For the current version, a main thread that spawns and manages several other worker threads would be used as can be seen in \fromfig{multh_illustration}.
@@
 or communucating with the GUI that will be disscussed in the next section.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\linewidth]{../../../figures/illustrations/multh_arc.png}
-    \vspace{20pt}
-    \caption{An Illustration of the multithreading architecture.}
-    \label{fig:multh_illustration}
-\end{figure}
 

### 2024-01-07 subsections/simulation/poc/poc.tex
Spiral corrected

@@
 \end{itemize}
-\clearpage
+
+After simulating the synchronous electron mentioned in \fromsec{cavity_of_a_rhodotron} 
+with $\phi_{lag}=15^\circ$, $P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz for one pass, 
+the results from POC, CST and \fromeq{W_gain_each_pass_pottier} were found to be
+% 40 kW total power
+% Emax = 0.96 in old, 2.08 in new version
+% R1 = 0.1882
+% R2 = 0.753
+% f = 107.5
+\vspace{-20pt}\begin{eqnarray}
+    E_{Pottier} &=& 0.593 MeV  , \\
+    E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
+    E_{POC} &=& 0.532 MeV . 
+\end{eqnarray}
+
 \begin{figure}[H]
@@
     \end{minted}
-    \vspace{20pt}
+    \vspace{-3pt}
     \caption{Core logic loop of the POC.}
@@
 
-After simulating the synchronous electron mentioned in \fromsec{cavity_of_a_rhodotron} 
-with $\phi_{lag}=15^\circ$, $P_{diss}=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz for one pass, 
-the results from POC, CST and \fromeq{W_gain_each_pass_pottier} were found to be
-% 40 kW total power
-% Emax = 0.96 in old, 2.08 in new version
-% R1 = 0.1882
-% R2 = 0.753
-% f = 107.5
-\vspace{-10pt}\begin{eqnarray}
-    E_{Pottier} &=& 0.593 MeV  , \\
-    E_{CST} &=& 0.521 MeV  ,  \label{eq:poc_E_results}\\
-    E_{POC} &=& 0.532 MeV . 
-\vspace{-20pt}\end{eqnarray}
+%\vspace{-15pt}
 
+\vspace{-15pt}
 As can be observed in \fromeq{poc_E_results}, POC software and CST produced similar results; $\Delta E_{(POC-CST)}/E_{CST} \approx 2\%$.

### 2024-01-07 subsections/theory/rhodotron/rhodotron.tex
calistay puısh
Spiral corrected

@@
 Special relativity governs the increase in mass and energy of the particles as they approach the speed of light, providing insights into the behavior of matter at high energies.
-% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
+
+\vspace{22pt}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=.9\textwidth]{../../../figures/kahvelab_linac.png}
-    \vspace{20pt}
+    \includegraphics[width=.7\textwidth]{../../../figures/kahvelab_linac.png}
+    %\vspace{22pt}
+    \vspace{-1pt}
     \caption{A linear proton accelerator in KAHVELab \cite{kahvelab_linac}.}
@@
     \centering
-    \includegraphics[width=.75\textwidth]{../../../figures/pill_box.jpeg}
-    \vspace{20pt}
+    \includegraphics[width=.5\textwidth]{../../../figures/pill_box.jpeg}
+    %\vspace{22pt}
+    \vspace{-1pt}
     \caption{An RF cavity used in KAHVELab.}
@@
 
-Rhodotron Accelerator is a type of particle accelerator that was proposed by \textit{Jacques POTTIER} in 1989 \cite{rhodo_pottier}. 
-First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. It is named after the greek word for rose, \textit{rhodos}, due to the shape of the design \cite{rhodos}.
+Rhodotron Accelerator is a type of particle accelerator that was proposed by Jacques POTTIER in 1989 \cite{rhodo_pottier}. 
+First prototype was built at CEA Saclay later in 1992 \cite{rhodo_prototype}. It is named after the greek word for rose, rhodos, due to the shape of the design \cite{rhodos}.
 
@@
 
-\subsubsection{Acceleration cycle of Rhodotron}
-
+\subsubsection{\hspace{4pt}Acceleration Cycle of Rhodotron}\hspace{4pt}
 Electrons undergo four different stages inside the accelerator. 
@@
     \qquad\subfigure[\centering $\vecthreeBF{B}$ field]{{\includegraphics[width=0.45\textwidth]{../../../figures/cst/cavity_B_field_dist.png} }}%
-    \vspace{20pt}
+    %\vspace{22pt}
+    \vspace{4pt}
     \caption{$\vecthreeBF{E}$ and $\vecthreeBF{B}$ eigenmode field distributions inside a coaxial cavity.}
@@
     \includegraphics[width=.55\textwidth]{../../../figures/illustrations/rhodo_integral_curve.pdf}
-    \vspace{20pt}
+    %\vspace{5pt}
+    \vspace{-20pt}
     \caption{Illustration of a simple coaxial cavity with the curve \textbf{C} in \fromeq{p_diss_C_curve}.}
@@
     S_i(\theta) &=& \int_0^{\theta} \frac{\sin(x)}{x} dx .
-\vspace{-10pt}\end{eqnarray}
+\end{eqnarray}
 
+\vspace{-10pt}
 For a relativistic electron crossing the axis at $2\pi f t_0 = \phi$ on the other hand, $T$ needs to be multiplied by $\cos(\phi)$ as
-\vspace{-10pt}\begin{equation}
+\vspace{-20pt}\begin{equation}
     T(\phi) = T \cos(\phi) .
-\vspace{-10pt}\end{equation} 
+\vspace{-20pt}\end{equation} 
 Putting all these calculations together, energy gain of a relativistic electron, passing the origin at $\phi / \omega$ as calculated by \textit{J. Pottier} is \cite{rhodo_pottier}
-\vspace{-10pt}\begin{eqnarray}
+\vspace{-18pt}\begin{eqnarray}
     \Delta E &=& q V_{acc}^{ef} \nonumber\\
              &=& q Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi)  ,
-\vspace{-20pt}\end{eqnarray}
+\end{eqnarray}
+
+\vspace{-40pt}
+\noindent
 where $ V_{acc}^{ef} = V_{acc} T(\phi)$ is the effective accelerating potential.
 If $\Delta E$ is taken in \textit{MeV}, $Z_{se}$ in $M\Omega$ and $P_{diss}$ in \textit{MW}, this equality becomes
-\vspace{-10pt}\begin{equation} \label{eq:W_gain_each_pass_pottier}
+\vspace{-18pt}
+\begin{equation} \label{eq:W_gain_each_pass_pottier}
     \Delta E = Z_{se}^{1/2}P_{diss}^{1/2} \cos(\phi) \quad MeV .
-\vspace{-10pt}\end{equation}
+\end{equation}
 
+\vspace{-18pt}
 With the expectation that the electrons will accelerate to speeds $\approx c$ after the first pass, a rhodotron cavity is designed so that the length of the path between successive passes is an integer multiple of $\lambda$, wavelength of the RF field ($l=p\lambda \label{eq:lpl}$).
@@
 In the \fromfig{pottier_table1}, optimized characteristics of a rhodotron cavity can be observed. 
+\vspace{15pt}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table1.png}
+    \includegraphics[width=.8\textwidth]{../../../figures/pottier_table1_cropped.png}
+    \vspace{-8pt}
     \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}.}
@@
 Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $\Delta E \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
+\vspace{15pt}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table2.png}
+    \includegraphics[width=.8\textwidth]{../../../figures/pottier_table2_cropped.png}
+    \vspace{-13pt}
     \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}.}
@@
 \end{figure}
+
+\vspace{-15pt}
 Total energy gain after $n$ passes, $\Delta E_n$, can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$, $P$ in \textit{W}, $\lambda$ in \textit{m} as
-\vspace{-10pt}\begin{equation}
+\vspace{-20pt}
+\begin{equation}
     \label{eq:W_total_gain_pottier}
     \Delta E_n \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV .
-\vspace{-10pt}\end{equation}
+\end{equation}
 
+\vspace{-15pt}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod1.pdf}
+    \includegraphics[width=0.6\textwidth]{../../../figures/illustrations/rhod1.pdf}
     \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron.}
@@
 \end{figure}
-\begin{figure}[H]
+\begin{figure}[!th]
     \centering
-    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod2.pdf}
+    \includegraphics[width=0.6\textwidth]{../../../figures/illustrations/rhod2.pdf}
     \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron.}
@@
     \centering
-    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod3.pdf}
+    \includegraphics[width=0.6\textwidth]{../../../figures/illustrations/rhod3.pdf}
     \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron.}
@@
 \end{figure}
+
+\vspace{-50pt}
 \begin{figure}[H]
     \centering
-    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod4.pdf}
+    \includegraphics[width=0.6\textwidth]{../../../figures/illustrations/rhod4.pdf}
     \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron.}

### 2024-01-07 subsections/tools/numericalmethods/leap-frog-runge-kutta.tex
Spiral corrected

@@
 %%%%%%
-\clearpage
 \section{Algorithms}

### 2024-03-23 msthesis.tex
hard copy ready

@@
 \usepackage{xcolor}
-\usepackage{showframe}
+%\usepackage{showframe}
 
@@
    \sym{Hz}{Hertz}
-   \sym{KAHVELab}{Kandilli Detector Accelerator and \\Instrumentation Laboratory}
-   \vspace{10pt}
+   \sym{KAHVELab}{Kandilli Detector Accelerator and \\Instrumentation Laboratory \vspace{5pt}}
    \sym{LF}{Leap-Frog}
@@
 
-\newcommand{\fromeq}[1]{Equation \ref{eq:#1}}
-\newcommand{\fromeqs}[2]{Equations \ref{eq:#1} and \ref{eq:#2}}
-\newcommand{\fromeqsth}[3]{Equations \ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3}}
-\newcommand{\fromeqsf}[4]{Equations \ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4}}
+\newcommand{\fromeq}[1]{Equation (\ref{eq:#1})}
+\newcommand{\fromeqs}[2]{Equations (\ref{eq:#1} and \ref{eq:#2})}
+\newcommand{\fromeqsth}[3]{Equations (\ref{eq:#1}, \ref{eq:#2} and \ref{eq:#3})}
+\newcommand{\fromeqsf}[4]{Equations (\ref{eq:#1}, \ref{eq:#2}, \ref{eq:#3} and \ref{eq:#4})}
 
@@
 
-\subsection{gnuplot}
-GNUPLOT is a popular open-source software used for creating and visualizing data plots and graphs  \cite{gnuplot}. 
+\subsection{Gnuplot}
+Gnuplot is a popular open-source software used for creating and visualizing data plots and graphs  \cite{gnuplot}. 
 It is widely utilized in various fields, including scientific research, data analysis, engineering, and more, 
@@
     \end{subfigure}
-    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.}
+    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{rhodo_design}.}
     \label{fig:magnet_design_illustrations}
@@
     \vspace{0pt}
-    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.} 
+    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{rhodo_design}.} 
     \label{fig:magnet_design_illustrations}
@@
 \begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
         for (double t=0; t<SimuTime; t+=dT){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
         int phase_opt(int phase_sweep_range){
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d CoaxialRFField::actOn(Electron& e){
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d MagneticField::actOn(Electron& e){
@@
     \begin{minipage}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d CoaxialRFField::actOn(Electron& e){
@@
     \begin{minipage}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d MagneticField::actOn(Electron& e){
@@
 \begin{figure}[H]
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
         vector3d CoaxialRFField::actOn(Electron& e){
@@
     \centering
-    \includegraphics[angle=270,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
+    \includegraphics[angle=90,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rho-A1.0.00.pdf}
     \vspace{5pt}
@@
     \centering
-    \includegraphics[angle=270,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \includegraphics[angle=90,origin=c, width=.95\linewidth]{./figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
     \vspace{10pt}
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             for(double i = 2; i < 9; i += dT_out){
@@
         \centering
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm,  fontsize=\scriptsize]{c++}
             double gecis(double r_pos, double vel, double Et, double &t){
@@
         %\captionsetup{justification=centering}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             int phase_opt(const vector<double>& Louts, int phase_sweep_range){
@@
     \begin{minipage}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             double vector3d::operator* (const vector3d& other){
@@
     \begin{minipage}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d vector3d::operator% (const vector3d& other){
@@
 \begin{figure}[H]
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
             vector3d MagneticField::actOn(Electron& e){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
         vector3d Electron2D::interactB_RK(const MagneticField& B, double time_interval){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
         bool isInsideHalfSphere(vector3d e_position, double r, vector3d hs_position){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
         void Electron2D::interactRK_ActorE(const RFField& E, const MagneticField& B, double time_interval){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         void Electron2D::interactRK(RFField& E, MagneticField& B, const double time, double time_interval){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         void RhodotronSimulator::_runMT(){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         void Gun::fireAllWithFireTimesMT(){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         void MultiThreadEngine::setupPool( double _time_interval, double _start_time, double _end_time, Gun& gun, 
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         void threadLoop(ThreadArguments thread_arguments){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         void UIThreadWork(UIThreadArgs args){
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         class Electron{
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         class Bunch{
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         class Gun{
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         class Simulator{        // E in MV/m,   En in MeV,   B in T,    t in ns
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
         class RhodotronSimulator : public Simulator{
@@
     \begin{minipage}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
             class RFField{
@@
     \begin{minipage}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny]{c++}
             class CoaxialRFField : public RFField{
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
         Optimal phase with the least RMS : -5
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
         Optimal phase with the least RMS : 0
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\tiny, style=staroffice]{c++}
         #            Rhodotron Simulation Configuration File
@@
     %\captionsetup{justification=centering}
-    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
+    \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize, style=staroffice]{c++}
         -- Simulation Configuration --
@@
     \centering
-    \includegraphics[angle=270,origin=c, width=.8\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
+    \includegraphics[angle=90,origin=c, width=.8\linewidth]{./figures/teknikcizim/Rho-A1.1.00.pdf}
     \vspace{10pt}

### 2024-03-23 subsections/production/technical_drawings/techd.tex
Spiral corrected
hard copy ready

@@
 
-\begin{figure}
+\vspace{-20pt}
+\begin{figure}[H]
     \centering
-    \includegraphics[angle=270,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
-    \vspace{20pt}
+    \includegraphics[angle=90,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
+    \vspace{5pt}
     \caption{Technical drawing of the rhodotron cavity \cite{sinan}.}
@@
 \end{figure}
-
-\begin{figure}
+\clearpage
+\begin{figure}[!th]
     \centering
-    \includegraphics[angle=270,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
-    \vspace{20pt}
+    \includegraphics[angle=90,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
+    \vspace{10pt}
     \caption{Technical drawing of middle part of the cavity which contains the beam line \cite{sinan}.}
@@
 \end{figure}
+
 %%%%%%

### 2024-03-23 subsections/simulation/intermediate_versions/intermediate.tex
hard copy ready

@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             double vector3d::operator* (const vector3d& other){
@@
     \begin{subfigure}{\textwidth}
-        \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
+        \begin{minted}[linenos=false, autogobble, frame=lines, framesep=2mm, fontsize=\scriptsize]{c++}
             vector3d vector3d::operator% (const vector3d& other){
